\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.52in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,mathtools}
\usepackage[table]{xcolor}
\usepackage{array,booktabs,longtable}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\input{../paper/release_info}
\pagestyle{empty}

\definecolor{pragmaInk}{HTML}{040609}
\definecolor{pragmaCyan}{HTML}{4EE7FF}
\definecolor{pragmaCyanText}{HTML}{0B5C6D}
\definecolor{pragmaMuted}{HTML}{6E7785}
\definecolor{pragmaLine}{HTML}{85CFE0}
\definecolor{pragmaSoft}{HTML}{F7FBFF}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.17em}
\setlength{\abovedisplayskip}{0.27em}
\setlength{\belowdisplayskip}{0.27em}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.18}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcommand{\sect}[1]{\vspace{0.28em}{\large\bfseries\color{pragmaCyanText}#1}\par\vspace{-0.1em}}
\newcommand{\tightline}{\vspace{0.12em}{\color{pragmaCyan}\hrule height 0.58pt}\vspace{0.08em}{\color{pragmaLine}\hrule height 0.34pt}\vspace{0.35em}}

\begin{document}
\fontsize{9.28pt}{10.72pt}\selectfont
\color{pragmaInk}
\arrayrulecolor{pragmaLine}

{\LARGE\bfseries\color{pragmaCyanText}A short proof of the Observer Patch Holography simulation model}\par
{\normalsize\color{pragmaMuted}From a self-containing screen to Newton's constant}\par
{\scriptsize\color{pragmaMuted}Paper release: \texttt{\OPHPaperReleaseID}\quad Released: \OPHPaperReleaseDate}\par
\tightline
{\bfseries\color{pragmaInk}Selected-scale branch gravity theorem.}\par

\sect{1. Purpose}
The goal of this short note is to state the compact mathematical case that OPH
is the correct fundamental theory of this Universe.  The starting hypothesis is
simple: reality is a simulation that contains itself.  It contains observers,
their records, and the rules by which those records are read back.  Constants
are therefore not external settings.  They are fixed points of the closed
readout structure.

Conventional particle-physics bookkeeping starts with the 19 fitted parameters
of the minimal Standard Model, then adds gravitational and cosmological
measured inputs such as \(G\) and \(\Lambda\).  OPH reduces the fundamental
closure data to two dimensionless screen quantities.  Their values are
computable as unique fixed points of OPH readback laws.  At the theorem target
level, OPH is therefore a zero-parameter theory: numerical constants are
readouts of the closed structure, with any remaining SI scale certificate stated as
an explicit certificate target.

The first two OPH closure values are \(P_\star\) and \(N_\star\).  \(P_\star\)
is the local pixel value of the screen.  It says how much area and shared edge
entropy one observer cell carries.  \(N_\star\) is the global capacity of the
closed screen.  It says how large the observer-facing de Sitter screen is.  A
finite screen simulator needs exactly these two dimensionless inputs: the size
of one pixel and the capacity of the whole screen.

The selected scale branch supplies the no-\(G\) metrological coordinate
\(\gamma_\star\), equivalently \(B_\star\).  This is the bridge from the
dimensionless OPH screen to SI metres.  With \(P_\star\), \(N_\star\), and the
selected scale certificate in place, the local area law has no adjustable
Newton constant.  The cell area and the shared edge entropy refer to the same
observer cell, so \(P_\star\) cancels and the area quantum becomes the Newton
coupling.

This note proves the selected-branch gravity implication
\[
\left(
\bar\ell_{\rm shared}=P_\star/4,\quad
a_{\rm cell}=P_\star\ell_\star^2,\quad
\ell_\star^2\hbox{ supplied by the scale certificate}
\right)
\Longrightarrow
G_{\rm SI}
=
6.674299995910528\times10^{-11}
{\rm m^3\,kg^{-1}\,s^{-2}} .
\]
It does not claim that \(P_\star,N_\star\) alone determine an SI metre.  The
scale-freedom lemma in Appendix A proves that such a claim would be false.
The scale certificate is stated explicitly.

\textbf{Claim status.}
This is a selected-branch scale certificate.  Once the no-\(G\) scale coordinate
\(\gamma_\star\), equivalently \(B_\star\), is supplied, the OPH area coordinate
and Newton constant are forced.  A source-only proof of the SI value requires a
source-only OPH readback map that emits \(\gamma_\star\) or \(B_\star\) without
using measured \(G\).

\sect{2. Fixed-point rule and the two closure variables}
For any branch whose readback law is a contraction \(F:I\to I\) on a complete
metric interval,
\[
  F(I)\subseteq I,\qquad d(F(x),F(y))\le q\,d(x,y),\qquad 0\le q<1,
\]
Banach's theorem gives exactly one fixed point.  Observation locates the branch
interval; the contraction certificate removes numerical freedom inside that
branch.

The compact OPH screen architecture has two dimensionless closure coordinates:
\[
  P \quad\hbox{local observer-cell pixel ratio},\qquad
  N \quad\hbox{global closed-screen capacity}.
\]
\(P\) is local.  It assigns one elementary observer cell its screen area and
shared edge entropy:
\[
  a_{\rm cell}=P\ell_\star^2,\qquad
  \bar\ell_{\rm shared}=P/4 .
\]
\(N\) is global.  It assigns the closed observer screen its total capacity and
therefore its dimensionless de Sitter branch:
\[
  N=\frac{3\pi}{\Lambda_\star\ell_\star^2}.
\]
A finite OPH screen computation needs exactly these two closure coordinates
before its readouts can have physical meaning: a pixel area/entropy unit for
each cell, and a capacity for the whole closed screen.

\textbf{Imported local pixel closure.}
On the declared OPH local-pixel branch, the readback equation
\[
  P=\Gamma(P)=\varphi+\frac{\sqrt\pi}{A_T(P)}
\]
has a unique selected fixed point \(P_\star\).  This branch theorem is imported
from the fine-structure surface.  The gravity proof below does not require the
numerical value of \(P_\star\), because \(P_\star\) cancels from the local area
law.  Informally, \(P_\star\) is the one local pixel value for which geometric
area and shared edge entropy describe the same observer cell.

\textbf{Imported global capacity closure.}
On the declared OPH cosmic record-capacity branch, the readback equation
\[
  N=\mathcal C(N)
\]
has a unique selected fixed point \(N_\star\).  Equivalently, on the
count-density presentation,
\[
  N_\star=\operatorname{MAR}\arg\max_N[\log|\Omega_N^{\rm sc}|-N]
\]
under the stated strict-concavity certificate.  This branch theorem is imported
from the capacity surface.  Informally, \(N_\star\) is the one total capacity
for which the closed screen and its observer-facing de Sitter capacity name the
same global object.  A rough display is \(N_\star\simeq3.31\times10^{122}\).

Before Newton's constant is emitted, the capacity identity is written with the
OPH area coordinate,
\[
  N_\star=\frac{A_{\rm dS}}{4\ell_\star^2}
  =\frac{3\pi}{\Lambda_\star\ell_\star^2}.
\]
The Planck-length notation is reserved for the downstream SI display after
\(G_{\rm SI}\) has been read out.

\sect{3. Dimensionless geometry from \(P_\star,N_\star\)}
Let
\[
  P_\star=\frac{a_{\rm cell}}{\ell_\star^2},\qquad
  N_\star=\frac{3\pi}{\Lambda_\star\ell_\star^2},
\]
and define \(B_\ell=\Lambda_\star N_\star\).  Then
\[
  \Lambda_\star\ell_\star^2=\frac{3\pi}{N_\star},\qquad
  \Lambda_\star a_{\rm cell}=\frac{3\pi P_\star}{N_\star},
\]
and
\[
  B_\ell\ell_\star^2=3\pi,\qquad
  B_\ell a_{\rm cell}=3\pi P_\star .
\]
These relations follow by substitution.  They are exactly what the two
dimensionless closure coordinates determine: dimensionless local/global
geometry.

\sect{4. Scale certificate}
\(P_\star\) and \(N_\star\) are dimensionless.  They fix the local pixel ratio
and the global screen capacity, then a branch coordinate must identify the SI
length scale.  OPH writes that coordinate as the no-\(G\) clock ratio
\(\gamma_\star\), equivalently \(B_\star=\Lambda_\star N_\star\).  The scale
certificate has to come from an OPH readback map that does not use measured
\(G\), \(\ell_P^2=\hbar G/c^3\), or \(\Lambda=3\pi/(GN_\star)\).  Appendix A
contains the short scale-freedom proof.

\sect{5. Selected scale certificate}
The primary scale coordinate is dimensionless:
\[
  \gamma_\star:=\frac{\ell_\star\nu_{\rm Cs}}{c},
\]
where \(\nu_{\rm Cs}=9\,192\,631\,770~{\rm s^{-1}}\) is the SI cesium frequency.
Assume the selected OPH scale branch supplies the no-\(G\) clock ratio
\[
\gamma_\star
=
4.9559743365484194636657782433696431879484319705825
\times10^{-34}.
\]
Then
\[
  \ell_\star^2
  =
  \left(\frac{\gamma_\star c}{\nu_{\rm Cs}}\right)^2
  =
  2.61228030237427777887347769215451001461202676866
  \times10^{-70}{\rm m^2}.
\]
Equivalently,
\[
  B_\star=\frac{3\pi}{\ell_\star^2}
  =
  3.607873914680321576051841480160172547687708307217
  \times10^{70}{\rm m^{-2}} .
\]
The displayed \(B_\star\) is the SI form of the same scale certificate, not an
additional pure OPH closure coordinate.

\sect{6. Local edge-entropy gravity law}
For a cut with \(N_\Sigma\) cells,
\[
  A=N_\Sigma a_{\rm cell},\qquad
  S_{\rm edge}=N_\Sigma\bar\ell_{\rm shared}.
\]
If the area law is
\[
  S_{\rm edge}=\frac{A}{4G_{\rm geom}},
\]
then substitution gives
\[
  N_\Sigma\bar\ell_{\rm shared}
  =
  \frac{N_\Sigma a_{\rm cell}}{4G_{\rm geom}},
  \qquad
  G_{\rm geom}=\frac{a_{\rm cell}}{4\bar\ell_{\rm shared}} .
\]

\sect{7. Pixel cancellation}
On the local OPH gravity branch,
\[
  a_{\rm cell}=P_\star\ell_\star^2,\qquad
  \bar\ell_{\rm shared}=\frac{P_\star}{4}.
\]
Therefore
\[
  G_{\rm geom}
  =
  \frac{P_\star\ell_\star^2}{4(P_\star/4)}
  =
  \ell_\star^2 .
\]
The numerical value of \(G_{\rm SI}\) is carried by the selected scale
certificate \(\gamma_\star\), equivalently \(B_\star\).  The local pixel
\(P_\star\) is load-bearing structurally: it makes the area and edge-entropy
readings refer to the same local cell, and then cancels.  The global capacity
\(N_\star\) is load-bearing in identifying the de Sitter scale branch through
\(B_\star=\Lambda_\star N_\star\).  If \(B_\star\) is supplied directly,
\(N_\star\) does not by itself determine the SI value.

\sect{8. SI Newton constant on the selected scale branch}
By pixel cancellation,
\[
  G_{\rm geom}=\ell_\star^2.
\]
The SI display relation is
\[
  G_{\rm SI}=\frac{c^3}{\hbar}G_{\rm geom}.
\]
Using
\[
  \ell_\star^2=\left(\frac{\gamma_\star c}{\nu_{\rm Cs}}\right)^2
\]
gives
\[
  G_{\rm SI}
  =
  \frac{c^5}{\hbar\nu_{\rm Cs}^2}\gamma_\star^2 .
\]
With exact SI definitions,
\[
  c=299792458~{\rm m\,s^{-1}},\qquad
  \nu_{\rm Cs}=9\,192\,631\,770~{\rm s^{-1}},\qquad
  \hbar=\frac{6.62607015\times10^{-34}}{2\pi}~{\rm J\,s},
\]
the selected-branch readout is
\[
  G_{\rm OPH}
  =
  6.674299995910528\ldots\times10^{-11}
  ~{\rm m^3\,kg^{-1}\,s^{-2}} .
\]
CODATA reference:
\[
  G=6.67430(15)\times10^{-11}~{\rm m^3\,kg^{-1}\,s^{-2}} .
\]

\sect{9. Derived readouts}
\begin{center}
\begin{tabular}{@{}p{0.23\linewidth}p{0.34\linewidth}p{0.35\linewidth}@{}}
\toprule
\textbf{Readout} & \textbf{Value} & \textbf{Meaning}\\
\midrule
\(P_\star\) &
\(1.6309682094039593\ldots\) &
exact local pixel fixed point\\
\(N_\star\) &
\(\simeq3.31\times10^{122}\) &
global closed-screen capacity fixed point\\
\(\gamma_\star\) &
\(4.95597433654841946\ldots\times10^{-34}\) &
dimensionless selected scale certificate\\
\(B_\star=\Lambda N_\star\) &
\(3.60787391468\ldots\times10^{70}{\rm m^{-2}}\) &
SI display of the scale certificate\\
\(\ell_\star^2\) &
\(2.61228030237\ldots\times10^{-70}{\rm m^2}\) &
OPH area quantum\\
\(a_{\rm cell}\) &
\(4.26054612722\ldots\times10^{-70}{\rm m^2}\) &
physical area of one screen pixel\\
\(\bar\ell_{\rm shared}\) &
\(0.407742052350989825\ldots\) &
shared edge entropy per local cell\\
\(G_{\rm geom}\) &
\(\ell_\star^2\) &
geometric Newton coupling\\
\(G_{\rm SI}\) &
\(6.674299995910528\times10^{-11}{\rm m^3kg^{-1}s^{-2}}\) &
SI Newton constant readout\\
\(\Lambda_{\rm CRC}\) &
\(\dfrac{3\pi}{G_{\rm geom}N_\star}\) &
downstream de Sitter display\\
\bottomrule
\end{tabular}
\end{center}

\sect{10. TL;DR}
OPH models reality as a closed self-referential mathematical structure.  The
observer does not invent the constants.  The observer locates the experienced
branch, and the OPH contraction laws return the unique fixed values on that
branch.

\(P_\star\) locks the local observer-cell pixel.  \(N_\star\) locks the total
closed-screen capacity.  These are the two quantities a screen computation
must have: a pixel area/entropy unit and a total capacity.  They determine the
dimensionless local/global geometry.  The selected scale certificate
\(\gamma_\star\), equivalently \(B_\star\), locks the SI area quantum
\(\ell_\star^2\).  Local edge entropy gives
\[
  G_{\rm geom}=\frac{a_{\rm cell}}{4\bar\ell_{\rm shared}}=\ell_\star^2 .
\]
Exact SI definitions then give
\[
  G_{\rm SI}=\frac{c^3}{\hbar}\ell_\star^2
  =
  6.674299995910528\times10^{-11}~{\rm m^3\,kg^{-1}\,s^{-2}}.
\]

If \(P\) is off its fixed point, the simulator has the wrong pixel.  The local
area reading and the local edge entropy reading stop describing one stable
observer cell.  If \(N\) is off its fixed point, the simulator has the wrong
screen.  The closed screen does not reproduce its own capacity branch.  If the
scale branch is off by \(r\) in length, the SI gravity readout is off by
\(r^2\).

The proof contains no adjustable Newton constant.  Gravity is the area readout
of the same observer-cell closure that defines the local screen unit.  The
selected-scale statement is the gravitational selection test for OPH: the
closed observer-patch model plus the no-\(G\) scale certificate produces the
measured SI coupling.  The agreement lands on the CODATA value because the
scale certificate gives the area quantum first, and SI then names the same area
as Newton's constant.

\sect{Appendix A. Audit checks}
\textbf{Scale freedom lemma.}
No expression using only \(P_\star,N_\star\), pure dimensionless constants, and
exact display constants \(c,\hbar\) determines \(B_\ell\) in \({\rm m^{-2}}\),
\(\ell_\star^2\) in \({\rm m^2}\), or \(G_{\rm SI}\) in SI units.

For any \(\lambda>0\), rescale
\[
  \ell_\star^2\mapsto\lambda^2\ell_\star^2,\qquad
  a_{\rm cell}\mapsto\lambda^2a_{\rm cell},\qquad
  \Lambda_\star\mapsto\lambda^{-2}\Lambda_\star .
\]
Then both closure coordinates are unchanged:
\[
  \frac{\lambda^2a_{\rm cell}}{\lambda^2\ell_\star^2}
  =\frac{a_{\rm cell}}{\ell_\star^2},
  \qquad
  \frac{3\pi}{(\lambda^{-2}\Lambda_\star)(\lambda^2\ell_\star^2)}
  =
  \frac{3\pi}{\Lambda_\star\ell_\star^2}.
\]
The same \(P_\star,N_\star\) therefore admit
\[
  B_\ell\mapsto\lambda^{-2}B_\ell,\qquad
  G_{\rm SI}\mapsto\lambda^2G_{\rm SI}.
\]
A separate scale certificate is required for the SI gravity row.

\textbf{Dependency ledger.}
\begin{center}
\begin{tabular}{@{}p{0.19\linewidth}p{0.37\linewidth}p{0.36\linewidth}@{}}
\toprule
\textbf{Object} & \textbf{Allowed role} & \textbf{Forbidden upstream use}\\
\midrule
\(P_\star\) &
local pixel fixed point &
does not set metres by itself\\
\(N_\star\) &
global screen-capacity fixed point &
does not set metres by itself\\
\(\gamma_\star\) &
dimensionless no-\(G\) scale certificate &
must not be fitted from measured \(G\)\\
\(B_\star\) &
SI display of the scale certificate &
must not be computed from \(3\pi/(GN_\star)\)\\
\(\ell_\star^2\) &
area coordinate from \(3\pi/B_\star\) &
must not be computed from \(\hbar G/c^3\)\\
\(G_{\rm geom}\) &
local edge-entropy output &
not an input to the scale certificate\\
\(\Lambda_{\rm CRC}\) &
downstream de Sitter display &
evaluated only after \(G_{\rm geom}\)\\
\bottomrule
\end{tabular}
\end{center}

\textbf{Minimal metrological bridge.}
Fix the exact SI constants \(c\), \(\hbar\), and the cesium clock frequency
\(\nu_{\rm Cs}=9\,192\,631\,770~{\rm s^{-1}}\).  A numerical SI Newton
constant is equivalent to the dimensionless scale ratio
\[
  \gamma_G:=
  \left(
  \frac{\hbar G_{\rm SI}\nu_{\rm Cs}^2}{c^5}
  \right)^{1/2}.
\]
The units cancel:
\[
\frac{
({\rm kg\,m^2\,s^{-1}})
({\rm m^3\,kg^{-1}\,s^{-2}})
({\rm s^{-2}})
}{
({\rm m\,s^{-1}})^5
}
=1.
\]
Solving the definition gives
\[
  G_{\rm SI}=
  \frac{c^5}{\hbar\nu_{\rm Cs}^2}\gamma_G^2 .
\]
Thus a no-\(G\) OPH emission of \(\gamma_\star\) is exactly a no-\(G\) SI
scale certificate.

\textbf{Equivalent scale charts.}
Given \(N_\star\), any one of
\[
\ell_\star^2,\qquad
B_\star=\Lambda_\star N_\star,\qquad
\Lambda_\star,\qquad
R_\star=\sqrt{3/\Lambda_\star},\qquad
t_\star=R_\star/c,\qquad
\gamma_\star=\ell_\star\nu_{\rm Cs}/c
\]
determines all the others.  The conversion formulas are
\[
  B_\star=\frac{3\pi}{\ell_\star^2},\qquad
  \Lambda_\star=\frac{B_\star}{N_\star},\qquad
  R_\star=\sqrt{\frac{3N_\star}{B_\star}},
\]
\[
  t_\star=\frac{1}{c}\sqrt{\frac{3N_\star}{B_\star}},
  \qquad
  \gamma_\star=\frac{\nu_{\rm Cs}}{c}\sqrt{\frac{3\pi}{B_\star}} .
\]
These are chart changes for one scale certificate, not independent constants.

\textbf{Anti-smuggling criterion.}
Let \(\mathcal B\) be the scale certificate used to compute \(G_{\rm SI}\).  The
numerical gravity row is a no-\(G\) derivation only if the dependency graph for
\(\mathcal B\) contains no path from
\[
G_{\rm exp},\qquad
\ell_P^2=\frac{\hbar G}{c^3},\qquad
\Lambda=\frac{3\pi}{G N_\star},\qquad
B_\ell=\frac{3\pi c^3}{\hbar G}
\]
to \(\mathcal B\).  If such a path exists, the row is a calibration of \(G\).
If no such path exists, the algebraic computation of \(G_{\rm SI}\) from
\(\mathcal B\) contains no measured-\(G\) dependency.

\textbf{Pixel insensitivity.}
On the local OPH gravity branch,
\[
a_{\rm cell}=P\ell_\star^2,\qquad
\bar\ell_{\rm shared}=P/4,\qquad
G_{\rm geom}=\frac{a_{\rm cell}}{4\bar\ell_{\rm shared}} .
\]
Substitution gives
\[
G_{\rm geom}=\frac{P\ell_\star^2}{4(P/4)}=\ell_\star^2,
\qquad
\frac{\partial G_{\rm geom}}{\partial P}=0.
\]
The local pixel value is structurally necessary because it identifies the two
readings of one cell.  The numerical area readout is insensitive to the
coordinate \(P\) after that identification.

\textbf{Planck area is downstream.}
If the OPH local gravity row emits
\[
G_{\rm SI}=\frac{c^3}{\hbar}\ell_\star^2,
\]
then the SI Planck area computed after the emission is
\[
\ell_{P,{\rm OPH}}^2:=
\frac{\hbar G_{\rm SI}}{c^3}
=\ell_\star^2.
\]
The symbol \(\ell_P^2\) can therefore name the emitted area downstream.  It
cannot be used upstream to derive it.

\textbf{Coupled closure uniqueness target.}
Let \(K=I_N\times I_\gamma\) be a complete product metric space with metrics
\(d_N,d_\gamma\).  Let
\[
\mathcal S(N,\gamma)
=
\bigl(S_N(N,\gamma),S_\gamma(N,\gamma)\bigr)
\]
be the joint capacity/scale certificate map.  Suppose there is a nonnegative matrix
\[
M=\begin{pmatrix}a&b\\ c&d\end{pmatrix},\qquad \rho(M)<1,
\]
such that
\[
d_N(S_N(x),S_N(y))
\le
a\,d_N(N_x,N_y)+b\,d_\gamma(\gamma_x,\gamma_y),
\]
\[
d_\gamma(S_\gamma(x),S_\gamma(y))
\le
c\,d_N(N_x,N_y)+d\,d_\gamma(\gamma_x,\gamma_y).
\]
Perron--Frobenius gives a positive vector \(w=(w_N,w_\gamma)\) and \(q<1\)
with \(Mw\le q w\).  The weighted metric
\[
d_w(x,y)=
\max\left\{
\frac{d_N(N_x,N_y)}{w_N},
\frac{d_\gamma(\gamma_x,\gamma_y)}{w_\gamma}
\right\}
\]
makes \(\mathcal S\) a contraction.  Banach's theorem gives a unique joint
fixed point \((N_\star,\gamma_\star)\) on \(K\).

\textbf{Residual and sensitivity certificates.}
If \(R:I\to I\) is a contraction with constant \(q<1\), and a candidate
\(x_0\) satisfies \(d(R(x_0),x_0)\le\varepsilon\), then the fixed point
\(x_\star\) obeys
\[
d(x_\star,x_0)\le\frac{\varepsilon}{1-q}.
\]
For equivalent scale coordinates,
\[
\frac{\delta G}{G}
=
\frac{\delta\ell_\star^2}{\ell_\star^2}
=
2\frac{\delta\gamma_\star}{\gamma_\star}
=
-\frac{\delta B_\star}{B_\star}.
\]
These two formulas convert a numerical readback residual into a certified
interval and show exactly how scale-coordinate errors move the gravity row.

\textbf{Frozen-branch retuning test.}
Let \(\mathcal B_\star\) denote the published scale certificate, written as
\(B_\star\), \(\ell_\star^2\), or \(\gamma_\star\).  If \(\mathcal B_\star\)
is changed after a new measurement of \(G\) is available, and the change is not
forced by a pre-existing no-\(G\) OPH readback certificate, then the numerical
gravity row is a calibration rather than a prediction.

\sect{Appendix B. OPH-predicted values}
The short proof isolates the gravity row.  The wider OPH claim is that the same
closure architecture fixes the local pixel, total screen capacity,
support-visible spacetime branch, realized gauge branch, and declared
quantitative particle branches.  The table separates direct measurements,
public limits, definitions, and values whose public measurement does not exist.

A numerical \(\sigma\) is shown only when the cited public source gives a
central value and a one-standard-deviation uncertainty.  Exact definitions and
rounded matches are marked as exact hits.  Limit rows, structural rows, and
non-Gaussian global-fit profiles are marked by status rather than forced into a
fake scalar sigma.  Rows whose OPH value carries more digits than public
measurement permits are sharper OPH readouts if the branch derivation is
accepted.

\begin{center}
\fontsize{6.75pt}{7.35pt}\selectfont
\setlength{\tabcolsep}{2.1pt}
\renewcommand{\arraystretch}{1.08}
\begin{longtable}{@{}L{0.13\linewidth}L{0.24\linewidth}L{0.36\linewidth}L{0.10\linewidth}L{0.10\linewidth}@{}}
\toprule
\textbf{Lane} & \textbf{OPH prediction} & \textbf{Measurement or public status} & \textbf{Residual} & \textbf{Source}\\
\midrule
\endhead
\endfoot
Local pixel &
\(P_\star=1.6309682094039593\ldots\) &
No direct laboratory measurement.  This is the local cell-area and edge-entropy
fixed point required by a finite OPH screen. &
\(n/a\) &
OPH\\

Local cell entropy &
\(\bar\ell_{\rm shared}=P_\star/4=0.407742052350989825\ldots\) &
No direct laboratory measurement.  It is the entropy weight assigned to one
observer cell by the same fixed point that fixes \(P_\star\). &
\(n/a\) &
OPH\\

Global capacity &
\(N_\star\simeq3.31\times10^{122}\) &
No direct count measurement.  Cosmological comparison uses de Sitter capacity
after the scale branch is supplied. &
\(n/a\) &
OPH\\

Scale certificate &
\(\begin{gathered}
\gamma_\star=4.95597433655\ldots\times10^{-34}\\
B_\star=3.60787391468\ldots\times10^{70}{\rm m^{-2}}
\end{gathered}\) &
No direct public measurement.  The gravity row below is the scalar test of this
selected SI scale certificate. &
\(n/a\) &
OPH\\

Area quantum and pixel area &
\(\begin{gathered}
\ell_\star^2=2.61228030237\ldots\times10^{-70}{\rm m^2}\\
a_{\rm cell}=4.26054612722\ldots\times10^{-70}{\rm m^2}
\end{gathered}\) &
No direct public measurement of an OPH screen cell.  The inferred area quantum
is tested through \(G_{\rm SI}\). &
\(n/a\) &
OPH\\

Newton coupling &
\(\begin{gathered}
G_{\rm geom}=\ell_\star^2\\
G_{\rm SI}=6.674299995910528\times10^{-11}
\end{gathered}\) &
\(G=6.67430(15)\times10^{-11}{\rm m^3\,kg^{-1}\,s^{-2}}\).  OPH prints more
digits than the CODATA uncertainty permits. &
\(-2.7\times10^{-5}\sigma\) &
S1\\

Cosmological constant &
\(\Lambda_{\rm CRC}\approx1.09\times10^{-52}{\rm m^{-2}}\) &
Planck 2018 gives the late-universe \(\Lambda\)CDM parameter surface; the
rounded OPH value agrees at displayed order. &
exact hit at shown precision &
S5\\

Static-patch rate &
\(H_{\rm dS}\approx55.759940256~{\rm km\,s^{-1}\,Mpc^{-1}}\) &
This is a de Sitter static-patch display, not the fitted local Hubble constant. &
not a fitted \(H_0\) &
OPH\\

Hubble benchmark &
\(H_0=67.4~{\rm km\,s^{-1}\,Mpc^{-1}}\) in compressed diagnostics &
Planck 2018 reports \(H_0=67.4\pm0.5~{\rm km\,s^{-1}\,Mpc^{-1}}\).  This row is
a benchmark input in the compressed comparison. &
\(0\sigma\) &
S5\\

Lorentz group &
\(\mathrm{Conf}^+(S^2)\cong\mathrm{SO}^+(3,1)\) &
Structural prediction.  Direct scalar sigma is not the right statistic; the
comparison is the Lorentz-kinematics branch. &
\(n/a\) &
OPH\\

Causal speed &
\(c=299792458~{\rm m\,s^{-1}}\) &
Exact SI definition.  This is a display convention for the Lorentz speed. &
exact hit by definition &
S3\\

Einstein branch &
Jacobson-type local Einstein equation &
Structural prediction.  Tests are GR/weak-field/null-energy comparisons rather
than one scalar value. &
\(n/a\) &
OPH\\

Gauge quotient &
\(\mathrm{SU}(3)_c\times\mathrm{SU}(2)_L\times\mathrm{U}(1)_Y/\mathbb Z_6\) &
Matches the observed Standard Model gauge quotient.  No one-number sigma. &
exact structural hit &
S6\\

Hypercharge, color, generations &
\(\begin{gathered}
\hbox{one-generation hypercharge lattice}\\
N_c=3,\quad N_g=3
\end{gathered}\) &
Matches observed Standard Model charge and family structure.  No one-number
sigma. &
exact structural hit &
S6\\

Massless protected carriers &
\(\begin{gathered}
m_\gamma=0\\
m_g=0\\
m_{\rm grav}=0
\end{gathered}\) &
Photon and gluon masslessness are gauge-branch structural hits.  Graviton
masslessness belongs to the diffeomorphism/Lorentz gravity branch.  Direct
measurements are public upper limits rather than exact mass measurements. &
\(\begin{gathered}
\gamma:\hbox{ structural hit}\\
g:\hbox{ structural hit}\\
{\rm grav}:\hbox{ structural hit}
\end{gathered}\) &
S6\\

Gauge proton decay &
\(\tau_p^{(\rm gauge)}=\infty\) &
Public searches give lower limits on proton decay channels.  The OPH gauge row
predicts no simple-GUT gauge boson decay mode. &
\(n/a\) &
S6\\

Fine-structure source trunk &
\(\alpha^{-1}_{\rm source}=136.994835164621649\ldots\) &
No direct public measurement.  It is the source calculation before the
declared hadronic/same-scheme endpoint payload. &
\(n/a\) &
OPH\\

Fine-structure endpoint &
\(\begin{gathered}
\alpha^{-1}(0)=137.035999177(21)\\
\alpha(0)=0.00729735256433\ldots
\end{gathered}\) &
CODATA gives \(\alpha^{-1}=137.035999177(21)\).  The public endpoint is not used
in the gravity proof. &
\(0\sigma\) &
S2\\

Electroweak source &
\(\begin{gathered}
\alpha_2(m_Z)=0.03377843630219015\\
\alpha_Y(m_Z)=0.010131601067241624
\end{gathered}\) &
Electroweak-fit comparison row.  A scalar sigma depends on scheme and fit
covariances, so it is not quoted here. &
\(n/a\) &
S6\\

Electroweak scale &
\(v=246.76711732749683~{\rm GeV}\) &
Derived from the electroweak branch and displayed in the particle surface.
Direct comparison depends on \(G_F\) convention and loop scheme. &
\(n/a\) &
S6\\

\(W/Z\) validation pair &
\(\begin{gathered}
M_W=80.377~{\rm GeV}\\
M_Z=91.18797809193725~{\rm GeV}
\end{gathered}\) &
PDG 2024 gives \(M_W=80.3692\pm0.0133~{\rm GeV}\) and
\(M_Z=91.1876\pm0.0021~{\rm GeV}\). &
\(\begin{gathered}0.59\sigma\\0.18\sigma\end{gathered}\) &
S6\\

Higgs/top branch &
\(\begin{gathered}
m_H=125.1995304097179~{\rm GeV}\\
m_t=172.35235532883115~{\rm GeV}
\end{gathered}\) &
PDG 2024 gives \(m_H=125.20\pm0.11~{\rm GeV}\) and direct
\(m_t=172.57\pm0.29~{\rm GeV}\). &
\(\begin{gathered}-0.004\sigma\\-0.75\sigma\end{gathered}\) &
S6,S7\\

Charged leptons &
\(\begin{gathered}
m_e=0.00051099895\\
m_\mu=0.1056583755\\
m_\tau=1.7769324651340912
\end{gathered}{\rm~GeV}\) &
PDG lepton summary gives the displayed central values.  The tau residual is
\(0.03\sigma\); \(e,\mu\) match at displayed precision. &
\(\le0.03\sigma\) &
S8\\

Quark sextet &
\(\begin{gathered}
u=0.00216,\quad d=0.00470\\
s=0.0935,\quad c=1.273\\
b=4.183\\
t=172.35235532883115\\
{\rm GeV}
\end{gathered}\) &
PDG quark summary gives the displayed light/heavy quark central values.  The
top comparison is listed in the Higgs/top row. &
\(0\sigma\) at shown precision &
S7\\

Neutrino masses &
\(\begin{gathered}
0.017454720257976796\\
0.019481987935919015\\
0.05307522145074924
\end{gathered}{\rm~eV}\) &
Individual absolute neutrino masses are not yet measured.  KATRIN gives a
direct upper limit on the effective electron-neutrino mass. &
\(n/a\) &
S10\\

Neutrino sum &
\(\sum m_\nu=0.09001192964464505~{\rm eV}\) &
Planck 2018 plus BAO gives \(\sum m_\nu<0.12~{\rm eV}\) at 95\% CL.  OPH lies
below the public upper limit. &
below limit &
S5,S11\\

Neutrino mixing display &
\(\begin{gathered}
\theta_{12}=34.2259^\circ,\ \theta_{23}=49.7228^\circ\\
\theta_{13}=8.68636^\circ,\ \delta=305.581^\circ
\end{gathered}\) &
NuFIT 6.0 gives global-fit profiles.  The profiles are non-Gaussian and
ordering-dependent, so a single scalar sigma is not quoted. &
\(n/a\) &
S9\\

Majorana phases &
\(\begin{gathered}
\alpha_{21}=153.618518^\circ\\
\alpha_{31}=257.003241^\circ
\end{gathered}\) &
Majorana phases are not yet measured.  They require neutrinoless double-beta
or equivalent absolute-phase information. &
\(n/a\) &
S11\\

Compressed matter budget &
\(\begin{gathered}
\Omega_{\Lambda,\rm OPH}=0.684423332\\
\Omega_A=0.264114401\\
\Omega_m=0.315484968
\end{gathered}\) &
Planck 2018 gives \(\Omega_m=0.315\pm0.007\).  Flat \(\Lambda\)CDM gives
\(\Omega_\Lambda\simeq0.685\pm0.007\). &
\(\begin{gathered}\Omega_m:0.07\sigma\\
\Omega_\Lambda:-0.08\sigma\end{gathered}\) &
S5\\

\end{longtable}
\end{center}

\textbf{Measurement source keys.}\par
\(\mathrm{S1}\): \href{https://physics.nist.gov/cgi-bin/cuu/Value?bg=}{NIST CODATA 2022 \(G\)}.\par
\(\mathrm{S2}\): \href{https://physics.nist.gov/cgi-bin/cuu/Value?alphinv=}{NIST CODATA 2022 \(\alpha^{-1}\)}.\par
\(\mathrm{S3}\): \href{https://physics.nist.gov/cgi-bin/cuu/Value?c=}{NIST CODATA \(c\), exact}.\par
\(\mathrm{S4}\): \href{https://physics.nist.gov/cgi-bin/cuu/Value?hbar=}{NIST CODATA \(\hbar\), exact}.  Used in the arithmetic certificate.\par
\(\mathrm{S5}\): \href{https://arxiv.org/abs/1807.06209}{Planck 2018 cosmological parameters}.\par
\(\mathrm{S6}\): \href{https://pdg.lbl.gov/2024/tables/rpp2024-sum-gauge-higgs-bosons.pdf}{PDG 2024 gauge and Higgs summary}.\par
\(\mathrm{S7}\): \href{https://pdg.lbl.gov/2024/tables/rpp2024-sum-quarks.pdf}{PDG 2024 quark summary}.\par
\(\mathrm{S8}\): \href{https://pdg.lbl.gov/2024/tables/rpp2024-sum-leptons.pdf}{PDG 2024 lepton summary}.\par
\(\mathrm{S9}\): \href{https://www.nu-fit.org/?q=node/294}{NuFIT 6.0 oscillation fit}.\par
\(\mathrm{S10}\): \href{https://www.science.org/doi/10.1126/science.adq9592}{KATRIN 2025 direct neutrino-mass limit}.\par
\(\mathrm{S11}\): \href{https://pdg.lbl.gov/2024/reviews/rpp2024-rev-sum-neutrino-masses.pdf}{PDG 2024 neutrino-mass review}.\par

\textbf{OPH paper keys.}\par
\(\mathrm{O1}\): \href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.tex}{Observers Are All You Need}.\par
\(\mathrm{O2}\): \href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.tex}{Reality as Consensus Protocol}.\par
\(\mathrm{O3}\): \href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.tex}{Screen Microphysics and Observer Synchronization}.\par
\(\mathrm{O4}\): \href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.tex}{Recovering Relativity and Standard Model Structure from Observer Overlap Consistency}.\par
\(\mathrm{O5}\): \href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.tex}{Deriving the Particle Zoo from Observer Consistency}.\par

\end{document}
