\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[shortlabels]{enumitem}
\usepackage{hyperref}
\usepackage{xurl}
\input{../paper/release_info}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\setlength{\emergencystretch}{3em}

\newtheorem{theorem}{Theorem}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\theoremstyle{plain}

\title{Finite \(E_8\)/\(\mathrm{Spin}(8)\) Triality Certificate for an \(\mathrm{Alt}(9)\) Double Cover}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\begin{center}
\small\textbf{Paper release:} \OPHPaperReleaseID\quad
\textbf{Released:} \OPHPaperReleaseDate
\end{center}

\begin{abstract}
This note records a compact finite exceptional-symmetry sidecar for OPH. The certificate concerns
exact matrix data for \(E_8\), \(\mathrm{Spin}(8)\), triality, and an
\(\mathrm{Alt}(9)\) Schur double cover. Its role is representation-closure bookkeeping. It is not a
proof of OPH, not a Standard Model selector, not a heterotic critical-worldsheet receipt, and not
hardware evidence.
\end{abstract}

\section{Role in the OPH Stack}

OPH uses finite observer-visible data, records, repair maps, quotient invariants, and public
receipts as primitive evidence carriers. The present certificate belongs to that finite exact
discipline on the exceptional-symmetry side:
\[
\mathrm{Spin}(8)\ \text{triality} + E_8\ \text{lattice preservation}
\quad\Rightarrow\quad
\text{finite exceptional representation certificate}.
\]
It supports the \(E_8\)-type representation-closure lane used by compact-gauge and heterotic-local
bookkeeping. It does not replace the recovered-core theorem stack, the MAR selection of the
Standard Model quotient, the critical-edge CFT gate, or any physical carrier evidence rule.

\section{Certificate Statement}

\begin{theorem}[Finite \(E_8/\mathrm{Spin}(8)\) triality certificate]
The certificate target is an exact finite matrix construction with the following data.
\begin{enumerate}[leftmargin=2em]
\item An \(A_8\) root subsystem inside the \(E_8\) root lattice. Its Weyl group is
\(W(A_8)\cong\mathrm{Sym}(9)\), and the even subgroup is \(\mathrm{Alt}(9)\).
\item The permutation involution \((12)(34)\in\mathrm{Alt}(9)\) lifts to \(\mathrm{Spin}(8)\) with
square \(-1\). Hence the preimage of \(\mathrm{Alt}(9)\) is the nonsplit Schur double cover
\(2\!\cdot\!\mathrm{Alt}(9)\), not \(2\times\mathrm{Alt}(9)\).
\item Under the positive half-spin representation \(\Delta^+\), the lifted group preserves an even
unimodular determinant-one lattice, hence an \(E_8\) lattice. The spin-side copy therefore lands in
\(\mathrm{Aut}(E_8)=W(E_8)\).
\item The vector and positive-half-spin mod-2 orbit fingerprints on
\(E_8/2E_8\setminus\{0\}\) are different:
\[
\mathrm{Alt}(9)_{\mathrm{vec}}:\{9,36,84,126\},
\qquad
(2\!\cdot\!\mathrm{Alt}(9))_{\Delta^+}:\{120,135\}.
\]
Thus the two copies are not conjugate in \(O_8^+(2)\).
\item The outer triality automorphism of \(\mathrm{Spin}(8)\) permutes the vector and two half-spin
eight-dimensional representations and identifies these otherwise nonconjugate presentations.
\end{enumerate}
\end{theorem}

\begin{remark}[Notation]
Here \(A_8\) denotes the root subsystem and \(\mathrm{Alt}(9)\) denotes the alternating group. The
shorthand \(A_9\) is avoided for the group because \(A_9\) also denotes a root system.
\end{remark}

\begin{remark}[Claim boundary]
This is a finite algebraic certificate. It supports exceptional representation-closure and
triality bookkeeping. It does not prove OPH, derive the Standard Model quotient, prove physical
\(E_8\) realization, close the heterotic edge CFT, or count as a hardware receipt.
\end{remark}

\begin{remark}[Public receipt gate]
For public verifier status, the repository bundle must include the Sage source, exact matrix data,
lattice bases, mod-2 orbit computation, stdout or machine-readable check receipts, and stable
hashes under \texttt{code/e8\_triality/}. Until that bundle is populated, this note records the
certificate statement and its OPH claim placement rather than a standalone public reproduction
bundle.
\end{remark}

\section{Remaining Extension}

This certificate concerns the nonsplit \(2\!\cdot\!\mathrm{Alt}(9)\) subgroup and its
triality-fused vector and positive-half-spin presentations. The full Griess--Lam
\(2.\mathrm{Sym}(9)\) double-cover construction requires adjoining odd Clifford lifts. Those odd
lifts exchange the two half-spin modules and carry the associated \(\sqrt 2\)-normalization. That is
a separate certificate gate.

\end{document}
