\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array}
\usepackage[shortlabels]{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{microtype}
\usepackage[numbers,sort&compress]{natbib}
\input{../paper/release_info}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue,
  pdftitle={Verified Projection-Event Calculus in Lean 4},
  pdfauthor={Bernhard Mueller}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\setlength{\emergencystretch}{3em}
\renewcommand{\arraystretch}{1.12}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\renewcommand{\_}{\textunderscore\allowbreak}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\Mn}{\mathrm{M}_n(\C)}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\one}{\mathbf 1}
\newcommand{\pinch}{\mathcal E}
\newcommand{\avg}{\mathcal A}
\newcommand{\lued}{\mathcal L}
\newcommand{\norm}[1]{\lVert #1\rVert}

\title{\textbf{Verified Projection-Event Calculus in Lean~4:\\
Bundled Arbitrary-Partition Pinching, L\"uders Retractions,\\
and CHSH Interoperability}}
\author{Bernhard Mueller\thanks{Corresponding author:
\href{mailto:bernhard@floatingpragma.ai}{\texttt{bernhard@floatingpragma.ai}}}\\
Pragma Research Inc., Washington, United States}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
Finite quantum measurement looks simple on paper: multiply matrices, take a
trace, and normalize. In Lean, each step crosses a different interface and
every side condition must be supplied. We build a Lean~4 library for
projection events over finite complex matrix algebras. A projective partition
defines a star-subalgebra of matrices that commute with its projectors and a
complex-linear pinching map onto that subalgebra. The map is unital, positive,
trace preserving, and idempotent; its range and fixed points are exactly the
partition commutant, and it satisfies the bimodule law, Hilbert--Schmidt
Pythagorean and contraction identities, and a trace-duality uniqueness
theorem. A second expectation averages onto the commutative span of the
partition. The two maps satisfy tower laws, the average preserves the Born
statistics of the partition, and conditioning on a partition member commutes
with averaging. L\"uders conditioning is available as a total matrix formula
and as a typed state update; the fixed states are exactly the states
assigning weight one to the event. A checked bound dominates every state
expectation by the operator norm of the observable, which turns an
operator-norm Tsirelson theorem, interoperable with Mathlib's
Clauser-Horne-Shimony-Holt (CHSH) interface, into a state-level CHSH bound
for projection events. We compare the library with Mathlib, Physlib,
Lean-Quantum, Lean-QIT, and Isabelle/HOL, and we record the Mathlib gaps met
during construction together with the workarounds that closed them. The
artifact pins its Lean and Mathlib revisions and records declaration-level
axiom dependencies. Complete positivity, a Physlib correspondence, rank-one
classicality, and a CHSH sharpness witness are outside the formalization.
\end{abstract}

\noindent\textbf{Keywords:} formal verification, Lean~4, projective measurement,
partition pinching, L\"uders update, CHSH

\medskip
\noindent\textbf{Mathematics Subject Classification (2020):}
Primary 68V20; Secondary 68V15, 81P15, 81P40, 46L53.

\section{Introduction}
\label{sec:intro}

Finite quantum measurement is short on paper. A proof calls a matrix a state,
inserts a projection, normalizes the result, and moves on. Lean asks for every
condition skipped in that sentence. The matrix must be positive and have unit
trace. The projection must be Hermitian and idempotent. Normalization needs a
nonzero denominator. Later norm estimates require a further set of
instances.

Machine-checked quantum information is an active area, spread over several
systems and several design philosophies. Mathlib \cite{mathlib2020}, the
central mathematics library of Lean~4 \cite{lean4}, contains an order-form
CHSH/Tsirelson theorem and the \texttt{IsCHSHTuple} interface
\cite{mathlibCHSH2026}. Physlib's \texttt{QuantumInfo.Finite.Pinching}
constructs the spectral pinching of a state as a completely positive
trace-preserving map and proves commutation, fixed-point, Pythagorean, and
pinching-bound results \cite{physlib,physlibPinching2026}. Lean-Quantum
provides basis-independent infrastructure for states, channels, tensor
products, Choi and Kraus representations, and trace inequalities
\cite{kasauraEtAl2026LeanQuantum}; Lean-QIT develops a compositional
infrastructure for quantum-information theory \cite{zhuEtAl2026LeanQIT}. Zhao
and Yu formalize CHSH rigidity in Lean~4 \cite{zhaoYu2026CHSHRigidity}.
Isabelle/HOL developments cover projective measurement, quantum computation,
and the CHSH upper bound
\cite{echenim2021afp,echenimmhalla2023afp,echenimmhalla2024,bordg2021}.
These developments choose different carriers for states and different
bundling conventions, and results proved in one seldom apply verbatim in
another. The engineering question underneath is interface design: which
objects stay bare predicates, which get bundled, and how finished results are
handed to the interfaces a large library expects. We make no priority claim
for projective measurement, pinching, or Tsirelson's inequality.

The library described here packages the side conditions of finite projective
measurement into a projection-event API over Mathlib matrices. Its main input
is an arbitrary projective partition of the identity. The partition induces
two canonical expectations: the pinching, which deletes off-block terms and
maps the matrix algebra onto the partition commutant, and the average, which
projects further onto the commutative span of the partition. The same event
definitions feed the L\"uders update and the CHSH adapter. This keeps
algebraic identities separate from results that use trace, positivity, or
state normalization.

The mathematics is classical: L\"uders introduced the selective update rule
\cite{lueders1950,buschlahti2009}; pinching by a family of orthogonal
projections is a standard averaging operation in matrix analysis
\cite{bhatia2000} and in quantum information \cite{hayashi2017}; the bimodule
and trace-duality laws proved here are the finite-matrix forms of the
defining properties of conditional expectations onto subalgebras
\cite{umegaki1954,takesaki1972}; and the CHSH combination with its quantum
bound goes back to Clauser, Horne, Shimony, and Holt \cite{chsh1969} and to
Tsirelson \cite{tsirelson1980}. The contribution of the library is the
checked interface: definitions bundled the way Mathlib expects, exact range
and uniqueness theorems for both expectations, and adapters into existing
Mathlib results.

Lean declaration identifiers are printed throughout in monospaced type, for
example \texttt{partitionPinching\_idem}; the underscore is part of the
identifier. To locate a declaration, search for the exact printed identifier,
after removing only TeX's protective backslash before each underscore, in the
\texttt{EventAlgebra/*.lean} files. In the public repository these files are
under \texttt{Lean/EventAlgebra/}; in the
standalone artifact they are under \texttt{event-algebra-lean/EventAlgebra/}.
Table~\ref{tab:modules} maps each module name to its subject matter, and the
top-level \texttt{EventAlgebra.lean} file imports all seven modules.

The submitted code adds seven pieces:

\begin{enumerate}[(i)]
\item an arbitrary supplied projective partition, independent of a selected
state or spectral resolution, with its commutant bundled as a
\texttt{StarSubalgebra} and its span bundled with multiplication, star,
commutativity, and centrality theorems;
\item partition pinching bundled as a complex \texttt{LinearMap}, with exact
range and fixed-point theorems, positivity, unitality, trace preservation, the
commutant bimodule law, Hilbert--Schmidt geometry, and map-level uniqueness;
\item partition averaging bundled as a complex \texttt{LinearMap} onto the
span, with exact range, trace duality, map-level uniqueness, tower laws
against the pinching, preservation of partition Born statistics, and a
classical-conditioning collapse theorem;
\item a typed nonzero-weight L\"uders state update, a support theorem and an
unguarded fixed-point characterization that exhibit conditioning as a
retraction onto its certainty set, and naturality of the typed update under
partition pinching for commutant events;
\item an event-to-observable CHSH client that discharges Mathlib-compatible
selfadjointness, involutivity, and cross-commutation hypotheses before
applying a complementary norm-form bound;
\item a checked state-expectation bound that converts the norm-form theorem
into a state-level CHSH bound; and
\item a reproducible, version-pinned artifact with per-declaration axiom
output, no proof placeholders, and a documented catalog of the Mathlib gaps,
scoped-instance hazards, and workarounds met during construction
(Section~\ref{sec:mathlib}).
\end{enumerate}

Four results are outside the current library. Neither expectation is bundled
as a completely positive trace-preserving channel. No theorem identifies an
arbitrary partition with Physlib's spectral partition. There is no rank-one
classical-representation theorem. The CHSH bounds carry no sharpness witness:
nothing asserts that $2\sqrt2$ is attained.

Section~\ref{sec:setting} fixes the mathematical and Lean interfaces.
Sections~\ref{sec:events} and \ref{sec:lueders} treat projection events and
selective update. Section~\ref{sec:pinching} gives the bundled partition
pinching and its geometry, and Section~\ref{sec:average} the averaging
expectation and the two-level structure. Sections~\ref{sec:functional} and
\ref{sec:chsh} describe the state functional and the CHSH clients.
Section~\ref{sec:mathlib} records the Mathlib engagement.
Section~\ref{sec:evaluation} reports the audit methodology, and
Section~\ref{sec:comparison} positions the development feature by feature.

\section{Mathematical and formal setting}
\label{sec:setting}

Let $\Mn$ be the complex $n\times n$ matrices, with conjugate transpose
$X\mapsto X^*$, trace $\Tr$, and identity $\one$. Following the standard
finite-dimensional setting \cite{vonneumann1932}, a projection event is a
Hermitian idempotent $P=P^*=P^2$, a state is a positive-semidefinite matrix
$\rho$ with $\Tr(\rho)=1$, and the trace pairing is
$\mu_\rho(M)=\Tr(\rho M)$.

Lean represents these interfaces as predicates over Mathlib matrices:
\texttt{IsEvent P} is the conjunction $P^*=P$ and $P^2=P$;
\texttt{IsState rho} is positive semidefiniteness and unit trace. For
functions that return states, the library defines the subtypes
\texttt{ProjectionEvent n} and \texttt{StateMatrix n}. The split is
practical. Algebraic lemmas use raw matrices. A function advertised as a state
update returns a value whose type carries the state conditions.

Table~\ref{tab:modules} lists the seven source modules. The comparison in
this work concerns their compiled interfaces and uses, not the number of
declarations in each file.

\begin{table}[ht]
\centering
\small
\begin{tabular}{@{}L{3.0cm}L{9.2cm}@{}}
\toprule
Module & Principal interface \\
\midrule
\texttt{Basic} & projection events, states, trace pairing, closure and Born
weight bounds \\
\texttt{Lueders} & totalized matrix formula, typed state update, repeatability,
composition, support, and fixed points \\
\texttt{PartitionPinching} & projective partitions, bundled commutant,
bundled linear pinching, exact range, geometry, bimodule law, and naturality \\
\texttt{PartitionAverage} & partition span with closure, commutativity, and
centrality; bundled averaging expectation with exact range, uniqueness, tower
laws, statistics preservation, and classical conditioning \\
\texttt{StateExpectation} & trace pairing bundled as a complex-linear
functional, normalization and positivity \\
\texttt{Tsirelson} & CHSH ring identity, norm theorem, Mathlib interoperability,
and event-level matrix client \\
\texttt{ExpectationBound} & state-expectation operator-norm bound and the
state-level CHSH corollary \\
\bottomrule
\end{tabular}
\caption{Module structure of the checked development.}
\label{tab:modules}
\end{table}

Three Mathlib scopes affect compilation. \texttt{ComplexOrder} equips
$\C$ with the partial order in which $0\le z$ means that $z$ is real and
nonnegative. \texttt{MatrixOrder} supplies the Loewner order.
\texttt{Matrix.Norms.L2Operator} activates the finite-matrix operator norm and
C*-ring instances used by the matrix CHSH theorems. Without the right scope,
Lean may report an instance problem even though the required theorem is in
scope; Section~\ref{sec:mathlib} describes the failure modes.

Documentation tags classify results as \emph{algebra-only} or
\emph{trace-dependent}. These tags do not define an import hierarchy. They
record whether a proof uses ring, star, and norm structure alone, or also uses
$\Tr(\rho M)$, positivity, or normalization.

\section{Projection events and the trace pairing}
\label{sec:events}

The event layer proves the expected closure rules. Zero, identity, and
$\one-P$ are events. Orthogonality is symmetric. Orthogonal sums and products
of commuting events are events. Subevent absorption holds on both sides, and
every event is positive semidefinite. The declaration
\texttt{IsEvent.one\_sub\_two\_smul\_involution} proves that
$\one-2P$ is a selfadjoint involution. The CHSH adapter in
Section~\ref{sec:chsh} uses this result.

The trace pairing is additive, homogeneous, compatible with finite sums, and
obeys the sandwich identity
\[
  \Tr(P\rho P)=\Tr(\rho P)
\]
for idempotent $P$. Hermiticity of $\rho$ and $P$ implies that the pairing is
real. Positivity of $\rho$ and the event property imply
$0\le\mu_\rho(P)$ in Mathlib's order on $\C$; for a state the upper bound is
$\mu_\rho(P)\le 1$. The order-form statements are strictly stronger than
their real-part corollaries, and both forms are provided.

The declaration
\texttt{isEvent\_add\_and\_bornWeight\_add\_of\_orthogonal} returns two facts:
the orthogonal sum is an event, and its Born weight is the sum of the two Born
weights. The event and orthogonality hypotheses carry the first conjunct; the
weight identity is linear and uses none of them.

\section{L\"uders update as a partial state interface}
\label{sec:lueders}

For raw matrices, the library uses the totalized formula
\[
 \lued_P(\rho)=\mu_\rho(P)^{-1}P\rho P.
\]
Lean's field inverse maps zero to zero, so the formula is total and covers
algebraic identities in the zero-weight case. Its return type is a raw matrix
and carries no state guarantee. The typed operation is
\[
\begin{aligned}
\texttt{luedersStateUpdate}:\quad&
 \texttt{StateMatrix n}\to\texttt{ProjectionEvent n}\\
 &\to(\mu_\rho(P)\ne0)\to\texttt{StateMatrix n}.
\end{aligned}
\]
This operation assumes \texttt{NeZero n}. The unique $0\times0$ matrix cannot
have unit trace, so a state-returning function must exclude that dimension.

\begin{proposition}[Checked L\"uders interface]
\label{prop:lueders}
For a state $\rho$, event $P$, and nonzero outcome weight:
\begin{enumerate}[(i)]
\item the raw formula is positive semidefinite and has trace one
(\texttt{luedersUpdate\_isState});
\item the updated state assigns weight one to $P$
(\texttt{bornWeight\_luedersUpdate\_self});
\item update is an idempotent retraction
(\texttt{luedersUpdate\_idem});
\item updates by commuting events compose and commute
(\texttt{luedersUpdate\_luedersUpdate\_of\_commute} and
\texttt{luedersUpdate\_comm});
\item when the state commutes with the event, the update is the normalized
block restriction $\mu_\rho(P)^{-1}\rho P$
(\texttt{luedersUpdate\_of\_commute}); and
\item the fixed-state equivalence
\[
  \lued_P(\rho)=\rho \quad\Longleftrightarrow\quad \mu_\rho(P)=1
\]
holds without a separate nonzero-weight hypothesis
(\texttt{luedersUpdate\_eq\_self\_iff}).
\end{enumerate}
\end{proposition}

The fixed-point theorem needs no nonzero-weight guard. A state fixed by a
zero-weight totalized update would equal the zero matrix, which has the wrong
trace. The raw function covers the zero-weight case; the state theorem
does not carry a redundant premise.

The module assembles these results into a fixed-point description of
conditioning. The set \texttt{certainStates} collects the states that assign
weight one to $P$. Conditioning any state of nonzero weight lands in that set
in a single step (\texttt{luedersUpdate\_mem\_certainStates}), acts on the
set as the identity, and, among states, fixes exactly its elements.
Conditioning on $P$ is therefore a retraction of the nonzero-weight states
onto its own fixed-point set. The identity case rests on a support theorem,
\texttt{mul\_eq\_self\_of\_bornWeight\_one}: a state certain of $P$ absorbs
the event on both sides, $\sigma P=P\sigma=\sigma$. The checked proof
compresses $\sigma$ by the complement event, whose weight vanishes; positive
semidefiniteness forces the zero-trace compression to vanish; and the
Cauchy--Schwarz property of the state's quadratic form eliminates
$\sigma(\one-P)$ itself.

\section{Bundled arbitrary-partition pinching}
\label{sec:pinching}

A \texttt{ProjectivePartition n k} consists of projections
$(P_i)_{i<k}$, pairwise orthogonality, and $\sum_iP_i=\one$. It induces
\[
 \pinch_\pi(X)=\sum_iP_iXP_i,
 \qquad
 N_\pi=\{X:XP_i=P_iX\text{ for every }i\}.
\]
The code defines $N_\pi$ as
\texttt{ProjectivePartition.commutant}, a
\texttt{StarSubalgebra} defined using Mathlib's centralizer, and bundles
$\pinch_\pi$ as \texttt{partitionPinchingLinearMap}. The membership theorem
\texttt{mem\_commutant\_iff} reduces membership to the pointwise commutation
equation.

The range is a block-diagonal commutant and need not be commutative. For this
reason, we do not call it a ``classical algebra''; the classical layer is the
span of Section~\ref{sec:average}. The library has no theorem identifying
the span with the center of the commutant, and no rank-one
classical-representation theorem.

\begin{theorem}[Bundled retraction and exact range]
\label{thm:pinching-range}
For every projective partition $\pi$, the map $\pinch_\pi$ is complex linear,
unital, positive, trace preserving, and idempotent. It lands in $N_\pi$ and
fixes $N_\pi$ pointwise. Consequently
\[
 \pinch_\pi(X)=X \Longleftrightarrow X\in N_\pi,
 \qquad
 \operatorname{range}(\pinch_\pi)=N_\pi
\]
where the second equality is the equality of the linear-map range and the
underlying submodule of the bundled commutant.
\end{theorem}

The corresponding declarations are
\texttt{partitionPinching\_unital},
\texttt{partitionPinching\_posSemidef},
\texttt{trace\_partitionPinching},
\texttt{partitionPinching\_idem},
\texttt{partitionPinching\_eq\_self\_iff\_mem\_commutant}, and
\texttt{range\_partitionPinchingLinearMap}. State preservation is exposed by
\texttt{partitionPinching\_isState}.

\begin{theorem}[Bimodule and Hilbert--Schmidt structure]
\label{thm:pinching-geometry}
If $A,B\in N_\pi$, then
\[
 \pinch_\pi(AXB)=A\pinch_\pi(X)B.
\]
Pinching is also selfadjoint for the trace pairing and satisfies the
Pythagorean identity
\[
 \Tr(X^*X)=
 \Tr(\pinch_\pi(X)^*\pinch_\pi(X))+
 \Tr((X-\pinch_\pi(X))^*(X-\pinch_\pi(X))),
\]
and hence contracts the squared Hilbert--Schmidt quantity. A
commutant-valued complex-linear map with the same trace pairings against every
commutant element equals \texttt{partitionPinchingLinearMap}.
\end{theorem}

The corresponding declarations are
\texttt{partitionPinching\_bimodule},
\texttt{trace\_conjTranspose\_partitionPinching\_mul},
\texttt{trace\_partitionPinching\_pythagoras},
\texttt{trace\_partitionPinching\_contraction},
\texttt{trace\_partitionPinching\_mul\_commutant}, and
\texttt{partitionPinchingLinearMap\_unique}. Together they make the map a
positive, unital, trace-preserving linear projection with a bimodule law and
a trace-duality characterization; these are the identities that
characterize the trace-preserving conditional expectation onto a subalgebra
in the operator-algebra literature \cite{umegaki1954,takesaki1972}. The
library proves the identities directly for this map. It does not instantiate
an operator-algebra conditional-expectation or channel interface because
complete positivity is not proved.

\subsection{L\"uders naturality}

If $P\in N_\pi$, compression commutes with pinching. After normalization,
trace preservation against commutant elements gives
\[
 \pinch_\pi(\lued_P(\rho))=
 \lued_P(\pinch_\pi(\rho)).
\]
The raw formula is
\texttt{partitionPinching\_luedersUpdate}. The theorem
\texttt{partitionPinching\_luedersStateUpdate} states the same naturality for
\texttt{StateMatrix n} and \texttt{ProjectionEvent n}: the input and output
are states, and the nonzero-weight proof is transported by
\texttt{bornWeight\_partitionPinching}. This checks the same operation through
the bundled state and event interfaces.

\section{Averaging on the partition span}
\label{sec:average}

The same partition carries a second canonical expectation. The
\emph{partition span}
\[
 D_\pi=\operatorname{span}\{P_i\}
\]
is bundled as \texttt{ProjectivePartition.span}. Its closure package is
proved by span induction.

\begin{proposition}[The commutative layer]
\label{prop:span}
$D_\pi$ contains every projector and the identity, and is closed under
multiplication and conjugate transposition
(\texttt{proj\_mem\_span}, \texttt{one\_mem\_span},
\texttt{mul\_mem\_span}, \texttt{conjTranspose\_mem\_span}). It is
commutative (\texttt{span\_mul\_comm}). It is contained in the commutant
(\texttt{span\_le\_commutant}), and every element of $D_\pi$ commutes with
every element of $N_\pi$
(\texttt{mul\_comm\_of\_mem\_span\_of\_mem\_commutant}): the span lies in the
center of the commutant.
\end{proposition}

Only the inclusion into the center is proved; the library does not claim the
reverse inclusion, which fails in the presence of zero projectors. The
averaging map is
\[
 \avg_\pi(X)=\sum_i\frac{\Tr(XP_i)}{\Tr(P_i)}\,P_i,
\]
bundled as \texttt{partitionAverageLinearMap}. Lean's zero-totalized inverse
makes the terms of zero projectors vanish, so no nonzero-block hypothesis
appears anywhere in the module: a zero projector contributes zero to both
sides of every identity below.

\begin{theorem}[Averaging expectation and exact range]
\label{thm:average}
For every projective partition $\pi$, the map $\avg_\pi$ is complex linear,
unital, positive, trace preserving, and idempotent. It lands in $D_\pi$,
fixes $D_\pi$ pointwise, and
\[
 \avg_\pi(X)=X \Longleftrightarrow X\in D_\pi,
 \qquad
 \operatorname{range}(\avg_\pi)=D_\pi.
\]
Against every $C\in D_\pi$ the average is invisible to the trace pairing,
$\Tr(\avg_\pi(X)\,C)=\Tr(XC)$, and any $D_\pi$-valued complex-linear map with
this property equals the bundled average.
\end{theorem}

The corresponding declarations are
\texttt{partitionAverage\_unital},
\texttt{partitionAverage\_posSemidef},
\texttt{trace\_partitionAverage},
\texttt{partitionAverage\_idem},
\texttt{partitionAverage\_eq\_self\_iff\_mem\_span},
\texttt{range\_partitionAverageLinearMap},
\texttt{trace\_partitionAverage\_mul\_of\_mem}, and
\texttt{partitionAverageLinearMap\_unique}; state preservation is
\texttt{partitionAverage\_isState}. The uniqueness proof mirrors the pinching
case: the difference lies in the star-closed span, is trace-orthogonal to its
own conjugate transpose, and vanishes by faithfulness of the trace.

\begin{theorem}[Two-level structure]
\label{thm:two-level}
The two expectations compose as a tower,
\[
 \avg_\pi\circ\pinch_\pi=\avg_\pi=\pinch_\pi\circ\avg_\pi ,
\]
(\texttt{partitionAverage\_partitionPinching},
\texttt{partitionPinching\_partitionAverage}). The average preserves the
Born statistics of the partition,
$\mu_{\avg_\pi(\rho)}(P_j)=\mu_\rho(P_j)$ for every $j$
(\texttt{bornWeight\_partitionAverage}). For a partition member $P_j$ of
nonzero weight, averaging commutes with L\"uders conditioning, and both
composites collapse to the normalized projector:
\[
 \avg_\pi(\lued_{P_j}(\rho))
 =\lued_{P_j}(\avg_\pi(\rho))
 =\Tr(P_j)^{-1}\,P_j
\]
(\texttt{partitionAverage\_luedersUpdate},
\texttt{partitionAverage\_luedersUpdate\_proj},
\texttt{luedersUpdate\_partitionAverage\_proj}).
\end{theorem}

The collapse identity is the finite-matrix form of classical conditioning:
on the commutative layer, conditioning on an observed partition member
replaces the averaged state by the indicator of that member, normalized. The
identity is stated for raw matrices; the only hypothesis is the nonzero
outcome weight.

\section{The bundled state expectation}
\label{sec:functional}

For a matrix $\rho$, \texttt{stateExpectationLinearMap rho} bundles
$M\mapsto\Tr(\rho M)$ as a complex-linear functional. If $\rho$ is a state it
maps identity to one. If $\rho$ and $M$ are positive semidefinite, then the
expectation is nonnegative. The proof of
\texttt{expectation\_nonneg} uses a finite spectral decomposition of $M$,
cycles the trace, and reduces the result to a sum of products of nonnegative
diagonal entries; Section~\ref{sec:mathlib} explains why this elementary
route was chosen. Additivity and homogeneity come from the bundled
\texttt{LinearMap} interface and are not repeated as pointwise lemmas.

\section{CHSH interoperability as a client}
\label{sec:chsh}

For selfadjoint involutions $a_0,a_1,b_0,b_1$ with cross commutation, set
\[
 S=a_0b_0+a_0b_1+a_1b_0-a_1b_1.
\]
The development first proves, in a bare ring,
\[
 S^2=4\one-(a_0a_1-a_1a_0)(b_0b_1-b_1b_0)
\]
(\texttt{chsh\_mul\_self}). In a nontrivial unital C*-ring this yields the
operator-norm bound $\norm{S}\le2\sqrt2$
(\texttt{tsirelson\_bound}), the norm form of Tsirelson's inequality
\cite{tsirelson1980} for the CHSH combination \cite{chsh1969}. The analytic
half is short: selfadjoint involutions have norm one by the C*-identity
(\texttt{norm\_eq\_one\_of\_selfAdjoint\_involution}), commutators of
norm-one elements have norm at most two
(\texttt{norm\_commutator\_le\_two}), and the square identity converts these
bounds into $\norm{S}^2\le8$. The precise Mathlib structure is a
\texttt{NormedRing}, \texttt{StarRing}, \texttt{CStarRing}, and
\texttt{Nontrivial}. The result is stated for a unital C*-ring.

The theorem \texttt{tsirelson\_bound\_of\_isCHSHTuple} accepts Mathlib's
\texttt{IsCHSHTuple}. The matrix instantiation,
\texttt{matrix\_tsirelson\_bound}, activates Mathlib's scoped operator
norm. The declaration \texttt{matrix\_tsirelson\_bound\_of\_events} accepts four
projection events plus the four cross-commutation equations, constructs the
dichotomic observables $\one-2P$, and returns the norm bound. This gives the
event layer a compiled path into the CHSH theorem.

Mathlib's \texttt{tsirelson\_inequality} is an order inequality in a
star-ordered real algebra \cite{mathlibCHSH2026}. The theorems in this
artifact are an operator-norm bound and its state-level corollary below;
they provide no equality witness.

\subsection{The state-level corollary}
\label{subsec:statechsh}

The bridge from norms to states is the checked bound
\[
 \lvert\Tr(\rho M)\rvert\le\norm{M}
\]
for every state $\rho$ and observable $M$
(\texttt{norm\_expectation\_le\_l2\_opNorm}). The proof diagonalizes the
state, cycles the trace to $\Tr\!\bigl(D\,(V^*MV)\bigr)$, dominates every
diagonal entry of the conjugated observable by the operator norm
(\texttt{norm\_diag\_entry\_le\_l2\_opNorm}, by testing against a standard
basis vector), uses that unitary conjugation does not increase the norm
(\texttt{norm\_eq\_one\_of\_mem\_unitaryGroup} with submultiplicativity), and
sums the nonnegative eigenvalues to one. Composing with the event-level norm
bound gives the state-level CHSH corollary
(\texttt{matrix\_state\_tsirelson\_bound\_of\_events}): for a state and four
projection events with cross-party commutation,
\[
 \bigl\lvert\Tr(\rho S)\bigr\rvert\le2\sqrt2
\]
for the CHSH combination $S$ of the dichotomic observables $\one-2P$. The
pairing $\Tr(\rho S)$ is real by \texttt{star\_bornWeight}, since $S$ is
selfadjoint, so the modulus bound is a two-sided real bound. No sharpness
witness is claimed.

\section{Working over Mathlib: scopes, gaps, and affordances}
\label{sec:mathlib}

This section records what the construction consumed from Mathlib, where the
library resisted, and which workarounds closed the gaps. The artifact
repeats the catalog in the notes file \texttt{MATHLIB\_NOTES.md}.

\subsection{Scoped instances}

The three scopes of Section~\ref{sec:setting} share a failure mode. The
partial order on $\C$ and the Loewner order are scoped instances; every
$0\le z$ goal and every positive-semidefiniteness statement over $\C$
elaborates only when the scope is open, and a missing scope surfaces as an
instance-resolution error far from its cause. \texttt{ComplexOrder} also
carries the scoped ordered-ring structure on $\C$ that supplies
multiplicativity of nonnegativity inside the complex order. There is no
global norm on Mathlib matrices; the operator norm, the
\texttt{NormedRing} structure, and the \texttt{CStarRing} instance arrive
only under \texttt{Matrix.Norms.L2Operator}, so the entire Tsirelson section
lives behind that scope. The \texttt{Nontrivial} instance for
$n\times n$ complex matrices with $n\ne0$ did not synthesize and is
constructed by hand, entrywise. The matrix unitary group is a submonoid
distinct from Mathlib's \texttt{unitary} bundle, so its norm-one property is
also proved by hand from the C*-identity.

\subsection{Gaps and workarounds}

\emph{Bilinear trace positivity.} Mathlib proves $0\le\Tr(A)$ for a single
positive-semidefinite matrix and covers sandwich forms $BAB^*$. The
bilinear statement $0\le\Tr(AB)$ for two positive-semidefinite factors is
absent. For Born weights the gap costs nothing, because
$\Tr(\rho P)=\Tr(P\rho P)$ for idempotent $P$. For
\texttt{expectation\_nonneg} the natural route, the C*-order equivalence
between nonnegativity and Gram factorization, fails to elaborate: two
continuous-functional-calculus instances are not synthesized for the matrix
algebra under its product topology. The proof takes the elementary route
instead, a spectral decomposition of the observable followed by a trace
cycle and termwise nonnegativity, in about a dozen lines.

\emph{The ring identity.} The square identity behind the Tsirelson bound is
pure noncommutative ring algebra under side relations: four involutivity
equations and four cross commutations. Lean has no noncommutative analogue
of \texttt{linear\_combination}, and \texttt{noncomm\_ring} does not use
hypotheses. The checked proof builds a small confluent rewrite system. Each
commutation hypothesis is recast as a universally quantified,
association-compatible form $b(ax)=a(bx)$, and each involution as
$a(ax)=x$; applied through \texttt{simp only}, these rules move every $b$
past every $a$ in right-associated words and cancel adjacent equal letters.
Every rewrite strictly decreases the number of letter pairs out of normal
order, so the system terminates, and \texttt{abel} closes the remaining
additive goal.

\emph{Higher-order motives.} Two steps needed their motives spelled out.
The binary span-induction principle behind the closure package of
Proposition~\ref{prop:span} does not infer its motive from the goal; the
predicate is passed explicitly. Rewriting with the unit-trace equation
inside a hypothesis whose proof term mentions the bundled state predicate
fails the motive typecheck, because the state predicate itself contains the
trace being abstracted; a term-level chain through injectivity of the real
embedding replaces the rewrite.

\emph{Rewriting discipline.} Unfolding the definition of the Born weight
rewrites the first syntactic occurrence, which in normalized expressions is
often the normalizing scalar $\mu_\rho(P)^{-1}$ instead of the intended trace
argument. The affected proofs isolate each trace identity as a standalone
step with explicit arguments to the trace commutation and cycling lemmas.

\subsection{Affordances}

The \texttt{Matrix.PosSemidef} API is complete enough that the development
never unfolds the definition of positive semidefiniteness: sandwich closure,
sums, scalar multiples, diagonal nonnegativity, trace nonnegativity, and the
Gram construction cover every need, and the scalar lemma accepts a complex
scalar that is nonnegative in the complex order, which makes the L\"uders
normalization a single application. Trace faithfulness is available in two
forms: the conjugate-transpose criterion powers the uniqueness theorems of
both expectations, and the zero-trace criterion together with the
Cauchy--Schwarz property of positive matrices powers the support theorem of
Section~\ref{sec:lueders}. On the analytic side, the C*-identity, the
norm-one property of the unit, and submultiplicativity reduce the norm half
of the Tsirelson bound to about forty lines over the four-typeclass
signature, and the matrix case is a two-line instantiation behind the norm
scope. The state-expectation bound of Section~\ref{subsec:statechsh} rests
on the scoped norm being definitionally the Euclidean operator norm: the
type synonym is identity-transparent, so a \texttt{show} converts
Euclidean-space statements to raw matrix-vector algebra, and the
basis-vector, submultiplicativity, and eigenvalue-trace lemmas finish the
proof in about sixty lines. Mathlib's CHSH file supplied the
\texttt{IsCHSHTuple} bundle, so interoperability with the order-form theorem
cost one conversion theorem.

\section{Artifact evaluation and proof audit}
\label{sec:evaluation}

The source is a Lake project. Its toolchain pins
\texttt{leanprover/lean4:v4.29.1}; its manifest pins Mathlib commit
\texttt{5e932f97dd25535344f80f9dd8da3aab83df0fe6}. Build the library with
\begin{center}
\texttt{lake build EventAlgebra}.
\end{center}
The canonical Lean modules are publicly available in the Observer Patch
Holography repository \cite{observerPatchHolographyRepo} at commit
\texttt{49ee36e01eb245d4d508e82c9b08fd47f7a85243}. The manuscript
source accompanies the submission. It includes a standalone archive
\cite{eventalgebra} with a byte-identical copy of those modules.

Table~\ref{tab:scale} describes the scale of the development. The counts are
descriptive; the comparison in Section~\ref{sec:comparison} concerns
interfaces, not counts.

\begin{table}[ht]
\centering
\small
\begin{tabular}{@{}lrr@{}}
\toprule
Module & Lines & Audited declarations \\
\midrule
\texttt{Basic} & 302 & 25 \\
\texttt{Lueders} & 294 & 14 \\
\texttt{PartitionPinching} & 474 & 27 \\
\texttt{PartitionAverage} & 513 & 30 \\
\texttt{StateExpectation} & 105 & 4 \\
\texttt{Tsirelson} & 275 & 8 \\
\texttt{ExpectationBound} & 174 & 4 \\
\texttt{EventAlgebra} (root) & 41 & 0 \\
\midrule
Total & 2178 & 112 \\
\bottomrule
\end{tabular}
\caption{Source lines and per-module counts of declarations covered by the
generated axiom audit.}
\label{tab:scale}
\end{table}

Every public result discussed in the paper appears under its Lean name. The
modules end with \texttt{\#print axioms} commands for the principal
declarations, and the artifact stores the generated output. Of the 112
audited declarations, 110 report exactly propositional extensionality,
classical choice, and quotient soundness, the standard Lean/Mathlib base.
The CHSH ring identity and the event-commutation adapter report
propositional extensionality and quotient soundness alone; the bare ring
algebra needs no classical choice. No declaration reports \texttt{sorryAx},
and a source scan finds no \texttt{sorry} placeholder in the submitted
modules.

The submitted API uses every orthogonality hypothesis in its orthogonal-sum
theorem. The sequential-update theorem has no unused event premise. State
update is typed and excludes dimension zero. The fixed-point equivalence has
no nonzero-weight guard, and the averaging module carries no nonzero-block
hypotheses. The commutant, span, and both expectations are bundled, and the
CHSH adapters are clients of the event definitions.

The release archive contains the toolchain, Lake manifest, source modules,
build command, checksums, captured axiom output, and a Creative Commons
BY-NC-SA 4.0 license. It has no public release tag or persistent archive
identifier.

\section{Feature-level comparison}
\label{sec:comparison}

Table~\ref{tab:comparison} compares compiled features. It does not treat a
count of elementary lemmas as a research contribution.

\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{@{}L{2.1cm}L{4.25cm}L{6.0cm}@{}}
\toprule
Feature & Closest checked infrastructure & This artifact \\
\midrule
Projective measurement & Isabelle/HOL projective-measurement developments;
state/measurement interfaces in current Lean libraries & finite matrix event
predicate, typed event/state subtypes, closure and trace-pairing lemmas; treated
as prerequisite; no priority claim \\
Pinching & Physlib spectral pinching is a state-selected bundled CPTP map with
fixed-point and geometric results & arbitrary supplied projective partition;
bundled linear map and commutant; no CPTP or Physlib correspondence theorem \\
Retraction structure & operator-algebra conditional expectations and channel
interfaces & exact range/fixed points, positive/unital/trace-preserving,
bimodule, Hilbert--Schmidt geometry, map-level trace-duality uniqueness \\
Commutative layer & conditional expectations onto commutative subalgebras in
operator-algebra practice & bundled averaging expectation onto the partition
span, exact range and uniqueness, tower laws with pinching, Born-statistics
preservation, classical-conditioning collapse \\
L\"uders update & Isabelle projective measurement and general channel
infrastructure & raw formula plus typed partial state API, support theorem,
unguarded state fixed-point equivalence, typed naturality with
arbitrary-partition pinching \\
CHSH/Tsirelson & Mathlib order theorem; Isabelle upper bound; Lean CHSH
rigidity & complementary norm theorem, event-level client, and
state-expectation corollary; no tightness claim \\
Reproducibility & public CI and archived releases are common best practice &
pinned Lean/Mathlib, clean artifact build instructions, checksums and static
axiom audit; no DOI claim \\
\bottomrule
\end{tabular}
\caption{Direct comparison with the closest formal infrastructure.}
\label{tab:comparison}
\end{table}

Physlib provides more channel structure: its spectral pinching is a
\texttt{CPTPMap} \cite{physlibPinching2026}. This artifact accepts a supplied
partition that need not come from the spectrum of a state. The two APIs
therefore have different inputs, and no correspondence theorem connects them.

Lean-Quantum and Lean-QIT cover a larger part of quantum information
\cite{kasauraEtAl2026LeanQuantum,zhuEtAl2026LeanQIT}. Here, the scope is
limited to connections among projections, commutants, spans, the two
expectations, selective update, and Mathlib's CHSH interface.

\section{Limitations and conclusion}
\label{sec:conclusion}

The library connects projection events, Born weights, a typed L\"uders
update, arbitrary projective partitions, the two expectations of a partition,
and event-level CHSH bounds in norm and state form. The pinching has the
bundled commutant as its exact range and the average has the bundled span;
each map is the unique trace-dual projection onto its range, the two compose
as a tower, and both interact with L\"uders conditioning by checked
theorems. Each statement in the paper points to a declaration in the
submitted source.

The construction follows one pattern: state algebraic content as predicates
over raw matrices, move to subtypes exactly where an API promises a state,
bundle the carrier and the projection so that range and uniqueness theorems
are exact, and hand finished objects to Mathlib interfaces through small
adapters. The pattern is independent of measurement theory and applies to
other finite-dimensional operator-algebra developments over Mathlib.

Complete positivity is not established, so neither expectation is a quantum
channel in the library. There is no theorem connecting the supplied
partition to Physlib's spectral pinching and no rank-one classical
specialization. The CHSH bounds have no sharpness witness. The entire
development is finite-dimensional and says nothing about normal maps on
infinite-dimensional von Neumann algebras.

Open work consists of four items: prove complete positivity, bundle the
maps as CPTP channels, connect spectral partitions to Physlib, and add a
two-qubit sharpness witness for the CHSH bounds. The present artifact
provides the arbitrary-partition pinching with its exact range and bimodule
law, the averaging expectation with its tower and classical-conditioning
laws, typed L\"uders naturality, and the state-level CHSH corollary.

\section*{Declarations}

\textbf{Funding.} No funding was received for this work.

\textbf{Competing interests.} The author declares no competing interests.

\textbf{Author contributions.} Bernhard Mueller is the sole author, designed
the study, reviewed the formal development, and takes responsibility for the
manuscript and artifact.

\textbf{Data and code availability.} No empirical data were generated. The
canonical Lean source is available in the Observer Patch Holography
repository \cite{observerPatchHolographyRepo} at commit
\texttt{49ee36e01eb245d4d508e82c9b08fd47f7a85243}. The Lean source, pinned
dependency files, build instructions, axiom report, and
checksums also accompany the submission \cite{eventalgebra}, under a Creative
Commons BY-NC-SA 4.0 license. No persistent archive identifier is
claimed.

\bibliographystyle{plainnat}
\bibliography{machine_checked_finite_event_algebras}

\end{document}
