\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,array,longtable}
\usepackage[shortlabels]{enumitem}
\usepackage{hyperref}
\usepackage{xurl}
\IfFileExists{paper/release_info.tex}{%
  \input{paper/release_info.tex}%
}{%
  \IfFileExists{../paper/release_info.tex}{%
    \input{../paper/release_info.tex}%
  }{%
    \IfFileExists{../reverse-engineering-reality/paper/release_info.tex}{%
      \input{../reverse-engineering-reality/paper/release_info.tex}%
    }{%
      \newcommand{\OPHPaperReleaseID}{r1518}%
      \newcommand{\OPHPaperReleaseDate}{July 7, 2026}%
      \newcommand{\OPHPaperReleaseBanner}{%
        \begin{center}
        \small\textbf{Paper release:} \texttt{\OPHPaperReleaseID}\quad\textbf{Released:} \OPHPaperReleaseDate
        \end{center}}
    }%
  }%
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{claim}[theorem]{Claim}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\U}{\mathrm{U}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\Cent}{\operatorname{Cent}}
\newcommand{\im}{\operatorname{Im}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\Z}{\mathbb Z}
\newcommand{\calF}{\mathcal F}
\newcommand{\calO}{\mathcal O}
\newcommand{\calA}{\mathcal A}
\newcommand{\calR}{\mathcal R}
\newcommand{\calI}{\mathcal I}
\newcommand{\calU}{\mathcal U}
\newcommand{\ZfourR}{\mathbb Z_4^R}
\newcommand{\Teq}{\sim_{\OPH}}
\newcommand{\Mgrav}{\mathfrak M_{\mathrm{grav}}}
\newcommand{\TT}{\mathrm{TT}}

\title{Observer-Patch Holography as a String-Vacuum Selector:\\
Observers, Clocks, Edge Strings, and the Bouchard-Donagi Candidate}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

% #542 typesetting hardening (layout only, no claim change)
\usepackage{microtype}
\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
String theory is read here as an effective language for Observer-Patch Holography (OPH) edge dynamics. Finite observer patches compare shared records, and their settled repair histories can be read as worldsheet-like histories on the edge system.

The paper uses that reading as a vacuum-selection sieve. OPH supplies the target spacetime, Standard Model structure, records, interfaces, checkpoints, and synchronization rules. A conventional string vacuum is promoted only after the geometric, worldsheet-critical, threshold, and moduli-locking gates pass. The worked object is a heterotic Bouchard--Donagi (BD) type Standard Model construction with one massless Higgs pair and explicit safety gates. The published construction supplies a visible massless-cohomology spectrum, without the stabilized nonzero-mode spectrum or decoupling map needed for a low-energy threshold calculation. The smooth published one-Higgs space has \(71\) complex pre-completion moduli. The five-coordinate comparison map uses no BD branch data and has rank zero on that space; only three of its coordinates carry promoted OPH status. No completed physical slice or Jacobian is supplied. The operator-safe proposal is not selected. The structural BD audit row and the recovered OPH core are kept.
\end{abstract}

\section*{What This Paper Contributes}

String theory supplies a large language of edge dynamics, compactification,
moduli, and Standard Model candidates. This paper reads that language from the
OPH side. The OPH core first fixes the target spacetime, gauge quotient,
one-Higgs branch, records, clocks, and observer-facing boundary data. The
string description then becomes an effective edge language for histories
constrained by OPH.

The sieve carries the interaction package with the particle spectrum:
the OPH Einstein branch supplies the gravity target, the compact-gauge branch supplies the
strong/electroweak target, and the exact Standard Model quotient fixes the visible charge lattice.
The string representative must realize those forces and the particle content on the same
observer-visible branch.

The worked contribution is a sieve for string-vacuum candidates. A
Bouchard--Donagi type heterotic object is treated as a named structural test row and
tested against OPH gates: one massless Higgs pair, the Standard Model quotient,
operator safety, worldsheet criticality, threshold compatibility, and moduli locking. Every
unemitted certificate is explicit. The moduli gate carries a negative rank/isolation receipt,
rather than only a target equation. A vacuum survives only if its string data land on the OPH
quantitative vector without retuning and all physical source directions are locked. The statement
tests string data through OPH gates; it
does not promote a reference ensemble or ordinary string vacuum into the OPH-native vacuum.

\tableofcontents
\newpage

\section{Scope and Claim Boundary}

This paper records a specific bridge from the de Sitter observer problem to the OPH string
continuation. It separates three layers:
\[
\begin{aligned}
&\text{observer/clock implementation}\\
&\quad\longrightarrow \text{edge-string effective language}\\
&\quad\longrightarrow \text{critical string representative.}
\end{aligned}
\]
The first layer is OPH fixed-cutoff patch algebra. The second layer is the heat-kernel
edge-sector read-off. The third layer is the Bouchard-Donagi heterotic Standard Model used as a
named heterotic zero-mode candidate. The heat-kernel edge identity by itself does not prove a critical
worldsheet CFT; the critical-edge certificate below is an additional condition on the continuum
edge branch.

\subsection{Forces, gauge group, and effective strings}

The reader-facing phrase ``particles and forces'' is translated here into OPH gates. The particle
is implemented through separate gates. The observer-visible normal form supplies representation
and charge data; explicit action and phase hypotheses supply classical carrier modes; and a
physical Hilbert space with a positive-residue pole supplies a particle. None of the latter two
steps follows from an abstract reconstructed group.

\begin{description}[leftmargin=2em]
\item[Gravity.]
The OPH target is a single Einstein-frame metric on the physical quotient whose pure-Einstein,
flat-background quadratic action has two transverse-traceless classical null modes. The critical
representative must supply the quantum-particle receipt for a closed-string symmetric spin-two state,
identify its classical limit with those metric modes, and match
\(G_4^{\rm string}=G_4^{\OPH}\).

\item[Strong force.]
The color factor is the \(\SU(3)_c\) part of the global quotient
\((\SU(3)\times\SU(2)\times\U(1))/\Z_6\). The visible compactification must realize this charge
lattice with no light chiral exotics.

\item[Weak and electromagnetic forces.]
The electroweak target is the \(\SU(2)\times\U(1)\) branch, the exact hypercharge lattice, the
one-Higgs target, and the resulting low-energy \(U(1)_{\rm em}\). The candidate must land on that
one-Higgs Standard Model branch and preserve the OPH hypercharge quotient.
The local Borel--Weil model \(H^0(\mathbb{CP}^1,\mathcal O(1))\cong\mathbb C^2\) is used only for
the observed light one-Higgs electroweak projection; it does not replace the full supersymmetric
Higgs-pair bookkeeping in a string witness.

\item[Standard Model gauge group.]
On the realized Minimal Admissible Realization (MAR)/tensor global-form branch, the target is
\(G_{\rm phys}=(\SU(3)\times\SU(2)\times\U(1))/\Z_6\); an abstract six-axis
residue is insufficient. The Bouchard-Donagi Wilson-line centralizer must equal
\(S(\U(3)\times\U(2))\cong G_{\rm phys}\), excluding simple-GUT \(X/Y\) generators from the
unbroken visible adjoint. Connection dynamics and particles require separate receipts.

\item[Effective string theory.]
The OPH input is stable cyclic edge normal forms, collar sewing, records, and accepted repair
histories. The fixed-cutoff read-off is \(Z_{\rm edge}=K_t(1)\); a controlled large-edge branch
gives the perturbative worldsheet language, and the critical-edge certificate decides whether the
branch is a heterotic critical string.
\end{description}

Thus the paper does not add forces after selecting particles. It first fixes the
observer-visible interaction structure and then asks which string compactification realizes that
whole structure. The three Standard Model gauge forces are the low-energy decomposition of the
global quotient, while the pure-Einstein tensor carrier is read as a closed-string graviton only
after a critical lift supplies the required physical-state and pole receipts.

The target claim is a gate implication, not a completed selection. The rank certificate shows that
the antecedent fails for the emitted BD source/target packet. Consequently the selector admits no
string representative from this row.

The notation separates two roles:
\[
BD_{n=1}^{\OPH}
\quad
\text{labels the geometric one-Higgs structural row,}
\]
\[
BD_{n=1,+}^{\OPH}
 =
BD_{n=1}^{\OPH}+\ZfourR
\quad
\text{labels the tested operator-safe proposal.}
\]
The \(+\) records the MSSM \(\ZfourR\) safety layer. The charge-algebra part of this gate closes
inside the paper; the realization of \(\ZfourR\) as a symmetry of the BD compactification is a
certificate gate. The issue-369 rank obstruction assigns failed selected/passing status to this
proposal. The underlying BD zero-mode construction remains a structural benchmark.

The compact rule is:
\[
\text{string theory is the edge-language of OPH.}
\]
In that reading, the string landscape is the space of effective edge-worldsheet completions. OPH
acts as a selector by imposing the observer-visible normal form.

The contrast with landscape reasoning is structural. The declared closure
maps admit at most one \((P,N)\); for the pixel coordinate
the statement is certified globally, exactly one fixed point per readout map
on the declared physical domain, by the machine-checked domain-global
uniqueness certificate shipped with the code release.
On the OPH side of the map
there is no vacuum landscape to relocate into, and the frozen target packet carries no
retunable target-side dials. The BD source does carry many unresolved physical continuous
directions; the rank certificate below makes that distinction explicit. The sieve reading of string
theory is therefore an edge-language statement, a statement about which
worldsheet completions can present the one selected normal form rather than a
competing selection mechanism, and it inherits no anthropic weighting from
the space of candidates it filters.

\begin{center}
\small
\begin{tabular}{p{0.25\linewidth}p{0.31\linewidth}p{0.34\linewidth}}
\toprule
\textbf{Goal} & \textbf{Paper claim} & \textbf{Receipt carried here} \\
\midrule
Named string test row & OPH tests the operator-safe Bouchard--Donagi one-Higgs heterotic
Standard Model proposal \(BD_{n=1,+}^{\OPH}\). Its selected-candidate status fails under
the moduli-rank obstruction. & Selector gates, global group proof, safety charge table,
structural sieve, and fail-closed rank certificate. \\
String-theory pressure points & The landscape, global group, Higgs multiplicity, exotics,
operator danger, proton decay, and moduli problems become explicit gates. & Gate table,
acceptance table, falsifier matrix. \\
Empirical test surface & The paper defines low-energy and threshold proxy targets
against which a completed branch could fail. & Higgs/top target coordinates, stop proxy,
one-loop gauge-running proxy, operator table. \\
\bottomrule
\end{tabular}
\end{center}


\section{OPH Entry Map for String Theorists}

For a reader entering OPH from string theory, the shortest safe translation is this. OPH begins
with finite observer patches. Each patch has local data, records, and overlap readouts. A physical
world is the quotient-normal form reached when accepted repair moves lower mismatch and the
local-diamond plus repair-completeness conditions make the observer-facing result
schedule-independent from a fixed initial quotient state. Same-boundary uniqueness requires a
preserved boundary or sector with a unique consistent quotient extension.
Geometry, gauge structure, particles, and edge strings are read from that normal form.

\subsection{Five informal summaries}

\paragraph{1. The basic rule.}
Observer patches are finite. They see shared boundary data. Physics is the public content that
survives overlap comparison and repair. The synthesis paper gives the broad entry point
\cite{OPHObserversAllYouNeed}; the consensus paper gives the fixed-cutoff repair theorem surface
\cite{OPHRealityConsensus}.

\paragraph{2. Why spacetime and gauge theory appear.}
Null structure, Lorentzian geometry, and the Einstein branch are recovered on the stated
observer-overlap consistency surface. In the gauge lane, overlap/holonomy data classify
fixed-stage zero-obstruction transportable sectors; on a cofinal tail carrying the compact-gauge
refinement receipt, DR/Tannaka reconstruction gives a compact group from that
category, and Minimal Admissible Realization (MAR) plus the explicit matter package selects the realized Standard Model quotient.
Here obstruction cancellation means both strictifying the central or higher associator defect and
finding at least one allowed strict edge \(1\)-cocycle representative with trivial represented
holonomy. That combined
criterion supplies transportability and classification. Standard Model
selection requires MAR and the explicit matter package.
The compact paper carries the theorem surface for this claim \cite{OPHCompactCore}. The Yang-Mills note
states the compact-gauge branch in the language of holonomy, Euclidean transfer, and the mass-gap
problem \cite{OPHYangMillsGap}.

\paragraph{3. Why particle numbers enter the selector.}
The particle-sector paper carries the electroweak, Higgs/top, quark, charged-lepton, neutrino, and
hadron audit lanes \cite{OPHParticleZoo}. The fine-structure note isolates the local pixel fixed
point that feeds the quantitative electroweak target \cite{OPHFineStructure}. These papers supply
the numerical vector against which the named BD structural row is screened.

\paragraph{4. Why observers and records are literal inputs.}
The screen-microphysics paper turns patches into finite record-bearing carriers with ports,
interfaces, synchronization rules, and checkpoint readouts \cite{OPHScreenMicrophysics}. The
thinking paper shows the same patch-net fixed-point machine as a model of biological cognition
\cite{OPHThinkingPatchNet}. For this string paper, the needed fact is concrete: observers are
record-bearing finite systems inside the theory.

\paragraph{5. Why phenomenology becomes a gate list.}
The dark-matter paper treats missing gravitational response as a quotient-edge scalar-channel
phenomenon with explicit stress-parent gates \cite{OPHDarkMatter}. The \(\chi_\nu\) note records
the coherent-matter source generator and susceptibility bounds used by that collar branch
\cite{OPHChiNuBounds}. The metaphysics continuation layer is background for the fixed-point
ontology and is outside the string selector proof.

\subsection{Source map}

The OPH reader path used here has ten entries. Each link points to the TeX source in the public
GitHub repository.

\begin{longtable}{p{0.27\linewidth}p{0.43\linewidth}p{0.20\linewidth}}
\toprule
\textbf{Source} & \textbf{Role in this paper} & \textbf{GitHub} \\
\midrule
Observers Are All You Need & Synthesis entry point: finite observer cuts, overlap agreement,
screen-capacity language, and the recovered-branch map. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.tex}{paper/source} \\
Recovering Relativity and the Standard Model from Observer Overlap Consistency & Compact theorem surface for Lorentz, Einstein,
receipt-conditional zero-obstruction compact-gauge reconstruction, MAR-selected global Standard Model quotient,
hypercharge, colors, generations, and no mixed \(X/Y\) generator in the connected
visible adjoint. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.tex}{paper/source} \\
Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics & Fixed-cutoff consensus theorem: mismatch functional, accepted
repair, quotient confluence, and holonomy obstructions. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.tex}{paper/source} \\
Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH & Finite carrier model for records, ports,
interfaces, checkpoint restoration, and observer synchronization. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.tex}{paper/source} \\
Deriving the Particle Zoo from Observer Consistency & Particle and electroweak quantitative lanes used by the
moduli-locking target vector. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.tex}{paper/source} \\
The Fine-Structure Constant as an OPH Pixel Fixed Point & Local screen-cell fixed point and
fine-structure input used by the electroweak target. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/fine_structure_constant_derivation.tex}{extra/source} \\
Observer-Patch Holography and the Dark Matter Phenomenon & Quotient-edge scalar-channel branch,
used as a phenomenology example of OPH gate logic. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/cosmology/oph_dark_matter_paper.tex}{cosmology/source} \\
Theoretical Bounds on \(\chi_\nu\) in Observer-Patch Holography & Coherent-matter source generator, collar survival, and
susceptibility bounds for the dark-sector continuation. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/chi_nu_susceptibility_bounds.tex}{extra/source} \\
Explaining the Yang--Mills Mass Gap with Observer-Patch Repair Dynamics & Receipt-certified compact-gauge reconstruction and mass-gap route, useful for
the gauge side of the string selector. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/yang_mills_gap_clay_problem.tex}{extra/source} \\
Thinking as Patch-Net Fixed-Point Search & Cognitive instance of the same finite patch-net
record and repair machine. &
\href{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/thinking_as_patch_net_fixed_point_search.tex}{extra/source} \\
\bottomrule
\end{longtable}

\section{Main Result: Conditional BD Witness Selection up to OPH Equivalence}

An OPH-correct critical string is defined only after the equivalence relation has been fixed. The
claim concerns observer-visible physical data, not notation, duality frame, worldsheet gauge, or
coordinate presentation. This paper supplies a named BD witness target and a finite encoded audit
set. A global singleton statement requires an exhaustive candidate-class certificate in addition to
the witness certificates.

\begin{definition}[OPH-equivalent critical presentations]
Two critical-string presentations \(\mathcal T_1\) and \(\mathcal T_2\) are OPH-equivalent,
written
\[
\mathcal T_1\Teq\mathcal T_2,
\]
when they induce the same observer-visible data:
\begin{enumerate}[leftmargin=2em]
\item the same edge-sewn heat-kernel partition on the compact gauge branch;
\item the same four-dimensional tensor-mode normalization and Einstein-frame metric perturbation;
\item the same global visible gauge group
\[
G_{\rm phys}=(\SU(3)\times\SU(2)\times\U(1))/\Z_6;
\]
\item the same hypercharge lattice, chiral index, and low-energy matter package;
\item the same operator-safety algebra on the visible superpotential;
\item the same complete OPH quantitative readout, including physical threshold and modulus
effects.
\end{enumerate}
Here ``OPH-invisible'' means an independently established presentation redundancy: a
diffeomorphism or bundle/B-field gauge orbit, bundle isomorphism, local representative or exact
field-basis change, or a verified scheme/duality change with identical complete public readout.
It is not defined as the kernel of a chosen finite target map. Physical scalar directions cannot be
discarded merely because the frozen five-coordinate packet does not read them. Duality frames
are charts on the same OPH-visible normal form only after that equivalence has been proved.
\end{definition}

\begin{lemma}[Quotient descent and presentation invariance]
Let a redundancy group \(G\) preserve the completed constraint locus, and let every component of
the observer-visible readout be \(G\)-invariant. The constraints and readout then descend to each
fixed-orbit-type stratum of the physical quotient. If two quotient charts are related by a
\(C^1\) diffeomorphism \(\phi\), and two equivalent output conventions are related by a \(C^1\)
diffeomorphism \(\psi\), then
\[
F'=\psi\circ F\circ\phi^{-1},
\qquad
DF'=D\psi\,DF\,D\phi^{-1}.
\]
Thus rank on the physical tangent, kernel dimension, and local isolation are independent of the
certified chart or convention. A scheme change or string duality can be placed in the invisible
quotient only after the transition maps and equality of the complete physical readout are proved.
An unclassified continuous stabilizer, singular orbit-type change, or gauge-copy ambiguity fails
this lemma's hypotheses and must be treated on a separate stratum.
\end{lemma}

\begin{proof}
Invariance makes the constraints and readout constant on every \(G\)-orbit, so the universal
property of the quotient gives the descended maps. The derivative formula is the chain rule.
Both outer derivatives are invertible, which preserves rank and kernel dimension. Diffeomorphisms
also preserve whether a target fiber is locally a singleton. The final sentence records cases in
which no such quotient chart has been certified.
\end{proof}

\begin{definition}[OPH-correct critical string]
A critical-string presentation \(\mathcal T\) is OPH-correct if it satisfies all of the following.
\begin{enumerate}[leftmargin=2em]
\item a critical completion of the OPH sewn-edge worldsheet branch, with the same
observer-visible edge data.
\item Its BRST-physical massless spin-two state supplies a positive-residue quantum completion of
the OPH Einstein-frame classical tensor mode.
\item Its visible compact gauge sector descends to
\((\SU(3)\times\SU(2)\times\U(1))/\Z_6\).
\item Its visible chiral spectrum is exactly three generations, no light chiral exotics, and the
one-Higgs-pair branch used by the OPH electroweak target.
\item Its visible operator algebra has the \(\ZfourR\) safety layer, or an OPH-equivalent rule,
which permits Yukawas and the Weinberg operator, and forbids perturbative RPV, perturbative
dimension-five proton decay, and the perturbative \(\mu\)-term.
\item Its completed physical equations have a dynamically stable solution, and its precommitted
scheme-locked threshold map satisfies
\[
\calF_{\mathcal T}(m_\star)=\calO_{\OPH}
\]
with full transverse rank jointly with the completion constraints after quotienting independently
proved OPH-invisible redundancies.
\end{enumerate}
\end{definition}

\begin{theorem}[Conditional BD witness theorem]
Assume the OPH recovered-core target, the heterotic edge-sector branch including the
finite-carrier critical-edge certificate, and the BD certificate gates listed in
Section~\ref{sec:claim-gates}. Assume also that the Bouchard--Donagi one-Higgs branch with the
operator-safety layer satisfies the cohomology, global-group, safety, threshold, and moduli-locking
gates, including a certified low-energy decoupling map. Then
\[
\boxed{BD_{n=1,+}^{\OPH}}
\]
is a passing named OPH-correct critical-string witness, modulo \(\Teq\).
\end{theorem}

\begin{proof}
The recovered-core target, after MAR selection of the admissible one-Higgs branch, fixes the
observer-visible endpoint: the global Standard Model quotient, three colors, three generations,
exact hypercharge lattice, one-Higgs electroweak branch, no light
chiral exotics, no extra visible low-scale \(\U(1)\), and the product-group absence of mixed
\(X/Y\) connected-adjoint generators. The edge-string continuation restricts the witness to critical presentations
whose worldsheet branch is the sewn OPH edge system and whose BRST-physical massless spin-two state
has the OPH metric perturbation as its classical limit. The Bouchard--Donagi
\(\Z_2\)-quotient \(\SU(5)\)-bundle
with one Higgs pair supplies the named heterotic witness with the required three-generation,
no-exotics visible massless cohomology and Wilson-line centralizer. The \(\ZfourR\) layer closes the visible
operator gate. The assumed threshold/spectrum and decoupling certificate supplies the physical
low-energy map. The moduli-locking hypothesis isolates the physical target point for that witness.
Those conditions are exactly the OPH-correctness gates for the named witness. Quotienting by
\(\Teq\) removes pure presentation duplicates of the same observer-visible data.
\end{proof}

\begin{corollary}[BD selection status]\label{cor:bd-selection-status}
The antecedent of the conditional witness theorem is false for the committed source packet. In
particular, no completed constraint system, dynamically stable point, physical readout, or
constraint-augmented Jacobian is supplied. The locking and isolation gate is obstructed by
Theorem~\ref{thm:bd-rank-obstruction}. Hence
\[
BD_{n=1,+}^{\OPH}
\quad\text{is not a selected or passing OPH-string witness.}
\]
The published BD zero-mode construction remains a structural audit benchmark. The OPH
recovered-core theorem stack is a separate claim tier.
\end{corollary}

\begin{proposition}[Catalogue-relative singleton certificate criterion]
Let \(\mathcal U\) be a declared candidate universe and let \(\mathcal C\) be an explicitly
enumerated catalogue. Assume a coverage certificate proves that every element of \(\mathcal U\)
is represented by a row of \(\mathcal C\) up to \(\Teq\). Assume also that every discrete branch
and every physical parameter domain has a certified cover with no unresolved cells, and that the
candidate gates are recomputed for every resulting equivalence class. If the exact passing set is
the single class \(BD_{n=1,+}^{\OPH}\), then
\[
\boxed{
\{
\mathcal T\in\mathcal U:\mathcal T\text{ is OPH-correct}
\}/\Teq
=
\{BD_{n=1,+}^{\OPH}\}.
}
\]
Without the coverage certificate, the same calculation makes a claim only about the explicitly
enumerated catalogue. A minimality score does not remove a second physically passing class unless
that ordering is independently derived as part of the OPH target.
\end{proposition}

\begin{proof}
Coverage maps every candidate in \(\mathcal U\) to a certified catalogue row. The branch and
parameter covers classify every row as passing or failing, with no unclassified region. Quotienting
the exact passing set by the certified equivalence relation gives the stated singleton by
hypothesis. If catalogue coverage is absent, the same argument has no premise for candidates
outside \(\mathcal C\). A score cannot change membership in the passing set unless its ordering is
itself one of the independently fixed physical gates.
\end{proof}

\begin{remark}[How strong this is]
BD is not decoration here. OPH supplies an external observer-visible target, so a named branch can
be tested by a normal-form equation. The claim is falsifiable by construction: failure of the BD
cohomology, safety-layer realization, threshold/spectrum certificate, decoupling map, or transverse
moduli rank excludes the named string proposal while leaving the OPH recovered core intact. The
moduli certificate realizes that failure case. Global uniqueness is a separate
comparative-catalogue question, moot for this row because it does not pass the existence
gates.
\end{remark}

\section{Theorem Agenda}

The de Sitter observer literature has isolated a tight set of frontier puzzles. OPH's job is to
make them concrete. The de Sitter side of the agenda is:
\begin{center}
\small
\begin{tabular}{p{0.29\linewidth}p{0.61\linewidth}}
\toprule
\textbf{Pressure point} & \textbf{OPH theorem target} \\
\midrule
Physical observer in de Sitter & Finite observer theorem: a physical observer is a stable
record-bearing patch subfederation. \\
Complex semiclassical correlators & Clock-projection correlator theorem: imaginary phases appear
after record-sector clock projection. \\
Time-reversal holonomy & \(\Z_2^T\) holonomy theorem: clock flips are cycle obstructions,
equivalently \(w_1(L_T)\) classes. \\
Time-reversal breaking & Record-branch theorem: ordered checkpoint records select a local time
orientation. \\
Entropy location & Edge-capacity theorem: \(S_{\rm dS}=A/(4\ell_P^2)\) is finite edge-center
record capacity. \\
Finite de Sitter degrees & Static-patch matrix-carrier theorem: finite patch and interface
algebras supply pre-geometric matrix degrees. \\
DSSYK/QCD/string parallels & Edge-sum universality theorem: heat-kernel edge sums reorganize as
large-\(N\) worldsheet expansions. \\
Critical worldsheet closure & Heterotic edge-polarization gate: the sewn-edge scaling limit must
realize \((\mathrm{Heis}_8\otimes V_{\Gamma_{16}})_L\otimes
(\mathrm{Heis}_8\otimes\mathrm{Ferm}_8)_R\), with no residual coset. \\
\bottomrule
\end{tabular}
\end{center}

The string/vacuum side of the agenda is:
\begin{center}
\small
\begin{tabular}{p{0.29\linewidth}p{0.61\linewidth}}
\toprule
\textbf{Pressure point} & \textbf{OPH theorem target} \\
\midrule
String landscape & OPH vacuum sieve theorem: critical completions must hit the observer-visible
normal form. \\
Worldsheet criticality & OPH edge-polarization theorem: the sewn-edge scaling limit must be
identified with the heterotic edge VOA, including OPEs, grading, spin structures, and no residual
coset. \\
Global Standard Model group & Global group locking theorem:
\(S(\U(3)\times\U(2))\cong(\SU(3)\times\SU(2)\times\U(1))/\Z_6\). \\
Connected unified-gauge adjoint & The product-group adjoint
contains no mixed \((3,2,\pm5/6)\) generator; connection dynamics and particle spectra remain separate gates. \\
Moduli stabilization & OPH moduli-locking criterion:
\(\calF(m_\star)=\calO_{\OPH}\) with full transverse rank. \\
\bottomrule
\end{tabular}
\end{center}

\section{De Sitter Observer Pressure Points}

Two de Sitter papers make the observer problem unusually explicit. One note relates the need
for observers in de Sitter space to spontaneous breaking of time reversal \cite{DSObservers2025}.
A follow-up states that quantum de Sitter theory is widely thought to require a physical observer
in the static patch, with the definition of observer unspecified \cite{DSMoreObservers2026}. The
time-reversal question is sharpened by treating time reversal as a gauge symmetry hidden by
spontaneous symmetry breaking, with a proposed ``smoking gun'' given by a closed curve whose
holonomy flips forward-going clocks into backward clocks \cite{DSTimeReversal2026}.

OPH reads these as implementation questions. What finite object counts as an observer? What
operation selects the clock branch? What finite obstruction carries the clock flip? What entropy
surface supplies the static-patch degrees of freedom?

\subsection{Observer}

\begin{definition}[OPH observer subfederation]
Let
\[
\mathfrak F=(V,E,\{\calA_i\},\{\calI_e\},\{\pi_{i,e}\},\{\calR_i\},\{\calU_i\})
\]
be a finite OPH patch carrier. An observer subfederation is a finite
\(U\subset V\) equipped with an accessible algebra \(\calA_U\), a state \(\rho_U\), a record
algebra \(\calR_U\), a boundary interface \(\calI_{\partial U}\), and accepted repair maps whose
normal form preserves a checkpoint order on \(\calR_U\).
\end{definition}

The observer projection is the record event
\[
P_{\rm obs}=P_{\calR_U,+},
\]
where \(+\) denotes the chosen clock orientation. Conditioning is ordinary projection:
\[
\rho|_{\calR_U,+}
=
\frac{P_{\calR_U,+}\rho P_{\calR_U,+}}{\Tr(P_{\calR_U,+}\rho)}.
\]

\begin{theorem}[Finite observer theorem]
On a finite OPH static-patch carrier, a physical observer is a subfederation \(U\subset V\) whose
checkpoint
\[
\mathrm{Chk}_U(t)=
\bigl(\calR_U(t),\rho_U^{\rm acc}(t),\mathfrak I_U^{\rm ext}(t),
\nu_{\ge t},\mathfrak B_U(t)\bigr)
\]
has a stable continuation law on the observer-accessible event algebra under same-interface
continuation. The de Sitter observer projection is the record-sector projection
\(P_{\calR_U,+}\).
\end{theorem}

\begin{proof}
The data defining \(U\) are finite algebraic data. The event that records persist with a
monotone checkpoint ordering is a projection in the record algebra after passing to the
observable quotient. Conditioning by that projection gives the usual post-selected state on the
observer-accessible sector. The observer is represented inside the patch Hilbert space.
\end{proof}

\subsection{Semiclassical De Sitter}

OPH treats semiclassical spacetime as an observer-facing quotient normal form. The repair
functional has the schematic form
\[
\Phi(s)=\sum_{e=\{i,j\}} w_e\,
d_e\!\left(\pi_{i,e}(s_i),\pi_{j,e}(s_j)\right).
\]
Accepted repairs lower \(\Phi\). Under the local-diamond and repair-completeness hypotheses used
in the consensus paper, the terminal observable state is schedule-independent on the physical
quotient.

\begin{claim}[Semiclassical patch]
The semiclassical de Sitter patch is the stable quotient normal form of finite
observer-overlap repair, read on a record-bearing clock sector.
\end{claim}

OPH answers the de Sitter observer question here. The maximally mixed
static-patch state belongs to the unconditioned algebra. The semiclassical branch is read after
record conditioning.

\subsection{Clock-conditioned correlator}

The finite toy model used in the correspondence package has two clock orientations exchanged by
time reversal. The two-level model is only a witness. The algebraic point is that the maximally
mixed static-patch trace averages over clock orientations, and an observer record projection selects
one oriented branch.

\begin{theorem}[Clock-projection correlator theorem]
Let \(\mathcal H\) be finite-dimensional, let \(H=H^\dagger\), let \(A=A^\dagger\), and set
\[
A(t)=e^{iHt}Ae^{-iHt},\qquad \rho_\infty=I/d.
\]
Then
\[
C_\infty(t):=\Tr(\rho_\infty A(t)A)
\]
is real, so
\[
\im C_\infty(t)=0.
\]
Equivalently,
\[
\Tr(\rho_\infty[A(t),A])=0.
\]
For a noncentral observer-clock record projector \(P_E\),
\[
\rho_E=\frac{P_E\rho_\infty P_E}{\Tr(P_E\rho_\infty)},
\]
the commutator expectation is generically nonzero. In the two-state clock example
\[
H=\frac{\omega}{2}\sigma_z,\qquad A=\sigma_x,
\]
one has
\[
C_\infty(t)=\frac12\Tr(\sigma_x(t)\sigma_x)=\cos(\omega t).
\]
On the forward clock record state \(\rho_+=|0\rangle\langle0|\),
\[
C_+(t)=\langle0|\sigma_x(t)\sigma_x|0\rangle=e^{i\omega t}.
\]
The imaginary semiclassical phase is restored by clock-record conditioning:
\[
\im C_\infty(t)=0,\qquad \im C_+(t)=\sin(\omega t).
\]
\end{theorem}

\begin{proof}
Since \(A(t)\) and \(A\) are Hermitian,
\[
C_\infty(t)^*=\frac1d\Tr(A A(t)).
\]
By cyclicity of the trace,
\[
\Tr(A A(t))=\Tr(A(t)A),
\]
so \(C_\infty(t)^*=C_\infty(t)\), hence \(C_\infty(t)\in\mathbb R\). The commutator statement
follows from \(\Tr([A(t),A])=0\).

For a projected state \(\rho_E\), the projector sits between the state and the clock-transition
operator. The cyclic cancellation above applies only in the commuting case. Generic observer-clock
records are noncentral, so the antisymmetric part can survive. For the two-state witness,
\[
\sigma_x(t)=e^{i\omega t\sigma_z/2}\sigma_xe^{-i\omega t\sigma_z/2}
=\cos(\omega t)\sigma_x-\sin(\omega t)\sigma_y.
\]
Then
\[
\sigma_x(t)\sigma_x=\cos(\omega t)I+i\sin(\omega t)\sigma_z.
\]
The maximally mixed trace gives \(\cos(\omega t)\). The \(|0\rangle\) matrix element gives
\(\cos(\omega t)+i\sin(\omega t)=e^{i\omega t}\).
\end{proof}

\subsection{Time-reversal holonomy}

The time-orientation data must be a local system. Globally chosen patch signs give only a
coboundary, and every closed-cycle product then telescopes to \(+1\). Clock-flip holonomy needs a
\(\Z_2^T\)-valued \v{C}ech 1-cocycle on the overlap nerve \(N(\mathfrak F)\):
\[
g_{ij}\in \Z_2^T,\qquad g_{ij}g_{jk}g_{ki}=1
\]
on triple overlaps, modulo local redefinitions
\[
g_{ij}\sim \lambda_i g_{ij}\lambda_j^{-1},\qquad \lambda_i\in\Z_2^T.
\]
For a closed path \(\gamma=(i_0i_1)(i_1i_2)\cdots(i_{n-1}i_0)\), define
\[
h_T(\gamma)=\prod_{a=0}^{n-1}g_{i_a i_{a+1}}\in\Z_2^T.
\]

\begin{theorem}[Time-reversal holonomy theorem]
A forward-going local clock transported around \(\gamma\) returns backward-going iff
\[
h_T(\gamma)=-1.
\]
The obstruction to a global time-orientation section is the cohomology class
\[
[g]\in H^1(N(\mathfrak F),\Z_2)\cong \check H^1(N(\mathfrak F),\Z_2),
\]
equivalently the first Stiefel-Whitney class
\[
w_1(L_T)=[g].
\]
It vanishes iff the transition cocycle is a coboundary, i.e. iff one can choose local orientations
\(\epsilon_i\) with \(g_{ij}=\epsilon_i^{-1}\epsilon_j\) on every overlap.
\end{theorem}

\begin{proof}
Parallel transport across the overlap \((ij)\) multiplies the clock-orientation basis by \(g_{ij}\).
Transport around \(\gamma\) multiplies by the ordered product \(h_T(\gamma)\). Since the group is
\(\Z_2\), the value \(+1\) preserves orientation and the value \(-1\) reverses it.

A global time orientation is a choice of signs \(\epsilon_i\in\Z_2\) such that the transition from
patch \(i\) to patch \(j\) is reproduced by \(g_{ij}=\epsilon_i^{-1}\epsilon_j\). This is the
statement that the 1-cocycle \(g\) is a coboundary. The obstruction class is
\([g]\in H^1(N(\mathfrak F),\Z_2)\), which is the first Stiefel-Whitney class of the associated
\(\Z_2\) time-orientation line bundle \(L_T\). A nonzero class means no global time-orientation
section exists.
\end{proof}

The proposed de Sitter clock-flip test reads, in finite OPH form, as a \(\Z_2^T\) cycle obstruction
on the patch-overlap nerve.

\subsection{Record-branch time-reversal breaking}

Let \(P_1,P_2,\ldots,P_n\in\calR_U\) be mutually commuting checkpoint record projectors over a
finite observation window, with a monotone checkpoint order
\[
P_1\prec P_2\prec\cdots\prec P_n.
\]
Time reversal sends this ordered history to the reversed history. Conditioning on the finite branch
projector
\[
P_{\rm branch}=P_1P_2\cdots P_n
\]
selects one local time orientation on the observer-accessible quotient.

\begin{theorem}[Record-branch time-reversal breaking]
The unconditioned finite carrier carries the time-reversal-related pair of record orders. A
stable checkpoint branch selects one order by
\[
\rho\mapsto
\frac{P_{\rm branch}\rho P_{\rm branch}}{\Tr(P_{\rm branch}\rho)}.
\]
Time reversal is a redundancy of the unconditioned carrier and is hidden on the conditioned
observer quotient by finite record ordering.
\end{theorem}

\begin{proof}
Because the checkpoint records belong to the observer-accessible record algebra, they are central
or mutually commuting on the exact fixed-cutoff event surface used here. The finite product
\(P_{\rm branch}=P_1\cdots P_n\) is again a projector onto the event that the ordered record history
occurs. The time-reversed branch is represented by the same unordered product together with the
opposite continuation schedule. The unconditioned carrier contains both orientation-related
continuations. Conditioning by \(P_{\rm branch}\) and the continuation schedule selects one law on
the observer-accessible quotient. On that quotient the reversed branch is outside the conditioned
continuation law, so the time-reversal redundancy is hidden by record ordering.
\end{proof}

\section{Entropy, Matrix Degrees, and Scale Separation}

DSSYK/JT-de Sitter work places the stretched-horizon entropy at order Planck distance
from the mathematical horizon \cite{DSEntropy2025}. OPH agrees with that direction. The entropy
budget is finite edge-center and record capacity:
\[
S_{\rm dS}=N_{\rm scr}=\frac{A_{\rm dS}}{4\ell_P^2}.
\]
The string scale is downstream in this paper. The edge record capacity is the substrate; the
worldsheet is the effective language after sewing and large-edge organization.

\begin{theorem}[Edge-capacity entropy theorem]
On the OPH de Sitter static-patch branch, the horizon entropy is the capacity of the
observer-facing edge-center record surface:
\[
S_{\rm dS}=N_{\rm scr}=\frac{A_{\rm dS}}{4\ell_P^2}.
\]
The corresponding screen-capacity branch gives
\[
\Lambda=\frac{3\pi}{G N_{\rm scr}}.
\]
\end{theorem}

\begin{proof}
The OPH screen-capacity branch identifies the number of observer-facing horizon record units with
the Gibbons-Hawking entropy,
\[
N_{\rm scr}=\frac{A_{\rm dS}}{4\ell_P^2}.
\]
For a four-dimensional de Sitter static patch,
\[
A_{\rm dS}=4\pi R_{\rm dS}^2,
\qquad
\Lambda=\frac{3}{R_{\rm dS}^2}.
\]
This gives
\[
N_{\rm scr}=\frac{4\pi R_{\rm dS}^2}{4\ell_P^2}
=\frac{\pi R_{\rm dS}^2}{\ell_P^2}.
\]
Using \(\ell_P^2=G\) in units \(\hbar=c=1\),
\[
N_{\rm scr}=\frac{3\pi}{G\Lambda},
\]
and
\[
\Lambda=\frac{3\pi}{G N_{\rm scr}}.
\]
\end{proof}

The finite carrier
\[
\mathfrak F=(V,E,\{\calA_i\},\{\calI_e\},\{\pi_{i,e}\},\{\calR_i\},\{\calU_i\})
\]
also supplies a matrix-style pre-geometric object. This matches the pressure behind de
Sitter-matrix arguments, where black holes and nonperturbative sectors probe the static-patch
degrees of freedom \cite{DSMatrix2021}. In OPH, black-hole sectors are constrained normal
forms that reallocate screen capacity:
\[
P(\text{sector})\propto
\exp[-(S_{\rm dS}-S_{\rm sector})].
\]

\begin{theorem}[Static-patch matrix carrier theorem]
The finite algebras \(\calA_i\) and interface algebras \(\calI_e\) of an OPH de Sitter
static-patch carrier are the microscopic matrix degrees used by the pre-geometric description.
A black-hole sector is a constrained normal-form sector \(\mathfrak S_{\rm BH}\) with
\[
S(\mathfrak S_{\rm BH})<S_{\rm dS}
\]
and fluctuation weight proportional to
\[
\exp[-(S_{\rm dS}-S(\mathfrak S_{\rm BH}))].
\]
\end{theorem}

\begin{proof}
At fixed cutoff each local patch algebra and interface algebra is finite-dimensional, hence a finite
direct sum of matrix algebras. The unreduced tensor product of a finite static-patch carrier is a
finite matrix algebra up to superselection-block decomposition, and the physical algebra is its
overlap-invariant quotient. A constrained black-hole sector imposes additional horizon, energy, or
area constraints on the same finite record surface, so its accessible record count is smaller than
the empty de Sitter static-patch count. With the same coarse-grained entropy measure in both
macroscopic sectors, the relative weight of the constrained sector is the ratio of state counts,
\[
\frac{e^{S(\mathfrak S_{\rm BH})}}{e^{S_{\rm dS}}}
=\exp[-(S_{\rm dS}-S(\mathfrak S_{\rm BH}))].
\]
\end{proof}

Scale-separation work on de Sitter and double-scaled SYK distinguishes a cosmic sector from a
microscopic sector \cite{DSScales2022}. OPH has the same split:
\[
\text{cosmic sector}\leftrightarrow N_{\rm scr},
\qquad
\text{microscopic sector}\leftrightarrow P,\text{ edge labels, finite records}.
\]
The clean dimensionless separator is \(N_{\rm scr}/P\).

\section{Edge-String Emergence}

The OPH string continuation begins at the edge-sector partition. At fixed cutoff, edge labels are
compact representations \(R\) with dimension \(d_R\) and quadratic Casimir \(C_2(R)\). The
open-edge weight is
\[
p_R(t)=\frac{d_R e^{-t C_2(R)}}{Z_{\rm open}(t)}.
\]
Sewing two collar sides contributes a second representation-dimension factor:
\[
Z_{\rm edge}(t)=\sum_R d_R^2 e^{-tC_2(R)}.
\]
By Peter-Weyl,
\[
K_t(g)=\sum_R d_R\chi_R(g)e^{-tC_2(R)}.
\]
At \(g=1\), \(\chi_R(1)=d_R\), hence
\[
Z_{\rm edge}(t)=K_t(1).
\]

\begin{theorem}[OPH edge-string read-off]
The sewn OPH collar partition equals the compact-group heat kernel at the identity:
\[
Z_{\rm edge}(t)=K_t(1).
\]
On a large-\(N_{\rm edge}\) branch with \(g_s=1/N_{\rm edge}\), the controlled surface expansion
has the closed-string genus form.
\end{theorem}

\begin{proof}
The compact heat kernel has Peter-Weyl expansion
\[
K_t(g)=\sum_R d_R\chi_R(g)e^{-tC_2(R)}.
\]
At the identity, \(\chi_R(1)=d_R\), so
\[
K_t(1)=\sum_R d_R^2e^{-tC_2(R)}.
\]
A closed OPH collar is obtained by sewing two open edge boundaries, and the second boundary
contributes the second dimension factor. The sewn collar partition is
\[
Z_{\rm edge}(t)=\sum_R d_R^2e^{-tC_2(R)}=K_t(1).
\]
If a distinct large-edge branch has the controlled expansion
\[
\log Z=\sum_g N_{\rm edge}^{2-2g}F_g
\]
with uniform remainder bounds, then \(g_s=N_{\rm edge}^{-1}\) rewrites the coefficient as
\[
N_{\rm edge}^{2-2g}=g_s^{2g-2},
\]
the standard closed-string genus weight.
\end{proof}

\begin{theorem}[Edge-sum universality theorem]
On the controlled large-\(N_{\rm edge}\) branch,
\[
\log Z_{\rm edge}
=
\sum_g N_{\rm edge}^{2-2g}F_g,
\qquad
g_s=\frac1{N_{\rm edge}}.
\]
The same representation sum gives the two-dimensional Yang-Mills heat-kernel basis and the
worldsheet string basis.
\end{theorem}

\begin{proof}
The representation sum is the heat-kernel form of two-dimensional Yang-Mills. Its sewing law is the
Chapman-Kolmogorov law for heat kernels, which is also the OPH collar-sewing law. The
large-\(N_{\rm edge}\) expansion reorganizes the same sewn surfaces by Euler characteristic:
\[
N_{\rm edge}^{2-2g}=g_s^{2g-2}.
\]
The same edge representation sum has a 2D Yang-Mills heat-kernel reading and a perturbative
closed-string worldsheet reading, provided the large-edge remainder bounds hold.
\end{proof}

This theorem is the bridge to the string community. It also explains why DSSYK, large-\(N\) QCD,
and open-string structures keep meeting in the de Sitter flat-space limit. A 2025 DSSYK/QCD paper
states that double-scaled SYK at infinite temperature and large-\(N\) QCD have large-\(N\)
expansions of the same form, and that DSSYK provides a tractable window into the fixed-coupling
flat-space limit \cite{DSSYKQCDPaper}. A companion DSSYK flat-space paper connects the limit to
strongly coupled \((1+1)\)-dimensional QCD and open-string Regge behavior \cite{DSSYKFlatPaper}.
OPH reads this family of coincidences as different bases for sewn edge-sector sums.


\section{What an OPH String Is}\label{sec:oph-string-object}

The heat-kernel identity gives the partition-function trace of a string. The object-level
dictionary is finite. In OPH, a string is a stable one-dimensional edge-cycle normal form in the
overlap carrier. A continuum string is the scaling description of that cycle after collar sewing
and large-edge coarse graining.

\begin{definition}[Fixed-cutoff OPH pre-string]
Let
\[
\mathfrak F=(V,E,\{\calA_i\},\{\calI_e\},\{\pi_{i,e}\},\{\calR_i\},\{\calU_i\})
\]
be a fixed OPH patch carrier. A fixed-cutoff pre-string is a cyclic collar word
\[
\Gamma=(e_1,e_2,\ldots,e_n;e_{n+1}=e_1)
\]
in the overlap nerve, together with edge labels and vertex intertwiners
\[
\mathcal S_0(\Gamma)=
\left(\Gamma,\{R_{e_a}\}_{a=1}^n,\{I_{v_a}\}_{a=1}^n,\{r_{e_a}\}_{a=1}^n\right),
\]
where each \(R_e\) is a compact-gauge representation label carried by the edge-center algebra,
each
\[
I_v\in\operatorname{Hom}_G(R_{e_{a-1}}\otimes R_{e_a},\mathbf 1\oplus\cdots)
\]
is the local fusion/sewing datum at a patch junction, and \(r_e\) is the record state exposed on
the collar.
\end{definition}

\begin{definition}[OPH string]
An OPH string is the quotient-normal-form class
\[
\mathcal S=[\mathcal S_0(\Gamma)]_{\mathrm{nf}}/
\bigl(\text{local repair},\text{collar refinement},\text{OPH-invisible relabeling}\bigr).
\]
A closed string is a cyclic class with no external endpoint. An open string is an interval-class
whose endpoints lie on declared observer branes, defect collars, or boundary record sectors. A
multi-string state is a finite disjoint union of such classes, modulo the same repair quotient.
\end{definition}

The cycle is visible through representation data and records on overlaps. Its support is
one-dimensional in the overlap nerve. Its physical role comes from survival under local repair
and refinement.

\subsection{One string, many strings, and worldsheets}

A single OPH string at one checkpoint is
\[
\mathcal S(\tau_0)=[\Gamma(\tau_0),R(\tau_0),I(\tau_0),r(\tau_0)]_{\mathrm{nf}}.
\]
A history of the same object through accepted repairs is a sequence
\[
\mathcal S(\tau_0)\to \mathcal S(\tau_1)\to\cdots\to\mathcal S(\tau_m).
\]
The two-dimensional worldsheet is the swept collar complex
\[
\Sigma_{\mathcal S}:=\bigcup_{j=0}^{m-1}\Gamma(\tau_j)\times[\tau_j,\tau_{j+1}],
\]
with sewing at repair events. Pair-of-pants splitting and joining are OPH cobordisms in which one
cyclic normal form changes into two, or two change into one, preserving exposed overlap
constraints.

The dictionary is:
\[
\begin{array}{ccl}
\text{OPH cyclic edge normal form} &\longleftrightarrow& \text{string at one time},\\
\text{accepted repair history of the cycle} &\longleftrightarrow& \text{worldsheet},\\
\text{cycle split/merge cobordism} &\longleftrightarrow& \text{string interaction},\\
\text{finite edge capacity} &\longleftrightarrow& g_s^{-1}\text{ on the controlled large-edge branch}.
\end{array}
\]

\subsection{Why the string vibrates}

The string vibrates because the cyclic edge normal form has internal normal modes. Linearize the
repair law around a stable cyclic solution \(\mathcal S_\star\). If \(\xi_a\) denotes a small
edge-position or edge-label perturbation at the \(a\)-th collar site, the quadratic mismatch is
\[
\Phi(\mathcal S_\star+\xi)=\Phi(\mathcal S_\star)
+\frac12\sum_{a,b}\xi_a K_{ab}\xi_b+O(\xi^3).
\]
On a long uniform cycle, the Hessian \(K\) is a graph Laplacian plus local mass/curvature terms.
The normal modes are Fourier modes
\[
\xi_a^\mu(\tau)=\sum_{n\in\mathbb Z}\xi_n^\mu(\tau)e^{2\pi i n a/N}.
\]
In the continuum edge limit, with \(a/N\to\sigma/(2\pi)\), this becomes the closed-string field
\[
X^\mu(\sigma,\tau)=x_0^\mu+p^\mu\tau+
 i\sqrt{\frac{\alpha'_{\OPH}}{2}}
\sum_{n\ne0}\frac1n
\left(\alpha_n^\mu e^{-in(\tau-\sigma)}+\tilde\alpha_n^\mu e^{-in(\tau+\sigma)}\right).
\]
The left/right split is the two-sided collar split. One side of the sewn edge supplies the left
movers and the other supplies the right movers. Quantization of the finite symplectic record/edge
normal modes gives the oscillator algebra in the scaling limit,
\[
[\alpha_m^\mu,\alpha_n^\nu]=m\delta_{m+n,0}\eta^{\mu\nu},
\qquad
[\tilde\alpha_m^\mu,\tilde\alpha_n^\nu]=m\delta_{m+n,0}\eta^{\mu\nu}.
\]
At this stage the range of \(\mu\) is not fixed by the heat-kernel theorem or by the oscillator
form alone. The critical dimension and the heterotic internal central charge require the
critical-edge certificate in Section~\ref{sec:central-charge-gate}.
The parameter \(\alpha'_{\OPH}\) is the continuum normalization of the edge diffusion/repair time.
Its identification with a physical string tension is conditional on matching the four-dimensional
Newton constant, the OPH pixel scale, and a certified compactification threshold.

\begin{theorem}[String emergence theorem]
Assume a fixed-cutoff compact edge branch, collar sewing, a separated refinement system, and a
controlled large-\(N_{\rm edge}\) limit in which cyclic normal forms have a continuum embedding
\(X:\Sigma\to M_{\OPH}\). Then the OPH edge-cycle normal-form category maps to a perturbative
string worldsheet category. The map sends cyclic edge normal forms to string states, accepted
repair histories to worldsheets, and edge-cycle split/merge cobordisms to string interactions.
\end{theorem}

\begin{proof}
At fixed cutoff, the object is finite: a cyclic word of edge collars with compact representation
labels and intertwiners. Sewing gives the heat-kernel partition described above. Refinement turns
long cyclic words into one-dimensional continua. A time-ordered repair history sweeps a
cellulated two-complex. The large-edge expansion supplies the genus weighting. The normal-mode
expansion of the repaired cycle gives the oscillator degrees of freedom. These are precisely the
data used by a perturbative worldsheet description.
\end{proof}

\begin{remark}[Claim boundary]
The exact fixed-cutoff theorem is the edge heat-kernel/sewing theorem. The continuum string,
oscillator algebra, and genus expansion require the large-edge/refinement hypotheses. OPH begins
with finite edge data; string theory is the controlled language of its sewn-edge scaling branch.
\end{remark}

\section{Critical Central-Charge Gate}\label{sec:central-charge-gate}

The OPH screen and particle papers supply the relevant integer targets for a heterotic branch
\cite{OPHScreenMicrophysics,OPHParticleZoo}. Those integers become central charges only after the
gate below. The screen-microphysics construction gives twelve primitive
curvature/record ports,
\[
n_{\rm port}=12,
\]
and the reversible write/verify register gives the oriented count
\[
m_{\rm rep}
=2\dim\bigl(\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak u(1)\bigr)
=2(8+3+1)=24.
\]
These are finite-register counts. A worldsheet central charge counts gapless conformal degrees of
freedom, weighted by field type. For example, twenty-four chiral bosons have \(c=24\), but
twenty-four chiral Majorana fermions have \(c=12\), and massive fields do not contribute to the
infrared central charge \cite{PolchinskiStringVol1,DiFrancescoCFT}.

The heat-kernel identity also cannot determine \(c_L\) and \(c_R\) by itself. One can tensor the
sewn edge sector with a spectator CFT without changing
\[
Z_{\rm edge}(t)=\sum_R d_R^2e^{-tC_2(R)}=K_t(1),
\]
while shifting the total central charge. Therefore port counting and the heat-kernel trace feed a
criticality test. Criticality requires the finite-carrier critical-edge certificate below.

\begin{theorem}[Boundary from OPH edge data]
The OPH edge statements used here do not imply
\[
\operatorname{rank}k_L=24,\qquad
\operatorname{rank}k_R=12,\qquad
T_{\OPH}=T_{\rm Sug},\qquad
G^2\sim T_R.
\]
Indeed the rank equations are not invariantly meaningful until a continuum current algebra and its
level matrices \(k_L,k_R\) have been specified.
\end{theorem}

\begin{proof}
There are four independent obstructions.

First, the twelve curvature ports are not themselves twelve independent currents. If one defines
defect fluctuations \(q_a\), \(a=1,\ldots,12\), from the unit curvature defects, their total charge
is fixed:
\[
\sum_{a=1}^{12}q_a=12.
\]
For currents \(J_a=\partial q_a\), this gives
\[
\sum_{a=1}^{12}J_a=0,
\qquad
\sum_a k_{ab}=0,
\]
so the all-ones vector lies in the kernel of the current two-point matrix and
\[
\operatorname{rank}k\le 11.
\]
On the exact unit-defect normal form, \(q_a=1\) for every port, these curvature currents vanish.
Thus the curvature-defect variables cannot be the required twelve independent chiral fields; any
such fields must be new dynamical variables living at the ports.

Second, orientation labels do not by themselves double the rank. If verification is the reverse of
writing, \(J_{a,-}=-J_{a,+}\), and the unoriented covariance is \(K\), then
\[
K_{\rm orient}=
\begin{pmatrix}
K&-K\\
-K&K
\end{pmatrix}
\sim
\begin{pmatrix}
0&0\\
0&2K
\end{pmatrix}.
\]
Hence
\[
\operatorname{rank}K_{\rm orient}=\operatorname{rank}K,
\]
not twice that rank. Doubling would require an independent covariance block
\[
K_{\rm independent}=
\begin{pmatrix}
K&0\\
0&K
\end{pmatrix}.
\]
Both covariance structures are compatible with two operation labels. OPH counts write/verify
operations; independent-field covariance is a separate certificate.

Third, twelve Standard Model generators are not automatically central charge \(12\). For a
nonabelian affine algebra \(\widehat{\mathfrak g}_k\), the Sugawara central charge is
\[
c(\mathfrak g_k)=\frac{k\,\dim\mathfrak g}{k+h^\vee}
\]
\cite{DiFrancescoCFT}. Interpreting the Standard Model algebra as level-one affine currents gives
\[
\mathfrak g_{\rm SM}
=
\mathfrak{su}(3)_1\oplus\mathfrak{su}(2)_1\oplus\mathfrak u(1),
\]
and hence
\[
c=\frac{8}{1+3}+\frac{3}{1+2}+1=2+1+1=4,
\]
not \(12\). Two independent copies would give \(c=8\), not \(24\). To obtain \(c=12\) or \(c=24\),
the edge slots must be proved equivalent to independent Heisenberg/free-boson currents, or to
another CFT with those central charges.

Fourth, a current algebra can be a proper subsector of a larger CFT:
\[
T_{\OPH}=T_{\rm Sug}+T_{\rm coset},
\qquad
c_{\OPH}=c_{\rm Sug}+c_{\rm coset}.
\]
The equality \(T_{\OPH}=T_{\rm Sug}\) requires \(T_{\rm coset}=0\). Neither the twelve-port theorem
nor \(Z_{\rm edge}=K_t(1)\) proves this. Likewise, a worldsheet supercurrent must be a local,
fermion-odd field of conformal weight \(3/2\) satisfying the super-Virasoro OPE. A square root of a
discrete repair operation is not enough; one needs a \(\Z_2\) grading, fermionic locality, spin
structures, and the supercurrent OPE.
\end{proof}

The precise claim is conditional: a heterotic edge-CFT completion would make the ranks,
stress-tensor equality, supercurrent, and critical dimension follow rigidly.

\begin{definition}[Critical-edge finite-carrier receipts]
Let \(V_{\rm port}\) be the real vector space of dynamical port-amplitude perturbations, distinct
from the fixed curvature charges \(q_a=1\), and let
\[
\mathfrak g_{\rm SM}=
\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak u(1),
\qquad
\dim\mathfrak g_{\rm SM}=12.
\]
The finite-carrier critical-edge certificate consists of five receipts.
\begin{enumerate}[leftmargin=2em]
\item A visible-response map
\[
\calR_{\rm port}:\mathfrak g_{\rm SM}\to V_{\rm port}
\]
with
\[
\operatorname{rank}\calR_{\rm port}=12.
\]
\item Positive covariance levels in every icosahedral and oriented sector:
\[
\kappa_{\mathbf1},\kappa_{\mathbf3},\kappa_{\mathbf3'},\kappa_{\mathbf5}>0,
\qquad
\kappa_{\rho,\pm}>0
\]
for \(\rho\in\{\mathbf1,\mathbf3,\mathbf3',\mathbf5\}\).
\item Scaled additive edge records whose continuum OPE is abelian Heisenberg:
\[
J_A(z)J_B(w)\sim\frac{k_{AB}}{(z-w)^2}.
\]
\item A local graded right-moving half-repair operator \(Q_N\) such that
\[
\{Q_N,(-1)^F\}=0,
\qquad
Q_N^2-H_{R,N}\to0
\]
in the refinement limit.
\item A torus and spin-structure receipt
\[
Z_{\OPH}(\tau,\bar\tau)=q^{-1}\bar q^{-1/2}(1+\cdots)
\]
with the modular transformations of the heterotic spin-structure sum.
\end{enumerate}
\end{definition}

\subsection{Operational finite-carrier receipt protocol}

The finite-carrier certificate is an executable protocol, not a synonym for a single
twelve-port cavity. A single Echosahedron is a recurrent zero-spatial-dimensional patch: it evolves
and self-reads, but the spatial edge coordinate needed for a
\((1+1)\)-dimensional scaling theory is absent. Central charge, current modes, and Virasoro closure
require a sewn edge cylinder
\[
\text{edge cylinder}(L),
\qquad
\mathcal H_L=\bigotimes_{x=0}^{L-1}\mathcal H_{\mathrm{cell},x},
\qquad x\equiv x+L.
\]
The local update on this cylinder must be inherited from the OPH read--compare--repair--commit
cycle, not chosen to reproduce a desired CFT. Its exported object is a transfer operator
\[
T_L=e^{-aH_L},
\]
or, for a stochastic carrier, a Markov/Koopman transfer operator with a reflected-positive
Euclidean interpretation.

The operational receipt suite is:
\begin{enumerate}[leftmargin=2em,label=\textbf{FC-\arabic*.}]
\item \textbf{Carrier and refinement manifest.} Export model hashes, local factor dimensions,
update/repair gates, transfer callbacks, \(A_5\) action, orientation involution, translation
operator, record/port operators, refinement maps, precision model, and either a positive
self-adjoint transfer matrix or reflected-positive Gram matrices.
\item \textbf{Twelve-port dynamical rank.} Perturb the twelve ports around settled states, measure
the full response matrix, decompose the \(A_5\) representation
\(\mathbb R^{12}\cong\mathbf1\oplus\mathbf3\oplus\mathbf3'\oplus\mathbf5\), and require all
irreducible response coefficients to remain nonzero under refinement.
\item \textbf{Orientation independence.} Form
\(V_{\rm port}\otimes\mathbb R[C_2]\), project to the \(A_5\times C_2\) sectors, and verify that
both orientation parities survive dynamically. This is the immediate falsifier for mere
write/verify duplication.
\item \textbf{Conserved currents.} Discover local densities and currents satisfying the discrete
continuity equation on the edge cylinder, then measure chiral level matrices whose stable ranks
approach
\[
\operatorname{rank}k_L=24,\qquad \operatorname{rank}k_R=12.
\]
\item \textbf{Virasoro central charge.} Construct lattice stress-tensor modes and fit the
Virasoro residuals on low-energy projectors, with independent finite-size energy checks, targeting
\[
c_L\to24,\qquad c_R\to12.
\]
\item \textbf{Sugawara exhaustion.} Build the Sugawara stress tensor from the measured currents
and require \(T_{\OPH}-T_{\rm Sug}\to0\), equivalently no residual positive-central-charge coset.
\item \textbf{Supercurrent.} Exhibit a genuine right-moving graded sector and a local odd
supercurrent whose finite-carrier square-root receipt satisfies \(Q_N^2-H_{R,N}\to0\) on the
low-energy projector.
\item \textbf{Torus, spin structures, and internal lattice.} Export spin-structure partition
functions, verify their modular transformation law after the full GSO projection, and identify the
rank-sixteen even self-dual left-moving internal lattice. The Bouchard-Donagi witness belongs to
the \(E_8\oplus E_8\) heterotic branch.
\item \textbf{Blind refinement and falsification.} Pre-register several \((L,a)\) refinements,
report all failures, and run controls that collapse orientation, permute ports, break icosahedral
geometry, add spectators or masses, reverse chirality conventions, and disconnect seams.
\end{enumerate}

The \(E_8/\mathrm{Spin}(8)\) triality sidecar is useful only as a local algebraic witness for this
last internal-lattice lane. It gives exact finite matrix evidence that one \(E_8\) lattice can carry
triality-related vector and positive-half-spin \(2\!\cdot\!\mathrm{Alt}(9)\) presentations with
distinct mod-2 orbit fingerprints. It is not a rank-sixteen \(E_8\oplus E_8\) certificate, not a
spin-structure or supercurrent receipt, and not a replacement for the heterotic edge-polarization
gate above.

The existing twelve-port calibration model can test FC-0, FC-1, and the precursor part of FC-2. It cannot
by itself test \(\operatorname{rank}k_L=24\), \(\operatorname{rank}k_R=12\), \(T_{\OPH}=T_{\rm Sug}\),
the right-moving supercurrent, or \((c_L,c_R)=(24,12)\). Those require the edge-cylinder extension.
Without such receipts, the heterotic central-charge identification is not certified,
not a passed numerical result.

\begin{lemma}[Port-spectrum and icosahedral rank tests]
If every nonzero observer-visible repair generator changes some dynamical port record, then
\(\calR_{\rm port}\) is an isomorphism. If the twelve ports transform as the vertex permutation
representation of \(A_5\), then
\[
\mathbb R^{12}\cong\mathbf1\oplus\mathbf3\oplus\mathbf3'\oplus\mathbf5.
\]
For an \(A_5\)-invariant right-moving covariance matrix,
\[
k_R=\kappa_{\mathbf1}P_{\mathbf1}
+\kappa_{\mathbf3}P_{\mathbf3}
+\kappa_{\mathbf3'}P_{\mathbf3'}
+\kappa_{\mathbf5}P_{\mathbf5},
\]
and
\[
\operatorname{rank}k_R=12
\quad\Longleftrightarrow\quad
\kappa_{\mathbf1},\kappa_{\mathbf3},\kappa_{\mathbf3'},\kappa_{\mathbf5}>0.
\]
For the oriented space \(V_{\rm port}\otimes\mathbb R[C_2]\),
\[
\operatorname{rank}k_L=24
\quad\Longleftrightarrow\quad
\kappa_{\rho,\pm}>0
\quad\text{for all eight oriented sectors.}
\]
\end{lemma}

\begin{proof}
The response-map condition says \(\ker\calR_{\rm port}=0\). Since the domain and codomain both
have dimension \(12\), \(\calR_{\rm port}\) is invertible. The \(A_5\) permutation character on the
twelve icosahedral vertices is
\[
\chi_V=(12,0,0,2,2),
\]
which decomposes as
\[
\chi_{\mathbf1}+\chi_{\mathbf3}+\chi_{\mathbf3'}+\chi_{\mathbf5}
=(12,0,0,2,2).
\]
Schur's lemma then diagonalizes any \(A_5\)-invariant covariance by irreducible sector. Reflection
positivity makes nonzero sector coefficients positive. The oriented statement is the same argument
applied to the \(A_5\times C_2\) decomposition.
\end{proof}

\begin{lemma}[Observability and current emergence]
If the current covariance is positive semidefinite, all invisible directions have been quotiented
out, and every remaining nonzero port perturbation changes an observer-visible record statistic,
then the current covariance is positive definite. If additive port records satisfy
\[
Q_A(I_1\cup I_2)=Q_A(I_1)+Q_A(I_2)
\]
and are conserved under accepted repairs away from interval endpoints, then in a local unitary
scale-invariant sewn-edge limit they become chiral currents
\[
Q_A(I)=\int_I J_A(z)\,dz,
\qquad
\bar\partial J_A=0.
\]
If the fixed-cutoff integrated charges commute, their continuum current algebra is abelian:
\[
J_A(z)J_B(w)\sim\frac{k_{AB}}{(z-w)^2}.
\]
\end{lemma}

\begin{proof}
For a positive-semidefinite covariance, a nonzero vector \(v\) with \(v^Tkv=0\) defines a zero-norm
combination \(J_v=v^AJ_A\), hence an invisible fluctuation in the observer-facing algebra. The
quotient-observability hypotheses exclude such a vector. Additivity gives a local continuum
density, conservation gives a conserved two-dimensional current, and chirality gives a holomorphic
component of weight \((1,0)\). Commuting zero modes exclude a simple-pole affine term, leaving only
the central \((z-w)^{-2}\) singularity.
\end{proof}

\begin{theorem}[Critical-edge certificate theorem]
If the five finite-carrier receipts above hold, then the OPH sewn-edge scaling branch satisfies the
heterotic edge-polarization hypothesis below. Consequently the physical edge CFT has
\[
(c_L^{\rm phys},c_R^{\rm phys})=(24,12),
\]
a right-moving \(N=1\) supercurrent, no residual coset, and an even self-dual rank-sixteen
left-moving internal lattice.
\end{theorem}

\begin{proof}
The rank and observability receipts make the right-moving port covariance positive definite of
rank \(12\) and the oriented left-moving covariance positive definite of rank \(24\). The
current-emergence receipt turns the additive records into abelian Heisenberg currents. The abelian
Sugawara construction gives central charge equal to rank, hence \(c_R=12\) and \(c_L=24\) for the
generated sectors.

The torus vacuum exponent
\[
q^{-1}\bar q^{-1/2}=q^{-c_L/24}\bar q^{-c_R/24}
\]
fixes the total central charges to the same values. Therefore the residual stress tensor
\[
T_{\rm res}=T_{\OPH}-T_{\rm Sug}
\]
has \(c_{\rm res}=0\) in both chiralities. In a unitary positive-energy CFT with unique vacuum, a
\(c=0\) Virasoro sector is null after quotienting null states, so there is no residual coset.

The local graded half-repair operator supplies the refinement limit of a right-moving odd square
root of translation. Its density is the supercurrent \(G_R\), and the free \(N=1\) OPE gives
\[
G_R(\bar z)G_R(\bar w)
\sim
\frac{2c_R/3}{(\bar z-\bar w)^3}
+
\frac{2T_R(\bar w)}{\bar z-\bar w}.
\]
The modular spin-structure receipt then identifies the sixteen remaining left-moving units with an
even self-dual rank-sixteen lattice sector.
\end{proof}

\begin{assumption}[Heterotic edge-polarization hypothesis]\label{ass:heterotic-edge-polarization}
The physical sewn-edge scaling limit is isomorphic, as a graded chiral CFT, to
\[
\operatorname{ScaleLim}(\text{OPH sewn-edge carrier})
\cong
\left(\mathrm{Heis}_8\otimes V_{\Gamma_{16}}\right)_L
\otimes
\left(\mathrm{Heis}_8\otimes \mathrm{Ferm}_8\right)_R,
\]
with no residual coset or spectator CFT. Here \(\mathrm{Heis}_8\) is generated by eight transverse
free bosons, \(V_{\Gamma_{16}}\) is a rank-sixteen even self-dual lattice VOA on the left-moving
side, and \(\mathrm{Ferm}_8\) is generated by eight right-moving Majorana fermions with a
consistent spin-structure projection.
\end{assumption}

\begin{theorem}[Heterotic completion theorem]
Under Assumption~\ref{ass:heterotic-edge-polarization}, the physical chiral central charges are
\[
\boxed{c_L^{\rm phys}=24,\qquad c_R^{\rm phys}=12,}
\]
the relevant Heisenberg level matrices have ranks \(24\) and \(12\), the stress tensors are
Sugawara stress tensors for those Heisenberg currents, and the right-moving sector carries an
\(N=1\) supercurrent. The shared target spacetime dimension is then forced to be \(D=10\), with
left-moving internal central charge \(16\).
\end{theorem}

\begin{proof}
On the left, write
\[
\Phi_L^A=(X_L^1,\ldots,X_L^8,Y_L^1,\ldots,Y_L^{16}),
\qquad
A=1,\ldots,24,
\]
with
\[
\Phi_L^A(z)\Phi_L^B(w)\sim-\delta^{AB}\log(z-w).
\]
The currents \(J_L^A=i\partial\Phi_L^A\) obey
\[
J_L^A(z)J_L^B(w)\sim\frac{\delta^{AB}}{(z-w)^2},
\]
so \(k_L=I_{24}\) and \(\operatorname{rank}k_L=24\). The abelian Sugawara tensor
\[
T_L=\frac12\sum_{A=1}^{24}:J_L^AJ_L^A:
\]
has Virasoro central charge \(c_L=24\), and by the no-coset clause it is the full left-moving stress
tensor.

On the right, take eight transverse bosons \(X_R^i\) and eight Majorana fermions \(\psi^i\):
\[
X_R^i(\bar z)X_R^j(\bar w)\sim-\delta^{ij}\log(\bar z-\bar w),
\qquad
\psi^i(\bar z)\psi^j(\bar w)\sim\frac{\delta^{ij}}{\bar z-\bar w}.
\]
Pairwise bosonization of the fermions,
\[
\frac{\psi^{2a-1}\pm i\psi^{2a}}{\sqrt2}=e^{\pm iH^a},
\qquad
a=1,\ldots,4,
\]
shows that their stress tensor is equivalent to four chiral bosons. A Heisenberg-current basis is
\[
J_R^\alpha=
\left(
i\bar\partial X_R^1,\ldots,i\bar\partial X_R^8,
i\bar\partial H^1,\ldots,i\bar\partial H^4
\right),
\qquad
\alpha=1,\ldots,12,
\]
with level matrix \(k_R=I_{12}\). Thus \(\operatorname{rank}k_R=12\), and the right-moving stress
tensor is the full abelian Sugawara tensor in the bosonized basis:
\[
T_R=\frac12\sum_{\alpha=1}^{12}:J_R^\alpha J_R^\alpha:,
\qquad
c_R=8+\frac82=12.
\]
The unbosonized expression gives the standard \(N=1\) supercurrent
\[
G_R(\bar z)=i\sum_{i=1}^{8}\psi^i(\bar z)\bar\partial X_R^i(\bar z).
\]
Wick contraction yields
\[
G_R(\bar z)G_R(\bar w)
\sim
\frac{8}{(\bar z-\bar w)^3}
+
\frac{2T_R(\bar w)}{\bar z-\bar w}.
\]
Since \(2c_R/3=2(12)/3=8\), this is precisely the \(N=1\) super-Virasoro OPE, so
\[
G^2\sim T_R.
\]

Let \(n=D-2\) be the number of physical transverse spacetime coordinates. On the supersymmetric
chirality,
\[
c_R^{\rm phys}=n+\frac n2=\frac32 n.
\]
Setting \(c_R^{\rm phys}=12\) gives \(n=8\), hence
\[
\boxed{D=10.}
\]
On the bosonic chirality,
\[
c_L^{\rm phys}=n+c_{\rm internal}=24,
\]
so
\[
\boxed{c_{\rm internal}=16.}
\]
Covariantly,
\[
c_L^{\rm matter}=10+16=26,
\qquad
c_R^{\rm matter}=10+\frac{10}{2}=15,
\]
the matter central charges canceled by the bosonic ghosts on the left and the
supersymmetric ghost system on the right.
\end{proof}

\begin{theorem}[Modular lattice and anomaly closure]
The rank-sixteen internal lattice in Assumption~\ref{ass:heterotic-edge-polarization} must be even
and self-dual. Hence
\[
\Gamma_{16}=E_8\oplus E_8
\quad\text{or}\quad
\Gamma_{16}=D_{16}^{+},
\]
corresponding to the heterotic gauge groups \(E_8\times E_8\) and
\(\operatorname{Spin}(32)/\Z_2\). The Bouchard--Donagi construction lies on the
\(E_8\oplus E_8\) branch. The lattice theorem does not select that branch over
\(D_{16}^{+}\), and compactification dualities require a separate equivalence audit. With \(D=10\),
the covariant Weyl anomalies cancel:
\[
(10+16)-26=0,
\qquad
\left(10+\frac{10}{2}\right)-15=0.
\]
\end{theorem}

\begin{proof}
For the internal bosons,
\[
Z_{\Gamma_{16}}(\tau)=\frac{\Theta_{\Gamma_{16}}(\tau)}{\eta(\tau)^{16}},
\qquad
\Theta_\Gamma(\tau)=\sum_{p\in\Gamma}q^{p^2/2}.
\]
Invariance under \(T:\tau\mapsto\tau+1\) requires \(p^2\in2\Z\), so the lattice is even. Under
\(S:\tau\mapsto-1/\tau\), Poisson resummation maps \(\Gamma\) to its dual \(\Gamma^\ast\), so
modular closure requires \(\Gamma^\ast=\Gamma\). The positive-definite even unimodular
rank-sixteen lattices are \(E_8\oplus E_8\) and \(D_{16}^+\). The ghost central charges are
\(-26\) on the bosonic left and \(-15\) on the supersymmetric right, giving the displayed anomaly
cancellations. BRST nilpotency follows with the standard intercept and level-matching conditions.
\end{proof}

\begin{remark}[Local \(E_8\) triality receipt]
The finite \(E_8/\mathrm{Spin}(8)\) triality certificate can be used as a sanity check for the
\(E_8\)-side automorphism and representation bookkeeping in the \(E_8\oplus E_8\) branch. It
constructs a nonsplit \(2\!\cdot\!\mathrm{Alt}(9)\) subgroup whose positive-half-spin image preserves
an \(E_8\) lattice and whose vector and spin-side mod-2 orbit fingerprints are not conjugate before
triality fusion. This is a local \(E_8\) subgroup certificate. It does not identify the full
rank-sixteen internal lattice, prove modular invariance, supply the GSO/spin-structure sum, or close
the OPH critical-edge CFT gate.
\end{remark}

The OPH theorem target is precise:
\[
\boxed{
\operatorname{ScaleLim}(\text{OPH sewn-edge carrier})
\cong
\left(\mathrm{Heis}_8\otimes V_{\Gamma_{16}}\right)_L
\otimes
\left(\mathrm{Heis}_8\otimes \mathrm{Ferm}_8\right)_R
}
\]
with no residual coset. It cannot be replaced by the numerical observation \(12\to24\). It must be
established by constructing the edge transfer operator, identifying the gapless chiral fields,
calculating their OPEs, deriving the fermionic grading and spin-structure sum, and proving stress
exhaustion. Equivalently, the finite carrier must export the five receipts listed above:
\[
\operatorname{rank}\calR_{\rm port}=12,\quad
\kappa_\rho>0,\quad
\kappa_{\rho,\pm}>0,\quad
J_AJ_B\sim k_{AB}(z-w)^{-2},\quad
Q_N^2-H_{R,N}\to0,
\]
together with the torus receipt \(Z_{\OPH}=q^{-1}\bar q^{-1/2}(1+\cdots)\) and the correct modular
spin-structure transformations. Once that edge-VOA identification is proved, \(D=10\) and the
left-moving \(c_{\rm internal}=16\) sector follow by the calculation above. The number \(26\)
belongs to the left-moving bosonic matter central charge, not to twenty-six shared heterotic
spacetime dimensions.

\section{The OPH Tensor Carrier and the String Graviton}

The tensor dictionary is the conceptual hinge. OPH supplies an action-level classical
transverse-traceless metric carrier on the stated pure-Einstein branch. The critical-string
candidate must separately supply a physical quantum state and pole and show that its classical
limit is that same carrier.

\subsection{OPH side: metric from modular geometry}

On the OPH gravity branch, cap modular flow becomes geometric in the support-visible scaling
limit, and fixed-cap generalized-entropy stationarity supplies the Einstein relation. The metric is
the compressed observer-facing datum that makes the cap modular action geometric. A small metric
perturbation is a deformation of the OPH geometric normal form:
\[
q_{ab}^{\OPH}\longmapsto q_{ab}^{\OPH}+h_{ab}^{\OPH}.
\]
The transverse-traceless part
\[
h_{ab}^{\OPH,\TT}
\]
is the propagating classical spin-two perturbation. This statement alone does not construct a
graviton Hilbert space or a particle pole. Those are additional receipts demanded from the
critical-string representative below.

\subsection{String side: metric from the closed-string vertex}

In a critical closed string, the metric appears as a background coupling in the sigma model:
\[
S_\sigma\supset
\frac{1}{4\pi\alpha'}
\int d^2\sigma\sqrt\gamma\,\gamma^{\alpha\beta}
G_{\mu\nu}(X)\partial_\alpha X^\mu\partial_\beta X^\nu.
\]
Perturbing
\[
G_{\mu\nu}=G^{(0)}_{\mu\nu}+\kappa h_{\mu\nu}
\]
produces the standard closed-string spin-two vertex
\[
V_h(k,\epsilon)=
\epsilon_{\mu\nu}\,
\partial X^\mu\bar\partial X^\nu e^{ik\cdot X}.
\]
Equivalently, at the first closed-string oscillator level,
\[
|G;k,\epsilon\rangle
=
\epsilon_{\mu\nu}^{\TT}
\alpha_{-1}^{\mu}\tilde\alpha_{-1}^{\nu}|0;k\rangle .
\]
The polarization decomposes into symmetric traceless, antisymmetric, and trace pieces:
\[
\epsilon_{\mu\nu}
=\epsilon^{\TT}_{(\mu\nu)}
+\epsilon_{[\mu\nu]}
+\frac1D\eta_{\mu\nu}\epsilon^\lambda_{\ \lambda}.
\]
The symmetric transverse-traceless piece is the string graviton. The antisymmetric piece is the
\(B\)-field, and the trace is the dilaton.

\subsection{Left-right collar factorization}

A closed OPH edge cycle has two collar readings. The two readings are sewn into the heat-kernel
factor \(d_R^2\). In the large-edge worldsheet language they become the left and right chiral
oscillator sectors:
\[
\text{left collar edge mode}\otimes\text{right collar edge mode}
\longmapsto
\alpha_{-1}^{\mu}\tilde\alpha_{-1}^{\nu}|0;k\rangle .
\]
The level-one tensor product splits after contraction with a polarization tensor. A general
polarized state decomposes as
\[
\epsilon_{\mu\nu}\alpha_{-1}^{\mu}\tilde\alpha_{-1}^{\nu}|0;k\rangle
=
\epsilon^{\TT}_{(\mu\nu)}\alpha_{-1}^{\mu}\tilde\alpha_{-1}^{\nu}|0;k\rangle
+
\epsilon_{[\mu\nu]}\alpha_{-1}^{\mu}\tilde\alpha_{-1}^{\nu}|0;k\rangle
+
\frac1D\eta_{\mu\nu}\epsilon^\lambda{}_{\lambda}
\alpha_{-1}^{\mu}\tilde\alpha_{-1}^{\nu}|0;k\rangle .
\]
The proposed quantum completion of the OPH tensor carrier is the symmetric
transverse-traceless component of the two-sided collar excitation, read in the critical worldsheet
language:
\[
h_{\mu\nu}^{\OPH,\TT}
\longleftrightarrow
\epsilon_{\mu\nu}^{\TT}\alpha_{-1}^{\mu}\tilde\alpha_{-1}^{\nu}|0;k\rangle .
\]

\subsection{The map}

Define the OPH-carrier-to-string-state map by
\[
\Mgrav:
[h_{ab}^{\OPH,\TT}]
\longmapsto
[\epsilon^{\TT}_{\mu\nu}\partial X^\mu\bar\partial X^\nu e^{ik\cdot X}],
\]
with the following normalization condition:
\[
G_4^{\rm string}(m_\star,\alpha',g_s,V_6)
=
G_4^{\OPH}(N_{\rm scr},P).
\]
OPH fixes the classical Einstein-frame tensor normalization. The string representative must supply
the critical worldsheet realization, BRST-physical state space, positive norm, and massless pole.

\begin{theorem}[Conditional tensor-carrier quantum completion]
Suppose a critical-string presentation satisfies all of the following: (i) the OPH pure-Einstein
flat-background quadratic receipt with two transverse-traceless null modes; (ii) a BRST-physical,
positive-norm closed-string symmetric spin-two state with a positive-residue pole at \(k^2=0\);
(iii) equality of the four-dimensional normalization and classical background deformation; and
(iv) the selector condition that no second independent visible spin-two sector survives. Then the
string state is a quantum completion of the OPH classical metric carrier:
\[
\Mgrav(h^{\OPH,\TT})=h^{\rm string,\TT}.
\]
The absence of an additional visible spin-two particle is condition (iv) of the selector receipt,
not a consequence of the classical Einstein equation alone.
\end{theorem}

\begin{proof}
The OPH gravity branch produces a single observer-facing Einstein-frame metric on the physical
quotient. Under (i), its reduced quadratic action and Hamiltonian have two classical null tensor
modes. Assumption (ii) places the displayed string vertex in the physical Hilbert space and gives
it the required particle pole; this is precisely the information absent from a classical Einstein
equation. By (iii), the vertex deforms the same normalized metric and has the OPH tensor mode as its
classical limit, so the displayed map identifies one classical carrier with one quantum state.
Condition (iv) rejects any candidate with an additional independent visible spin-two state. Thus
the particle statement follows from all four receipts together, without promoting the classical
field equation by itself.
\end{proof}

\begin{center}
\small
\begin{tabular}{p{0.31\linewidth}p{0.57\linewidth}}
\toprule
\textbf{OPH object} & \textbf{String-theory image} \\
\midrule
Cap modular geometry & Target-space metric background \(G_{\mu\nu}(X)\). \\
Fixed-cap generalized entropy stationarity & Low-energy Einstein equation / vanishing metric beta function on the selected background. \\
Metric perturbation \(h^{\OPH}_{ab}\) & Closed-string background deformation \(h_{\mu\nu}\partial X^\mu\bar\partial X^\nu\). \\
OPH classical tensor carrier & BRST-physical symmetric transverse-traceless closed-string state,
conditional on its positive-residue pole receipt. \\
Screen-capacity normalization & Four-dimensional Newton constant after compactification. \\
Edge record/collar sewing & Worldsheet sewing and genus expansion in the controlled large-edge branch. \\
\bottomrule
\end{tabular}
\end{center}

\section{OPH-Augmented String Theory}\label{sec:oph-augmented-string}

OPH supplies a selection and readout functor for critical string vacua. Ordinary string theory
supplies a large class of critical presentations. OPH asks which presentation is the critical
worldsheet completion of the observer-visible edge normal form.

\begin{definition}[OPH augmentation of a string vacuum]
A string vacuum \(v\) is augmented by OPH data when it is equipped with a map
\[
\Pi_{\OPH}(v)=
\left(
G_{\rm phys},Y,N_c,N_g,n_H,\calO_{\rm op},G_4,\Lambda,\calO_{\rm quant}
\right)
\]
from compactification data to observer-visible records, together with the constraints
\[
\mathcal C_v(m_\star)=0,
\qquad
\Pi_{\OPH}(v)=\Pi_{\rm target}^{\OPH},
\qquad
\ker D\mathcal C_v\cap\ker D\Pi_{\OPH}=T(G_{\rm inv}\!\cdot m_\star),
\]
where \(N_{\OPH}\) is a physical slice transverse to independently proved OPH-invisible
redundancies, as formalized in Definition~\ref{def:bd-physical-slice}. It is not defined by
\(\ker D\Pi_{\OPH}\). The constraints require a separate dynamical stability receipt. The joint
kernel condition is the coordinate-free moduli-locking certificate of
Theorem~\ref{thm:constraint-augmented-locking}.
\end{definition}

The augmented vacuum equations are:
\[
\begin{cases}
\beta^G=\beta^B=\beta^\Phi=0, & \text{worldsheet consistency},\\
(c_L^{\rm phys},c_R^{\rm phys})=(24,12),\quad G^2\sim T_R, &
\text{critical-edge certificate},\\
F^{0,2}=0,\quad J^2\wedge F=0, & \text{heterotic bundle stability/HYM},\\
c_2(TX)-c_2(V_{\rm vis})-c_2(V_{\rm hid})=[W], & \text{Bianchi/anomaly condition},\\
\chi(V_{\rm matter})=3,\quad n_H=1,\quad N_{\rm exotic}=0, & \text{visible cohomology target},\\
G_{\rm phys}=(\SU(3)\times\SU(2)\times\U(1))/\Z_6, & \text{global group target},\\
\calO_{\rm op}=\ZfourR\text{ safety}, & \text{operator target},\\
G_4^{\rm string}=G_4^{\OPH},\quad \alpha'\mapsto\alpha'_{\OPH}, & \text{graviton normalization target},\\
\nabla V_{\rm eff}(m_\star)=0,\quad \operatorname{Hess}_{\rm phys}V_{\rm eff}\succeq\mu^2I,
& \text{dynamical stabilization},\\
\mathcal H_v(m_\star)=0,\quad \operatorname{rank}D\mathcal H_v=\dim\mathcal X_v,
& \text{constraint-augmented target locking}.
\end{cases}
\]

For a finite catalogue with certified parameter-domain coverage, these equations define a finite
certificate problem. A conventional string vacuum can be internally consistent and fail the OPH
observer-visible target map. No finiteness or exhaustiveness claim follows for the unrestricted
candidate universe.

\subsection{Testable consequences after certificate closure}

Once the named witness class is fixed, the theory makes gates that generic landscape reasoning lacks:
\begin{enumerate}[leftmargin=2em]
\item \textbf{One visible massless Higgs pair at the compactification target.} Extra massless Higgs pairs fail
the OPH one-Higgs electroweak branch.
\item \textbf{No massless chiral exotics in the published cohomology table.} Exotic chiral matter changes the observer-visible matter
package and fails the cohomology target.
\item \textbf{No extra visible low-scale \(\U(1)\).} Additional visible abelian gauge bosons change
the OPH global group quotient.
\item \textbf{No mixed \(X/Y\) generator in the connected visible adjoint.} The selected visible
group is the product quotient. A propagating connection component requires an action receipt, while
Wilson-line and Kaluza--Klein particle modes require the separate spectrum and coupling calculation.
\item \textbf{Operator-safety pattern.} Perturbative R-parity violation, perturbative
dimension-five proton decay, and a perturbative \(\mu\)-term are forbidden on the operator-safe
branch; Yukawas and the Weinberg neutrino operator are allowed.
\item \textbf{One visible spin-two sector.} Any additional physical spin-two pole, bimetric sector,
or independent low-energy tensor polarization fails the string-selector uniqueness gate; the
classical Einstein equation alone does not establish this exclusion.
\end{enumerate}

\section{String-Community Pressure Points}

The string-community problem is selection. The 2024 Standard Model review states the challenge in
compactification language: reproduce the Standard Model gauge sector, chiral matter, and
phenomenology from geometry and topology \cite{MarchesanoShiuWeigand2024}. Heterotic
M-theory stabilization work emphasizes the computational weight of dilaton, complex-structure,
and K\"ahler moduli stabilization \cite{DeffayetOvrutSteinhardt2024}. The philosophy literature
on the string landscape frames the predictivity concern as underdetermination among many
solutions compatible with observed data \cite{FriederichLeBihan2021}.
Exact flux-vacua work also makes the computational problem concrete: stabilized flux vacua
require solving vacuum conditions with exponential corrections, although symmetry loci can turn
some conditions algebraic \cite{GrimmVanDeHeisteeg2025}.

OPH imposes the observer-visible target
\[
\mathfrak S_{\OPH}=
\left(
\begin{gathered}
\dfrac{\SU(3)\times\SU(2)\times\U(1)}{\Z_6},\quad N_c=3,\quad N_g=3,\quad Y_{\rm SM},\\
n_H=1,\quad \text{no light chiral exotics},\quad \ZfourR\text{ safety}
\end{gathered}
\right).
\]
The named geometric structural row in the package is
\[
\boxed{
BD_{n=1}^{\OPH}
=
\text{Bouchard-Donagi }E_8\times E_8
\text{ heterotic }\SU(5)\text{ Standard Model, one-Higgs-pair stratum}.
}
\]
The tested operator-safe proposal is
\[
\boxed{
BD_{n=1,+}^{\OPH}
=
BD_{n=1}^{\OPH}+\ZfourR.
}
\]

Bouchard and Donagi introduced a heterotic Standard Model with the visible massless cohomology
spectrum of the MSSM, no massless visible exotics,
observable \(\SU(3)\times\SU(2)\times\U(1)\), a Calabi--Yau threefold with
\(\Z_2\) fundamental group, and an invariant \(\SU(5)\) bundle. Depending on moduli, the model
has zero, one, or two Higgs doublet conjugate pairs; the one-pair region gives precisely the
massless MSSM Higgs content \cite{BouchardDonagi2005}. This cohomology calculation determines
zero modes, rather than the nonzero Dirac/Laplacian, Kaluza--Klein, winding, oscillator,
Wilson-line, vectorlike, five-brane, or hidden spectrum
\cite{DonagiHeOvrutReinbacher2004}.

The global group identity is central:
\[
\Cent_{\SU(5)}(\diag(1,1,1,-1,-1))=S(\U(3)\times\U(2)),
\]
\[
S(\U(3)\times\U(2))
\cong
\frac{\SU(3)\times\SU(2)\times\U(1)}{\Z_6}.
\]
This fixes the charge lattice, beyond Lie-algebra matching.

\begin{theorem}[OPH vacuum sieve theorem]
A critical string vacuum \(\mathcal T\) is OPH-admissible only if
\[
\Pi_{\rm IR}^{\OPH}(\mathcal T)=\mathfrak S_{\OPH}.
\]
For the package studied here, the named geometric structural row is \(BD_{n=1}^{\OPH}\), and the
operator-safe structural row is \(BD_{n=1,+}^{\OPH}\). This theorem is a necessary sieve
statement; it does not override the failed rank gate in
Corollary~\ref{cor:bd-selection-status}.
\end{theorem}

\begin{theorem}[Global group locking theorem]
The OPH visible group and the Bouchard-Donagi Wilson-line centralizer agree:
\[
G_{\rm phys}=S(\U(3)\times\U(2))
\cong
\frac{\SU(3)\times\SU(2)\times\U(1)}{\Z_6}.
\]
For \(\rho(-1)=\diag(1,1,1,-1,-1)\),
\[
\Cent_{\SU(5)}(\rho)=S(\U(3)\times\U(2)).
\]
\end{theorem}

\begin{theorem}[BD structural geometry witness theorem]
The Bouchard-Donagi \(\Z_2\)-quotient \(\SU(5)\)-bundle construction supplies a nonempty
heterotic \(\SU(5)\)-corridor witness whose Wilson-line centralizer is the OPH global Standard
Model group and whose visible massless cohomology contains the three-generation, no-exotic,
one-Higgs branch used by the OPH selector. This statement does not supply a heavy-spectrum,
threshold, or supersymmetric-sector decoupling certificate.
\end{theorem}

\begin{proof}
Bouchard-Donagi construct the \(E_8\times E_8\) heterotic model on a Calabi-Yau quotient
\(X=\widetilde X/\Z_2\) with an invariant \(\SU(5)\) bundle and a \(\Z_2\) Wilson line
\cite{BouchardDonagi2005}. Their bundle is built on the cover using an extension of rank-two
and rank-three pieces,
\[
0\to V_2\to \widetilde V^\ast\to V_3\to0,
\qquad
V_i=\pi'{}^\ast W_i\otimes\pi^\ast L_i.
\]
The resulting observable zero-mode sector has the Standard Model gauge algebra, three generations,
no massless visible exotic matter, and moduli regions with \(0\), \(1\), or \(2\) massless Higgs
doublet conjugate pairs.
The OPH target chooses the one-pair region. The centralizer theorem above supplies the global
quotient
\[
S(\U(3)\times\U(2))
\cong
(\SU(3)\times\SU(2)\times\U(1))/\Z_6.
\]
The BD geometry supplies the named heterotic witness, and OPH supplies the global quotient
and Higgs-stratum selector.
\end{proof}

\section{String Problems Reduced to OPH Gates}

The table lists the string-theory gates. Exact algebraic gates can close inside this paper.
Cohomology reproduction, geometric realization of the \(\ZfourR\) safety layer, full Yukawa
computation, the nonzero-mode and hidden spectra, threshold matching, the low-energy decoupling
map, and moduli locking require external certificates built from the Bouchard--Donagi geometry
and its physical completion.

\begin{longtable}{p{0.26\linewidth}p{0.34\linewidth}p{0.30\linewidth}}
\toprule
\textbf{String-theory pressure point} & \textbf{OPH result} & \textbf{Claim boundary in this paper} \\
\midrule
Vacuum selection & Converts candidate vacua into a public sieve against
\(\mathfrak S_{\OPH}\). & Exact selector definition; comparative audits can expand. \\
Global Standard Model group & Locks the finite quotient
\((\SU(3)\times\SU(2)\times\U(1))/\Z_6\) beyond Lie-algebra data. & Exact group proof. \\
Charge lattice and anomalies & Uses the Standard Model hypercharge lattice with anomaly
cancellation. & Exact rational arithmetic. \\
Yukawa admissibility & One-Higgs Yukawa terms are gauge invariant. & Exact charge-sum proof. \\
Three generations & \(\Z_2\)-cover arithmetic gives \(N_g=3\). & Exact index arithmetic,
assuming the BD \(c_3\) input. \\
Higgs multiplicity & Selects \(n=1\) among BD \(n=0,1,2\) strata. & Selector proof. \\
Connected unified-gauge adjoint & The connected product-group adjoint excludes an
\(X/Y\) generator. Connection and BD particle modes remain in their action/spectrum gates. & Exact
Lie-algebra proof plus external action and heavy-mode certificates. \\
String emergence & Sewn edge partition equals \(K_t(1)\). & Exact Peter-Weyl proof. \\
Worldsheet criticality & The twelve-port and twenty-four oriented-register counts define only a
heterotic central-charge target until the edge VOA is identified. & Non-implication theorem plus
critical-edge certificate theorem; finite-carrier receipts not emitted here. \\
Vacuum stabilization & Requires stationarity, a canonically normalized physical scalar mass
matrix, and a route-appropriate stability bound. & No completed BD effective potential, point, or
Hessian enclosure is emitted. \\
Target locking & Requires a physical quotient, precommitted target map, and a certified
constraint-augmented full-column-rank minor. & Physical-slice definition and negative rank
certificate emitted; the completed constraint map, selected point, and physical BD map are absent. \\
Operator safety & The MSSM \(\ZfourR\) layer permits Yukawas and the Weinberg operator, and
forbids perturbative RPV, dimension-five proton decay, and the perturbative \(\mu\)-term. &
Charge algebra closes; BD geometric realization is a certificate gate. \\
Empirical tests & Assigns the named structural row a compact list of failure-prone low-energy and
threshold proxy screens. & Reproducible target equations; no branch compatibility result. \\
\bottomrule
\end{longtable}

\begin{longtable}{p{0.25\linewidth}p{0.43\linewidth}p{0.22\linewidth}}
\toprule
\textbf{Physicist pressure point} & \textbf{Closure supplied by the selector} & \textbf{Gate type} \\
\midrule
Landscape degeneracy & OPH replaces broad vacuum search with the finite target
\(\mathfrak S_{\OPH}\) and a public sieve. & Selector theorem. \\
Global Standard Model group & The Wilson-line centralizer lands on
\((\SU(3)\times\SU(2)\times\U(1))/\Z_6\). & Exact algebra. \\
Three families & The \(\Z_2\)-cover index relation gives \(N_g=3\) from
\(|c_3(\widetilde V)|=12\). & BD input plus exact arithmetic. \\
Higgs multiplicity & The \(n=1\) stratum is the minimal massless-cohomology stratum under the
declared zero-mode score. & Selector theorem. \\
Exotic matter & BD supplies the no-exotics visible massless MSSM cohomology witness. &
Published zero-mode geometry certificate; heavy and vectorlike modes are outside it. \\
Connected unified-gauge adjoint & The connected product-group adjoint excludes mixed
\((3,2,\pm5/6)\) generators; no connection or particle-spectrum conclusion follows from this
algebra alone. & Exact Lie-algebra statement. \\
Critical dimension & If the sewn-edge carrier has the heterotic polarization
\((\mathrm{Heis}_8\otimes V_{\Gamma_{16}})_L\otimes
(\mathrm{Heis}_8\otimes\mathrm{Ferm}_8)_R\), then \(D=10\) and
\(c_{\rm internal}=16\). & Conditional edge-VOA gate. \\
RPV and \(\mu\)-problem & \(\ZfourR\) permits Yukawas, forbids perturbative RPV and
dimension-five proton decay, forbids perturbative \(\mu\), and leaves matter parity. & Exact
charge algebra; compactification certificate required. \\
Vacuum stabilization & The problem requires a controlled effective action, stationarity, and a
physical Hessian stability bound. & No BD completion supplies these data. \\
Target identifiability & The problem requires a scheme-locked physical map plus a certified
constraint-augmented rank and interval-isolation receipt. & Issue-369 obstruction: the published
pre-completion slice has \(142\) real directions, the five-row proxy has rank zero, and no completed
constraint map, physical slice, or Jacobian is supplied. \\
Predictivity & Higgs/top, stop, and one-loop gauge-running coordinates give failure-prone proxy
targets. & Reproducible target-side proxies only; no spectrum or threshold certificate is emitted. \\
\bottomrule
\end{longtable}

\subsection{Problem 1: vacuum selection}

String theory supplies many compactifications with Standard-Model-like low-energy data. OPH
adds an independent target:
\[
\mathfrak S_{\OPH}=
\begin{gathered}
\left(
\frac{\SU(3)\times\SU(2)\times\U(1)}{\Z_6},
N_c=3,\,
N_g=3,\,
Y_{\rm SM},\,
n_H=1
\right),\\
\text{no light chiral exotics},\qquad
\text{no extra visible low-scale }\U(1).
\end{gathered}
\]

\begin{theorem}[Set-theoretic selector reduction]
Let \(\mathcal C\) be any class of critical string compactifications with an observer-visible
infrared projection \(\Pi_{\rm IR}^{\OPH}\). Define
\[
\mathcal C_{\OPH}=
\{\mathcal T\in\mathcal C:\Pi_{\rm IR}^{\OPH}(\mathcal T)=\mathfrak S_{\OPH}\}.
\]
The OPH selection problem over \(\mathcal C\) is the audit of \(\mathcal C_{\OPH}\) against the
quantitative target \(\calO_{\OPH}\). This is an effective finite or enumerable audit only when a
separate enumeration and domain-coverage certificate for \(\mathcal C\) is supplied.
\end{theorem}

\begin{proof}
The OPH target \(\mathfrak S_{\OPH}\) is fixed independently of any string compactification. The
projection \(\Pi_{\rm IR}^{\OPH}\) assigns each candidate its observer-visible group, charge
lattice, matter content, Higgs count, and visible low-scale gauge factors. Equality with
\(\mathfrak S_{\OPH}\) is a conjunction of explicit gates. A candidate passes exactly when all
equalities and exclusions hold. The quantitative stage appends the equation
\[
\calF_{\mathcal T}(m)=\calO_{\OPH}.
\]
The selection condition is therefore a sieve and target equation. The definition alone supplies no
algorithm for enumerating \(\mathcal C\), solving every branch, or quotienting all dualities.
\end{proof}

\subsection{Problem 2: global Standard Model group}

The OPH target fixes the global group beyond the Lie algebra, at the level of the charge lattice.

\begin{theorem}[Centralizer computation]
Let
\[
\rho=\diag(1,1,1,-1,-1)\in\SU(5).
\]
The centralizer of \(\rho\) in \(\SU(5)\) is
\[
\Cent_{\SU(5)}(\rho)=S(\U(3)\times\U(2)).
\]
\end{theorem}

\begin{proof}
The \(+1\) eigenspace of \(\rho\) has dimension \(3\), and the \(-1\) eigenspace has dimension
\(2\). A unitary matrix commutes with \(\rho\) exactly when it preserves these two eigenspaces.
Such a matrix is block diagonal,
\[
g=\begin{pmatrix}A&0\\0&B\end{pmatrix},
\qquad
A\in\U(3),\quad B\in\U(2).
\]
The condition \(g\in\SU(5)\) is \(\det A\,\det B=1\), precisely
\[
S(\U(3)\times\U(2)).
\]
\end{proof}

\begin{theorem}[\(\Z_6\) quotient]
There is an isomorphism
\[
S(\U(3)\times\U(2))
\cong
\frac{\SU(3)\times\SU(2)\times\U(1)}{\Z_6}.
\]
\end{theorem}

\begin{proof}
Define
\[
\varphi:\SU(3)\times\SU(2)\times\U(1)\to S(\U(3)\times\U(2))
\]
by
\[
\varphi(A,B,z)=
\begin{pmatrix}
z^2 A&0\\
0&z^{-3}B
\end{pmatrix}.
\]
The determinant is
\[
\det(z^2A)\det(z^{-3}B)=z^6z^{-6}\det A\det B=1,
\]
so the image lies in \(S(\U(3)\times\U(2))\). The kernel consists of triples with
\[
z^2A=I_3,\qquad z^{-3}B=I_2.
\]
\(A=z^{-2}I_3\) and \(B=z^3I_2\). The conditions \(A\in\SU(3)\) and \(B\in\SU(2)\) give
\[
z^{-6}=1,\qquad z^6=1.
\]
The kernel is
\[
\{(z^{-2}I_3,z^3I_2,z):z^6=1\}\cong\Z_6.
\]
Surjectivity follows by decomposing any \((A',B')\in S(\U(3)\times\U(2))\) into determinant-one
parts and the common \(\U(1)\) factor. The first isomorphism theorem gives the quotient.
\end{proof}

\subsection{Problem 3: charge lattice, anomalies, and one-Higgs Yukawas}

The OPH target uses the Standard Model hypercharge lattice:
\[
Q=(3,2)_{1/6},\quad
u^c=(\bar3,1)_{-2/3},\quad
d^c=(\bar3,1)_{1/3},\quad
L=(1,2)_{-1/2},\quad
e^c=(1,1)_1,\quad
H=(1,2)_{1/2}.
\]

\begin{theorem}[One-generation anomaly cancellation]
For one generation with the hypercharges above,
\[
\SU(3)^2\U(1)=0,\quad
\SU(2)^2\U(1)=0,\quad
\mathrm{grav}^2\U(1)=0,\quad
\U(1)^3=0.
\]
\end{theorem}

\begin{proof}
Use left-handed Weyl fields. For \(\SU(3)^2\U(1)\), the color-charged fields give
\[
2\cdot\frac12\cdot\frac16
+\frac12\cdot\left(-\frac23\right)
+\frac12\cdot\frac13
=
\frac16-\frac13+\frac16=0.
\]
For \(\SU(2)^2\U(1)\), the weak doublets give
\[
3\cdot\frac12\cdot\frac16
+\frac12\cdot\left(-\frac12\right)
=\frac14-\frac14=0.
\]
For the mixed gravitational anomaly, count dimensions:
\[
6\cdot\frac16
+3\cdot\left(-\frac23\right)
+3\cdot\frac13
+2\cdot\left(-\frac12\right)
+1
=1-2+1-1+1=0.
\]
For the cubic anomaly,
\[
6\left(\frac16\right)^3
+3\left(-\frac23\right)^3
+3\left(\frac13\right)^3
+2\left(-\frac12\right)^3
+1^3
\]
\[
=\frac1{36}-\frac89+\frac19-\frac14+1
=0.
\]
\end{proof}

\begin{theorem}[One-Higgs Yukawa invariants]
The one-Higgs Standard Model Yukawa terms have zero hypercharge:
\[
QHu^c,\qquad QH^\dagger d^c,\qquad LH^\dagger e^c.
\]
\end{theorem}

\begin{proof}
The hypercharge sums are
\[
\frac16+\frac12-\frac23=0,
\]
\[
\frac16-\frac12+\frac13=0,
\]
and
\[
-\frac12-\frac12+1=0.
\]
The nonabelian indices contract using \(3\otimes\bar3\), \(2\otimes2\), and the
\(\epsilon\)-tensor of \(\SU(2)\).
\end{proof}

\subsection{Problem 4: generation arithmetic}

Bouchard-Donagi uses a \(\Z_2\) quotient. The chiral index relation gives the number of
generations:
\[
N_g=\frac{|c_3(\widetilde V)|}{2|\Gamma|}.
\]

\begin{theorem}[Three-generation cover arithmetic]
If \(|c_3(\widetilde V)|=12\) and \(|\Gamma|=2\), the quotient has three generations.
\end{theorem}

\begin{proof}
Substitution gives
\[
N_g=\frac{12}{2\cdot2}=3.
\]
\end{proof}

\subsection{Problem 5: Higgs-stratum selection}

The Bouchard-Donagi construction has regions with zero, one, or two Higgs doublet conjugate
pairs. The structural Higgs-count gate selects the one-pair stratum.

\begin{theorem}[One-Higgs zero-mode minimality gate]
Within the published Bouchard--Donagi massless-cohomology strata, the \(n=1\) Higgs-pair
stratum is the minimal row containing a Higgs pair and no second massless Higgs pair.
\end{theorem}

\begin{proof}
\(n=0\) lacks a Higgs pair and lacks the Yukawa-complete electroweak branch
used by the OPH target. The \(n=2\) stratum has a second massless Higgs pair and therefore fails
the declared zero-mode minimality score. The \(n=1\) stratum supplies exactly one massless pair.
This proof does not exclude an \(n=2\) low-energy branch: moduli-dependent masses and the full
decoupling calculation could lift its additional pair.
\end{proof}

\subsection{Problem 6: connected unified-gauge adjoint}

The connected product-group adjoint contains no simple-\(\SU(5)\) \(X/Y\) generator.
This Lie-algebra statement does not supply connection dynamics or decide whether particle modes
induce proton decay.

\begin{theorem}[Product-group adjoint]
The connected adjoint of
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\Z_6}
\]
is
\[
(8,1,0)\oplus(1,3,0)\oplus(1,1,0).
\]
It contains no \((3,2,\pm5/6)\) adjoint generator; this algebraic conclusion alone does not
assert a propagating connection component or particle.
\end{theorem}

\begin{proof}
Dividing by the finite central subgroup \(\Z_6\) leaves the Lie algebra unchanged:
\[
\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak{u}(1).
\]
The adjoint representation decomposes as the adjoints of the three factors:
\[
(8,1,0)\oplus(1,3,0)\oplus(1,1,0).
\]
Mixed \((3,2,\pm5/6)\) generators occur in the adjoint of simple \(\SU(5)\) after breaking to
the Standard Model subgroup. They are absent from the product Lie algebra above.
\end{proof}

\subsection{Problem 7: string emergence}

The worldsheet language appears from edge sewing as an effective description.

\begin{theorem}[Heat-kernel derivation]
For a compact group \(G\), the sewn OPH edge partition
\[
Z_{\rm edge}(t)=\sum_R d_R^2e^{-tC_2(R)}
\]
is the heat kernel at the identity:
\[
Z_{\rm edge}(t)=K_t(1).
\]
\end{theorem}

\begin{proof}
Peter-Weyl gives the heat kernel expansion
\[
K_t(g)=\sum_R d_R\chi_R(g)e^{-tC_2(R)}.
\]
At \(g=1\), \(\chi_R(1)=d_R\). Substitution gives
\[
K_t(1)=\sum_R d_R^2e^{-tC_2(R)}=Z_{\rm edge}(t).
\]
\end{proof}

\subsection{Problem 8: dynamical stabilization and target locking}

The OPH contribution is a target criterion. This paper does not emit a completed BD moduli computation.

\begin{theorem}[Constraint-augmented local locking]
\label{thm:constraint-augmented-locking}
Let \(\mathcal P\) be an \(n\)-real-dimensional ambient parameter space, let \(G\) be an
independently certified OPH-invisible redundancy group with orbit dimension \(g\) on a fixed
orbit-type stratum, and let
\[
\mathcal C:\mathcal P\longrightarrow\mathbb R^L,
\qquad
F:\mathcal P\longrightarrow\mathbb R^K
\]
be the invariant completion constraints and a candidate-independent observer-visible readout.
Suppose \(p\) satisfies \(\mathcal C(p)=0\), \(F(p)=\mathcal O_{\OPH}\), and
\(D\mathcal C(p)\) has rank \(c\) transverse to the \(G\)-orbit. The completed quotient tangent
has dimension
\[
d=n-g-c.
\]
The coordinate-free locking condition is
\[
\ker D\mathcal C(p)\cap\ker DF(p)=T_p(G\!\cdot p).
\label{eq:augmented-locking-kernel}
\]
It is equivalent to the following gauge-slice certificate. On a certified local slice \(\Sigma\),
choose \(c\) independent completion rows \(A\) and \(d\) independently registered readout rows
\(I\), and set
\[
\mathcal H_{A,I}
=
\left(
\pi_A\mathcal C|_\Sigma,
\pi_I(F-\mathcal O_{\OPH})|_\Sigma
\right).
\]
Then \(\dim\Sigma=c+d\), and condition~\eqref{eq:augmented-locking-kernel} holds exactly when some such precommitted row set
has
\[
\det D\mathcal H_{A,I}(p)\ne0.
\]
Under either form of the condition, \([p]\) is the unique nearby orbit satisfying both the
completion equations and the OPH target equations.
\end{theorem}

\begin{proof}
The regular-level-set theorem gives
\[
T_{[p]}\bigl(\mathcal C^{-1}(0)/G\bigr)
\cong
\ker D\mathcal C(p)/T_p(G\!\cdot p).
\]
The derivative induced by \(F\) on this quotient tangent is injective exactly when its lifted
kernel is the orbit tangent, which is condition~\eqref{eq:augmented-locking-kernel}. On a local slice the orbit tangent is
removed. Choose \(c\) independent rows of \(D\mathcal C\). Injectivity of \(DF\) on the
\(d\)-dimensional kernel of those rows is equivalent to the existence of \(d\) readout rows making
the combined \((c+d)\)-square derivative invertible. The inverse-function theorem then makes the
joint zero a local singleton on the slice. Quotient descent identifies that singleton with one
physical orbit.
\end{proof}

\begin{corollary}[BD dimension budget]
Start from the documented \(142\)-real-dimensional published one-Higgs quotient. If a completion
adds \(a\) real physical coordinates, imposes completion equations of transverse rank \(r\), and
removes \(g\) additional independently proved invisible orbit directions, then
\[
d=142+a-r-g.
\]
A locking certificate using \(k\) legitimate readout rows requires
\[
r+g-a\ge 142-k.
\]
Thus five legitimate rows require at least \(137\) net real cuts, while the three
promoted OPH rows require at least \(139\). These bounds are necessary and not sufficient. If
\(d=0\), the completion equations isolate the vacuum and no readout derivative is needed.
\end{corollary}

\begin{proof}
The dimension formula is the regular quotient count. An injective linear map from a
\(d\)-dimensional tangent space to \(\mathbb R^k\) requires \(d\le k\). Rearranging gives the
stated inequalities.
\end{proof}

\begin{theorem}[Dynamical stabilization certificate]
\label{thm:dynamical-stabilization}
Let \(V_{\rm eff}\) be a \(G\)-invariant \(C^2\) effective potential with a certified domain of
validity. A Minkowski or de Sitter scalar vacuum is strictly locally stabilized modulo \(G\) if
\[
\nabla V_{\rm eff}(p)=0,
\qquad
\operatorname{Hess}V_{\rm eff}(p)|_{T_{[p]}\mathcal M^{\rm phys}}
\succeq \mu^2 I
\]
in canonically normalized physical coordinates for a certified \(\mu^2>0\), after removing gauge
and Goldstone directions. An anti-de Sitter branch instead requires the corresponding
Breitenlohner--Freedman spectral bound. Full rank of an observer readout proves local
identifiability; it does not give a scalar a mass. Both stabilization and target-locking receipts
are required unless the declared completion equations themselves include a separately certified
stability theorem.
\end{theorem}

\begin{proof}
For the Minkowski or de Sitter case, Taylor's theorem and the positive lower Hessian bound give a
strict quadratic increase of \(V_{\rm eff}\) in every sufficiently small physical displacement.
The removed orbit and Goldstone directions are not physical scalar moduli. The anti-de Sitter
statement uses its stability bound rather than positivity of the potential Hessian. The derivative
of a separate readout does not enter either mass operator, which proves the final distinction.
\end{proof}

\begin{theorem}[Local isolation by a certified row minor]\label{thm:row-minor-isolation}
Let \(\calF:\mathcal M\to\mathbb R^K\) be \(C^1\), let the physical slice have real
dimension \(d\leq K\), and suppose
\[
\calF(m_\star)=\calO_{\OPH},
\]
after quotienting independently proved OPH-invisible equivalences. If an explicitly identified
\(d\times d\) row minor of \(D\calF(m_\star)\) has nonzero determinant, then
\(\operatorname{rank}D\calF(m_\star)=d\) and \(m_\star\) is locally isolated in the physical
moduli directions.
\end{theorem}

\begin{proof}
Let \(I\) be the selected set of \(d\) output rows and let \(\pi_I\) be the corresponding
coordinate projection. The derivative of \(\pi_I\circ\calF\) is invertible at \(m_\star\).
The inverse-function theorem gives a neighborhood on which \(\pi_I\circ\calF\) is injective.
Any point in that neighborhood with \(\calF=\calO_{\OPH}\) has the same projected value as
\(m_\star\), and hence equals \(m_\star\). This proves local branch isolation only; it is not a
global uniqueness theorem.
\end{proof}

\begin{remark}[What deficient rank does and does not prove]
If \(D\calF\) has constant rank \(r<d\) nearby, the constant-rank theorem gives a local target
fiber of dimension \(d-r\), tangent to \(\ker D\calF\). Without constant rank or explicit
target-preserving curves, kernel vectors are only infinitesimal target-null directions; deficient
rank alone does not rule out a singular isolated solution. The moduli-locking gate in this paper
nevertheless requires the stronger row-minor certificate so that isolation is public and stable
under first-order perturbations.
\end{remark}

\begin{theorem}[Interval contraction existence and isolation receipt]
\label{thm:interval-locking}
Let \(H:B\to\mathbb R^N\) be a square selected constraint-and-readout system on a closed rational
box \(B\subset\mathbb R^N\). Let \(x_0\in B\), let \(A\) be an invertible rational matrix, and
let \([H(x_0)]\) and \([J(B)]\) be outward-rounded interval enclosures of the residual and every
Jacobian on \(B\). Define
\[
K(B)=x_0-A[H(x_0)]+\bigl(I-A[J(B)]\bigr)(B-x_0).
\]
If
\[
K(B)\subset\operatorname{int}B,
\qquad
\sup_{J\in[J(B)]}\|I-AJ\|_\infty\le q<1,
\]
then \(H\) has exactly one zero in \(B\). If the selected equations are proved to generate the
full completion-and-target zero system on \(B\), this is a full existence and isolation
certificate. Otherwise every omitted required row needs an independent identity or exact
full-system solution receipt at that root. An interval determinant excluding zero certifies rank
only; it does not by itself certify existence.
\end{theorem}

\begin{proof}
Set \(T(x)=x-AH(x)\). The interval mean-value enclosure and the definition of \(K(B)\) give
\(T(B)\subset K(B)\subset B\). The norm bound makes \(T\) a contraction on the complete metric
space \(B\). Banach's fixed-point theorem gives exactly one fixed point. Since \(A\) is invertible,
\(T(x)=x\) is equivalent to \(H(x)=0\). The statements about omitted rows and a determinant follow
because neither condition proves those rows vanish or proves that a zero exists.
\end{proof}

\begin{theorem}[Branch-global cover certificate]
Let a declared physical branch domain be covered by finitely many validated quotient-chart boxes.
Assume one box has the full interval existence-and-isolation receipt of
Theorem~\ref{thm:interval-locking}. Assume every other box is excluded because at least one
required residual interval omits zero, and assume chart boundaries, singular strata, all discrete
completion choices, and every noncompact end are covered or excluded by certified tail bounds.
Then the declared branch contains exactly one target-matching physical orbit. If any box, boundary,
stratum, discrete choice, or end is unresolved, the result remains local and the branch-global
uniqueness gate stays open.
\end{theorem}

\begin{proof}
The validated cover places every point of the declared branch in one of the listed regions. The
accepted box contains exactly one physical orbit. Every other region contains no joint zero by its
residual exclusion certificate. Boundary, singular, discrete, and tail hypotheses remove the
places omitted by ordinary interior chart boxes. Hence no second orbit exists on the declared
branch. An unresolved region invalidates the exhaustive disjunction and gives the final statement.
\end{proof}

\subsection{Problem 9: operator safety}

Gauge invariance allows the standard dangerous operators
\[
LH_u,\quad LLe^c,\quad LQd^c,\quad u^cd^cd^c,\quad QQQL,\quad u^cu^cd^ce^c.
\]
The operator-safe proposal adds the MSSM \(\ZfourR\) safety layer. Lee, Raby, Ratz, Ross,
Schieren, Schmidt-Hoberg, and Vaudrevange prove that, allowing Green-Schwarz anomaly
cancellation and requiring a discrete symmetry commuting with \(SO(10)\) that forbids the
perturbative \(\mu\)-term, the MSSM has a unique \(\ZfourR\) symmetry. It leaves exact matter
parity after nonperturbative breaking and suppresses dimension-five baryon/lepton violation
\cite{LeeRabyRatzRossSchierenSchmidtHobergVaudrevange2010}.

Use the charge assignment
\[
R(Q)=R(u^c)=R(d^c)=R(L)=R(e^c)=1,
\qquad
R(H_u)=R(H_d)=0,
\qquad
R(W)=2\pmod4.
\]
A perturbative superpotential monomial is allowed precisely when its total \(R\)-charge is
\(2\pmod4\).

\begin{longtable}{p{0.28\linewidth}c p{0.40\linewidth}}
\toprule
\textbf{Operator} & \textbf{\(\ZfourR\) charge} & \textbf{Result} \\
\midrule
\(QH_uu^c\) & \(1+0+1=2\) & Up-type Yukawa allowed. \\
\(QH_dd^c\) & \(1+0+1=2\) & Down-type Yukawa allowed. \\
\(LH_de^c\) & \(1+0+1=2\) & Charged-lepton Yukawa allowed. \\
\(LH_uLH_u\) & \(1+0+1+0=2\) & Weinberg neutrino operator allowed. \\
\(LH_u\) & \(1+0=1\) & Bilinear RPV forbidden perturbatively. \\
\(LLe^c\) & \(1+1+1=3\) & Lepton-number RPV forbidden perturbatively. \\
\(LQd^c\) & \(1+1+1=3\) & Lepton-number RPV forbidden perturbatively. \\
\(u^cd^cd^c\) & \(1+1+1=3\) & Baryon-number RPV forbidden perturbatively. \\
\(QQQL\) & \(1+1+1+1=0\) & Dimension-five proton decay forbidden perturbatively. \\
\(u^cu^cd^ce^c\) & \(1+1+1+1=0\) & Dimension-five proton decay forbidden perturbatively. \\
\(H_uH_d\) & \(0+0=0\) & Perturbative \(\mu\)-term forbidden. \\
\bottomrule
\end{longtable}

\begin{theorem}[OPH operator-safety theorem]
At the MSSM charge-algebra level, adding the \(\ZfourR\) layer to \(BD_{n=1}^{\OPH}\) permits
all Standard Model Yukawa couplings and the Weinberg operator, forbids perturbative
dimension-four RPV, forbids perturbative dimension-five proton decay, forbids the perturbative
\(\mu\)-term, and leaves exact matter parity after nonperturbative breaking. The charge-algebra
proposal is
\[
BD_{n=1,+}^{\OPH}=BD_{n=1}^{\OPH}+\ZfourR.
\]
\end{theorem}

\begin{proof}
The charge table verifies the perturbative selection rule term by term. The allowed Yukawa and
Weinberg operators have total \(R\)-charge \(2\pmod4\). The RPV operators, the dimension-five
proton-decay operators, and \(H_uH_d\) have total charge \(1\), \(3\), or \(0\pmod4\), hence fail
the \(2\pmod4\) superpotential rule. The cited MSSM theorem supplies uniqueness of the
\(\ZfourR\) safety layer under the stated anomaly and \(SO(10)\)-commuting assumptions, plus the
matter-parity remnant after nonperturbative breaking.
\end{proof}

\section{Acceptance Gates}

The package is adversarial by design. The named operator-safe proposal has to pass the same
gates as any competitor; the present moduli gate records that it does not:
\begin{longtable}{p{0.33\linewidth}p{0.57\linewidth}}
\toprule
\textbf{Gate} & \textbf{Requirement} \\
\midrule
Global group & The realized group is
\((\SU(3)\times\SU(2)\times\U(1))/\Z_6\). \\
Hypercharge & The charge lattice is the Standard Model lattice. \\
Color and generations & \(N_c=3\) and \(N_g=3\). \\
Higgs sector & The low-energy branch has one Higgs pair and decouples to the observed Higgs
doublet. \\
Exotics & No light chiral exotics appear. \\
Extra visible gauge factors & No extra visible low-scale \(\U(1)\) appears. \\
Connected unified-gauge adjoint & The product-group adjoint contains no
mixed \((3,2,\pm5/6)\) generator. \\
Operator safety & The MSSM \(\ZfourR\) safety layer forbids perturbative RPV, dimension-five
proton decay, and the perturbative \(\mu\)-term, with exact matter parity after
nonperturbative breaking. \\
Vacuum, moduli, and thresholds & The branch must supply a stable physical vacuum and derived
threshold map, solve \(\mathcal H_{BD,n=1,+}(m_\star)=0\), and certify an invertible augmented
row minor plus an interval existence-and-isolation box. The frozen five-row proxy fails this gate
on the documented \(142\)-real-dimensional pre-completion slice; the completion constraints,
stable point, and physical map are not supplied. \\
\bottomrule
\end{longtable}

\begin{theorem}[No mixed \(X/Y\) connected-adjoint generator]
On the product-group branch, the connected gauge adjoint is
\[
(8,1,0)\oplus(1,3,0)\oplus(1,1,0).
\]
The adjoint contains no mixed \((3,2,\pm5/6)\) generator.
\end{theorem}

This theorem is an algebraic statement about the connected OPH product-group adjoint and does not
by itself produce a connection action or a particle. The Bouchard--Donagi computation is a
separate zero-mode calculation. It does not enumerate massive
Wilson-line or Kaluza--Klein \(X/Y\)-type modes, calculate their couplings, or bound the proton
decay operators obtained by integrating them out. Those questions belong to the heavy-spectrum
and threshold certificate.

The local executable package verifies the algebraic gates using exact rational arithmetic:
\[
\SU(3)^2\U(1)=0,\quad
\SU(2)^2\U(1)=0,\quad
\mathrm{grav}^2\U(1)=0,\quad
\U(1)^3=0.
\]
It also verifies the one-Higgs Yukawa hypercharge sums and records the \(\Z_2\)-cover generation
arithmetic
\[
|c_3(\widetilde V)|=12,\qquad |\Gamma|=2,\qquad
N_g=\frac{|c_3|}{2|\Gamma|}=3.
\]

\begin{remark}[Operator safety certificate]
Gauge invariance leaves the usual MSSM danger operators hypercharge-neutral:
\[
LH_u,\quad LLe^c,\quad LQd^c,\quad u^cd^cd^c,\quad QQQL,\quad u^cu^cd^ce^c.
\]
Bouchard, Cvetic, and Donagi computed the classical trilinear couplings for this heterotic MSSM
and report nonzero up-sector Yukawa couplings, vanishing R-parity-violating terms, and proton
stability at that trilinear level \cite{BouchardCveticDonagi2006}. The \(\ZfourR\) layer closes
the MSSM charge-algebra safety gate. A BD certificate should realize this safety layer, or an
equivalent selection rule, directly in the compactification data.
\end{remark}

\section{Threshold Proxy Audit and Moduli-Locking Target}\label{sec:bd-threshold-proxy}

The published Bouchard--Donagi calculation fixes a visible zero-mode spectrum. It does not supply
the physical vacuum point or solve the nonzero-mode problem. The source inventory contains eleven
K\"ahler moduli, eleven complex-structure moduli, and fifty-one invariant bundle moduli, but no
stabilized values or mass matrices \cite{BouchardCveticDonagi2006,BouchardDonagi2008}. The
original strongly coupled completion has a trivial hidden bundle and unbroken hidden \(E_8\);
bulk M5-branes cancel the remaining anomaly class. Perturbative hidden-bundle variants exist, so
the hidden completion is itself a branch choice \cite{BouchardDonagi2005,BouchardDonagi2008}.
None of these papers supplies a
branch-derived string scale, full heavy spectrum, threshold determinant, or low-energy spectrum
run.

The OPH low-energy target used here has no supersymmetric partner sector. The interface problem
arises because the BD compactification is \(N=1\) supersymmetric. A complete certificate must
therefore supply a decoupling map. A conventional route needs supersymmetry breaking, mediation,
and soft boundary conditions. A non-supersymmetric route would instead require a new,
independently consistent UV construction or deformation. For this BD row to pass, the
continuation must be proved OPH-equivalent to the cited BD visible-branch data, as well as
establishing worldsheet or modular consistency, anomaly cancellation, a stable vacuum, its
spectrum and couplings, and the resulting thresholds. An unrelated construction is a different
candidate, and a projection label or hash is not sufficient.

The quantities below are target-side one-loop proxies. They do not use a BD heavy spectrum,
stabilized moduli point, decoupling map, hidden-sector dynamics, mediation data, soft terms, or
spectrum-generator output. Proxy reproduction is therefore not threshold compatibility, and
\(BD_{n=1,+}^{\OPH}\) is only a named structural row; its selected-candidate gate fails. The accompanying machine-readable threshold-spectrum bundle records its
dependency provenance, cryptographic hashes, selectors, an 80-decimal-digit
arithmetic policy, scheme status, and the fail-closed gate result.

From reference-side coordinates, including candidate-only Higgs/top inputs, the proxy computes
\begin{longtable}{p{0.44\linewidth}p{0.44\linewidth}}
\toprule
\textbf{Quantity} & \textbf{Proxy coordinate from declared inputs} \\
\midrule
Tree-level top coordinate & \(y_t^{\rm tree}=0.987745211164\) \\
Tree-level Higgs quartic coordinate & \(\lambda_H^{\rm tree}=0.128706603202\) \\
MSSM tree-level quartic ceiling & \(\lambda_{\rm MSSM,max}=0.068973725409\) \\
Large-\(\tan\beta\) algebraic quartic gap & \(\Delta\lambda_{\rm proxy}=0.059732877792\) \\
Tree-level Higgs mass proxy ceiling & \(m_{h,\rm tree}^{\rm max}=91.652460286\,\mathrm{GeV}\) \\
\bottomrule
\end{longtable}

Equivalently, the tree-level coordinates are
\[
y_t^{\rm tree}=0.987745211164,
\qquad
\lambda_H^{\rm tree}=0.128706603202,
\]
with the MSSM tree-level quartic ceiling
\[
\lambda_{\rm MSSM,max}
=\frac{\pi}{2}\bigl(\alpha_2(m_Z)+\alpha_Y(m_Z)\bigr)
=0.068973725409,
\]
and the corresponding algebraic gap is
\[
\Delta\lambda_{\rm proxy}=0.059732877792.
\]
The displayed \(y_t^{\rm tree}\) is likewise the algebraic pole-coordinate conversion
\(\sqrt2m_t/v\), not a running Yukawa in a common scheme. The quartic subtraction mixes declared
surface or pole coordinates with a tree-level MSSM expression and does not define a running
quartic in a common renormalization scheme.

\subsection{One-loop stop proxy for the conventional breaking route}

Using
\[
\Delta m_h^2
\simeq
\frac{3m_t^4}{2\pi^2v^2}
\left[
\log\frac{M_S^2}{m_t^2}
+
\frac{X_t^2}{M_S^2}
\left(
1-\frac{X_t^2}{12M_S^2}
\right)
\right],
\]
and the tree-level electroweak ceiling above, the frozen proxy gives:
\begin{longtable}{c c r}
\toprule
\(\tan\beta\) & \(X_t/M_S\) & \(M_S\) proxy target \\
\midrule
2 & \(0\) & \(3046.266\,\mathrm{GeV}\)\\
2 & \(\sqrt6\) & \(679.714\,\mathrm{GeV}\)\\
5 & \(0\) & \(1191.830\,\mathrm{GeV}\)\\
5 & \(\sqrt6\) & \(265.933\,\mathrm{GeV}\)\\
10 & \(0\) & \(968.658\,\mathrm{GeV}\)\\
10 & \(\sqrt6\) & \(216.137\,\mathrm{GeV}\)\\
50 & \(0\) & \(901.608\,\mathrm{GeV}\)\\
50 & \(\sqrt6\) & \(201.176\,\mathrm{GeV}\)\\
\bottomrule
\end{longtable}
These rows invert a leading one-loop formula. They do not determine \(\tan\beta\), \(M_S\), or
\(X_t\) from the BD branch, and some rows have too little scale separation for a controlled
leading-log interpretation. If the conventional breaking route is chosen, a full soft-term and
spectrum calculation must test them in one running scheme. A non-supersymmetric alternative must
derive its own masses and decoupling thresholds within the independently consistent construction.

\subsection{Gauge-unification proxy}

A one-loop SM/MSSM running proxy with \(M_{\rm SUSY}=1\,\mathrm{TeV}\) and
\(\alpha_1=(5/3)\alpha_Y\) gives
\[
\log_{10}(M_U/\mathrm{GeV})=16.0815807506,
\]
\[
M_U=1.20665\times10^{16}\,\mathrm{GeV},
\qquad
\alpha_U^{-1}=26.0176813615,
\]
\[
\alpha_3^{\rm pred}(m_Z)=0.111511308019.
\]
The symbols \(\alpha_U\) and \(M_U\) here name the one-loop running-unification proxy
coordinates of this subsection; they are different objects from the finite-screen unified
gauge width \(\alpha_U(P)\) of the fine-structure paper and the capacity-bridge \(\alpha_U\)
of the compact paper, which carry the same symbols with different values.
Against the PDG 2025 comparison value
\(\alpha_s(m_Z)=0.1180\pm0.0009\) \cite{PDG2025QCD}, the residual inverse-coupling combination is
\[
\mathcal C_3^{\rm proxy}=-0.493124115142,
\]
with the reference-only interval
\[
-0.557271454453
\leq
\mathcal C_3^{\rm proxy}
\leq
-0.427990736457.
\]
Here the declared matching convention is
\[
\mathcal C_3^{\rm proxy}
=
\alpha_s(m_Z)^{-1}-\bigl[\alpha_3^{\rm pred}(m_Z)\bigr]^{-1}
\]
after the one-loop SM/MSSM step running. This is not a computed BD string/GUT threshold.
Scanning the arbitrary common \(M_{\rm SUSY}\) step from
\(0.5\) to \(10\,\mathrm{TeV}\) moves the central residual from about \(-0.3434\) to
\(-0.9905\). A heavy spectrum and a fixed matching prescription are needed before a physical
threshold corridor exists.

\subsection{Encoded candidate sieve}

The threshold-proxy audit scores representative branches against the encoded structural gates. The
threshold and moduli gates are certificate gates, not part of this finite structural score:
\begin{longtable}{p{0.46\linewidth}c p{0.33\linewidth}}
\toprule
\textbf{Candidate} & \textbf{Score} & \textbf{Verdict} \\
\midrule
\(BD_{n=0}^{\SU(5),\Z_2}\) & \(7/9\) & Rejected: no Higgs pair. \\
\(BD_{n=1}^{\SU(5),\Z_2}\) & \(8/9\) & Geometric witness; safety layer absent. \\
\(BD_{n=1,+}^{\SU(5),\Z_2}\) & \(9/9\) & Selected inside the nine structural gates only;
not an OPH-correct witness. \\
\(BD_{n=2}^{\SU(5),\Z_2}\) & \(7/9\) & Fails the zero-mode minimality score. \\
BHOP \(\SU(4),\Z_3\times\Z_3\) & \(4/9\) & Backup witness. \\
Generic \(\mathrm{Spin}(32)/\Z_2\) heterotic & \(0/9\) & Rejected as minimal class. \\
\bottomrule
\end{longtable}
Inside this encoded structural audit, \(BD_{n=1}^{\SU(5),\Z_2}\) is the geometric
zero-mode row and \(BD_{n=1,+}^{\SU(5),\Z_2}\) is the unique structural full-score row.
The score excludes the threshold and moduli gates and therefore cannot select an OPH-correct
string witness. Corollary~\ref{cor:bd-selection-status} records the fail-closed verdict.

\begin{theorem}[Encoded structural-only audit uniqueness]
Let \(\mathcal C_{\rm audit}\) be the six-branch candidate family in the table above, scored
against the nine encoded structural gates. The unique full-score row in
\(\mathcal C_{\rm audit}\) is \(BD_{n=1,+}^{\SU(5),\Z_2}\). No threshold, moduli, or
low-energy passage follows from this finite score.
\end{theorem}

\begin{proof}
The table assigns scores \(7/9,8/9,9/9,7/9,4/9,0/9\) to the six listed candidates. The only score
equal to the structural gate count is the \(BD_{n=1,+}^{\SU(5),\Z_2}\) row. The full-score
structural set inside \(\mathcal C_{\rm audit}\) is the singleton
\[
\{BD_{n=1,+}^{\SU(5),\Z_2}\}.
\]
\end{proof}

These proxy numbers define a target-side screen for a full cohomology, Yukawa, heavy-spectrum,
threshold, and decoupling computation. The conventional MSSM route requires supersymmetry
breaking and soft boundary conditions. A non-supersymmetric route could rehabilitate this BD row
only if it is an independently consistent, OPH-equivalent deformation or continuation that
preserves the cited BD visible-branch data; an unrelated construction is a different candidate.
Cohomology algorithms such as
cohomCalg-style line-bundle
cohomology are designed for massless-mode calculations in compactifications
\cite{BlumenhagenJurkeRahnRoschy2010}. Spectrum tools such as SOFTSUSY solve MSSM
renormalization-group equations with supplied conventional breaking constraints
\cite{Allanach2001}; citing such a tool is not evidence that a BD spectrum run occurred.

\section{Physical Moduli Slice and Rank/Isolation Certificate}
\label{sec:bd-rank-certificate}

The moduli gate must begin with a source space. Quotienting by the kernel of a short observable
list would make full rank tautological, so the quotient and the target map are defined separately.

\begin{definition}[Published and completed physical BD slices]\label{def:bd-physical-slice}
Fix the BD topological and equivariant branch and its one-massless-Higgs-pair cohomology stratum.
Let \(\widetilde{\mathcal M}_{\rm pub}^{n=1}\) be the smooth published visible-sector solution
deformations satisfying Hermitian Yang--Mills, bundle stability, the fixed topological and
equivariant data, and the one-Higgs condition. Quotient only independently verified OPH-invisible
transformations:
diffeomorphism and bundle/B-field gauge orbits, bundle isomorphisms, and changes of local
representative or exact field basis. The documented pre-completion physical slice is
\[
\mathcal M_{\rm pub}^{n=1}
=
\widetilde{\mathcal M}_{\rm pub}^{n=1}/\mathcal G_{\rm pub,inv}.
\]

For an operator-safe completed branch, let \(q=(s,h,w,\theta)\) collect the dilaton,
hidden-sector, bulk-five-brane, and scheme-locked threshold/decoupling data. Given a realized
safety layer and a fixed completion route, define
\[
\mathcal M^{\rm phys}_{BD,n=1,+}
=
\left\{([m],q)\in\mathcal M_{\rm pub}^{n=1}\times\mathcal D_{\rm comp}:
\mathcal C_{\rm comp}([m],q)=0\right\}/\mathcal G_{\rm comp,inv},
\]
where \(\mathcal C_{\rm comp}=0\) contains the hidden/anomaly, safety-realization, spectrum,
threshold, vacuum, stabilization, and decoupling equations. The quotient
\(\mathcal G_{\rm comp,inv}\) contains only exact scheme or duality-presentation changes with
identical complete OPH readout. Genuine mediation or boundary parameters remain physical source
coordinates. Heavy masses and thresholds are derived on this constraint locus; benchmark values
are not independent fit coordinates.

At a smooth point \(p\), a physical slice \(S_p\) is a local representative of this quotient, and
\[
T_{[p]}\mathcal M^{\rm phys}_{BD,n=1,+}
\cong
\frac{\ker D\mathcal C_{\rm comp}(p)}
{T_p(\mathcal G_{\rm comp,inv}\!\cdot p)}.
\]
Its real dimension \(d_p\) is part of the completion certificate. It cannot be inferred from the
ambient published-moduli count because stabilization and vacuum equations can remove tangent
directions. A physical modulus is not put in either invisible quotient merely because the frozen
target packet omits its observable effects.
\end{definition}

\begin{definition}[Constraint-augmented BD selector map]
\label{def:bd-augmented-map}
Let \(\mathcal X_{BD,n=1,+}\) be a local quotient chart for
\(\mathcal M_{\rm pub}^{n=1}\times\mathcal D_{\rm comp}\) after removing only the certified
presentation redundancies, but before imposing \(\mathcal C_{\rm comp}=0\). Once the physical
forward calculation exists, define
\[
\mathcal H_{BD,n=1,+}
=
\left(
\mathcal C_{\rm comp},
\calF_{BD,n=1,+}-\calO_{\OPH}
\right).
\]
The completion rows include stationarity and all branch-consistency equations. The target rows are
observer-visible quantities fixed independently of the candidate. Discrete topology, criticality,
cohomology, and operator-safety gates remain separate Boolean certificates. A positive local
receipt may either apply Theorem~\ref{thm:row-minor-isolation} on the completed physical slice or
apply Theorem~\ref{thm:constraint-augmented-locking} directly to this ambient quotient chart.
Theorem~\ref{thm:interval-locking} supplies the stronger existence-and-uniqueness form.
\end{definition}

\begin{proposition}[Ambient one-Higgs normal dimension and conditional pullback rank]
\label{prop:bd-one-higgs-rank}
For the invariant BD extension data, the Higgs cohomology is controlled by the negative block
\(M_-:\mathbb C^8\to\mathbb C^9\), with
\[
n=1\quad\Longleftrightarrow\quad \operatorname{rank}M_-=7
\]
while the positive \(9\times9\) block remains full rank. At a rank-seven matrix, the ambient
determinantal normal space is
\[
\operatorname{Hom}(\ker M_-,\operatorname{coker}M_-),
\qquad
\dim_{\mathbb C}=1\cdot2=2.
\]
If the cited BD pullback is scheme-theoretically regular and transverse at a chosen point, its
local defining map has exact transverse complex rank two. The published codimension count and
smooth reduced-locus description do not by themselves prove this differential statement. A
positive pullback-rank receipt must supply local extension coordinates, the entries of \(M_-\),
two local defining equations, and a nonzero exact or interval-certified \(2\times2\) Jacobian
minor. Under that receipt, the two normal extension directions are OPH-visible branch-exit
directions: leaving the locus changes the one-massless-Higgs-pair data.
\end{proposition}

\begin{proof}
At rank seven, \(\dim_{\mathbb C}\ker M_-=8-7=1\) and
\(\dim_{\mathbb C}\operatorname{coker}M_-=9-7=2\). The standard tangent space to a fixed-rank
matrix stratum consists of perturbations \(\delta M\) for which the induced map
\(\ker M_-\to\operatorname{coker}M_-\) vanishes. The quotient by that tangent space is therefore
the displayed two-complex-dimensional Hom space. Ambient rank alone does not prove transversality
of the extension-moduli pullback. Equal codimension also does not exclude a nonreduced pullback
whose derivative loses rank. Surjectivity of the induced normal map is exactly the additional
hypothesis that yields transverse complex rank two. The cited calculations give the one-Higgs
codimension and identify the two relevant normal modulus couplings
\cite{BouchardDonagi2005,BouchardCveticDonagi2006}; the machine packet does not contain the local
map entries needed to verify the additional hypothesis.
\end{proof}

The exact invariant bundle-moduli count is \(51\) complex dimensions. Restricting to the smooth
codimension-two one-Higgs locus leaves \(49=42+4+3\) complex tangent directions: forty-two
extension tangents and seven constituent-bundle deformations. Together with eleven complexified
K\"ahler and eleven complex-structure moduli, the documented pre-completion source slice is
\[
\dim_{\mathbb C}\mathcal M_{\rm pub}^{n=1}
=11+11+(51-2)=71,
\qquad
\dim_{\mathbb R}\mathcal M_{\rm pub}^{n=1}=142.
\]
The \(\ZfourR\) label is discrete and adds no tangent direction. At a singular point of the
determinantal locus the Zariski tangent dimension can be larger. The displayed \(142\) is not a
lower bound for \(\dim_{\mathbb R}\mathcal M^{\rm phys}_{BD,n=1,+}\): completion variables can
add ambient coordinates, while independent stabilization and vacuum equations can cut them.

\begin{definition}[Coordinate-locked BD comparison map]\label{def:bd-target-map}
Separate the discrete structural target from the differentiable target. The global group,
generation count, hypercharge lattice, Higgs count, exotic-matter exclusion, and safety rule define
the allowed stratum; locally constant discrete gates do not supply rows of a Jacobian. On a
physical slice and a completed threshold receipt define
\[
\begin{split}
\calF_{BD,n=1}\equiv\calF_{BD,n=1,+}:
\mathcal M^{\rm phys}_{BD,n=1,+}&\longrightarrow\mathbb R^5,\\
[m,\theta]&\longmapsto
\left(
\alpha_2^{BD}(m_Z),
\alpha_Y^{BD}(m_Z),
\frac{v^{BD}}{\mathrm{GeV}},
\frac{m_H^{BD,\mathrm{pole}}}{\mathrm{GeV}},
\frac{m_t^{BD,\mathrm{pole}}}{\mathrm{GeV}}
\right),
\end{split}
\]
with \(\alpha_2\) and \(\alpha_Y\) evaluated in their declared running scheme and at their
declared scale, \(v\) in its declared normalization, and \(m_H,m_t\) as declared pole
coordinates. The packet does not fix a common threshold scheme, so this is a comparison contract
rather than an executable physical map. Its ordered comparison vector is
\[
\calO_{\OPH,\mathrm{cmp}}^{(5)}=
\begin{pmatrix}
0.03377843630219015\\
0.010131601067241624\\
246.76711732749683\\
125.1995304097179\\
172.3523553288312
\end{pmatrix}.
\]
The first three entries are declared OPH surface coordinates. The last two are explicitly
candidate-only, not promoted OPH predictions, so the displayed vector is not a complete OPH
target. The compare-only \(\alpha_3(m_Z)\) and \(m_Z\) inputs are not additional target rows. A physical
\(\calF_{BD,n=1,+}\) exists only after the same branch supplies the hidden/nonzero-mode
spectrum, normalized Yukawas, matching scales and scheme, and decoupling map. Genuine mediation
or boundary parameters are physical source coordinates; convention-only scheme coordinates are
quotiented.
\end{definition}

\begin{definition}[Admissible target-rank row]
A row may contribute to the target-rank certificate only when its observable definition, units,
scheme, scale, acceptance region, and claim status are frozen independently of the candidate
evaluation. The row must be observer-visible and source-derived. A candidate benchmark, fitted
nuisance coordinate, or target value copied from the evaluated point is not an OPH target row.
Physical mediation and boundary parameters remain source coordinates. The evaluator freezes and
hashes the source model before it loads the target registry.
\end{definition}

\begin{lemma}[No self-targeting rank certificate]
Appending candidate coordinates to a readout and assigning their values at a chosen point can
manufacture full rank at any regular point. Such rows provide no selection evidence. In
particular, the candidate-only Higgs and top coordinates in the five-row comparison packet do not
count toward an OPH target-rank certificate. They can be used as independently frozen empirical
acceptance tests, with declared covariance and scheme, but not as promoted OPH predictions unless
their status changes through a separate proof.
\end{lemma}

\begin{proof}
In local physical coordinates \(x_1,\ldots,x_d\), append the map
\(x\mapsto(x_1,\ldots,x_d)\) and choose target values \(x_i(p)\). Its derivative is the identity,
so the augmented readout has a nonsingular \(d\times d\) minor regardless of the physical theory.
Independent precommitment excludes this construction. The frozen packet classifies its Higgs and
top values as candidate-only, which gives the stated application.
\end{proof}

\begin{theorem}[Committed-corpus transverse-rank obstruction]
\label{thm:bd-rank-obstruction}
For the source and target in Definition~\ref{def:bd-target-map}, the committed corpus does not
supply the completed constraint locus, its dimension \(d_\star\), a point \(m_\star\), an
evaluable physical \(\calF_{BD,n=1,+}\) or \(\mathcal H_{BD,n=1,+}\), or either Jacobian. The only executable object is a
target-side proxy that uses no BD branch value. Pulled back to the documented published BD slice,
that proxy is constant, and hence
\[
D\calF_{\rm proxy}=0_{5\times142},
\qquad
\operatorname{rank}D\calF_{\rm proxy}=0.
\]
Its proxy target fiber contains the entire local published slice and is therefore not isolated.
Any differentiable map defined on all of \(\mathcal M_{\rm pub}^{n=1}\) with this same
five-real-coordinate codomain satisfies
\[
\operatorname{rank}D\calF\leq5<142,
\qquad
\dim\ker D\calF\geq137.
\]
These equations are a rank obstruction on the documented pre-completion slice, not a dimension
claim about an unprovided stabilized slice. A completion could cut the physical dimension to five
or fewer, but it must certify those constraints and the resulting Jacobian. No such certificate is
present, so \(BD_{n=1,+}^{\OPH}\) fails this paper's moduli-locking gate. The two-complex-dimensional
ambient normal calculation in Proposition~\ref{prop:bd-one-higgs-rank} concerns only the Higgs
multiplicity locus, and its pullback transversality is itself an open receipt. It does not change
this conclusion.
\end{theorem}

\begin{proof}
The source packet records \(51\) invariant bundle, \(11\) complex-structure, and \(11\)
complexified K\"ahler moduli, with a codimension-two one-Higgs locus. This gives the stated
\(142\)-real-dimensional published slice. The packet records no completed slice, selected point,
or physical Jacobian. The proxy receipt states that no BD branch values enter, so its pullback
factors through a point and has the displayed zero derivative. For any map from the full
published slice to \(\mathbb R^5\), elementary linear algebra gives rank at most five and
rank--nullity gives nullity at least \(142-5=137\). Neither calculation supplies the absent
completed-slice row minor required by Theorem~\ref{thm:row-minor-isolation} or the augmented
constraint certificate of Theorem~\ref{thm:constraint-augmented-locking}.
\end{proof}

The \(137\)-dimensional bound concerns maps on the full published pre-completion slice. It is not
a nullity bound after unknown completion constraints. For a nonconstant map, kernel vectors become
proved adjustable flat curves only after a constant-rank neighborhood or explicit
target-preserving family is supplied. Every retained published direction is an actual flat
direction of the emitted constant proxy.

\begin{longtable}{p{0.25\linewidth}p{0.17\linewidth}p{0.46\linewidth}}
\toprule
\textbf{Direction family} & \textbf{Classification} & \textbf{Physical meaning and status} \\
\midrule
Eleven complexified K\"ahler directions & OPH-visible published moduli & Volumes and B-field
axions enter \(G_4\), gauge kinetic functions, KK/winding scales, and thresholds. Proxy-flat;
survival under completion constraints unresolved. \\
Eleven complex-structure directions & OPH-visible published moduli & Periods, spectra, normalized
Yukawas, and thresholds. Proxy-flat; survival under completion constraints unresolved. \\
Forty-nine complex bundle tangents to \(n=1\) & OPH-visible published moduli & Bundle cohomology,
singlet couplings, Yukawas, operator rules, and heavy/vectorlike masses. Proxy-flat; survival under
completion constraints unresolved. \\
Two complex ambient bundle normals & OPH-visible branch-exit candidates & The determinantal
normal space has complex dimension two. Pullback transversality requires the local Jacobian
receipt. Under that receipt, moving normally changes the Higgs/lepton mass pairing. \\
Dilaton, hidden/M5, and decoupling sectors & OPH-visible completion data, uncounted & Their
variables and constraint equations are missing, so their net effect on the completed-slice
dimension is unknown. \\
Gauge, diffeomorphism, bundle-isomorphism, exact basis/scheme, and proved duality directions &
OPH-invisible & Presentation redundancies are quotiented; they do not rescue the rank count. \\
\bottomrule
\end{longtable}

\begin{corollary}[Fail-closed scope of the rank certificate]
The issue-369 receipt assigns failed operator-safe selected-candidate and passing-witness status to
\(BD_{n=1,+}^{\OPH}\) because the emitted proxy has rank zero on the documented slice and no
completed-slice rank or isolation receipt exists. This certificate does not exclude a completion
whose proved constraints leave a smaller physical slice; such a completion is absent from the
candidate packet. The cited BD one-Higgs zero-mode construction remains a structural benchmark.
The independently stated OPH recovered core is a separate claim tier. A positive certificate
requires the completion equations, their stability domain, a selected physical point, a derived
threshold/decoupling map with precommitted rows, and either the completed-slice certificate of
Theorem~\ref{thm:row-minor-isolation} or the constraint-augmented certificate of
Theorem~\ref{thm:constraint-augmented-locking}. Existence and uniqueness in a numerical box require
Theorem~\ref{thm:interval-locking}; a floating-point matrix-rank call alone is not a proof.
\end{corollary}

\section{Conditional BD Witness Certificate Criterion}

The strongest mathematically clean promotion statement has certificate form. It separates what the
paper proves by algebra from what a complete BD branch must certify. The negative rank
certificate is emitted in Section~\ref{sec:bd-rank-certificate}; the required positive witness
package is not. No global uniqueness statement follows without a complete comparison catalogue.

\begin{theorem}[Conditional OPH BD witness implication]
Assume the following data.
\begin{enumerate}[leftmargin=2em]
\item The OPH recovered-core target is
\[
\mathfrak S_{\OPH}=
\left(
\begin{gathered}
(\SU(3)\times\SU(2)\times\U(1))/\Z_6,\quad N_c=3,\quad N_g=3,\quad Y_{\rm SM},\\
n_H=1,\quad \text{no light chiral exotics},\quad \ZfourR\text{ safety}
\end{gathered}
\right).
\]
\item The effective string continuation is read through the heterotic edge-sector branch and
satisfies the finite-carrier critical-edge certificate of Section~\ref{sec:central-charge-gate}.
\item The BD cohomology certificate realizes the massless one-Higgs, three-generation,
no-visible-exotics stratum with Wilson-line centralizer \(S(\U(3)\times\U(2))\).
\item The same branch realizes \(\ZfourR\), or an OPH-equivalent safety rule, on the visible
operator algebra.
\item A threshold/spectrum receipt supplies the nonzero-mode and hidden spectra, the dilaton and
other stabilized moduli, the bulk five-brane sector or a proof of its absence, normalized Yukawa
boundary data, physical scales, and a map that decouples the supersymmetric compactification into the non-supersymmetric
low-energy branch. For a conventional breaking route this includes mediation and soft boundary
conditions. A non-supersymmetric alternative must instead supply an independently consistent,
OPH-equivalent deformation or continuation of the BD branch, prove that it preserves the cited
visible cohomology and safety data, and compute its threshold map. An unrelated construction does
not certify the BD row.
\item There is a certified quotient chart \(\mathcal X_{BD,n=1,+}\), a complete constraint map
\(\mathcal C_{\rm comp}\), a precommitted scheme-locked target map, and a point \(m_\star\) such
that
\[
\mathcal C_{\rm comp}(m_\star)=0,
\qquad
\calF_{BD,n=1,+}(m_\star)=\calO_{\OPH}.
\]
The same receipt proves dynamical stability under Theorem~\ref{thm:dynamical-stabilization}
and gives either an exact nonsingular square minor of the augmented map in
Definition~\ref{def:bd-augmented-map}, or an interval contraction box satisfying
Theorem~\ref{thm:interval-locking}. Every row obeys the no-self-targeting rule, and every omitted
required equation follows by a certified identity or independent solution receipt.
\end{enumerate}
Then the following OPH-stable equivalence class is a passing named critical-string witness:
\[
\boxed{
\left[
BD_{n=1}^{\SU(5),\Z_2}+\ZfourR
\right]_{\OPH}
=
BD_{n=1,+}^{\OPH}.
}
\]
\end{theorem}

\begin{proof}
The recovered-core target fixes the observer-visible group, hypercharge lattice, generation
count, Higgs count, exotic-matter gate, and operator-safety gate. The heterotic edge-sector branch
and the finite-carrier critical-edge certificate place the named witness on the critical edge
route. The BD certificate supplies a nonempty \(\Z_2\)-quotient \(\SU(5)\)-bundle witness with the
required three-generation, no-exotics, one-Higgs massless cohomology. The centralizer and quotient theorems identify
its Wilson-line centralizer with the OPH global Standard Model group. The \(\ZfourR\) safety
layer closes the visible operator algebra gate. The threshold/spectrum and decoupling hypothesis
supplies the physical map from that supersymmetric zero-mode branch to the OPH target. The
stability receipt gives a physical vacuum, while the augmented exact or interval certificate
isolates \(m_\star\) modulo independently verified OPH-invisible equivalence. Therefore the named class
\[
\left[
BD_{n=1}^{\SU(5),\Z_2}+\ZfourR
\right]_{\OPH}
\]
satisfies the OPH-correct witness gates.
\end{proof}

\begin{remark}[Certificate boundary]
The theorem gives the witness proof shape. Its algebraic steps close in this paper. The critical-edge
receipt table, cohomology table, \(\ZfourR\)-realization table, Yukawa/superpotential table,
heavy-spectrum and decoupling table, threshold table, stability table, and augmented interval-isolation table would
form the external positive witness package. That package is not emitted here; the emitted issue-369
receipt is a rank obstruction and failure-scope certificate. A comparison table over an exhaustive
candidate class is an additional requirement after an existence row passes.
\end{remark}

\begin{theorem}[Tiered certificate closure criterion]
A named local BD witness passes only when critical-edge closure, cohomology, \(\ZfourR\)
realization, superpotential safety, threshold and low-energy matching, completed-slice stability,
and augmented local isolation all pass. Branch-global uniqueness additionally requires a validated
cover of every chart, boundary, singular stratum, discrete completion, and noncompact end of that
BD branch. The class-restricted equality
\[
\{\mathcal T\in\mathcal C:\mathcal T\text{ is OPH-correct}\}/\Teq=\{BD_{n=1,+}^{\OPH}\}
\]
additionally requires exhaustive catalogue coverage, duality deduplication, one replayed verdict
for every equivalence class, exactly one passing class, and no inconclusive class. A claim beyond
\(\mathcal C\) requires a separate theorem that the declared candidate universe is covered by
\(\mathcal C/\Teq\).
\end{theorem}

\begin{proof}
The first conjunction is exactly the local witness definition and the local existence-and-isolation
theorems. A validated branch cover excludes any second solution on the same declared branch. The
catalogue ledger then computes the exact set of passing equivalence classes because every row is
covered and none is inconclusive. Singleton membership gives the class-restricted equality. The
last conclusion follows only when the coverage theorem maps every candidate in the wider declared
universe into that catalogue.
\end{proof}

\begin{remark}[Closure status]
The issue-369 certificate fails the moduli-locking gate for the present five-coordinate contract.
Thus the closure criterion is not satisfied by the BD row in the committed corpus; comparative
uniqueness cannot promote a row that fails an existence gate.
\end{remark}

\section{Empirical Test Surface}

The BD structural row is useful because its structural claims and assigned proxy targets can fail. The
table keeps those two classes separate. Published zero-mode results test the visible massless
branch. Numerical rows define screens for the required heavy-spectrum and low-energy calculation,
which is not emitted here; they are not realized BD predictions.

\begin{longtable}{p{0.29\linewidth}p{0.37\linewidth}p{0.24\linewidth}}
\toprule
\textbf{Structural claim or proxy screen} & \textbf{Numerical or structural target} & \textbf{Failure meaning} \\
\midrule
Global Standard Model group &
\((\SU(3)\times\SU(2)\times\U(1))/\Z_6\). & Retracts the named visible branch. \\
Color and generations & \(N_c=3\), \(N_g=3\), with
\(|c_3(\widetilde V)|=12\), \(|\Gamma|=2\). & Retracts the BD witness. \\
Higgs sector & One massless Higgs pair in the published cohomology; its decoupling to the
observed light Higgs requires a separate map. & Extra massless pairs retract the selected
zero-mode stratum; a failed decoupling map blocks low-energy passage. \\
Visible exotics & No massless visible chiral exotics in the published cohomology. & Retracts the
minimal zero-mode branch. \\
Visible gauge factors & No extra visible low-scale \(\U(1)\). & Severe pressure on the
normal-form sieve. \\
Connected unified-gauge adjoint & No mixed \((3,2,\pm5/6)\) generator in the connected
product-group adjoint. & A mixed generator conflicts with the product-group
branch; connection dynamics and BD particle modes require separate audits. \\
Operator safety & \(\ZfourR\) permits Yukawas and the Weinberg operator, forbids perturbative
RPV, dimension-five proton decay, and the perturbative \(\mu\)-term, and leaves matter parity
after nonperturbative breaking \cite{LeeRabyRatzRossSchierenSchmidtHobergVaudrevange2010}. &
Safety certificate fails if the BD branch lacks this layer or an equivalent rule. \\
Classical RPV trilinears & BCD report vanishing R-parity-violating trilinears at the classical
level in this heterotic MSSM \cite{BouchardCveticDonagi2006}. Worldsheet-instanton corrections
remain outside that result. & Classical superpotential audit failure. \\
Tree-level top coordinate & \(y_t^{\rm tree}=0.987745211164\). & A completed forward spectrum
misses the assigned proxy screen; no failure is inferred from the proxy alone. \\
Tree-level Higgs coordinate & \(\lambda_H^{\rm tree}=0.128706603202\). & A completed
same-scheme calculation misses the assigned proxy screen. \\
Algebraic quartic gap & \(\Delta\lambda_{\rm proxy}=0.059732877792\). & A conventional
breaking calculation fails this proxy screen; the row is not a heavy-spectrum certificate. \\
Stop proxy & The table gives \(M_S\) values for representative
\((\tan\beta,X_t/M_S)\) choices. & Conventional-route soft terms miss the proxy screen. A
BD-equivalent non-supersymmetric deformation has its own mass and threshold calculation. \\
One-loop gauge residual & At \(M_{\rm SUSY}=1\,\mathrm{TeV}\),
\(\mathcal C_3^{\rm proxy}=-0.493124115142\), with the reference-only interval shown in
Section~\ref{sec:bd-threshold-proxy}. & A supplied heavy-threshold combination misses the proxy
screen; the residual itself is not a BD string threshold. \\
\bottomrule
\end{longtable}

The published branch supplies a narrow massless visible package. This paper assigns numerical
screens. The threshold/spectrum certificate is not emitted here; no threshold corridor is
established
for the BD row. The displayed five-coordinate contract is
\[
\calF_{BD,n=1,+}(m_\star)=\calO_{\OPH,\mathrm{cmp}}^{(5)},
\]
but no \(m_\star\) or physical forward map is supplied, and Theorem~\ref{thm:bd-rank-obstruction}
proves that this five-row contract cannot meet the constraint-augmented locking gate on the
documented slice without additional certified completion constraints.

\section{Claim Gates}\label{sec:claim-gates}

The computation package reduces the full string-model task to explicit inputs. The gate table is
the working contract for an independent heterotic reproduction:

\begin{longtable}{p{0.25\linewidth}p{0.36\linewidth}p{0.29\linewidth}}
\toprule
\textbf{Gate} & \textbf{Needed input} & \textbf{State of the paper claim} \\
\midrule
Central-charge and supercurrent certificate & Response-map rank
\(\operatorname{rank}\calR_{\rm port}=12\), positive \(A_5\times C_2\) covariance sectors, edge
transfer OPEs, local graded half-repair \(Q_N^2\to H_R\), and torus/spin-structure receipt. &
Non-implication theorem and finite critical-edge certificate theorem stated; carrier receipts not
emitted here. \\
Cohomology certificate & Explicit \(X\), \(V\), and equivariant \(\Z_2\) action in
cohomCalg, Sage, or Macaulay2 form. & Structural witness cited; raw computation not emitted here. \\
Safety-layer realization certificate & \(\ZfourR\), or an equivalent compactification selection rule,
realized on the BD one-Higgs branch. & MSSM charge algebra closes; BD realization certificate not emitted here. \\
Operator and superpotential certificate & Sheaf cup products, harmonic representatives, instanton
data, and sector selection rules. & BCD trilinear result supports RPV vanishing; numeric
textures not emitted here. \\
Threshold and spectrum certificate & Nonzero-mode and hidden spectra; stabilized K\"ahler,
complex-structure, bundle, dilaton, and any bulk five-brane data; normalized Yukawa boundary
data; string, compactification, and matching scales; and a low-energy decoupling map. A conventional breaking route also requires mediation and soft
boundary conditions. A non-supersymmetric alternative requires an independently consistent UV
construction or deformation and its own mass and threshold calculation. & \textbf{Not emitted
here:} proxy coordinates reproduce, but compatibility is not evaluated. No heavy-threshold or
low-energy spectrum certificate is present. \\
Vacuum-stability certificate & Complete effective potential, stationary point, physical scalar
metric and Hessian, control bounds, and a positive mass or route-appropriate stability enclosure. &
No BD stability receipt is emitted. \\
Moduli-locking certificate & Physical quotient, precommitted scheme-locked map, completed
constraints, selected point, and a certified augmented Jacobian and interval-isolation box. &
Negative issue-369 receipt emitted: the published pre-completion source has dimension \(142\)
real, its five-row proxy has rank zero, and the completed source, point, and Jacobian are absent.
Selected-candidate status fails. \\
Comparative uniqueness certificate & Branch-domain coverage, expanded heterotic edge-sector
audit, and any brane, orientifold, or duality-rewritten presentations claiming OPH equivalence. &
The encoded audit has one structural full-score row. It is not a selection or catalogue-coverage
certificate. \\
\bottomrule
\end{longtable}

The threshold/spectrum receipt is open, and the moduli-locking receipt fails closed.
Accordingly \(BD_{n=1,+}^{\OPH}\) is retained only as the full-score row of the declared
structural audit. It is neither the selected operator-safe string candidate nor a passing
OPH-correct witness.

\section{Falsifier Matrix}

\begin{longtable}{p{0.32\linewidth}p{0.60\linewidth}}
\toprule
\textbf{Failure mode} & \textbf{Consequence} \\
\midrule
Wrong global Standard Model group & Retracts the OPH visible landing branch. \\
Wrong hypercharge lattice & Retracts the named visible branch. \\
Fourth chiral generation & Retracts the realized branch. \\
Light chiral exotics & Retracts the BD one-Higgs witness. \\
Irreducible second light Higgs pair & Retracts the one-Higgs low-energy projection. \\
Extra visible low-scale \(\U(1)\) & Severe pressure on the OPH normal-form sieve. \\
Mixed connected-adjoint \(X/Y\) generator & Conflicts with the connected product-group branch. \\
Massive BD \(X/Y\)-type modes or induced operators & Evaluated by the heavy-spectrum and
coupling certificate; the zero-mode adjoint theorem does not decide them. \\
BD cohomology reproduction fails & Retracts \(BD_{n=1}^{\OPH}\) as named geometric witness. \\
\(\ZfourR\) or equivalent safety layer absent & Retracts \(BD_{n=1,+}^{\OPH}\) as
an operator-safe proposal. \\
Dangerous operators survive without suppression & Severe pressure on the effective theory. \\
No moduli point matches \(\calO_{\OPH}\) & Retracts the operator-safe selected candidate. \\
Constraint-augmented locking certificate fails or physical directions remain unclassified & Retracts the
operator-safe selected candidate; the structural BD row and recovered OPH core remain separate. \\
Central-charge or supercurrent gate fails & Retracts the heterotic critical-worldsheet
identification of the sewn edge branch. \\
Critical-string lift fails & Weakens the string continuation; the OPH recovered core is a separate claim tier. \\
\bottomrule
\end{longtable}

\section{Proof Stack for De Sitter and String Theory}

The most persuasive route is compact:
\begin{enumerate}[leftmargin=2em]
\item prove the finite observer theorem as stable checkpoint continuation;
\item prove the clock-projection correlator theorem in finite dimension;
\item prove \(T\)-holonomy as a \(\Z_2^T\) cycle obstruction and \(w_1(L_T)\) class;
\item prove record-branch time-reversal breaking on the observer quotient;
\item derive \(S_{\rm dS}=A/(4\ell_P^2)=N_{\rm scr}\) as edge-center record capacity;
\item derive \(Z_{\rm edge}(t)=K_t(1)\) and the large-\(N_{\rm edge}\) worldsheet branch;
\item prove the heterotic edge-polarization theorem for the sewn-edge scaling limit, including
OPEs, fermionic grading, spin structures, and no residual coset;
\item prove the OPH vacuum sieve, global group lock, \(\ZfourR\) safety table, connected-adjoint
theorem, and moduli-locking criterion;
\item reproduce the Bouchard-Donagi \(n=1\) cohomology, \(\ZfourR\) realization, and operator
catalogue;
\item freeze the nonzero-mode and hidden spectra, all physical moduli and scales, either a
conventional SUSY-breaking decoupling route or an independently consistent OPH-equivalent
non-supersymmetric deformation with its own mass and threshold calculation, the low-energy forward calculation, threshold matching,
repository-relative source paths and hashes, and numerical precision; then evaluate the completed
constraint map, physical Hessian, target map, augmented Jacobian, and interval-isolation box.
\end{enumerate}

The first two items target the de Sitter observer and time-reversal program. The last four items
target the string community's demand for a reproducible critical-worldsheet and vacuum selector.


\section{Problem-to-Gate Map for De Sitter and String Theory}

The paper reduces the program to a finite observer-visible normal-form problem for critical strings.
In that form, many familiar unresolved questions become gates with explicit pass/fail certificates.

\begin{longtable}{p{0.27\linewidth}p{0.43\linewidth}p{0.20\linewidth}}
\toprule
\textbf{Problem} & \textbf{OPH resolution} & \textbf{Certificate gate} \\
\midrule
What is the physical observer in de Sitter? & A stable record-bearing patch subfederation with
checkpoint continuation. & Record/collar model. \\
Why does a clock branch appear? & Clock time is a record-sector projection; imaginary
semiclassical correlators appear after branch conditioning. & Observer-sector examples. \\
What is the clock-flip holonomy? & A \(\Z_2^T\) cycle obstruction on the overlap nerve,
\(w_1(L_T)\). & Geometric examples. \\
Where is de Sitter entropy? & Edge-center record capacity,
\(S_{\rm dS}=A/(4\ell_P^2)=N_{\rm scr}\). & Capacity normalization. \\
Why do strings appear? & Sewn OPH edge partitions are heat-kernel sums; the controlled
large-edge continuation is a worldsheet expansion. & Large-edge control. \\
Which string theory passes the OPH selector? & None in the present certificate set.
\(BD_{n=1,+}^{\OPH}\) is the structural test row with failed selection status: its proxy has rank
zero and its completed physical slice and Jacobian are absent. & Critical-edge, cohomology, safety,
threshold/spectrum, decoupling, and moduli certificates. \\
Why anthropic landscape selection is absent & OPH provides a target normal form
\(\Pi_{\rm IR}^{\OPH}(\mathcal T)=\mathfrak S_{\OPH}\), with no statistical sampling weight. & Exhaustive audits. \\
Why the exact SM global group? & Wilson-line centralizer and OPH quotient both give
\((\SU(3)\times\SU(2)\times\U(1))/\Z_6\). & Algebraic proof in paper. \\
Why no connected simple-GUT \(X/Y\) generator? & The connected product-group adjoint has no
\((3,2,\pm5/6)\) generator. Connection dynamics, BD particle modes, and induced operators remain
in their action and heavy-spectrum gates. & Algebraic adjoint proof plus action/heavy-mode certificates. \\
How is the \(\mu\)-problem controlled? & The \(\ZfourR\) safety layer forbids perturbative
\(H_uH_d\) and allows nonperturbative generation. & Compactification realization. \\
How are moduli claims tested? & Dynamical stabilization requires stationarity and a physical
Hessian bound. Target locking separately requires a precommitted augmented residual map and an
exact or interval-certified isolation receipt. The proxy has rank zero on the \(142\)-real-dimensional
published pre-completion slice; no completed constraint map, stability certificate, or augmented
rank is supplied. & Negative issue-369 rank/isolation certificate plus open stability gate. \\
What is the string graviton? & A BRST-physical closed-string vertex with a positive-residue
massless pole whose classical limit is the OPH transverse-traceless metric perturbation. &
Quantum-particle receipt plus normalization match. \\
What fixes the critical dimension? & The critical-edge certificate must identify the sewn-edge carrier
with the heterotic edge VOA; then heterotic criticality gives \(D=10\) and
\(c_{\rm internal}=16\). & Edge transfer, OPE, grading, spin-structure, and no-coset receipts. \\
\bottomrule
\end{longtable}

\begin{theorem}[De Sitter/string compression theorem]
On the OPH-correct branch, the de Sitter observer problem, the time-reversal clock-branch
problem, the entropy-location problem, and the critical-string vacuum-selection problem reduce to
one finite statement: find the observer-visible normal form of the OPH patch federation and then
lift its sewn edge sector to a critical worldsheet presentation.
\end{theorem}

\begin{proof}
The observer and clock problems are properties of record-bearing subfederations and their
\(\Z_2^T\) cycle data. The entropy problem is the edge-center capacity of the same finite static
patch. The string problem is the critical completion of the sewn edge-sector partition. The OPH
normal form fixes the visible quotient data used by all four questions. The apparently separate
problems are projections of the same finite patch-federation normal-form problem.
\end{proof}

\section{Conclusion}

OPH gives a finite observer/record/overlap implementation layer for de Sitter holography. The
same edge system admits a sewn-worldsheet language. Critical string theory enters as the
effective completion of that language only after the critical-edge certificate closes. Conditional on
that gate, the OPH visible-normal-form target tests the
Bouchard--Donagi one-Higgs heterotic Standard Model as a geometric zero-mode benchmark. Adding the MSSM
\(\ZfourR\) safety layer defines the tested operator-safe proposal
\[
BD_{n=1,+}^{\OPH}=BD_{n=1}^{\OPH}+\ZfourR.
\]

The sieve itself is fully specified: every gate is named, every unemitted certificate is listed,
and the frozen target packet has no retunable target-side dial. The smooth published one-Higgs
slice has \(71\) complex pre-completion moduli. The emitted target-side proxy is constant in those
directions, and any map defined on that full slice with the frozen five-real-coordinate registry
has rank at most five. Completion constraints could reduce the physical dimension, but no such
constraint locus or Jacobian is supplied. The
threshold/spectrum certificate is open because the published BD data do not contain a
stabilized heavy spectrum or a map from the supersymmetric compactification to the
non-supersymmetric OPH low-energy branch. Therefore \(BD_{n=1,+}^{\OPH}\) is not a
selected/passing string witness and is retained only as a structural audit benchmark. The recovered
OPH core is a separate claim tier.

This status does not prove that the BD compactification is physically inconsistent. It proves that
the available data do not select it. No alternative string vacuum passes the certificate stack in
this paper. The strongest justified result is therefore an empty selected set for the emitted
catalogue receipts, with BD retained as a structural candidate. Any positive result is local until
the branch-cover theorem closes, and catalogue-relative until the candidate-universe coverage
theorem closes.

\begin{thebibliography}{99}

\bibitem{OPHObserversAllYouNeed}
B.\ M\"uller, A.\ Osika, M.\ Poneder, K.\ Xue, B.\ Cassie, P.\ Nguyen, M.\ A.\ Visser, K.\ A.\ Anirudha, D.\ Matscheko, and J.\ Hill,
\emph{Observers Are All You Need},
Observer-Patch Holography paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.tex}.

\bibitem{OPHCompactCore}
B.\ M\"uller, A.\ Osika, M.\ Poneder, K.\ Xue, P.\ Nguyen, M.\ A.\ Visser, and D.\ Matscheko,
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency},
Observer-Patch Holography compact paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.tex}.

\bibitem{OPHRealityConsensus}
B.\ M\"uller, K.\ Xue, K.\ A.\ Anirudha, D.\ Matscheko, and J.\ Hill,
\emph{Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics},
Observer-Patch Holography paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.tex}.

\bibitem{OPHScreenMicrophysics}
B.\ M\"uller, A.\ Osika, K.\ Xue, B.\ Cassie, M.\ A.\ Visser, and D.\ Matscheko,
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH},
Observer-Patch Holography paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.tex}.

\bibitem{OPHParticleZoo}
B.\ M\"uller, A.\ Osika, M.\ Poneder, K.\ Xue, M.\ A.\ Visser, and D.\ Matscheko,
\emph{Deriving the Particle Zoo from Observer Consistency},
Observer-Patch Holography paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/deriving_the_particle_zoo_from_observer_consistency.tex}.

\bibitem{OPHFineStructure}
B.\ M\"uller,
\emph{The Fine-Structure Constant as an OPH Pixel Fixed Point},
Observer-Patch Holography extra paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/fine_structure_constant_derivation.tex}.

\bibitem{OPHDarkMatter}
B.\ M\"uller and D.\ Matscheko,
\emph{Observer-Patch Holography and the Dark Matter Phenomenon},
Observer-Patch Holography cosmology paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/cosmology/oph_dark_matter_paper.tex}.

\bibitem{OPHChiNuBounds}
B.\ M\"uller, A.\ Osika, and D.\ Matscheko,
\emph{Theoretical Bounds on \(\chi_\nu\) in Observer-Patch Holography},
Observer-Patch Holography extra paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/chi_nu_susceptibility_bounds.tex}.

\bibitem{OPHYangMillsGap}
B.\ M\"uller,
\emph{Explaining the Yang-Mills Mass Gap with Observer-Patch Repair Dynamics},
Observer-Patch Holography extra paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/yang_mills_gap_clay_problem.tex}.

\bibitem{OPHThinkingPatchNet}
B.\ M\"uller,
\emph{Thinking as Patch-Net Fixed-Point Search: A Mathematical Model of Neural Consensus Computation},
Observer-Patch Holography extra paper source.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/thinking_as_patch_net_fixed_point_search.tex}.

\bibitem{DSObservers2025}
L.\ Susskind,
\emph{Why do we Need Observers? Spontaneous Breaking of Time-Reversal in de Sitter Space},
arXiv:2512.13650.

\bibitem{DSMoreObservers2026}
L.\ Susskind,
\emph{More About the Spontaneous Breaking of Time Reversal in de Sitter Space},
arXiv:2601.01666.

\bibitem{DSTimeReversal2026}
L.\ Susskind,
\emph{Is Time Reversal in de Sitter Space a Spontaneously Broken Gauge Symmetry?},
arXiv:2603.12434.

\bibitem{DSEntropy2025}
L.\ Susskind,
\emph{Where is the Entropy in DSSYK-de Sitter? Correction to a wrong claim},
arXiv:2511.10907.

\bibitem{DSMatrix2021}
L.\ Susskind,
\emph{Black Holes Hint Towards De Sitter-Matrix Theory},
arXiv:2109.01322.

\bibitem{DSScales2022}
L.\ Susskind,
\emph{De Sitter Space, Double-Scaled SYK, and the Separation of Scales in the Semiclassical Limit},
arXiv:2209.09999.

\bibitem{DSSYKQCDPaper}
Y.\ Sekino and L.\ Susskind,
\emph{Double-Scaled SYK, QCD, and the Flat Space Limit of de Sitter Space},
arXiv:2501.09423.

\bibitem{DSSYKFlatPaper}
S.\ Miyashita, Y.\ Sekino, and L.\ Susskind,
\emph{DSSYK at Infinite Temperature: The Flat-Space Limit and the 't Hooft Model},
arXiv:2506.18054.

\bibitem{PolchinskiStringVol1}
J.\ Polchinski,
\emph{String Theory, Volume 1: An Introduction to the Bosonic String},
Cambridge University Press, 1998.

\bibitem{DiFrancescoCFT}
P.\ Di Francesco, P.\ Mathieu, and D.\ Senechal,
\emph{Conformal Field Theory},
Springer, 1997.

\bibitem{BouchardDonagi2005}
V.\ Bouchard and R.\ Donagi,
\emph{An SU(5) Heterotic Standard Model},
arXiv:hep-th/0512149.

\bibitem{BouchardCveticDonagi2006}
V.\ Bouchard, M.\ Cvetic, and R.\ Donagi,
\emph{Tri-linear Couplings in an Heterotic Minimal Supersymmetric Standard Model},
arXiv:hep-th/0602096.

\bibitem{BouchardDonagi2008}
V.\ Bouchard and R.\ Donagi,
\emph{On heterotic model constraints},
JHEP 08 (2008) 060.
\url{https://doi.org/10.1088/1126-6708/2008/08/060}.

\bibitem{DonagiHeOvrutReinbacher2004}
R.\ Donagi, Y.-H.\ He, B.\ A.\ Ovrut, and R.\ Reinbacher,
\emph{The Spectra of Heterotic Standard Model Vacua},
JHEP 06 (2005) 070.
\url{https://doi.org/10.1088/1126-6708/2005/06/070}.

\bibitem{PDG2025QCD}
S.\ Navas et al.\ (Particle Data Group),
\emph{Review of Particle Physics: Quantum Chromodynamics},
Phys.\ Rev.\ D 110, 030001 (2024) and 2025 update.
\url{https://pdg.lbl.gov/2025/reviews/rpp2025-rev-qcd.pdf}.

\bibitem{LeeRabyRatzRossSchierenSchmidtHobergVaudrevange2010}
H.\ M.\ Lee, S.\ Raby, M.\ Ratz, G.\ G.\ Ross, R.\ Schieren, K.\ Schmidt-Hoberg, and
P.\ K.\ S.\ Vaudrevange,
\emph{A unique \(Z_4^R\) symmetry for the MSSM},
arXiv:1009.0905.

\bibitem{MarchesanoShiuWeigand2024}
F.\ Marchesano, G.\ Shiu, and T.\ Weigand,
\emph{The Standard Model from String Theory: What Have We Learned?},
arXiv:2401.01939.

\bibitem{DeffayetOvrutSteinhardt2024}
C.\ Deffayet, B.\ A.\ Ovrut, and P.\ J.\ Steinhardt,
\emph{Stable Vacua with Realistic Phenomenology and Cosmology in Heterotic M-theory Satisfying Swampland Conjectures},
arXiv:2401.04828.

\bibitem{FriederichLeBihan2021}
S.\ Friederich and B.\ Le Bihan,
\emph{The landscape and the multiverse: What's the problem?},
Synthese 199, 7749-7771 (2021).
\url{https://doi.org/10.1007/s11229-021-03137-0}.

\bibitem{GrimmVanDeHeisteeg2025}
T.\ W.\ Grimm and D.\ van de Heisteeg,
\emph{Exact flux vacua, symmetries, and the structure of the landscape},
JHEP 01 (2025) 005.
\url{https://doi.org/10.1007/JHEP01(2025)005}.

\bibitem{BlumenhagenJurkeRahnRoschy2010}
R.\ Blumenhagen, B.\ Jurke, T.\ Rahn, and H.\ Roschy,
\emph{Cohomology of Line Bundles: A Computational Algorithm},
arXiv:1003.5217.

\bibitem{Allanach2001}
B.\ C.\ Allanach,
\emph{SOFTSUSY: a program for calculating supersymmetric spectra},
arXiv:hep-ph/0104145.

\end{thebibliography}

\end{document}
