\section*{Physical A5/SM and W/Z status}

The finite icosahedral package is an exact conditional QFT-Q0 recognition result.
On its declared packet it gives the twelve-port representation, compact
current algebra, \(3+2\) block structure, conditional \(\mathbb Z_6\) quotient,
a rank-15 internal representation witness, a canonical rank-three candidate
screen band, and three invariant cubic tensor slots. It does not prove that
the target-free OPH source law emits the packet, attaches that band to three
physical chiral families, or supplies a chiral quantum field theory. Physical
promotion requires source-selected observer-like patches with bounded local
state, operational ports and boundaries, readback records, admissible repair
moves, and public evidence, together with the named geometry, current, Spin,
family, scalar, interaction, positivity, and refinement receipts.

The conditional field-theory implication stack is explicit. QFT-Q1 gives
an exact finite gauge-invariance/locality theorem, with the familiar
electroweak tree kernel conditional on a separate canonical
continuum/action-normalization bridge. QFT-Q2-E and QFT-Q2-H are parallel exact
finite measure and Hamiltonian criteria. QFT-Q3 is the separate formal
perturbative/BV branch and contains the strict finite-order \(W/Z\) pole
theorem. QFT-Q4 gives an observable-sector OS implication and a distinct
continued-sheet resonance-stability implication. QFT-Q2 and QFT-Q3 are
parallel descendants of QFT-Q1; neither implies the other, and a QFT-Q3 pole
does not imply QFT-Q4.

These theorems state what follows from typed packets; they do not show that
the target-free OPH source emits those packets. No source-selected QFT-Q1
action and normalization, full QFT-Q2 construction, target-clean QFT-Q3
matching/FJ/two-engine packet, independently replayed ST/Nielsen/current
amplitudes, source law and covariance, numerical uncertainty freeze,
operational clock, or QFT-Q4 tower and continued-sheet packet is present. The
current numerical fixture remains a post-exposure imported-backend regression.
No OPH-native dimensionless or physical-unit \(W/Z\) pole is promoted.

\noindent\texttt{CONDITIONAL\_QFT\_TIER\_DAG\_AND\_STRICT\_WZ\_POLE\_ALGEBRA\_DEFINED\_\_Q1\_SOURCE\_CONSTRUCTION\_Q2\_Q4\_OBJECTS\_Q3\_VALIDATION\_AND\_OPH\_PRODUCERS\_OPEN}

\noindent\texttt{DRAFT\_SUFFICIENCY\_STACK\_DEFINED\_\_SIMULATION\_RECEIPTS\_OPEN\_\_NO\_OPH\_NATIVE\_POLE\_PROMOTION}

\noindent\texttt{CONDITIONAL\_STRICT\_1L\_POLE\_MAP\_NOT\_OPH\_NATIVE\_PHYSICAL}
