\begin{definition}[Correctable public-record capacity map]
\label{def:self-closure-density}
At regulator \(r\), freeze one capacity-carrier type and set
\[
D=\dim\mathcal H_{{\rm cap},r,D},
\qquad N=\log D.
\]
Let \(\widetilde\Omega_{r,D}\) be the nonempty terminal physical quotient
fiber reachable from the source-derived trial universe \(\mathfrak U_{r,D}\),
with no capacity-equals-\(D\) membership predicate. For
\(q\in\widetilde\Omega_{r,D}\), let \(X_O(q)\) and \(X_e(q)\) be the local
and interface record-atom sets and let
\(r_{Oe}:X_O(q)\to X_e(q)\) be the source-derived atom readouts. Define
\[
X_{\rm pub}(q)=
\{(x_O)_O:r_{Oe}(x_O)=r_{O'e}(x_{O'})
\text{ on every shared interface}\}.
\]
Let \(X_{\rm reach}(q)\subseteq X_{\rm pub}(q)\) contain exactly the sections
reachable by admissible endogenous semantic histories. Freeze an authorized
publicness policy \(\mathfrak P(q)\) and a globally coupled family of joint
semantic checkpoint kernels \(\mathfrak K(q)\) whose observer marginals agree
with the local checkpoint packets.

For \(K\in\mathfrak K(q)\), let
\(S_K(x)=\{y:K(y\mid x)>0\}\). The compound confusability graph \(G_q\) on
\(X_{\rm reach}(q)\) joins \(x\ne x'\) when
\(S_K(x)\cap S_K(x')\ne\varnothing\) for at least one declared continuation.
The exact public readback is
\[
M_0(q)=\alpha(G_q).
\]
For a frozen tolerance and finite channel family or horizon, let
\(M_\varepsilon(q)\) be the largest code having worst-input decoding error at
most \(\varepsilon\) for every declared channel. The primary finite map is
set-valued:
\[
\boxed{
\mathfrak F_{r,\varepsilon}(D)=
\{M_\varepsilon(q):q\in\widetilde\Omega_{r,D}\}.
}
\]
A scalar \(\widehat F_{r,\varepsilon}(D)\) exists only when the whole
nonempty terminal fiber has one common defined value. Robust exact closure is
\[
\boxed{
\mathfrak F_{r,0}(D_\star)=\{D_\star\},
\qquad N_{\rm CRC}=\log D_\star.
}
\]
\end{definition}

\begin{theorem}[Conditional finite correctable-record closure]
\label{thm:conditional-operational-n-closure}
Under the atom-readout, reachability, publicness, global-coupling, and finite
capacity-carrier receipts of Definition~\ref{def:self-closure-density}:
\begin{enumerate}[leftmargin=2em,label=(\roman*)]
\item compatible public sections and their function algebra are finite and
natural under record-diagram isomorphism;
\item a code is zero-error correctable for every declared continuation exactly
when it is an independent set of \(G_q\), hence \(M_0(q)=\alpha(G_q)\);
\item the support-relation semigroup for all finite continuation words closes
after finitely many steps, and injective deterministic continuation gives
\(M_0(q)=|X_{\rm reach}(q)|\);
\item if corresponding channel rows are within \(\delta\) in total variation,
then \(M_{\varepsilon+\delta}(\widehat{\mathfrak K})
\ge M_\varepsilon(\mathfrak K)\);
\item nonzero orthogonal record projections on the \(D\)-dimensional capacity
carrier give \(M_\varepsilon(q)\le D\); equality at zero error forces a
rank-one complete public record basis;
\item the set-valued map scalarizes exactly when the whole terminal fiber has
one common defined readback;
\item a total monotone deflationary scalar map on a declared finite positive
dimension chain reaches its greatest fixed point by iteration from the top;
\item record injections reflecting confusability make capacity monotone under
capacity extension, and at fixed \(D\) give eventual exact stabilization
along each cofinal refinement sequence.
\end{enumerate}
\end{theorem}

\begin{proof}
Public sections satisfy finite compatibility constraints. Pairwise disjoint
channel supports are equivalent to perfect decoding, so a common code is an
independent set of the union graph. The support relations form a finite
semigroup. Total variation changes each correct-decoding event by at most
\(\delta\). The carrier bound is orthogonal-rank additivity. Scalarization is
the singleton-image criterion. The remaining statements are finite-chain and
independent-set transport arguments. Full proofs and receipt schemas are in
Ref.~\cite{ophsynthesis}.
\end{proof}

\begin{theorem}[Capacity definitions do not select a cosmic dimension]
\label{thm:capacity-protocol-nonidentifiability}
The finite implication theorem does not force a unique physical \(D\).
Identity continuation on \(D\) reachable labels gives
\(\widehat F(D)=D\) for every \(D\), while a compatible erasure family gives
\(\widehat F(D)=1\). Both are monotone and deflationary. In addition, a cyclic
permutation of \(m\) labels has a one-dimensional fixed function algebra but
correctable capacity \(m\), and arbitrarily small full-support noise collapses
zero-error capacity from \(m\) to one.
\end{theorem}

\begin{proof}
Identity and erasure give the stated support graphs. A cycle is invertible even
though only constant functions are invariant. Full-support noise makes every
pair of inputs confusable.
\end{proof}

\begin{remark}[Physical producer, scaling law, and downstream bridges]
\label{rem:self-closure-counting-target}
The exact unclosed kernel is
\[
K_r(D,m)=
|\{q\in\widetilde\Omega_{r,D}:M_0(q)=m\}|.
\]
The condition \(K_r(D,D)>0\) proves only existential closure. Robust closure
requires the whole row support to be \(\{D\}\). The large-screen uniqueness
problem is the finite-size slack
\[
\boxed{s_r(D)=\log D-\log M_{0,r}(D)}.
\]
Unit asymptotic capacity density does not locate a zero: \(M(D)=D\) and
\(M(D)=D-1\) have the same limiting density. A physical \(N\)-closure needs
an exact transfer or fiber-product recurrence, or a seam theorem with a sharp
subleading term, proving one physical zero of \(s(D)\).

After robust direct closure, \textsc{HORIZON-RECORD-SATURATION} gives
\[
N_{\rm CRC}=\log D_\star=\frac{A_{\rm dS}}{4\ell_\star^2},
\qquad
\Lambda\ell_\star^2=\frac{3\pi}{N_{\rm CRC}}.
\]
The independent \textsc{COMMON-EW-LOAD-CARRIER} receipt, together with the
screen-sieve and D10 source laws, gives
\[
R_{\rm EW}=
\alpha_U(P)\log\frac{N_{\rm CRC}}{\pi}-\frac{6\pi}{P}=0,
\qquad
N_{\rm bridge}=
\pi\exp\!\left[\frac{6\pi}{P\alpha_U(P)}\right].
\]
Neither bridge constructs \(M_0\). The operational residual
\(R_\rho=\log M_0-\pi/\rho_{\rm op}^2\) is also downstream.

The open source objects are the record-atom restrictions, endogenous
reachability, frozen publicness policy, global checkpoint coupling,
capacity-carrier representation, whole-fiber scalar producer,
no-new-confusability extension/refinement packets, finite-size slack law,
horizon-record saturation, and common screen/electroweak load carrier. QCD
and hadronic transport are not dependencies of this closure program.
\end{remark}
