\paragraph{Direct public-record closure for total capacity.}\label{sec:n-closure}
The global counterpart of the local \(P\)-closure begins with a supplied
positive integer capacity-carrier dimension
\[
D=\dim\mathcal H_{{\rm cap},r,D},
\qquad N=\log D.
\]
The official universe-level readback equation is
\[
\boxed{N=M_0(\mathfrak U_N)}.
\]
Here the argument fixes the type. For a terminal state $q$, $M_0(q)$ below
is the multiplicative code size. Once the complete terminal fiber scalarizes,
the overloaded universe-level notation means
\[
M_0(\mathfrak U_N):=\log \widehat F_{r,0}(e^N).
\]
Thus the public equation is exactly the logarithmic form of robust direct
capacity closure, not a new producer or an appeal to a measured target.
The carrier type is frozen in the branch contract. Boundary, total,
edge-center, and other Hilbert spaces are not interchangeable. Let
\(\widetilde\Omega_{r,D}\) be the terminal physical quotient fiber reached
from the source-derived trial universe \(\mathfrak U_{r,D}\). Its members are
repair-normal and pass the declared local, obstruction, and provenance gates.
Membership contains no capacity-equals-\(D\) predicate.

For \(q\in\widetilde\Omega_{r,D}\), observer \(O\) has a finite commutative
record algebra \(\mathcal R_O(q)\) with atom set
\(X_O(q)=\operatorname{At}\mathcal R_O(q)\). Each shared interface \(e\)
has an atom set \(X_e(q)\) and a source-derived record-atom readout
\[
r_{Oe}:X_O(q)\longrightarrow X_e(q).
\]
This atom-level construction is used because the generic visible maps on full
observer algebras need not be unital \(^*\)-homomorphisms in the direction
required by an algebra equalizer. The compatible public global sections are
\[
X_{\rm pub}(q)=
\left\{(x_O)_O:
r_{Oe}(x_O)=r_{O'e}(x_{O'})
\text{ on every shared interface}\right\},
\qquad
\mathcal R_{\rm pub}(q)=C(X_{\rm pub}(q)).
\]

\begin{theorem}[Public global sections]\label{thm:public-global-sections}
For every finite observer record diagram, \(X_{\rm pub}(q)\) is finite and
\(C(X_{\rm pub}(q))\) is a finite commutative unital \(C^*\)-algebra. Every
isomorphism of observer record diagrams induces a bijection of public global
sections and a \(^*\)-isomorphism of their function algebras.
\end{theorem}

\begin{proof}
The public sections form the subset of the finite product
\(\prod_OX_O(q)\) satisfying finitely many equalities. A diagram isomorphism
transports the atom sets and interface maps, hence compatible tuples
bijectively; pullback transports their function algebras.
\end{proof}

Only endogenously writable records count. Define
\[
X_{\rm reach}(q)=
\{x\in X_{\rm pub}(q):x\text{ terminates an admissible endogenous semantic history}\}.
\]
The history may use declared source data, accepted repair, semantic
continuation, and quotient-visible writes. It may not use a target record,
supplied-capacity metadata, measured \(\Lambda\), or the electroweak bridge.
The publicness policy is a frozen nonempty family
\[
\mathfrak P(q)\subseteq2^{\mathcal O(q)}\setminus\{\varnothing\}
\]
of authorized observer subsets. Collective, universal-local, and quorum
publicness are distinct theorem branches.

For every \(x\in X_{\rm reach}(q)\), authorized set
\(A\in\mathfrak P(q)\), and allowed same-interface semantic continuation
\(\kappa\), the source construction must emit a joint stochastic kernel
\[
K_{A,\kappa}(y\mid x),
\qquad y\in Y_{A,\kappa},
\]
whose observer marginals agree with the local checkpoint packets. The joint
kernel is an independent receipt. It cannot be manufactured from local
marginals.

\begin{theorem}[Local marginals do not determine public capacity]
\label{thm:local-marginal-capacity-nogo}
There are two binary-input joint checkpoint channels with identical
observer-by-observer marginals and different public capacities.
\end{theorem}

\begin{proof}
Let \(U\) be uniform. The channel
\((Y_1,Y_2)=(U,U\oplus x)\) has uniform input-independent marginals, while
the joint parity recovers \(x\). Independent uniform outputs have the same
marginals and carry no information about \(x\). Thus the joint capacities are
two and one, respectively.
\end{proof}

For a channel \(K\), write
\(S_K(x)=\{y:K(y\mid x)>0\}\). A code
\(C\subseteq X_{\rm reach}(q)\) is zero-error correctable for \(K\) when a
decoder \(d_K\) satisfies
\[
K(d_K^{-1}(x)\mid x)=1
\qquad(x\in C).
\]

\begin{theorem}[Support criterion and compound zero-error capacity]
\label{thm:compound-public-capacity}
A code is zero-error correctable for \(K\) exactly when the supports
\(S_K(x)\), \(x\in C\), are pairwise disjoint. Let \(\mathfrak K(q)\)
contain every authorized checkpoint channel and every declared finite
composition. Define the compound confusability graph \(G_q\) on
\(X_{\rm reach}(q)\) by joining \(x\ne x'\) whenever their output supports
overlap for at least one \(K\in\mathfrak K(q)\). Then the exact public-record
capacity is
\[
\boxed{M_0(q)=\alpha(G_q)},
\]
where \(\alpha\) is the graph independence number.
\end{theorem}

\begin{proof}
A successful decoder cannot assign one output to two inputs, which proves the
support criterion in one direction. Pairwise disjoint supports admit the
decoder that returns the unique supporting input. A code valid for every
declared channel is therefore exactly an independent set in the union of the
channel confusability graphs.
\end{proof}

For exact indefinite continuation, replace each kernel by its support relation
\(R_K=\{(x,y):K(y\mid x)>0\}\). Boolean relation composition generates at
most \(2^{|X_{\rm reach}|^2}\) relations, so the support semigroup and its
compound confusability graph close after finitely many steps.

\begin{theorem}[Reversible fast branch]\label{cor:reversible-public-capacity}
If every authorized continuation is a known injective deterministic map on
\(X_{\rm reach}(q)\), then
\[
M_0(q)=|X_{\rm reach}(q)|.
\]
\end{theorem}

\begin{proof}
Injectivity keeps every pair of inputs distinguishable for every
continuation, so \(G_q\) has no edges.
\end{proof}

Checkpoint invariance is not the capacity definition. A cyclic permutation
of \(m\) labels has a one-dimensional fixed function algebra, while its
inverse decodes all \(m\) labels. Thus a fixed-projector count can undercount
the correctable capacity arbitrarily.

For a frozen finite channel family or continuation horizon and tolerance
\(\varepsilon\), let \(M_\varepsilon(q)\) be the largest code for which every
declared channel has a decoder with worst-input error at most
\(\varepsilon\).

\begin{theorem}[Approximate-capacity robustness and zero-error discontinuity]
\label{thm:capacity-robustness}
If corresponding channel rows obey
\[
\sup_{K,x}d_{\rm TV}(K(\cdot\mid x),\widehat K(\cdot\mid x))\le\delta,
\]
then
\[
M_{\varepsilon+\delta}(\widehat{\mathfrak K})
\ge M_\varepsilon(\mathfrak K).
\]
Zero-error capacity is discontinuous at every identity channel on more than
one symbol: adding arbitrarily small full-support noise collapses \(M_0\) to
one.
\end{theorem}

\begin{proof}
Total-variation control changes the probability of each correct-decoding
event by at most \(\delta\). For the second statement,
\((1-\delta)I+\delta U\), with \(U\) full support, makes every pair of inputs
confusable for every \(\delta>0\).
\end{proof}

The capacity carrier is an exact finite Hilbert space
\(\mathcal H_{{\rm cap},r,D}\) of dimension \(D\). Each reachable public
record class has a nonzero projection \(P_x\) on this carrier, and distinct
records have orthogonal projections.

\begin{theorem}[Carrier bound and saturation rigidity]
\label{thm:public-capacity-carrier-bound}
Every correctable public code \(C\) satisfies
\[
|C|\le D,
\qquad
\log M_\varepsilon(q)\le\log D=N.
\]
If \(M_0(q)=D\), the code projections are rank one and sum to the identity.
\end{theorem}

\begin{proof}
The ranks of nonzero orthogonal projections add and their sum has rank at
most \(D\). Equality with \(D\) codewords forces every rank to be one and
the sum to have full rank.
\end{proof}

The primary finite readback remains set-valued:
\[
\boxed{
\mathfrak F_{r,\varepsilon}(D)=
\{M_\varepsilon(q):q\in\widetilde\Omega_{r,D}\}.
}
\]
A scalar \(\widehat F_{r,\varepsilon}(D)\) exists exactly when the nonempty
terminal fiber has one common defined value. The evaluator must distinguish
an empty readback, an ambiguous readback, and a singleton scalar readback.
Existential closure means \(D\in\mathfrak F_{r,0}(D)\); selector-free robust
closure means
\[
\boxed{\mathfrak F_{r,0}(D)=\{D\}.}
\]
Equivalently, the unclosed kernel
\[
K_r(D,m)=
|\{q\in\widetilde\Omega_{r,D}:M_0(q)=m\}|
\]
has support only at \(m=D\). One saturated branch is insufficient when the
terminal fiber is ambiguous.

The full capacity packet consists of observer lineage, record atoms,
interface maps, reachable public sections, publicness policy, global kernels,
and carrier projections. An isomorphism preserving that packet transports
every exact confusability edge, approximate decoder error, and projection
rank. Hence \(M_\varepsilon\) is implementation invariant under packet
isomorphism.

Once scalarized, the active map
\(f(D)=\widehat F_{r,0}(D)\) is deflationary. It cannot attract a positive
fixed point from below. If \(f\) is total on a declared finite admissible
chain, monotone, and deflationary, iteration from its top element stabilizes
at the greatest fixed point. This is a conditional order theorem, not a
uniqueness or cutoff-independence theorem. The identity family
\(f(D)=D\) fixes every dimension; an erasure family \(f(D)=1\) fixes only the
bottom. Both satisfy monotonicity and deflation. A physical principle must
therefore select a nontrivial cutoff-independent zero of the capacity slack.

Capacity extension and regulator refinement are distinct. For
\(D\le D'\), an injection of reachable records that reflects confusability,
\[
e_{DD'}(x)\sim_{G_{D'}}e_{DD'}(x')
\Longrightarrow x\sim_{G_D}x',
\]
maps every coarse independent set to a fine independent set and gives
\(M_0(D)\le M_0(D')\). At fixed \(D\), refinement injections with the same
property make \(M_{0,r}(D)\) a nondecreasing integer bounded by \(D\), hence
eventually constant along each cofinal sequence.

For regions \(A,B\) sewn along public seam \(S\), exact public records form
the fiber product
\[
X_{A\cup B}=X_A\times_{X_S}X_B,
\qquad
|X_{A\cup B}|=
\sum_{z\in X_S}|r_A^{-1}(z)|\,|r_B^{-1}(z)|.
\]
This gives an exact CSP, tensor-network, or model-counting route on the
reversible branch. A cosmological conclusion additionally requires an exact
transfer recurrence, exact fiber-product recursion, or a seam theorem with a
certified subleading term.

Define the finite-size slack
\[
\boxed{s_r(D)=\log D-\log M_{0,r}(D).}
\]
If \(\limsup_{D\to\infty}\log M_0(D)/\log D<1\), closure is excluded at all
sufficiently large dimensions. Unit asymptotic density is still insufficient:
\(M(D)=D\) and \(M(D)=D-1\) have the same limiting density but opposite
fixed-point behavior. Full physical \(N\)-closure requires a source-derived
finite-size law proving
\[
s(D_\star)=0,
\qquad s(D)>0\quad(D\ne D_\star)
\]
on the declared physical domain, or an equally explicit physical selector.

Two independent physical identifications follow only after robust direct
closure. The receipt \textsc{HORIZON-RECORD-SATURATION} identifies the same
capacity carrier with the de Sitter horizon record:
\[
N_\star=\log D_\star=\frac{A_{\rm dS}}{4\ell_\star^2},
\qquad
A_{\rm dS}=\frac{12\pi}{\Lambda}
\quad\Longrightarrow\quad
\boxed{\Lambda\ell_\star^2=\frac{3\pi}{N_\star}}.
\]
Separately, \textsc{COMMON-EW-LOAD-CARRIER} is a positive, unital,
refinement-natural identification
\[
\Xi_r:\mathcal L_{{\rm screen},r}\longrightarrow
\mathcal L_{{\rm EW},r}.
\]
Given the independent screen-sieve and D10 source laws,
\[
\Gamma_{\rm scr}=\frac{P}{12}\log\frac{N_\star}{\pi},
\qquad
\log\frac{E_{\rm cell}}v=\frac{\pi}{2\alpha_U(P)},
\qquad
\Xi_r(\Gamma_{\rm scr})=\log\frac{E_{\rm cell}}v,
\]
it gives the conditional Higgs/electroweak residual and coordinate
\[
\boxed{
R_{\rm EW}=
\alpha_U(P)\log\frac{N_\star}{\pi}-\frac{6\pi}{P}=0,
\qquad
N_{\rm bridge}=
\pi\exp\!\left[\frac{6\pi}{P\alpha_U(P)}\right].
}
\]
Neither physical identification constructs the public-record map. The
independently frozen operational-resolution residual
\[
R_\rho=\log M_0-\frac{\pi}{\rho_{\rm op}^2}
\]
is likewise a downstream test and never a producer definition.

The current theorem status is therefore precise. The finite global-section,
correctable-code, compound-capacity, approximate-robustness, carrier-bound,
scalarization, order, extension, refinement, and sewing implications are
closed. The missing physical objects are
\textsc{RECORD-ATOM-RESTRICTION},
\textsc{PUBLIC-RECORD-REACHABILITY}, the frozen publicness policy,
\textsc{GLOBAL-PUBLIC-CHECKPOINT-COUPLING},
\textsc{PUBLIC-RECORD-BOUNDARY-REPRESENTATION}, a whole-fiber scalar producer,
\textsc{NO-NEW-CONFUSABILITY} extension/refinement packets, the finite-size
slack law with one physical zero, \textsc{HORIZON-RECORD-SATURATION}, and
\textsc{COMMON-EW-LOAD-CARRIER}. No QCD or hadronic backend is a dependency of
this program.
