\section{Physical Scale Bridge and Mode Calibration}\label{sec:physical-scale-bridge}

This fragment owns the OPH physical scale bridge used by the staged cosmology branch.  It separates
physical comoving wavenumber, source-screen angular sectors, observed-sky transfer multipoles,
finite graph labels, cap labels, and repair-cycle labels.

\begin{definition}[cosmology claim tiers]\label{def:cosmology-claim-tiers}
Every cosmology artifact has one of three claim tiers:
\[
\text{diagnostic proxy},\qquad
\text{conditional physical},\qquad
\emph{source-native physical}.
\]
\emph{diagnostic proxy} covers cap angles, graph mode numbers, repair cycles, sorted covariance
indices, unit strings, and other finite labels without a physical scale bridge.
\emph{conditional physical} imports a frozen FLRW geometry packet and proves the downstream
spectral, clock, freezeout, source, transfer, and likelihood contracts relative to that packet.
\emph{source-native physical} requires the geometry packet and source embedding to be read from the
OPH quotient carrier.
\end{definition}

\begin{definition}[notation firewall]\label{def:cosmology-notation-firewall}
The bridge uses separate symbols for separate objects:
\[
T_r,\qquad \tau,\qquad \eta,\qquad \chi,\qquad K_{\rm FLRW},\qquad
k,\qquad \ell_{\rm src},\qquad L_{\rm CMB},\qquad \ell_\star,\qquad L_{\rm IR}.
\]
\(T_r\) is a finite source-clock label.  \(\tau\) is proper time, \(\eta\) is conformal time,
\(\chi\) is comoving radial distance, and \(K_{\rm FLRW}\in\{-1,0,+1\}\) is the spatial-curvature
branch.  \(k\) is physical comoving wavenumber on a reconstructed spatial slice.
\(\ell_{\rm src}\) is an angular representation sector on the finite primordial source screen.
\(L_{\rm CMB}\) is the observed-sky multipole produced by Boltzmann line-of-sight transfer.
Cap openings, graph mode numbers, and repair-cycle indices are diagnostic labels.  The canonical
internal unit for \(k\) is \({\rm Mpc}^{-1}\); \(h\,{\rm Mpc}^{-1}\) is a display unit only after
\(h\) is frozen and provenance-typed.
\end{definition}

\begin{definition}[finite cosmological geometry packet]\label{def:finite-cosmo-geometry-packet}
At regulator \(r\), a finite cosmological geometry packet is
\[
\mathfrak G_r=
\left(
Q_r,\{\Sigma_{r,n}\},\{\mathcal K_{r,n}\},\{h_{r,n}\},\{\mu_{r,n}\},
\{N_{r,n}\},\{\beta^i_{r,n}\},\{u^a_{r,n}\},\mathcal L_r,\mathcal B_r,
\{\iota_{sr}\},\mathcal R_{\ell_\star}
\right).
\]
It consists of the quotient carrier \(Q_r\), common-clock spatial slices, finite cell complexes,
positive spatial metric or Dirichlet-form data, volume measures, lapse, shift, observer congruence,
lineage, topology and boundary data, refinement maps, and a dimensional scale-certificate receipt.
The native readout has type
\[
\mathsf{CosmoGeomRead}_r:
\operatorname{nf}(\Sigma_r/\Gamma_r)
\longrightarrow
[\mathfrak G_r]_{\rm diff/iso}.
\]
The codomain is modulo the declared discrete diffeomorphism, frame, and isometry redundancies.
It is a quotient-natural OPH readout only when
\[
x\sim_{\Gamma_r}y
\quad\Longrightarrow\quad
\mathsf{CosmoGeomRead}_r(x)\simeq\mathsf{CosmoGeomRead}_r(y),
\]
and when port relabeling, worker partition, queue order, repair schedule, retry history, and hidden
carrier coordinates leave the packet invariant.  Positivity and nondegeneracy require
\[
0<c^-_r |v|^2\le h_{r,n}(v,v)\le c^+_r |v|^2,\qquad
N_{r,n}\ge N_{\min}>0.
\]
Metric, volume, area, Jacobian, frame, connection, and transport readouts must agree within declared
residuals; for instance \(d\mu_{h_r}=\sqrt{\det h_r}\,d^3x\) must match
\(\mathsf{AreaVolumeRead}\) and \(\mathsf{VolumeJacobianRead}\).  Physical length is tied to the
scale certificate by \(L_{\rm phys}=\ell_\star L_{\rm dimensionless}\).  Refinement naturality
requires
\[
\mathcal R_{sr}\circ\mathsf{CosmoGeomRead}_s
\simeq
\mathsf{CosmoGeomRead}_r\circ n_{sr},
\]
with discrepancy tending to zero on the cofinal refinement family.
\end{definition}

\begin{definition}[physical mode basis]\label{def:physical-mode-basis}
For each sector \(s=0,1,2\), let \(\{\phi_i^{(s)}\}\) be a conforming finite basis on the
reconstructed physical geometry.  Define
\[
M^{(s)}_{r,ij}=\int_{\Sigma_r}
\langle\phi_i^{(s)},\phi_j^{(s)}\rangle\,d\mu_{\gamma_r},
\]
\[
K^{(s)}_{r,ij}=
\mathfrak a_r^{(s)}(\phi_i^{(s)},\phi_j^{(s)}).
\]
For scalars,
\[
\mathfrak a_r^{(0)}(f,g)=
\int_{\Sigma_r}\gamma_r^{ab}\nabla_a f\nabla_b g\,d\mu_{\gamma_r}.
\]
Vector and tensor sectors use declared Hodge and Lichnerowicz-type operators after gauge and
constrained zero modes are removed.  The physical basis solves
\[
K_r^{(s)}V_r^{(s)}=M_r^{(s)}V_r^{(s)}\Lambda_r^{(s)},\qquad
V_r^{(s)\dagger}M_r^{(s)}V_r^{(s)}=I.
\]
The evidence bundle must report
\[
\epsilon_{\rm orth}=\left|V^\dagger M V-I\right|
\]
and, for every eigenpair,
\[
\epsilon_{{\rm eig},j}
=
\frac{
\left|Kv_j-\lambda_jMv_j\right|_{M^{-1}}
}{
\left(|K|+|\lambda_j||M|\right)|v_j|
}.
\]
Degenerate sectors are projector-valued.  For a spectral interval \(I\),
\[
P_{r,I}=\frac{1}{2\pi i}
\oint_{\partial I}\left(z-M_r^{-1}K_r\right)^{-1}dz,
\]
and every physical result must be invariant under
\[
V_{r,I}\longmapsto V_{r,I}U_I,\qquad
U_I\in U(\operatorname{rank}P_{r,I}).
\]
\end{definition}

\begin{definition}[finite spectral measure and quadrature]\label{def:finite-spectral-measure}
The finite density of states is intrinsic to the physical operator:
\[
\nu_r(f)=\frac1{V_r}\operatorname{Tr}
f\!\left(\sqrt{M_r^{-1}K_r}\right).
\]
Equivalently,
\[
d\nu_r(k)=\frac1{V_r}\sum_I
\operatorname{rank}(P_{r,I})\,\delta(k-k_{r,I})\,dk.
\]
On a large flat domain the resolved-band target is
\[
d\nu(k)=\frac{k^2}{2\pi^2}\,dk.
\]
The \(d\ln k\) quadrature weights used by the primordial bridge must be derived from this
normalization or from another declared quadrature theorem.
\end{definition}

\begin{definition}[source angular sector]\label{def:source-angular-sector}
For a closed source screen \(S_r\), set
\[
R_{A,r}=\sqrt{\frac{\operatorname{Area}(S_r)}{4\pi}},
\qquad
\overline{\mathcal L}_{S,r}=-R_{A,r}^{2}\Delta_{S_r}.
\]
A spectral projector \(P_{\ell,r}\) may be labeled by \(\ell_{\rm src}\) only if
\[
\operatorname{rank}P_{\ell,r}=2\ell+1
\]
and
\[
\epsilon_{\ell,r}=
\frac{
\left|(\overline{\mathcal L}_{S,r}-\ell(\ell+1))P_{\ell,r}\right|
}{
1+\ell(\ell+1)
}
\le \bar\epsilon_\ell.
\]
It must also refine by
\[
\left|J_{sr}P_{\ell,r}-P_{\ell,s}J_{sr}\right|\to0.
\]
The scalar primordial contract normally starts at \(\ell_{\rm src}\ge2\).  A cap or masked screen
requires either a certified full-screen extension or a certified mode-coupling operator
\[
\widetilde a_\alpha=\sum_{\ell m}\mathcal K_{\alpha,\ell m}a_{\ell m}.
\]
Without that operator the label is \(\text{pseudo ell}\) or \(\text{cap mode index}\).
The observed multipole is produced only after transfer:
\[
C_{L_{\rm CMB}}^{XY}
=4\pi\int d\ln k\,
\mathcal P_\zeta(k)\Delta_{L_{\rm CMB}}^X(k)\Delta_{L_{\rm CMB}}^Y(k).
\]
\end{definition}

\begin{definition}[source-screen embedding packet]\label{def:source-screen-embedding-packet}
A screen mode has radial meaning only after an embedding packet
\[
\mathfrak E_r=
\left(
S_r,\jmath_r:S_r\hookrightarrow\Sigma_{r,\star},O_r,\chi,W_r(\chi),J_r
\right)
\]
has been supplied.  \(S_r\) is the source screen, \(\jmath_r\) embeds it in the initial slice,
\(O_r\) is the observer or radial origin, \(\chi\) is comoving geodesic distance, \(W_r\) is the
radial release window, and \(J_r\) is the area/volume Jacobian.  The window obeys
\[
W_r(\chi)\ge0,\qquad \int W_r(\chi)\,d\chi=1.
\]
\end{definition}

\begin{proposition}[dimensional rescaling no-go]\label{prop:scale-bridge-rescaling-nogo}
If the finite data used by a proposed calibration are unchanged under \(h\mapsto s^2h\), then
\(\Delta_{s^2h}=s^{-2}\Delta_h\) and physical wavenumber transforms as \(k\mapsto k/s\).
Cap angle, graph incidence, patch count, sorted covariance index, and normalized covariance cannot
determine nonzero physical \(k\) without a dimensional metric receipt.
\end{proposition}

\begin{proposition}[angular projection cannot determine radial \(k\)]\label{prop:angular-radial-nogo}
At finite angular cutoff the map
\[
T:f(k)\mapsto\left\{\int d\ln k\,\Psi_\ell(k)f(k)\right\}_{\ell\le L}
\]
has finite-dimensional codomain and infinite-dimensional domain.  Hence it has a nontrivial kernel.
A single angular screen supplies a forward radial projection plus a null-space ledger, not a unique
radial spectrum.
\end{proposition}

\begin{proposition}[clock and unit-string no-goes]\label{prop:clock-scale-nogo}
A rank-one source family \(\mathcal F=\widehat{\mathcal F}\circ T_r\) fixes a common ordering, not
proper elapsed time, because \(f\circ T_r\) gives the same fibers for any strictly increasing
\(f\).  Likewise \(h=a^2\gamma\) is invariant under
\(a\mapsto ca,\ \gamma\mapsto c^{-2}\gamma\).  A lapse or operational clock receipt and the
normalization \(a(\tau_0)=1\) are separate physical inputs.  Relabeling
\(\texttt{inverse\_cap\_opening\_angle\_proxy}\) as \(\texttt{Mpc}^{-1}\) changes no numerical
object and proves no calibration.
\end{proposition}

\begin{theorem}[physical comoving \(k\)]\label{thm:physical-comoving-k}
Assume a valid geometry packet, FLRW reduction, dimensional ruler, topology and boundary sector,
solver convention, physical mode operator, projector-valued basis, density of states, and mode
normalization.  On the flat comoving branch,
\[
-\Delta_{\gamma_r}v_{rj}=\lambda_{\gamma,rj}v_{rj},\qquad
k_{rj}=\sqrt{\lambda_{\gamma,rj}}.
\]
If the operator is assembled from \(h_{ij}^{\rm phys}(\tau)=a(\tau)^2\gamma_{ij}\), then
\[
\lambda_{h,rj}=\frac{k_{rj}^2}{a_r^2},\qquad
k_{rj}=a_r\sqrt{\lambda_{h,rj}}.
\]
For dimensionless eigenvalue \(\widehat\lambda_{h,rj}=\ell_\star^2\lambda_{h,rj}\),
\[
k_{rj}=\frac{a_r}{\ell_\star}\sqrt{\widehat\lambda_{h,rj}}.
\]
The verifier recomputes this equation and reports
\[
\epsilon_{k,rj}
=
\frac{|k_{rj}^2-a_r^2\lambda_{h,rj}|}{k_{rj}^2+k_{\rm floor}^2}.
\]
For \(K_{\rm FLRW}\ne0\), the solver convention must specify
\[
k_{\rm solver}=\kappa_{K_{\rm FLRW}}(\lambda)
\]
and use the matching hyperspherical kernels.
\end{theorem}

\begin{theorem}[screen-to-spatial mode association]\label{thm:screen-to-spatial-mode-association}
There is no physical theorem of the form \(\ell_{\rm src}\mapsto k\).  The spatial geometry defines
the physical \(k\)-basis, and the source embedding plus radial window define a forward projection
from that basis to the screen:
\[
\Psi_{\ell j}^{(K)}=
\int d\chi\,W_r(\chi)\,\Phi_{\ell,k_j}^{(K)}(\chi),
\]
where \(\Phi_{\ell,k}^{(0)}=j_\ell(k\chi)\) on the flat branch and the curved branches use the
declared hyperspherical functions.  Then
\[
C_{\ell_{\rm src},r}^{q}
=4\pi\sum_j w_{rj}^{\ln k}
\Delta_{\zeta,r}^{2}(k_{rj})
\left|\Psi_{\ell_{\rm src},j}^{(K)}\right|^2.
\]
If an inverse reconstruction \(C^q=Ap\) is attempted, the evidence reports prior and support,
positivity constraints, singular values, effective rank, null basis, resolution kernels, prior
sensitivity, and forward residuals.  The Limber estimate \(L+1/2\simeq k\chi_\star\) is a
projection check on a completed bridge; it does not define \(k\), \(L_{\rm CMB}\), or \(\chi_\star\).
\end{theorem}

\begin{theorem}[proper time, scale factor, conformal time, and redshift]\label{thm:physical-time-scale}
Let the selected congruence be
\[
u^a=N^{-1}\left[(\partial_t)^a-\beta^a\right].
\]
Proper time is operationally \(d\tau=N\,dt\) along the congruence, with shift and threading handled
by the lineage map.  For a lineage-tracked comoving domain \(D_r(\tau)\),
\[
V_{D,r}(\tau)=\int_{D_r(\tau)}d\mu_{h_r},\qquad
a_{V,r}(\tau)=
\left[\frac{V_{D,r}(\tau)}{V_{D,r}(\tau_0)}\right]^{1/3}.
\]
Independently,
\[
\log\frac{a_{\Theta,r}(\tau)}{a_{\Theta,r}(\tau_0)}
=
\int_{\tau_0}^{\tau}
\frac{\langle\Theta\rangle_{D,r}}{3}\,d\tau',
\qquad
\Theta=\nabla_a u^a.
\]
The scale-factor consistency residual is
\[
\epsilon_{a,r}=
\sup_\tau
\left|\log a_{V,r}(\tau)-\log a_{\Theta,r}(\tau)\right|.
\]
The Hubble variables are \(H=a^{-1}da/d\tau\) and \(\mathcal H=aH\), while
\[
\eta(\tau)-\eta(\tau_0)=\int_{\tau_0}^{\tau}\frac{d\tau'}{a(\tau')}.
\]
On a certified comoving FLRW branch \(1+z=1/a\).  Outside that branch,
\[
1+z=\frac{(u_\mu p^\mu)_{\rm emit}}{(u_\mu p^\mu)_{\rm obs}}.
\]
The FLRW residual vector contains normalized shear, vorticity, acceleration, spatial-curvature
gradient, domain backreaction, Hamiltonian constraint, momentum constraint, and energy-conservation
components.  Friedmann and conservation equations are consistency checks, not definitions chosen to
force a desired \(a(\tau)\).
\end{theorem}

\begin{theorem}[mode freezeout and common initial surface]\label{thm:mode-freezeout-common-surface}
For every resolved mode \(k_j\), define
\[
\mathcal E_j(\tau)=
\left(
\epsilon_{\zeta,j},
\epsilon_{{\rm nad},j},
\epsilon_{{\rm iso},j},
\epsilon_{{\rm dec},j},
\epsilon_{{\rm rep},j},
\epsilon_{{\rm phase},j},
\epsilon_{{\rm constr},j}
\right).
\]
The physical mode-freezeout time is
\[
\tau_{\star,j}=
\inf\left\{
\tau:\mathcal E_j(\tau')\le\overline{\mathcal E}
\quad\forall \tau'\in[\tau,\tau+\Delta\tau_{\rm pers}]
\right\}.
\]
This proves a \(\text{physical mode freezeout map receipt}\).  A Boltzmann initial-value
problem additionally requires a common spacelike Cauchy slice.  For
\(\Sigma_{\star,r}=\{x:T_r(x)=T_{\star,r}\}\) and signature \((-+++)\), spacelikeness requires
\[
g^{ab}\nabla_aT_r\nabla_bT_r<0
\]
on the resolved surface.  A common surface is certified either by coincident freezeout,
\[
\Delta_\star=
\sup_{j\in\mathcal B_{\rm safe}}
\left|H_\star(\tau_{\star,j}-\bar\tau_\star)\right|
\le\bar\delta_\star,
\]
or by evolution to a later common slice \(\tau_c\) with no independent stochastic source and a
bounded conserved-state residual.  The finite initial packet contains
\[
\mathfrak I_{\star,r}=
\left(
\Sigma_{\star,r},h_{ij}^\star,K_{ij}^\star,
\{X_{\star,rj}\},\{n^a\nabla_aX_{\star,rj}\},
\mathcal C_{\rm H},\mathcal C_{\rm M},
\hbox{phase convention},\hbox{basis hashes}
\right).
\]
A mode-dependent map alone cannot satisfy
\(\text{physical freezeout surface receipt}\).
\end{theorem}

\begin{theorem}[common primordial and anomaly basis]\label{thm:common-primordial-anomaly-basis}
Primordial covariance and dark/anomaly response use the same physical mode projectors.  For a finite
anomaly response operator \(\mathcal K_{A,r}^{(\rho)}(a)\),
\[
K_{A,r;IJ}^{(\rho)}(a)=
P_{r,I}\mathcal K_{A,r}^{(\rho)}(a)P_{r,J}.
\]
The physical contrast response is initially a matrix,
\[
B_{A,r;IJ}(a)=
\frac{\bar\rho_b(a)}{\bar\rho_{A,\rm eq}(a)}
K_{A,r;IJ}^{(\rho)}(a).
\]
It may be reduced to a scalar \(B_A(k,a)\) only when
\[
\epsilon_{\rm off}(a)=
\frac{\left(\sum_{I\ne J}|P_I\mathcal K_AP_J|^2\right)^{1/2}}
{|\mathcal K_A|+\epsilon_0}
\le\bar\epsilon_{\rm off}
\]
and, inside each degenerate sector,
\[
P_I\mathcal K_AP_I=b_I(a)P_I+E_I,\qquad
\frac{|E_I|}{|b_I|+\epsilon_0}\le\bar\epsilon_{\rm iso}.
\]
The same rule applies to repair rates.  A transition eigenvalue per repair cycle is a diagnostic
number.  With certified physical interval \(\Delta\tau_r\) and a contractive active response block,
\[
\Gamma_{{\rm rec},I}
=-\frac1{\Delta\tau_r}\log\rho(P_IL_{\perp,r}P_I),
\]
or a declared Lyapunov/semigroup norm bound for a nonnormal block.
\end{theorem}

\begin{theorem}[regulator convergence]\label{thm:scale-bridge-regulator-convergence}
Let \(r\) be a directed regulator containing UV mesh size, IR volume, time step, sampling size, and
boundary approximation.  Physical scale-bridge receipts require Cauchy or convergence statements:
\[
\left|J_{sr}P_{r,I}-P_{s,I}J_{sr}\right|\le\epsilon_{sr}^{\rm spec},\qquad
\epsilon_{sr}^{\rm spec}\to0,
\]
\[
\left|\int f(k)\,d\nu_s(k)-\int f(k)\,d\nu_r(k)\right|\to0
\]
for every bounded test function \(f\),
\[
|a_s-a_r|_\infty+|H_s-H_r|_\infty+|\eta_s-\eta_r|_\infty\to0,
\]
and
\[
d_H(\Sigma_{\star,s},J_{sr}\Sigma_{\star,r})\to0,\qquad
\left|J_{sr}^{*}X_{\star,s}-X_{\star,r}\right|\to0.
\]
The directed limit must be independent of the order in which UV, IR, sampling, and time refinements
are taken.  Every residual \(e_\alpha(r)\) has a frozen tolerance \(\bar e_\alpha\), a proof that
\(e_\alpha(r)\le\bar e_\alpha\), and a refinement statement \(e_\alpha(r)\to0\).
\end{theorem}

\begin{theorem}[finite physical scale bridge]\label{thm:finite-physical-scale-bridge}
Assume valid receipts for geometry or imported conditional geometry, spatial physical \(k\),
screen-to-\(k\) association, source angular sector, proper time and scale-factor history,
mode-freezeout map, common primordial initial surface, common primordial/anomaly mode basis,
regulator convergence, cross-receipt identity, source-only no-data-use provenance, and no post-hoc
calibration.  Then
\[
\mathcal S_{{\rm OPH},r}:
\left(
P^{\rm screen}_{r,\ell},P^{\rm spatial}_{r,I},T_{r,n}
\right)
\longmapsto
\left(
k_{r,I},\ell_{\rm src},a_r(\tau_n),z_r(\tau_n),\eta_r(\tau_n),
\Sigma_{\star,r},\mathfrak I_{\star,r}
\right)
\]
is unique modulo the declared spatial diffeomorphism/isometry quotient, unitary rotations inside
degenerate spectral projectors, frozen topology and boundary sector, curvature convention, and
solver convention.  It converges on the declared safe physical band.  The tier is
\(\text{conditional physical}\) when \(\mathfrak G_r\) is imported and frozen.  The tier is
\(\text{source-native physical}\) when \(\mathsf{CosmoGeomRead}_r\) and the source embedding are
proved from the OPH quotient carrier.
\end{theorem}

\begin{target}[exact physical-scale receipt conjunctions]\label{target:physical-scale-receipts}
The code and papers use recomputable receipt conjunctions.  Physical spatial \(k\) is
\[
\begin{aligned}
R_{k,\rm spatial}={}&
R_{\rm geometry}\wedge R_{\rm scale}\wedge R_{\rm FLRW}\wedge
R_{\rm operator}\wedge R_{\rm eigenresidual}\wedge R_{\rm normalization}\\
&\wedge R_{\rm k\ equation}\wedge R_{\rm lineage}\wedge
R_{\rm refinement}\wedge R_{\rm nofit}.
\end{aligned}
\]
Then
\[
\texttt{physical\_k\_units\_calibrated}
\iff
\emph{physical spatial k receipt}
\iff
R_{k,\rm spatial}.
\]
The screen association is
\[
R_{\rm screen\to k}
=
R_{k,\rm spatial}\wedge R_{\rm embedding}\wedge R_{\rm radial\ kernel}
\wedge R_{\rm geometry\ compatibility}\wedge R_{\rm nullspace}
\wedge R_{\rm forward\ residual}.
\]
The angular sector is
\[
R_{\ell_{\rm src}}=
R_{\rm closed/extension}\wedge R_{\rm angular\ operator}\wedge
R_{\rm cluster}\wedge R_{\rm multiplicity}\wedge R_{\rm angular\ refinement}.
\]
The scale-factor history is
\[
\begin{aligned}
R_a={}&
R_{\rm proper\ time}\wedge R_{\rm lineage}\wedge R_{\rm volume}
\wedge R_{\Theta}\wedge R_{a_V=a_\Theta}\\
&\wedge R_{\rm FLRW}\wedge R_{\rm constraints}\wedge
R_{\rm refinement}\wedge R_{\rm nofit}.
\end{aligned}
\]
The mode-freezeout map is
\[
R_{\rm modefreeze}=
R_{\zeta}\wedge R_{\rm adiabatic}\wedge R_{\rm isocurvature}
\wedge R_{\rm growing}\wedge R_{\rm repair}\wedge R_{\rm phase}
\wedge R_{\rm constraints}\wedge R_{\rm persistence}.
\]
The common surface is
\[
R_{\Sigma_\star}=
R_{\rm modefreeze}\wedge R_{\rm spacelike}
\wedge (R_{\rm coincident}\vee R_{\rm transport\ to\ common})
\wedge R_{\rm initial\ data}\wedge R_{\rm refinement}.
\]
Only \(R_{\Sigma_\star}\) instantiates
\(\text{physical freezeout surface receipt}\).  The aggregate scale bridge is
\[
R_{\rm scale}=R_{k,\rm spatial}\wedge R_{\rm screen\to k}\wedge
R_{\ell_{\rm src}}\wedge R_a\wedge R_{\Sigma_\star}\wedge
R_{\rm common\ basis}\wedge R_{\rm cross}\wedge R_{\rm nofit}.
\]
Every child receipt repeats the same regulator family, generation, geometry, background, clock,
scale certificate, source embedding, mode basis, mode lineage, boundary condition, solver
convention, freezeout-surface, and source-DAG hashes.  An empty cross-receipt manifest fails.
\end{target}

\begin{target}[native geometry extraction]\label{target:cosmo-geometry-extraction}
\(\text{source-native physical}\) requires
\[
\mathsf{CosmoGeomRead}_r:\operatorname{nf}(\Sigma_r/\Gamma_r)
\to(\mathfrak G_r,\mathfrak E_r)
\]
as a quotient-natural, positive, nondegenerate, causal-order-compatible, observer-clock-compatible,
executor-independent, refinement-convergent, physically scaled source embedding.  Without that
construction, the physical route has tier \(\text{conditional physical}\) with an imported
frozen FLRW geometry packet.
\end{target}

\begin{target}[falsifiers]\label{target:physical-scale-falsifiers}
The physical scale gate fails under any of the following conditions: dimensional rescaling failure;
unit-string relabeling; direct cap-angle calibration; direct \(\ell_{\rm src}\to k\) inversion from
one angular shell without null-space and radial-prior receipts; CMB peak alignment; conflating
\(\ell_{\rm src}\) with \(L_{\rm CMB}\); dependence on rotations inside degenerate eigenspaces;
hidden mode mixing in scalar \(B_A(k,a)\) tables; repair cycles used as proper time; excessive
scale-factor, FLRW, or constraint residuals; a mode-dependent freezeout map reported as a common
surface; non-spacelike release; lack of persistence; regulator drift; limit-order dependence;
vacuous cross receipts; or imported geometry labeled as native.
\end{target}
