% Issue #330 radial-lift integration fragment.
% Full proofs and simulator receipts: RADIAL_LIFT_THEOREMS_330.tex.

\paragraph{Complete radial-lift theorem packet.}
\label{par:oph330-complete-radial-lift}
The screen-to-radial map is a forward restriction with a nonunique unrestricted inverse.
For a flat source window $W$ and geometric normalization $Z_q$,
\[
 C_{\ell,W}^q
 =4\pi Z_q^2\int_0^\infty d\ln k\,
 \Delta_\zeta^2(k)|\Psi_{\ell,W}(k)|^2,
 \qquad
 \Psi_{\ell,W}(k)=\int W(dr)j_\ell(kr).
\]
The physical radial packet must select exactly one of the two uniqueness branches
below; a finite prior continuation has the type \textsc{ConditionalRadialContinuation}.

\textbf{Theorem (one-shell correlation restriction and exact no-go).}
\label{thm:oph330-shell-correlation-restriction}
For a thin shell of radius $R$, the complete angular covariance satisfies
\[
 K_R(\mu)
 =Z_q^2\xi_\zeta\!\left(R\sqrt{2-2\mu}\right)
 =\sum_{\ell\ge0}\frac{2\ell+1}{4\pi}C_{\ell,R}^qP_\ell(\mu).
\]
Hence even the noiseless sequence $\{C_{\ell,R}^q\}_{\ell\ge0}$ determines the
three-dimensional correlation only on $0\le s\le2R$.  The full one-shell
operator has an infinite-dimensional kernel, including positivity-preserving
ambiguities.  Explicitly, for any nonzero
$g\in C_c^\infty((2R,\infty))$,
\[
 h_g(k)=\frac{2k^3}{\pi}\int_0^\infty r^2g(r)j_0(kr)\,dr
\]
has correlation perturbation $\xi_{h_g}=g$ and therefore changes no shell
multipole.  Choosing $B=|h_g|+w$ with any strictly positive integrable $w$ makes
$B$ and $B+h_g$ two distinct positive spectra with the same complete shell
covariance.

\textit{Proof.}
The spherical-Bessel addition theorem gives the displayed restriction identity.
The map $\mu\mapsto R\sqrt{2-2\mu}$ covers exactly $[0,2R]$.  Radial Fourier
inversion gives $\xi_{h_g}=g$ and is injective, so the kernel contains an
infinite-dimensional copy of $C_c^\infty((2R,\infty))$.  The positive pair differs
by the same null element.  \hfill$\square$

\textbf{Corollary (exact low-mode-removed kernel).}
\label{cor:oph330-low-mode-shell-kernel}
For a continuous signed correlation perturbation \(\xi_h\), invisibility to
every shell multipole \(\ell\ge0\) is equivalent to
\(\xi_h(s)=0\) on \(0\le s\le2R\). Invisibility to every retained OPH
multipole \(\ell\ge2\) is equivalent to
\[
\xi_h(s)=a+b\left(1-\frac{s^2}{2R^2}\right),
\qquad 0\le s\le2R,
\]
for constants \(a,b\). Legendre completeness gives the first statement.
Removing \(\ell=0,1\) leaves the span of \(P_0\) and \(P_1\) invisible, which
gives the second.


\textbf{Producer theorem (source-refinement orbit to physical dilation).}
\label{thm:oph330-source-orbit-transfer}
Let $\mathcal H^{\rm src}_r$ be the scale-labelled scalar mode space generated by
the cofinal refinement orbit of the released screen, including its scale label.
A single angular cut is insufficient. Let $U_r$ map the orbit unitarily onto the physical rank-one adiabatic source
subspace.  If
\[
 D_{s,r}U_r=U_rR_{s,r},\qquad
 C_{\zeta,r}=U_rC_{{\rm src},r}U_r^*,
\]
then
\[
 D_{s,r}^{-1}C_{\zeta,r}D_{s,r}-u_r(s)C_{\zeta,r}
 =U_r\left(R_{s,r}^{-1}C_{{\rm src},r}R_{s,r}
           -u_r(s)C_{{\rm src},r}\right)U_r^*.
\]
Thus the source and physical operator residuals have equal norm.  If the finite
covariances converge strongly with a uniform norm bound, the finite dilation maps
and their inverses converge strongly, $u_r(s)\to u(s)$, and this residual tends to
zero, then $D_s^{-1}C_\zeta D_s=u(s)C_\zeta$ in the continuum.

\textit{Proof.}
Conjugate the source covariance by $U_r$ and use the commuting square; unitary
invariance gives the residual identity.  For the limit, add and subtract the
finite conjugated expression.  Strong convergence, uniform boundedness, scalar
convergence, and the norm-residual hypothesis send the three resulting terms to
zero.  \hfill$\square$

\textbf{Theorem (source-dilation uniqueness).}
\label{thm:oph330-source-dilation-uniqueness}
Let $C_\zeta=M_{\Delta_\zeta^2}$ on the common physical
$L^2(d\ln k\,d\Omega_k)$ mode basis.  Define
\[
 (D_sf)(k,\hat k)=f(e^{-s}k,\hat k).
\]
If the source refinement packet proves
\[
 D_s^{-1}C_\zeta D_s=u_q(s)C_\zeta,
 \qquad
 u_q(s+t)=u_q(s)u_q(t),
 \qquad
 -\left.\frac{d}{ds}\ln u_q(s)\right|_{s=0}=\theta,
\]
then $u_q(s)=e^{-\theta s}$ and there is $A>0$ such that
\[
 \Delta_\zeta^2(k)=Ak^{-\theta}\quad\text{almost everywhere}.
\]
For a continuous source representative and pivot $k_\star$,
\[
 \boxed{\Delta_\zeta^2(k)=A_\zeta(k/k_\star)^{-\theta}},
 \qquad A_\zeta=\Delta_\zeta^2(k_\star).
\]

\textit{Proof.}
Strong continuity solves the multiplicative Cauchy equation for $u_q$.
Conjugation of the multiplication operator gives
$\Delta_\zeta^2(e^sk)=e^{-\theta s}\Delta_\zeta^2(k)$ almost everywhere for
each $s$.  In logarithmic coordinates,
$e^{\theta t}\Delta_\zeta^2(e^t)$ is invariant under all rational translations
on one common full-measure set; bounded-transform convolution makes it constant
almost everywhere.  Continuity upgrades the identity to every $k$.  \hfill$\square$

\textbf{Theorem (exact flat thin-shell lift).}
\label{thm:oph330-exact-flat-thin-shell-lift}
On the source-dilation branch, for $-2<\theta<4$ and $\ell\ge2$,
\[
 \int_0^\infty\frac{dx}{x}x^{-\theta}j_\ell^2(x)
 =\frac{\sqrt\pi}{4}
  \frac{\Gamma(1+\theta/2)}{\Gamma(3/2+\theta/2)}
  \frac{\Gamma(\ell-\theta/2)}{\Gamma(\ell+2+\theta/2)},
\]
so
\[
 C_{\ell,R_\star}^q
 =A_q\frac{\Gamma(\ell-\theta/2)}
            {\Gamma(\ell+2+\theta/2)},
\]
with the complete amplitude conversion
\[
 \boxed{
 A_\zeta
 =\frac{A_q}{\pi^{3/2}Z_q^2(k_\star R_\star)^\theta}
  \frac{\Gamma(3/2+\theta/2)}{\Gamma(1+\theta/2)}.}
\]

\textit{Proof.}
Insert the source power law into the exact forward map, set $x=kR_\star$, and
apply the Weber--Schafheitlin square integral.  The convergence strip follows
from $j_\ell(x)\sim x^\ell/(2\ell+1)!!$ at zero and $j_\ell(x)=O(x^{-1})$ at
infinity.  \hfill$\square$

\textbf{Corollary (source-family injectivity and multipole consistency).}
\label{cor:oph330-source-family-injectivity}
Fix \(\theta,Z_q,k_\star\), and a source window for which the forward
coefficient is positive and finite. The forward map is injective in
\(A_\zeta\) on the family
\(\Delta_\zeta^2=A_\zeta(k/k_\star)^{-\theta}\). For each retained multipole,
\[
A_\zeta^{(\ell,W)}
=\frac{C_{\ell,W}^q}
{4\pi Z_q^2k_\star^\theta
\int d\ln k\,k^{-\theta}|\Psi_{\ell,W}(k)|^2}.
\]
Every \(A_\zeta^{(\ell,W)}\) must agree. A disagreement falsifies the declared
window/dilation packet and cannot be repaired with an \(\ell\)-dependent
amplitude.

\textbf{Theorem (finite-window bound).}
\label{thm:oph330-finite-window-bound}
For $0<\theta<2\ell$, define
\[
 I_\ell(\theta)=\int d\ln x\,x^{-\theta}j_\ell^2(x),
\quad
 J_\ell(\theta)=I_\ell(\theta-2)
 -\left[\ell(\ell+1)-\frac{\theta(\theta+1)}2\right]I_\ell(\theta),
\]
\[
 \eta_{\ell,W}
 =\frac{2\sqrt{J_\ell(\theta)}}{\theta}
  \int W(dr)|r^{\theta/2}-R_\star^{\theta/2}|.
\]
Then
\[
 |C_{\ell,W}^q-C_{\ell,R_\star}^q|
 \le4\pi Z_q^2A_\zeta k_\star^\theta\eta_{\ell,W}
 \left(2R_\star^{\theta/2}\sqrt{I_\ell(\theta)}+\eta_{\ell,W}\right).
\]

\textit{Proof.}
In the Hilbert norm
$\|f\|_\theta^2=\int d\ln k\,k^{-\theta}|f(k)|^2$,
$\|j_\ell(kr)\|_\theta=r^{\theta/2}\sqrt{I_\ell}$ and
$\|\partial_rj_\ell(kr)\|_\theta=r^{\theta/2-1}\sqrt{J_\ell}$.
The fundamental theorem of calculus, Minkowski, and
$|\|f\|^2-\|g\|^2|\le\|f-g\|(\|f\|+\|g\|)$ give the bound.  \hfill$\square$

\textbf{Theorem (finite singular-value and prior continuation).}
\label{thm:oph330-finite-prior-continuation}
For a declared finite radial basis, write \(C=Ap\). If
\(A\in\mathbb R^{N_\ell\times N_k}\) has rank \(r\), then
\(\dim\ker A=N_k-r\), and every exact solution is
\(p=p_{\rm part}+V_0a\) for a right-null basis \(V_0\). Given a prior center
\(p_0\) and \(Q\succ0\), the unique minimizer of
\(\frac12(p-p_0)^{\mathsf T}Q(p-p_0)\) subject to \(Ap=C\) is
\[
\boxed{
p_*=p_0+Q^{-1}A^{\mathsf T}
(AQ^{-1}A^{\mathsf T})^+(C-Ap_0).}
\]
The run publishes the singular values, rank threshold, right-null basis,
resolution operator, unresolved projector, positivity active set, and prior
sensitivity. The output type is \textsc{ConditionalRadialContinuation}.

\textbf{Theorem (unrestricted tomographic uniqueness).}
\label{thm:oph330-radial-tomography}
For
\[
 C_\ell(r,r')=\frac2\pi\int_0^\infty k^2P_\zeta(k)
 j_\ell(kr)j_\ell(kr')\,dk,
\]
the covariance operator on $L^2(r^2dr)$ obeys
\[
 Q_\ell=\mathcal H_\ell^{-1}M_{P_\zeta}\mathcal H_\ell.
\]
Thus a complete radial cross-covariance operator determines $P_\zeta$ uniquely
almost everywhere.  Fixing one radius $r_0$, the family $C_\ell(r,r_0)$ known for
all $r$ suffices: its spherical-Hankel transform is
$\sqrt{2/\pi}\,P_\zeta(k)j_\ell(kr_0)$, and the Bessel zeros are discrete.

\textit{Proof.}
Apply spherical-Hankel inversion in the first radial variable.  Unitary
conjugation exposes the multiplication operator; equal multiplication operators
have equal multipliers almost everywhere.  \hfill$\square$

\textbf{Theorem (branch-typed radial boundary).}
\label{thm:oph330-branch-typed-radial-boundary}
The ordinary spherical-Bessel and gamma-function formulas apply to
\textsc{FlatExact} and \textsc{FlatAssumed} branches. Open and closed spatial
branches use their declared hyperspherical eigenfunctions and spectral
measures. An unresolved curvature branch blocks physical radial promotion, and
the flat thin-shell amplitude formula cannot certify a curved branch.

\textbf{Promotion rule.}
A source-derived primordial packet requires all source-stress, single-clock,
freezeout, growing-mode, phase, physical-scale, source-amplitude, null-space,
positivity, and non-fitting forward-residual receipts, together with either a
radial-dilation intertwiner certificate or a radial-tomography certificate. A
finite inverse selected before evaluation is a conditional radial
continuation. It does not promote temperature or polarization spectra to
physical observables.

\textbf{Corollary (transfer firewall).}
Radial promotion changes no temperature, polarization, lensing, recombination,
foreground, nuisance, covariance, or likelihood status. Those outputs require
the independent transfer and likelihood system.
