\section{Finite Screen Spectrum Theorem Package}\label{sec:screen-spectrum-theorems}

This fragment owns the screen-level spectrum theorem used by the staged cosmology branch.  It does
not own TT, TE, EE, lensing, likelihoods, or physical CMB promotion.  Those remain downstream
Boltzmann and data-contract gates.

\begin{definition}[finite screen regulator]\label{def:oph-screen-regulator}
For regulator \(r\), a finite screen regulator is
\[
  \mathfrak S_r=(\mathcal T_r,M_r,\Gamma_r,\mathcal Q_r,C_{sr},J_{rs}),
\]
where \(\mathcal T_r\) is a finite cellulation of the screen, \(M_r\succ0\) is the
area/quadrature mass matrix, \(\Gamma_r\) is the hidden-presentation groupoid,
\(\mathcal Q_r=\Sigma_r/\Gamma_r\) is the physical quotient, and \(C_{sr}\), \(J_{rs}\) are the
coarse-graining and interpolation maps.  Shape regularity and quadrature convergence require
\[
  f^{\mathsf T}M_rg \to \int_{S^2}fg\,d\Omega
\]
with an explicit band-limited error bound
\[
  \left|f^{\mathsf T}M_rg-\int f g\,d\Omega\right|
  \le \varepsilon_{M,r}(L)\|f\|_{H^s}\|g\|_{H^s}.
\]
Patch count alone is therefore not an angular-resolution certificate.
\end{definition}

\begin{definition}[geometric screen scalar]\label{def:oph-screen-scalar}
Let the quotient-visible collar-volume readout be
\[
  J_{X,r}(x)=\lambda_r(x)\sqrt{\det\sigma_{AB,r}(x)}>0,
\]
and let \(\bar J_{X,r}\) be emitted by an independently defined homogeneous or frozen-background
branch, not by a CMB fit.  Define
\[
  q_{0,r}=\frac13\log\frac{J_{X,r}}{\bar J_{X,r}}.
\]
On a certified spherical chart, with \(B_r=[1,n_x,n_y,n_z]\),
\[
  \Pi_{<2,r}=B_r(B_r^{\mathsf T}M_rB_r)^{-1}B_r^{\mathsf T}M_r,\qquad
  q_r=(I-\Pi_{<2,r})q_{0,r}.
\]
On an irregular screen, \(B_r\) is replaced by the certified generalized eigenprojector onto the
finite \(\ell=0,1\) subspace.  Hard-coded feature z-scores or observer-summary weights are
diagnostic proxies, not \(q_r\).
\end{definition}

\begin{proposition}[quotient invariance]\label{prop:oph-screen-scalar-invariance}
If a recharting \(U\) preserves the screen inner product and geometric readout,
\[
  U^{\mathsf T}M'_rU=M_r,\qquad q'_{0,r}=Uq_{0,r},\qquad B'_r=UB_r,
\]
then \(\Pi'_{\ge2,r}U=U\Pi_{\ge2,r}\), and \(q'_r=Uq_r\).
\end{proposition}

\begin{proof}
Substitution gives
\[
\begin{aligned}
\Pi'_{<2,r}U
&=UB_r(B_r^{\mathsf T}U^{\mathsf T}M'_rUB_r)^{-1}B_r^{\mathsf T}U^{\mathsf T}M'_rU\\
&=UB_r(B_r^{\mathsf T}M_rB_r)^{-1}B_r^{\mathsf T}M_r=U\Pi_{<2,r}.
\end{aligned}
\]
Subtracting from \(U\) gives the high-mode identity.
\end{proof}

\begin{definition}[physical scalar precision and action]\label{def:oph-screen-precision}
The scalar precision \(K_r\) must have a physical origin on \(V_r=\operatorname{im}\Pi_{\ge2,r}\).
Allowed branches are:
\[
  K_r^{\rm Hess}=\left.\nabla^2\Phi_r\right|_{q=0},
\]
for a quotient-visible mismatch or release free energy; a repair Dirichlet form
\[
  K_r^{\rm diss}=H_r-T_r^{\mathsf T}H_rT_r,\qquad T_r^{\mathsf T}H_rT_r\preceq H_r;
\]
or the reversible generator form
\[
  K_r^{\rm Dir}=-\frac12(L_r+L_r^{\dagger_H}).
\]
A raw nonsymmetric repair matrix or caller-supplied \(\kappa\) is not a precision operator.  The
absolute normalization must be fixed independently, for example by
\[
  K_0Y_{\ell m}=\ell(\ell+1)Y_{\ell m}
\]
on the \(\theta=0\) branch.  Once normalized,
\[
  S_{{\rm scr},r}[q]=\frac{1}{2A_{q,r}}\langle q,K_rq\rangle_r
  =\frac{1}{2A_{q,r}}q^{\mathsf T}M_rK_rq .
\]
\end{definition}

\begin{theorem}[finite MaxEnt screen covariance]\label{thm:oph-screen-maxent}
Let \(K_re_i=\kappa_i e_i\) with an \(M_r\)-orthonormal basis of \(V_r\), \(\kappa_i>0\), and
\(d_r=\dim V_r\).  Among continuous densities in coefficients \(q=\sum_i a_ie_i\) with
\(\mathbb E[a_i]=0\) and
\[
  \frac12\mathbb E\langle q,K_rq\rangle_r=E^{\rm src}_{q,r},
\]
the unique entropy maximizer is
\[
  d\mu_r(q)=Z_r^{-1}
  \exp\!\left[-\frac{1}{2A_{q,r}}\langle q,K_rq\rangle_r\right]dq,
  \qquad
  A_{q,r}=\frac{2E^{\rm src}_{q,r}}{d_r},
\]
and
\[
  \mathbb E[a_ia_j]=\delta_{ij}\frac{A_{q,r}}{\kappa_i}.
\]
\end{theorem}

\begin{proof}
The Euler--Lagrange equation for entropy with normalization and quadratic-energy constraints gives
a Gaussian density with inverse temperature \(\beta_r\).  The expected energy is
\[
  E^{\rm src}_{q,r}=\frac12\sum_i\kappa_i\frac1{\beta_r\kappa_i}=\frac{d_r}{2\beta_r}.
\]
Thus \(A_{q,r}=\beta_r^{-1}=2E^{\rm src}_{q,r}/d_r\).  Strict concavity of entropy gives
uniqueness.
\end{proof}

\begin{remark}[discrete quotient branch]
For a discrete finite quotient with intrinsic base weight \(m_r(q)\), the exact Gibbs law is
\[
  \mu_r(q)=Z_r^{-1}m_r(q)e^{-\beta_r E_r(q)}.
\]
A Gaussian statement on that branch requires a separate Laplace or central-limit theorem with
controlled higher-order terms.
\end{remark}

\begin{definition}[source release energy]\label{def:oph-screen-release-energy}
Let \(m_r^0\) be the tracially pointed base weight on the finite physical collar quotient.
Let \(F_{r,a}\) be a finite ledger of primitive collar observables: scalar occupancy,
protected-center presence, released volume, conserved source charges, and the release clock.
The ledger excludes screen energy, sky spectra, CMB residuals, likelihoods, fitted amplitudes,
and measurement-calibrated proxies.  For source-emitted constraint values
\(c_{r,a}^{\rm col}\), the selected release law is
\[
  \nu^{\rm rel}_r(x)=\frac{m_r^0(x)
  \exp[-\sum_a\lambda_{r,a}F_{r,a}(x)]}{Z_r},
  \qquad
  \mathbb E_{\nu_r^{\rm rel}}F_{r,a}=c_{r,a}^{\rm col}.
\]
Strict concavity of relative entropy gives uniqueness on full support.  A boundary optimum uses
the same form on its certified support.  The constraint ledger, base weight, source DAG,
multipliers, support, and refinement maps belong to the receipt.

For this independently selected quotient ensemble on released collar normal forms, define
\[
  E^{\rm src}_{q,r}
  =\frac12\int \langle q_r(x),K_rq_r(x)\rangle_r\,d\nu^{\rm rel}_r(x).
\]
The receipt must expose \(\nu^{\rm rel}_r\), the base measure, \(K_r\), \(d_r\),
\(E^{\rm src}_{q,r}\), \(A_{q,r}\), no-observation ancestry, and the same operator normalization
used in the action.  MaxEnt alone does not determine amplitude.
\end{definition}

\begin{proposition}[microscopic-law necessity]\label{prop:oph-screen-amplitude-nogo}
For fixed positive \(K_r\), the Gaussian family
\(Z(A)^{-1}\exp[-\langle q,K_rq\rangle/(2A)]\) exists for every \(A>0\).
The quadratic MaxEnt form therefore leaves one positive scale free.  The source release law in
Definition~\ref{def:oph-screen-release-energy}, or an equivalent source-only vacuum law, supplies
the energy that fixes \(A_{q,r}=2E^{\rm src}_{q,r}/d_r\).
\end{proposition}

\begin{theorem}[rotational screen spectrum]\label{thm:oph-screen-angular-spectrum}
If the continuum precision \(K_\theta\) commutes with the \(SO(3)\) action on scalar functions,
then by Schur's lemma each \(\mathcal H_\ell\) is an eigenspace.  For the exact conformal-shell
family,
\[
  \Lambda_\ell(\theta)
  =\frac{\Gamma(\ell+2+\theta/2)}{\Gamma(\ell-\theta/2)},\qquad \ell\ge2.
\]
Then \(\Lambda_\ell(0)=\ell(\ell+1)\), and the MaxEnt covariance gives
\[
  C_\ell^q
  =A_q\,\frac{\Gamma(\ell-\theta/2)}{\Gamma(\ell+2+\theta/2)}.
\]
Consequently \(\mathcal D_\ell^q=\ell(\ell+1)C_\ell^q/(2\pi)\sim(A_q/2\pi)\ell^{-\theta}\).
\end{theorem}

\begin{definition}[source-derived conformal precision]\label{def:oph-screen-conformal-precision}
Let \(L_r\succeq0\) be the normalized detailed-balanced scalar collar Dirichlet operator on
\(V_r\), with continuum limit \(-\Delta_{S^2}\).  Set
\[
  B_r=(L_r+\tfrac14I)^{1/2},\qquad
  K_{\theta,r}=
  \frac{\Gamma(B_r+\frac32+\frac\theta2)}
       {\Gamma(B_r-\frac12-\frac\theta2)}.
\]
For \(-2<\theta<4\) on the retained \(\ell\ge2\) branch, this operator is positive.  The
gamma recurrence gives \(K_{0,r}=L_r\) exactly.  The finite receipt carries detailed balance,
positivity, the \(\ell(\ell+1)\) normalization, anisotropy splitting, and refinement residuals.
\end{definition}

\begin{theorem}[finite refinement error]\label{thm:oph-screen-refinement}
Suppose that for \(2\le\ell\le L\)
\[
  \left|\frac{\lambda_{\ell m,r}}{\Lambda_\ell(\theta)}-1\right|\le\varepsilon_{K,r}(L),
  \qquad
  \left|\frac{A_{q,r}}{A_q}-1\right|\le\varepsilon_{A,r},
  \qquad \varepsilon_{K,r}<1 .
\]
Then \(C_{\ell m,r}^q=A_{q,r}/\lambda_{\ell m,r}\) satisfies
\[
  \left|
  \frac{C_{\ell m,r}^q}{A_q/\Lambda_\ell(\theta)}-1
  \right|
  \le
  \frac{\varepsilon_{A,r}+\varepsilon_{K,r}}{1-\varepsilon_{K,r}} .
\]
\end{theorem}

\begin{proof}
Write \(A_{q,r}=A_q(1+a_r)\) and
\(\lambda_{\ell m,r}=\Lambda_\ell(1+b_{\ell m,r})\).  Then
\[
  \frac{C_{\ell m,r}^q}{A_q/\Lambda_\ell}=\frac{1+a_r}{1+b_{\ell m,r}},
\]
and the displayed bound follows from \(|a_r|\le\varepsilon_A\),
\(|b_{\ell m,r}|\le\varepsilon_K\).
\end{proof}

\begin{theorem}[refinement-semigroup tilt]\label{thm:oph-screen-tilt}
Let \(R_b\) be the scalar refinement map for scale ratio \(b>1\).  If one isolated scalar
covariance mode has positive eigenvalue \(\lambda(b)\), \(\lambda(b_1b_2)=\lambda(b_1)\lambda(b_2)\),
and \(\lambda\) is continuous, then there is a unique real \(\theta\) with
\[
  \lambda(b)=b^{-\theta},\qquad
  \theta=-\frac{\log\lambda(b)}{\log b}.
\]
\end{theorem}

\begin{proof}
Set \(g(t)=-\log\lambda(e^t)\).  The semigroup law gives \(g(t+s)=g(t)+g(s)\).  Continuity makes
\(g(t)=\theta t\), hence the result.
\end{proof}

\begin{definition}[edge-center reserve generator receipt]\label{def:oph-screen-reserve-generator}
Write \(s=\log b\) for logarithmic refinement thickness.  Let \(u_{\rm full}(s)\) be the
scalar-conditioned covariance-survival cocycle across a full oriented collar, and let \(u_q(s)\)
be its source-facing half-collar restriction.  The receipt requires
\[
u(s+t)=u(s)u(t),\qquad u(0)=1,
\]
strong continuity at zero, the source-derived full-collar density
\[
-u'_{\rm full}(0)=\frac{P_\star}{24},
\]
and the orientation-reversal coarea identity
\[
-u'_q(0)=\frac12[-u'_{\rm full}(0)]=\frac{P_\star}{48}.
\]
These are infinitesimal generator statements.  A one-step survival probability has exponent
\(-\log u_q(\log b)/\log b\).
\end{definition}

\begin{theorem}[edge-center tilt and repair-clock reconciliation]
\label{thm:oph-p-over-48-tilt}
Under Definition~\ref{def:oph-screen-reserve-generator},
\[
u_q(s)=e^{-\theta s},\qquad
\theta=\frac{P_\star}{48},\qquad
n_s=1-\frac{P_\star}{48}.
\]
In the coordinate \(\theta=\kappa_{\rm rep}(P_\star-\varphi)\), the same branch has
\[
\kappa_{\rm rep}^{\rm edge}
=\frac{P_\star}{48(P_\star-\varphi)}.
\]
The value \(e\) is a separate diagnostic hypothesis unless an additional identity equates it
with this source-derived coordinate.
\end{theorem}

\begin{proof}
For \(g(s)=-\log u_q(s)\), the cocycle law gives the continuous Cauchy equation.  Hence
\(g(s)=\theta s\).  Differentiation at zero and the half-collar identity give
\(\theta=P_\star/48\).  The formula for \(\kappa_{\rm rep}^{\rm edge}\) is algebraic.
\end{proof}

\begin{theorem}[homogeneous radial source family]\label{thm:oph-screen-radial-source-family}
Assume source-stress closure, a single clock, freezeout, multicenter consistency, and
translation/rotation covariance. Let \(C_\zeta=M_{\Delta_\zeta^2}\) on the common physical
\(d\ln k\) mode basis. If a scale-natural source embedding transports refinement to physical
dilation and its finite operator residual converges to
\[
D_s^{-1}C_\zeta D_s=e^{-\theta s}C_\zeta,
\qquad (D_sf)(k,\hat k)=f(e^{-s}k,\hat k),
\]
then every positive measurable representative satisfies
\[
\Delta_\zeta^2(k)=A_\zeta(k/k_\star)^{-\theta}
\]
almost everywhere. Continuity gives the pointwise identity. A single shell has an
infinite-dimensional radial kernel, including positive ambiguities; complete radial
cross-covariances give the independent spherical-Hankel tomography route.
\end{theorem}

\begin{proof}
Conjugation of the multiplication operator gives
\(\Delta_\zeta^2(e^sk)=e^{-\theta s}\Delta_\zeta^2(k)\) almost everywhere. In logarithmic
coordinates, rational-translation invariance on a common full-measure set forces
\(e^{\theta t}\Delta_\zeta^2(e^t)\) to be constant almost everywhere. The one-shell and
tomography statements follow from the correlation-restriction and spherical-Hankel theorems in
the primordial bridge packet.
\end{proof}

\begin{theorem}[thin-shell power-law lift]\label{thm:oph-thin-shell-powerlaw-lift}
Assume \(q(\hat n)=Z_\star\Pi_{\ell\ge2}\zeta_\star(R_\star\hat n)\) and
\[
  \Delta_\zeta^2(k)=A_\zeta(k/k_\star)^{-\theta}.
\]
Then
\[
  C_\ell^q=4\pi Z_\star^2\int d\ln k\,
  \Delta_\zeta^2(k)j_\ell^2(kR_\star),
\]
and, for \(-2<\theta<4\),
\[
  A_q
  =\pi^{3/2}Z_\star^2A_\zeta(k_\star R_\star)^\theta
  \frac{\Gamma(1+\theta/2)}{\Gamma(3/2+\theta/2)} .
\]
Thus
\[
  A_\zeta
  =\frac{A_q}{\pi^{3/2}Z_\star^2(k_\star R_\star)^\theta}
  \frac{\Gamma(3/2+\theta/2)}{\Gamma(1+\theta/2)} .
\]
\end{theorem}

\begin{proposition}[finite-window bound]\label{prop:oph-finite-window-bound}
Let \(\Psi_\ell(k)=\int dr\,W(r)j_\ell(kr)\), \(W\ge0\), \(\int Wdr=1\), with mean \(R_\star\)
and variance \(\sigma_R^2\).  If
\[
  \delta_\ell(k)=\frac{k^2\sigma_R^2}{2}
  \sup_{r\in{\rm supp}\,W}|j_\ell''(kr)|,
\]
then
\[
  |C_{\ell,W}^q-C_{\ell,{\rm shell}}^q|
  \le
  4\pi Z_\star^2\int d\ln k\,\Delta_\zeta^2(k)
  \left[2\delta_\ell(k)+\delta_\ell(k)^2\right].
\]
\end{proposition}

\begin{proposition}[radial non-identifiability]\label{prop:oph-radial-null}
For a finite radial basis, \(C=Ap\).  If \(A\in\mathbb R^{N_\ell\times N_k}\) has rank \(r\),
then \(\dim\ker A=N_k-r\), and every \(p+v\) with \(v\in\ker A\) gives the same screen spectrum.
Radial promotion therefore requires either a source theorem restricting \(p\), or a declared prior
with a published null basis, resolution kernels, positivity checks, and prior-sensitivity report.
\end{proposition}

\begin{theorem}[conditional source-spectrum promotion]\label{thm:oph-screen-spectrum-promotion}
One hash-locked source DAG may emit
\[
(q_r,S_{{\rm scr},r},\theta,A_{q,r},C_{\ell,r}^q,A_{\zeta,r},
\Delta_{\zeta,r}^2)
\]
as a conditional primordial packet only when the geometric-scalar, collar-law, release-energy,
reserve-generator, conformal-precision, refinement, source-stress, single-clock, freezeout,
adiabaticity, isocurvature, phase-coherence, thin-shell, radial-null, finite-window, and forward-
residual receipts pass on that DAG.  Any measurement, likelihood, fitted parameter, or
measurement-calibrated ancestor fails the source packet.  Physical temperature and polarization
spectra require the independent Boltzmann, recombination, nuisance, covariance, and likelihood
gates.
\end{theorem}

\begin{target}[screen-spectrum receipt set]\label{target:oph-screen-spectrum-receipts}
A concrete source-derived spectrum requires the following receipt families before primordial
promotion:
\begin{enumerate}[leftmargin=2em]
\item geometry, scalar quotient, low-mode projector, scalar precision, and operator normalization;
\item quotient ensemble selection, scalar release energy, and MaxEnt screen covariance;
\item the infinitesimal reserve generator, scalar refinement tilt, and angular screen spectrum
with a finite error budget;
\item source-stress, clock, freezeout, radial-window, radial-null, forward-residual, and transfer
firewall receipts.
\end{enumerate}
The theorem and algorithm packet is complete.  Construction of one finite source DAG that passes
this receipt set is work in progress.
\end{target}
