\subsubsection*{Strict-one-loop W/Z pole-map kernel}

The finite-order theory map is now explicit and machine checked.  Let the
renormalized one-doublet electroweak input at scale \(Q\) be
\(\theta(Q)=(g,g',v_F,\ldots)\), with canonical Higgs kinetic term and
\(v_F>0\), and set
\[
w=\frac{g^2v_F^2}{4},\qquad
z=\frac{(g^2+g'^2)v_F^2}{4}.
\]
Use the inverse-propagator convention
\[
\Gamma^T(s)=s-m_0^2-\Delta^T(s)
=s-m_0^2+\Pi^T(s),\qquad \Delta^T=-\Pi^T,
\]
where each \(\Delta^{(1)}\) already contains its one-loop factor,
counterterms, tadpoles, and the complete declared strict-one-loop mask.
Relative to the coefficient convention of
Theorem~\ref{thm:qft-q3-strict-wz-coefficients},
\[
\Delta_{ij}^{(1)}(s)=-\kappa\Pi_{ij}^{(1)}(s),
\qquad \kappa=(16\pi^2)^{-1}.
\]
The two notations are translations of one pole equation, not independent
results.

\begin{proposition}[Strict-one-loop charged and neutral pole map]
\label{prop:strict-one-loop-wz-map}
Assume the tree roots \(w,z>0\) are simple and the declared one-loop entries
are holomorphic near them on the frozen analytic sheet.  Then
\[
s_W^{[1]}=w+\Delta_{WW}^{(1)}(w),\qquad
s_Z^{[1]}=z+\Delta_{ZZ}^{(1)}(z).
\]
In the neutral tree-level photon--\(Z\) basis,
\[
\Gamma_N^T(s)=
\begin{pmatrix}
s-\Delta_{AA}^{(1)}(s)&-\Delta_{AZ}^{(1)}(s)\\
-\Delta_{ZA}^{(1)}(s)&s-z-\Delta_{ZZ}^{(1)}(s)
\end{pmatrix}+O(\epsilon^2).
\]
The product
\(\Delta_{ZA}^{(1)}\Delta_{AZ}^{(1)}\) has loop power two and is excluded
from a strict-one-loop root.  Its leading Schur-complement contribution is
\[
-\frac{\Delta_{ZA}^{(1)}(s)\Delta_{AZ}^{(1)}(s)}{s},
\]
which belongs only in a separately complete two-loop map together with the
genuine two-loop entries and pole-iteration derivatives.
\end{proposition}

\begin{proof}
Write \(s_W=w+\epsilon\sigma_W+O(\epsilon^2)\) in the charged inverse
entry.  Its order-\(\epsilon\) coefficient is
\(\sigma_W-\delta_{WW}^{(1)}(w)\).  For the neutral determinant, write
\(s=z+\epsilon\sigma_Z+O(\epsilon^2)\).  The order-\(\epsilon\) coefficient
is \(z[\sigma_Z-\delta_{ZZ}^{(1)}(z)]\); both off-diagonal entries start at
order \(\epsilon\), so their product starts at order \(\epsilon^2\).
\end{proof}

For \(s_V=m_{V,0}^2+\Delta_V^{(1)}\), the strict energy-pole coefficients are
\[
\delta M_V^{(1)}=\frac{\operatorname{Re}\Delta_V^{(1)}}{2m_{V,0}},
\qquad
\Gamma_V^{(1)}=-\frac{\operatorname{Im}\Delta_V^{(1)}}{m_{V,0}}.
\]
They are distinct from the exact coordinate transform of the truncated
complex number.  On the lower-half-plane branch,
\[
M_V=\sqrt{\frac{|s_V|+\operatorname{Re}s_V}{2}},\qquad
\Gamma_V=\sqrt{2\bigl(|s_V|-\operatorname{Re}s_V\bigr)},
\qquad s_V=(M_V-i\Gamma_V/2)^2.
\]
Applying this nonlinear square root exactly resums kinematic powers of the
one-loop coefficient.  It is a useful display coordinate, not a strict
two-loop calculation and not the object to compare in a finite-order Nielsen
test.

\begin{proposition}[Evidence cannot self-attest]
\label{prop:wz-evidence-nonself-attestation}
An untrusted input boolean asserting an external FJ, matching, source-law,
gauge/BRST, clock, or ancestry property cannot certify that property.  A
promotion verifier must resolve an independent hash-bound witness, validate
it, and bind it to the exact numerical subject, order, mask, scheme, and
analytic sheet.
\end{proposition}

\begin{proof}
Choose a subject for which the external property is false and set the
untrusted boolean to true while preserving every relation recomputed by the
verifier.  If the verifier resolves no independent witness, it follows the
same accepting path.  Hence acceptance would admit a false instance.
\end{proof}

The released fail-closed receipt implements these rules and rejects
self-promotion, unrelated-but-self-consistent poles, substituted empty
fixtures, inflated tolerances, corrupted redundant fields, and altered
neutral diagnostics.  Its archived SMDR order-one fixture at \(Q=160\) GeV
evaluates to
\[
\begin{aligned}
s_W^{[1]}&=(6459.842027569383-160.532752773045i)\;\mathrm{GeV}^2,\\
s_Z^{[1]}&=(8222.835212344102-218.292761806439i)\;\mathrm{GeV}^2.
\end{aligned}
\]
The corresponding strict readouts are
\((M_W,\Gamma_W)=(80.374161202712,2.007425074735)\) GeV and
\((M_Z,\Gamma_Z)=(90.680036075608,2.402420059845)\) GeV.  These numbers
reconstruct an archived backend row; they are not an independent self-energy
evaluation and have target ancestry, no OPH-selected FJ \(v_F\), no complete
neutral matrix, no source covariance, no independent gauge/BRST receipt, and
no source clock.  The exact classification is therefore
\[
\texttt{CONDITIONAL\_STRICT\_1L\_POLE\_MAP\_NOT\_OPH\_NATIVE\_PHYSICAL},
\]
with \(\texttt{physical\_promotion\_allowed=false}\).  What is proved is the
implication from a complete declared renormalized strict-one-loop packet to
the separated pole and mass/width readouts; OPH has not yet produced that
antecedent.
