\section*{One carrier stack, three paper surfaces}

The microphysics, consensus, and compact SM/GR papers describe one typed
construction. The microphysics paper owns the finite carrier and its public
interfaces. The consensus paper owns accepted repair and the quotient public
normal form. The compact paper owns the conditional maps from that public
normal form into support geometry, gravity, compact currents, and matter. A
claim may cross from one paper to another only through the exported object and
premises named here.

\subsection*{Three meanings of screen}

The word ``screen'' is used for three related objects that must not be
identified without a receipt.

\begin{enumerate}[leftmargin=2em]
\item The \emph{local carrier boundary} is the twelve-port oriented interface
of one Echosahedral carrier on the declared branch. Its incidence has
\((V,E,F)=(12,30,20)\).
\item The \emph{federation screen} is the routed system of interfaces,
records, repairs, and checkpoints of many carriers at finite cutoff.
\item The \emph{support screen} is the observer-facing geometric chart. On
the spherical branch it is the refined conformal \(S^2\) used for caps,
collars, modular flow, and Lorentz reconstruction.
\end{enumerate}

Local icosahedral incidence does not determine the topology of the federation
nerve. A federation of identical local carriers can be routed as a path, a
cycle, a higher-genus complex, or a spherical complex. The map from routed
carriers to a support-visible spherical nerve is therefore a physical bridge,
not a change of notation.

\subsection*{Structure-sensitive, presentation-invariant physics}

OPH is not neutral under arbitrary changes of substrate. It is invariant under
changes of presentation that preserve the complete observer-visible carrier
signature. On the Echosahedral branch that signature contains

\[
\mathcal C_{i,r}=
\bigl(
\mathcal A_{i,r},\rho_{i,r},P_{i,r},I_{i,r}^{\rm or},
\mathcal R_{i,r},\mathcal U_{i,r},\mathsf{Chk}_{i,r},
\mathsf{Resp}_{i,r},c_{sr}
\bigr),
\]

where \(P_{i,r}\) is the port set, \(I_{i,r}^{\rm or}\) is oriented
incidence, \(\mathcal R_{i,r}\) is the record algebra,
\(\mathcal U_{i,r}\) is the repair or feedback interface,
\(\mathsf{Resp}_{i,r}\) is the visible response law, and \(c_{sr}\) is the
refinement lineage. Hidden coordinates, port names, worker partitions,
materials, and wiring presentations are silent when an isomorphism preserves
this whole tuple and its error model. A change in port number, incidence,
orientation, accessible algebra, response, repair law, clock, or refinement
lineage need not be silent. A cube and an icosahedron are therefore different
carrier contracts even when both are built from the same material.

A carrier body is not automatically an observer. It realizes an observer only
when it supplies bounded access, self-readback, durable records,
record-conditioned feedback, boundary prediction against controls, and
checkpoint continuation. One carrier may pass that test. A connected
subfederation may pass it instead. No theorem fixes primitive observer size by
counting carrier bodies.

\subsection*{The common finite computation}

At cutoff \(r\), source-bound carrier data are routed into an observer-patch
federation. Accepted repair then acts on the physical quotient:

\[
\begin{aligned}
\mathsf{SourceCarrierTower}_r
&\xrightarrow{\;\mathsf{realize/route}\;}
\mathsf{ObserverFederation}_r\\
&\xrightarrow{\;\pi_r\;}
\mathsf{PhysicalQuotient}_r
\xrightarrow{\;\operatorname{Rep}_r\;}
\mathsf{PublicNormalForm}_r.
\end{aligned}
\]

The last arrow is the consensus result only under semantic-dependency-complete
transactions, coherent union-collar payloads, repair completeness, local
diamonds, protected records, and the stated endpoint conditions. A collection
of oscillators with equal frequency does not supply those clauses.

Physical phase locking can instantiate one synchronization layer. For a
routed edge \(e=((i,a),(j,b))\), a source-produced phase record may certify
frequency entrainment and a stable relative phase,

\[
\dot\theta_{i,a}-\dot\theta_{j,b}\longrightarrow0,
\qquad
d_{S^1}(\theta_{i,a}-\theta_{j,b},\delta_e)\le\varepsilon_e.
\]

That certificate becomes a consensus parent only when the phase record fixes
a commensurability map for the exposed packets and is tied to the accepted
repair ledger, semantic records, an independently calibrated clock, and the
confluence premises. Phase locking can synchronize an interface. It does not
by itself make the interface an observer, settle semantic disagreement, or
produce physical time.

\subsection*{Two downstream projections of one source}

The public normal form has two separately typed projections:

\begingroup\small
\[
\begin{aligned}
\mathsf{PublicNormalForm}_r
&\xrightarrow{\;\mathsf{carrier\text{-}to\text{-}support}\;}
\bigl(\mathsf{Support}_{S^2,r},\mathsf{FiniteCapBWCertificate}_r\bigr),\\
\left.
\begin{gathered}
\mathsf{FiniteCapBWCertificate}_r\\
\mathsf{MGNS\text{-}1}_r\ \text{independently complete}
\end{gathered}
\right\}_{\text{same tower}}
&\longrightarrow \mathsf{BW/KMS}_r
\longrightarrow \mathsf{Lorentz/H^3}_r\\
&\longrightarrow \mathsf{Events}_{3+1,r}
\longrightarrow \mathsf{Einstein}_r ,
\end{aligned}
\]
\endgroup
\[
\begin{aligned}
\mathsf{PublicNormalForm}_r
&\xrightarrow{\;\mathsf{port\text{-}response}\;}
(\mathsf{A5Carrier}_r,J_r)\\
&\longrightarrow \mathsf{CompactCurrent}_r
\longrightarrow \mathsf{SM}_{Q0,r}\\
&\longrightarrow \mathsf{Matter/QFT}_r .
\end{aligned}
\]

The carrier-to-support leg requires full interface algebra homomorphisms,
higher-overlap coherence, spherical incidence, refinement-natural mesh and
cross-ratio data, and an independently normalized geometric \(2\pi\)-KMS
comparison. It emits the support \(S^2\) and
\(\mathsf{FiniteCapBWCertificate}\). The state tower, common-comparison maps,
compatible state/vector data, modular controls, and cofinal modulus belong to
the independently produced \(\mathsf{MGNS\text{-}1}\) package. The BW theorem
consumes both inputs on the same tower. Once the support leg produces a conformal \(S^2\),
\(\operatorname{Conf}^+(S^2)\cong\operatorname{SO}^+(3,1)\) and
\(H^3=\operatorname{SO}^+(3,1)/\operatorname{SO}(3)\) is exactly
three-dimensional. \(H^3\) is the observer-frame fiber. A \(3{+}1\)-dimensional
event manifold requires the population/realization, separation, rank-four
affine-chart, overlap-cocycle, held-out quadratic-cone, and causal-reachability
receipts \(\mathsf{(E1)}\)--\(\mathsf{(E6)}\), together with the
\(\mathsf{MI}\)/assembly premise. Operational-clock gluing separately requires
observer-readable transitions, event correspondence, affine calibration,
cycle identity, and normal-form invariance. The Einstein relation additionally requires
the common-domain stress, entropy, vacuum, coupling, scale, and remainder
packet. Hidden Cartesian coordinates of a finite carrier are ineligible as
support-screen, event, or Lorentz data.

The second projection begins with an exact finite result on the certified
Echosahedral lineage. The twelve-port module decomposes as

\[
P_{12}\cong_{A_5}\mathbf1\oplus\mathbf3\oplus\mathbf3'\oplus\mathbf5.
\]

The source selector derives the twelve unit lines, antipodal pairing, proper
\(A_5\) action, and rank-three Gram frame. These register facts become gauge
facts only after a source-produced, full-rank, compact, skew-adjoint,
commutator-closed physical current lift carries the same inner \(A_5\) action
through refinement. Noncentral action of the five-dimensional block then
selects the Standard-Model Lie type from the compact classification. Trace
balance, Spin and deck descent, matter selection, exclusion of extra sectors,
family attachment, and quantum-field construction remain separate maps.

The compact sector-category and Minimal Admissible Realization route
conditionally reconstructs an abstract Standard Model quotient of the same
type by a logically independent route.
Physical unification requires a source-bound commuting square identifying its
reconstructed compact group with the group acting through the Echosahedral
current response:

\[
\begin{array}{ccc}
\mathsf{A5PortResponse}_r & \longrightarrow & G_r^{\rm screen}\\
\downarrow & & \downarrow\scriptstyle{\simeq}\\
\mathsf{TransportableSectorCategory}_r & \longrightarrow & G_r^{\rm DR/MAR}.
\end{array}
\]

On those premises the abstract Lie-type agreement is exact. The physical vertical maps and the
source identity of the two group actions are open. In the same way, the
rank-three face band is a canonical candidate family carrier, while three
physical generations require the complex rank-45 attachment and
complement-complete refinement receipts. The value \(N_g=3\) in the compact
paper is the minimum of the declared economy class, not a consequence of the
icosahedral graph alone.

\subsection*{Finite controls and status boundaries}

The finite \(A_5\) evaluator control has \(60\) reachable correctable public
records on \(\mathcal H_k=\ell^2(A_5)\otimes\mathbb C^k\):

\[
M_0=60,\qquad D_{\rm raw}=60k,\qquad
\Delta_{\rm raw}=60(k-1).
\]

Raw equality occurs only at \(k=1\). Publicly inert multiplicity makes
\(D_{\rm raw}\) implementation-dependent, so the result is an evaluator
control rather than physical capacity closure.

The unified claim has a precise scope. Consensus, geometry/gravity,
and gauge/matter are composable branches of one source-bound self-reading
carrier tower. Its full quotient-visible architecture can constrain both
branches; local icosahedral incidence by itself constrains only the local
carrier route. The physical maps that turn those constraints into one
inhabited universe are named premises. Matching dimensions or symmetry labels
does not supply them.
