\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\IfFileExists{../paper/release_info.tex}{
  \input{../paper/release_info.tex}
}{
  \newcommand{\OPHPaperReleaseDate}{\today}
  \newcommand{\OPHPaperReleaseBanner}{Draft}
  \newcommand{\OPHPaperReleaseID}{local-cosmology-staging}
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{target}[theorem]{Target}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\Conf}{\mathrm{Conf}}
\newcommand{\LCDM}{\Lambda\mathrm{CDM}}
\newcommand{\Zsix}{\mathbb Z_6}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\rhoA}{\bar\rho_A}
\newcommand{\GammaRec}{\Gamma_{\rm rec}}
\newcommand{\Azeta}{A_\zeta}
\newcommand{\Bkernel}{B_A}
\newcommand{\NCRC}{N_{\rm CRC}}
\newcommand{\rhoAeq}{\bar\rho_{A,\mathrm{eq}}}
\newcommand{\csA}{c_{s,A}^2}
\newcommand{\sigmaA}{\sigma_A}
\newcommand{\QA}{Q_A^\mu}
\newcommand{\pathref}[1]{\nolinkurl{#1}}
\newcommand{\SimSourceRepo}{\url{https://github.com/muellerberndt/oph-physics-sim}}
\newcommand{\SimSourceCommit}{\texttt{aeea9e502491a277b5e21a80bb89df6d089a074d}}
\newcommand{\SimSourceCommitURL}{\url{https://github.com/muellerberndt/oph-physics-sim/commit/aeea9e502491a277b5e21a80bb89df6d089a074d}}

\title{OPH Cosmology as a Finite-Source Prediction Program:\\
Observer-Screen Synchronization, Dark Stress, and the Physical CMB Gate}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
This paper stages the OPH cosmology branch inside the public core repository without yet promoting
it to the published paper set. It consolidates the inflation-free observer-screen synchronization
draft, the dark/anomaly stress paper, the screen-microphysics paper, the compact OPH theorem stack,
and the latest OPH-FPE simulator diagnostics into one finite-source prediction program. The central
claim is deliberately conditional. OPH may replace the logical jobs of inflation by finite
observer-screen synchronization: flatness by visible holonomy selection, horizon coherence by a
same-boundary or low-\(k\) repair gate, near scale invariance by a screen Green spectrum, hot
initial data by MaxEnt release, and acoustic peaks by ordinary Boltzmann transfer from source-only
finite OPH artifacts. The latest 256k-patch OPH-FPE run strengthens the program because its best
diagnostic CMB curve has shape correlation \(0.9951542364\), normalized RMSE \(0.0984455548\), and
zero mean peak-location error against the local binned TT table. It also hardens the claim boundary:
the physical CMB prediction receipt remains false until finite source provenance, physical scale
calibration, a covariant collar-packet stress parent, physical \(\rho_A(a)\), \(B_A(k,a)\), and
\(\Gamma_{\rm rec}(k,a)\) kernels, Boltzmann transfer, and frozen likelihood receipts pass.
\end{abstract}

\section*{What This Paper Contributes}

The OPH core papers recover local observer-facing geometry, records, modular flow, gauge/matter
structure, and finite screen microphysics. The cosmology work asks a different question: which
large-scale data can be predicted once the finite observer-screen state is released into an
Einstein-Boltzmann cosmology?

This staging paper contributes four things.
\begin{enumerate}[leftmargin=2em]
\item It consolidates the inflation-free OPH cosmology branch into the core repository under
\pathref{cosmology/}, while keeping it outside the release build until the theorem gates close.
\item It separates diagnostic simulator outputs from physical predictions. A good visual or
measurement-facing CMB overlay is not a physical CMB prediction unless its inputs are source-only
finite OPH artifacts fixed before likelihood comparison.
\item It names the finite objects that must exist before simulation work should resume on physical
CMB, vacuum, or cosmological uses of the dark sector: source provenance, physical mode calibration,
freezeout, covariant stress, anomaly kernels, transfer, likelihood, and quotient ensemble receipts.
The dark-sector derivations themselves remain in \pathref{extra/}.
\item It gives the open GitHub theorem issues a single paper-side target.
\end{enumerate}

\tableofcontents
\newpage

\section{Claim Boundary}

This is a continuation paper, not a release checkpoint and not a published OPH paper bundle member.
It is part of the public core repository so that later paper and simulator work can target one
coherent cosmology contract.

The branch claim is:
\[
\boxed{
\begin{gathered}
\text{OPH can replace the logical jobs of inflation on a finite-source branch:}\\
\text{flatness by visible-holonomy selection, horizon coherence by same-boundary repair,}\\
\text{near scale invariance by the screen Green spectrum, hot initial data by MaxEnt release,}\\
\text{and acoustic peaks by Boltzmann transfer from source-only OPH artifacts.}
\end{gathered}}
\]

Here ``can'' means ``can on the declared Phase III finite-source continuation branch if the listed
source, stress, lift, transfer, and likelihood gates close.'' It does not mean that inflation
replacement, CMB spectra, or dark-sector cosmology are part of the recovered Phase I SM/GR core.

The branch does not currently claim a physical CMB prediction, a completed Planck/ACT likelihood
run, an OPH-native quantum vacuum, a full cosmological dark-matter likelihood, or a production
particle-formation simulation. The latest simulator run is measurement-facing and useful, but its
own promotion receipts keep the physical claim closed.

\begin{remark}[No simulator shortcut]
The paper-side theorem gates are not bureaucratic checks. They are the distinction between a
simulation that happens to resemble CMB data and a prediction whose input artifacts were fixed
without using CMB data. The simulator should not resume physical CMB promotion until those gates are
mathematically specified here and then implemented as deterministic receipts.
\end{remark}

\section{Compatibility With the Current Core Stack}

This section records the compatibility pass against the current core papers after the recent issue
closures. It is the guardrail for importing the older inflation-free draft.

\begin{longtable}{@{}p{0.28\textwidth}p{0.62\textwidth}@{}}
\toprule
Imported draft idea & Current core-compatible reading\\
\midrule
\endhead
\bottomrule
\endfoot
Inflation-free replacement &
Phase III continuation only. The compact paper's recovered core does not include an inflation
replacement, physical CMB likelihood, \(H_0/S_8\) branch, or dark-sector cosmology claim.\\
Finite normal form &
Use quotient-level fixed-cutoff normal forms on the declared branch, unique only modulo boundary
redundancy, implementation hiding, inert ancillary stabilization, and any required same-boundary
unique-extension condition. Do not read the old draft as selecting a unique microscopic
representative.\\
Screen Green spectrum and \(n_s=1-P/48\) &
Screen-level theorem or target until the source-only primordial bridge passes. Physical \(A_s\),
\(n_s\), running, isocurvature, phase coherence, and TT/TE/EE spectra require the source-stress,
single-clock, repair-gap, freezeout, radial-prior, null-space, and forward-residual receipts.\\
Dark/anomaly slot &
Imported from \pathref{extra/}. For a source-only primordial certification run, the dark
continuation is \texttt{OFF} unless a supplied abundance is explicitly typed
\texttt{CONDITIONAL\_SOURCE\_STATE}; transported \(Q_A\) is not by itself an OPH derivation of the
homogeneous anomaly abundance.\\
Scalar anomaly rows &
Rows for \(\rhoA\), \(\rhoAeq\), and \(\Bkernel\) are diagnostics unless the finite covariant
parent also emits \(w_A\), \(\csA\), \(\sigmaA\), \(\QA\), \(\GammaRec\), recipient stress when
\(\GammaRec>0\), gauge-independent variables, CDM-limit recovery, and refinement convergence.\\
Boltzmann and likelihood comparison &
Physical promotion requires immutable source, solver, and likelihood hashes, official likelihood
execution, and global CDM-limit reductions. Shard-local \texttt{any()} rollups or nonlinear
averages before global pooling do not satisfy the contract.\\
Vacuum language &
Finite reference states and free-field/lattice baselines remain reference ensembles. OPH-native
vacuum promotion requires the quotient-ensemble selector and positive-transfer or
reflection-positive gate from the compact/screen-microphysics theorem surface.\\
Simulator receipts &
Any future receipt cited here must carry exact source/config/solver/likelihood hashes. The 256k run
used for diagnostics records \texttt{git\_commit=unknown}, so it is not used as exact replay
provenance.\\
\end{longtable}

\section{Source Corpus}

This paper consolidates these active surfaces.
\begin{longtable}{@{}p{0.28\textwidth}p{0.62\textwidth}@{}}
\toprule
Surface & Imported role\\
\midrule
\endhead
\bottomrule
\endfoot
\pathref{cosmology/inflation_without_inflaton_observer_screen_synchronization.tex} &
Main inflation-free branch: finite screen federation, flatness, horizon coherence, screen Green
spectrum, amplitude, MaxEnt release, anomaly slot, transfer, and likelihood gates.\\
\pathref{cosmology/physical_cmb_theorem_program.md} &
Recent theorem-roadmap file identifying the missing physical CMB source, scale, stress, kernel,
transfer, and likelihood contracts.\\
\pathref{paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.tex} &
Compact recovered-core claim boundary and the first surface for later propagation.\\
\pathref{paper/tex_fragments/PAPER.tex} &
Main technical paper surface for global OPH theorem language.\\
\pathref{paper/tex_fragments/PRIMORDIAL_BRIDGE_THEOREMS.tex} &
Primordial bridge theorem status and screen-to-primordial finite-source conditions.\\
\pathref{paper/screen_microphysics_and_observer_synchronization.tex} &
Finite observer-screen carriers, records, patch ports, evidence bundles, and implementation
invariance.\\
\pathref{extra/oph_dark_matter_paper.tex} &
Collar-remainder dark/anomaly stress, galaxy equilibrium, dynamic stress, and cosmological kernel
contracts. This paper imports those contracts by reference; it does not duplicate the dark-sector
derivations.\\
\pathref{oph-physics-sim/runs/gcp_large_vis_256k_modkernel_20260623} &
Latest 256k-patch simulator evidence: strong CMB diagnostics, explicit false physical-prediction
receipt, and full visualizer export data. The run manifest records \texttt{git\_commit=unknown};
the canonical simulator repository is \SimSourceRepo, and the current public source reference
available during this consolidation is
\SimSourceCommit.\\
\end{longtable}

\begin{remark}[Simulator receipt provenance]
Whenever this paper mentions simulator receipts, the receipt artifacts should be traced to the
responsible commit in the canonical simulator repository, \SimSourceRepo. For the 256k run used here, the local artifact
\pathref{runs/gcp_large_vis_256k_modkernel_20260623/manifest.json} reports
\texttt{git\_commit=unknown}. Therefore the numerical run is cited as diagnostic evidence with
incomplete commit provenance. The available public source context at the time of this consolidation
is \SimSourceCommitURL, but that link is not asserted to be an exact run-replay hash for the 256k
artifacts. Future physical-promotion receipts must carry exact source, config, solver, and
likelihood hashes.
\end{remark}

\begin{remark}[Ownership boundary for extra papers]
Published and staging papers under \pathref{extra/} keep ownership of the dark-sector theory:
collar-remainder stress, galaxy equilibrium, dynamic repair-stress transport, cluster behavior, and
the detailed perturbation-kernel derivations. This cosmology program paper only records the
interface those papers must expose to the physical CMB/large-scale-structure pipeline. When it names
\(\rhoA(a)\), \(\Bkernel(k,a)\), \(\GammaRec(k,a)\), stress closure, or repair-stress transport, it
is naming imported source functions and receipts, not rederiving the dark sector here.
\end{remark}

\section{Imported Theorem Map}

The long inflation-free draft contains many theorem statements. This paper does not copy every proof
verbatim. Instead it gives them one public-core landing surface and keeps their dependency roles
visible.

\begin{longtable}{@{}p{0.30\textwidth}p{0.60\textwidth}@{}}
\toprule
Imported theorem family & Role in this paper\\
\midrule
\endhead
\bottomrule
\endfoot
Finite synchronization normal form &
Defines the early observer-facing quotient state whose repair normal form replaces an assumed
smooth primordial substrate, with uniqueness read modulo the current compact-paper quotient
equivalences.\\
FLRW curvature holonomy, flat-sector selection, and curvature damping &
Owns the flatness branch: exact \(k=0\) when zero visible holonomy is selected, or a bounded
residual when the curvature-repair margin stays positive.\\
Diffusive horizon no-go, same-boundary coherence, and low-\(k\) repair gap &
Separates a failed purely local diffusion story from the allowed same-boundary or uniform low-\(k\)
synchronization mechanisms.\\
Screen Green spectrum, Mellin lift, edge-center scalar opportunities, \(\Zsix\) reserve, and
half-collar sampling &
Owns the screen-level near-scale-invariant covariance and the red tilt target \(n_s=1-P/48\);
physical primordial status waits for the source-only bridge receipts.\\
Finite release collar state, scalar release code, and scalar amplitude theorem &
Owns \(\Azeta\) as a finite source artifact rather than a fitted amplitude.\\
MaxEnt release, entropy transport, BBN-safe release, recombination inheritance, and adiabaticity &
Connects the synchronized finite screen/collar state to a hot radiation branch with ordinary
low-energy thermal history.\\
Freezeout, scalar quotient record, gauge-invariant \(\zeta\), isocurvature decay, and
superhorizon conservation &
Imported only through the stricter primordial bridge: total stress closure, single clock, repair
gap, freezeout, growing mode, isocurvature, phase coherence, radial prior, null-space, and forward
residual.\\
Finite homogeneous anomaly charge, no double counting, packet moments, cold anomaly, Bianchi
exchange, no-slip lensing, and linear anomaly transfer &
Imported from the dark-sector papers in \pathref{extra/}; this paper only records the CMB/LSS
handoff interface and receipt gates.\\
Universe Simulation certificate bundle, no-data-use theorem, finite-certificate branch, Boltzmann
stability, likelihood promotion, and CMB admissibility &
Owns the promotion rule: source-only finite artifacts first, frozen transfer and likelihood second,
physical CMB claim last.\\
Tensor repair gap and finite-collar non-Gaussianity &
Records secondary predictions to be tested only after the primary scalar/source/stress gates close.\\
\end{longtable}

\section{Extended Cosmology Agenda}

The local cosmology notes identify several OPH-native prediction surfaces beyond the immediate CMB
gate. They are not independent claims yet; they are the next paper tracks once the finite-source
contract is stable.

\begin{enumerate}[leftmargin=2em]
\item \textbf{CMB as observer-consensus fossil.} The highest-value target is still the CMB: largest
observable scales should carry relics of finite observer synchronization, not merely a fitted
inflationary initial spectrum.
\item \textbf{\(\Lambda\) from observer capacity.} The screen-capacity branch relates the de Sitter
scale to finite horizon capacity. A full cosmology paper should derive the equation of state,
possible time evolution, and any deviation from \(w=-1\).
\item \textbf{Full cosmological dark sector.} The dark paper's galaxy layer is not enough. CMB,
BAO, weak lensing, growth, and \(S_8\) need the transported repair-stress perturbation branch.
\item \textbf{\(H_0\) and \(S_8\) predictions.} Once the scale bridge and anomaly kernels are fixed,
the branch should emit blind values or intervals for \(H_0\) and \(S_8\), rather than tuning toward
the current tensions.
\item \textbf{Large-scale topology.} Finite observer-accessible screens make global topology and
matching-circle style signatures natural tests.
\item \textbf{Consensus hierarchy of structure.} Galaxy, cluster, and supercluster formation should
be investigated as a hierarchy of stable consensus attractors, not only as density perturbation
growth in a fixed background.
\item \textbf{Cosmological arrow of time.} OPH has native records, checkpoints, and continuation
laws; these should be used to formulate the low-entropy past condition as a finite-record boundary
condition.
\item \textbf{Cosmological neutrino background.} The particle/mass branch should eventually feed
neutrino background and free-streaming predictions into the same frozen likelihood contract.
\end{enumerate}

\section{Finite Cosmological State}

\begin{definition}[Early OPH screen federation]
An early OPH cosmological state at regulator \(r\) is a finite patch federation
\[
\mathcal F_r=
\left(
V_r,E_r,\{\mathcal A_i,\rho_i,\mathcal R_i\}_{i\in V_r},
\{\mathcal I_e,\pi_{i,e}\}_{e\in E_r},
\mathcal U_r,\mathrm{Chk}_r
\right),
\]
with finite accessible algebras, record algebras, visible overlap interfaces, repair instruments,
and checkpoint data. Its physical content is the quotient under hidden carrier coordinates that do
not affect visible interface records, repair maps, or checkpoint continuation.
\end{definition}

\begin{definition}[Source-only finite artifact]
A finite artifact \(X\) is source-only for cosmology if it is a deterministic functional of declared
OPH source data, release-branch constants, and standard non-CMB physical constants, and if its
dependency manifest excludes CMB, BAO, supernova, weak-lensing, RSD, SPARC, cluster, or other
observational likelihood values used to evaluate the prediction.
\end{definition}

\begin{definition}[Physical CMB promotion]
An OPH CMB run is physically promoted only when the primordial source, scale bridge, dark/anomaly
stress kernels, Boltzmann solver input files, solver version/tolerances, and likelihood code/data
hashes are all frozen before likelihood evaluation, and all source functions are source-only finite
artifacts.
\end{definition}

\section{Inflation-Free Branch}

The inflation-free branch replaces inflation's jobs rather than reproducing an inflaton. Its
load-bearing theorem stack is:
\begin{enumerate}[leftmargin=2em]
\item quotient-level observer-facing normal form for the early screen/collar federation, with the
current compact-paper quotient equivalences;
\item zero visible spatial holonomy or positive curvature-holonomy damping for flatness;
\item same-boundary scalar normal form or a low-\(k\) repair gap for horizon coherence;
\item screen Green spectrum for near scale invariance;
\item protected \(\Zsix\) half-collar reserve for the red spectral exponent;
\item finite scalar release code for \(\Azeta\);
\item MaxEnt release and common release clock for a hot adiabatic start;
\item imported dark/anomaly stress variables for the pre-recombination CDM-like slot, when the
\pathref{extra/} dark-sector source contract permits them;
\item Boltzmann transfer and frozen likelihood for observational comparison.
\end{enumerate}

\begin{theorem}[Conditional OPH replacement of inflation]
Assume a cofinal family of finite early OPH screen federations has a quotient-level
observer-facing normal-form projection on a declared branch, with uniqueness understood modulo
boundary redundancy, implementation hiding, inert ancillary stabilization, and any same-boundary
unique-extension condition required by the branch. Assume visible FLRW curvature holonomy is
selected to zero or dynamically damped, every CMB-scale scalar mode shares the same boundary normal
form or satisfies a uniform low-\(k\) repair gap, the scale-free scalar screen repair cascade realizes
the half-collar spectral reserve, the source-only primordial bridge receipts pass, the finite release
code emits \(\Azeta\), and the imported dark/anomaly sector supplies a permitted CDM-like source
state through recombination. Then the branch supplies flatness, horizon coherence, near scale
invariance, hot adiabatic initial data, and acoustic-transfer input without an inflaton degree of
freedom.
\end{theorem}

\begin{proof}
The proof is a dependency composition. The quotient normal-form projection gives a finite
observer-facing early state on the declared branch, not a unique hidden representative. Visible
holonomy selection or damping gives the flat sector. Same-boundary repair or a low-\(k\) gap gives
coherence on the observed CMB band. The screen Green spectrum with half-collar reserve gives the
screen-level power law
\[
\Delta_\zeta^2(k)=\Azeta\left(\frac{k}{k_\star}\right)^{-P/48},
\qquad
n_s=1-\frac{P}{48}.
\]
The source-only bridge receipts type that screen scalar as a primordial curvature source; without
them it remains a screen theorem. The finite release code fixes the amplitude before comparison.
MaxEnt release gives a hot radiation state and the common clock gives adiabatic leading
perturbations. If the imported anomaly stress branch is an admissible source state through
recombination, the acoustic peaks are computed by ordinary Einstein-Boltzmann transfer from those
finite inputs.
\end{proof}

\begin{remark}[Current status of the theorem]
The theorem is conditional because several premises are still open theorem issues. The branch is
sharp enough to simulate, but not sharp enough to promote diagnostic CMB agreement to a physical
prediction.
\end{remark}

\section{Physical CMB Finite-Source Contract}

The simulator's false physical CMB receipt identified a precise theorem contract. The following
objects must be theorem-grade finite artifacts:
\[
\Azeta,\qquad q_{\rm IR},\qquad \ell_{\rm IR},\qquad
\rhoA(a),\qquad \rhoAeq(a),\qquad \Bkernel(k,a),\qquad \GammaRec(k,a),
\]
plus full stress variables, freezeout, physical mode calibration, and \(\NCRC\) provenance.

\begin{target}[Finite-source input contract]
The paper stack must define pass/fail receipts for:
\begin{enumerate}[leftmargin=2em]
\item a source-provenance dependency DAG for all CMB source inputs;
\item globally pooled sufficient-statistic reducers before nonlinear source estimates;
\item the status of \(\NCRC\) as a consensus invariant, additive capacity, or theorem-side constant;
\item finite derivations of \(\Azeta\), \(q_{\rm IR}\), and \(\ell_{\rm IR}\);
\item total stress closure, single-clock normal form, entropy repair gap, curvature evolution,
adiabatic growing mode, isocurvature bound, phase coherence, screen-to-radial lift, radial null-space,
forward residual, and finite freezeout receipts;
\item physical \(k\), \(\ell\), scale-factor, and redshift calibration;
\item source-only imported dark-sector functions \(\rhoA(a)\), \(\rhoAeq(a)\), \(w_A(a)\),
\(\csA(k,a)\), \(\sigmaA(k,a)\), \(\QA\), \(\Bkernel(k,a)\), and \(\GammaRec(k,a)\), where the
chosen dark-continuation mode permits them.
\end{enumerate}
\end{target}

\begin{proposition}[Why the 256k CMB curve is not yet a physical prediction]
The 256k OPH-FPE run may be used as a measurement-facing diagnostic, but not as a physical CMB
prediction, because its promotion report marks the finite-source input contract false and lists
missing source provenance, missing pooled reducers, missing \(\NCRC\) invariant status, non-finite
\(\Azeta\), missing screen-to-primordial lift, non-finite \(q_{\rm IR}\) and \(\ell_{\rm IR}\),
non-finite \(\rhoA\) and \(\Bkernel\), missing finite covariant parent receipt, missing stress
closure, missing full fluid/exchange variables, missing gauge/causal/refinement certificates,
missing freezeout, missing official likelihood and CDM-limit reductions, and missing frozen solver
and likelihood hashes.
\end{proposition}

\section{Physical Scale Bridge}

The screen simulator has natural finite labels: patches, caps, overlaps, spherical harmonics,
repair depths, and collar coordinates. A physical CMB prediction needs more. It needs a theorem that
maps those labels to physical comoving \(k\), multipole \(\ell\), scale factor \(a\), redshift
\(z\), and freezeout surface.

\begin{target}[OPH scale bridge]
Define a finite bridge
\[
\mathcal S_{\rm OPH}:
(r,\hbox{screen mode},\hbox{collar mode},\hbox{repair clock})
\longmapsto
(k,\ell,a,z,\eta)
\]
that is invariant under hidden carrier representatives, compatible with regulator refinement, and
independent of post-hoc peak alignment.
\end{target}

Proxy variables such as inverse cap opening angle can remain useful diagnostics. They cannot clear
the physical \(k\)-gate unless the scale bridge proves that the proxy converges to the physical
comoving mode label used by the transfer solver.

\section{Dark/Anomaly Interface Imported from Extra}

The dark/anomaly slot is the largest cosmology-facing bridge between the OPH dark-matter paper and
the CMB program. The dark-sector papers in \pathref{extra/} own the derivation: collar remainder
stress, settled galaxy response, dynamic transport, cluster behavior, and perturbation kernels.
This paper only states the interface the CMB program requires from those papers. Cosmology needs the
imported dark sector to expose a transported stress component with background density,
perturbations, exchange terms, gauge-invariant variables, and the CDM-limit switch-off check.

\begin{definition}[Imported finite covariant collar-packet parent interface]
For the purpose of this cosmology program, the finite covariant collar-packet parent is an imported
\pathref{extra/}-owned finite artifact interface
\[
\mathcal P_A=
(\mathcal C_r,Z_r,A_r,R_r,G_r,\pi_r,L_r,Q_r,D_r)
\]
where \(Z_r\) splits anomaly and recipient packet states, \(\pi_r\) is the finite equilibrium
packet functional, \(L_r\) is the repair generator, \(Q_r\) records energy-momentum reaction
channels, and \(D_r\) records any causal auxiliary response. The interface emits packet stress
moments
\[
\rho_A,\quad P_A,\quad q_A,\quad \pi_A,
\]
and source variables
\[
\rhoA(a),\quad \rhoAeq(a),\quad w_A(a),\quad \csA(k,a),\quad
\sigmaA(k,a),\quad \QA,\quad \Bkernel(k,a),\quad \GammaRec(k,a),
\]
with explicit conservation or exchange equations, recipient stress for nonzero exchange, gauge
projection, causal response, regulator-refinement convergence, and \(B_A\) built from the
anomaly-frame baryon density \(n_b^{(A)}=-u_{A\mu}J_b^\mu\).
\end{definition}

\begin{target}[Imported stress-parent receipt]
The simulator receipt for the imported parent must fail unless the owning dark-sector paper and its
evidence bundle certify all of the following:
\begin{enumerate}[leftmargin=2em]
\item exact finite stress-energy closure for anomaly plus recipient stresses;
\item explicit recipient stress whenever \(\GammaRec\ne0\);
\item detailed balance or a declared nonequilibrium exchange law;
\item gauge independence of the emitted perturbation variables, including the anomaly-frame
baryon-density definition of \(B_A\);
\item causal response with subluminal finite characteristics;
\item convergence under regulator refinement;
\item recovery of the CDM branch when exchange, pressure, sound speed, and anisotropic stress are
switched off.
\end{enumerate}
\end{target}

\begin{remark}[Dark continuation modes]
For a source-only primordial certification run, the current dark-sector paper recommends
\texttt{dark\_continuation = OFF}. A supplied dark abundance may enter only as
\texttt{dark\_continuation = CONDITIONAL\_SOURCE\_STATE} until the \pathref{extra/} theorem surface
derives the homogeneous anomaly abundance and finite kinetic stress construction.
\end{remark}

\section{Physical Kernel Interface}

The physical kernels are not scalar rows in a table. They are imported finite functionals with
units, gauge-invariant definitions, paired controls, and refinement margins. Their derivation stays
in \pathref{extra/}; this paper only states what the CMB/LSS pipeline must receive.

\begin{target}[Physical anomaly kernel interface]
The \pathref{extra/} dark-sector papers must define deterministic receipts
\[
\texttt{RHO\_A\_SOURCE\_RECEIPT},\qquad
\texttt{B\_A\_KERNEL\_RECEIPT},\qquad
\texttt{GAMMA\_REC\_SOURCE\_RECEIPT}.
\]
These receipts pass only when \(\rhoA(a)\), \(\Bkernel(k,a)\), and \(\GammaRec(k,a)\) are emitted
with \(\rhoAeq(a)\), \(w_A(a)\), \(\csA(k,a)\), \(\sigmaA(k,a)\), and \(\QA\) from the finite
parent, physical scale calibration, gauge consistency, paired perturbation controls, CDM-limit
recovery, and refinement convergence. The cosmology program consumes the emitted functions but does
not redefine the dark-sector source law.
\end{target}

Diagnostic rows remain useful for debugging. They should be plotted, stress-tested, and compared to
controls. They should not be accepted by the physical CMB contract unless they are promoted by the
kernel receipts above.

\section{Boltzmann Transfer and Frozen Likelihood}

Once source functions are finite and physical, the transfer problem becomes ordinary cosmology.
OPH does not need a special CMB plotting rule. It needs a frozen handoff to CAMB, CLASS, or a
declared independent Einstein-Boltzmann solver.

\begin{target}[Frozen transfer and likelihood protocol]
A physical OPH CMB prediction requires:
\begin{enumerate}[leftmargin=2em]
\item immutable hashes for source artifacts;
\item immutable hashes for solver source, version, tolerances, and input files;
\item immutable hashes for likelihood code, datasets, covariances, masks, and nuisance priors;
\item a no-data-use manifest showing that observational likelihood values did not enter source
artifact generation;
\item global pooled reducers for nonlinear source estimates and global CDM-limit checks;
\item official likelihood execution readiness, not only a diagnostic binned-table comparison;
\item a falsification rule fixed before the likelihood run.
\end{enumerate}
\end{target}

\begin{remark}[Global reducers only]
Shard-local nonlinear averages and shard-local \texttt{any()} rollups are not promotion rules. The
source artifact must pool additive sufficient statistics globally, with validated units, coordinate
grids, coverage, duplicate policy, interpolation policy, and covariance, before any nonlinear
quantity such as amplitude, rank, condition number, isocurvature leakage, \(\Bkernel\), \(\rhoA\),
or \(\GammaRec\) is evaluated.
\end{remark}

\begin{remark}[Comparison versus prediction]
The current best OPH diagnostic model is scientifically useful because it is close: shape
correlation \(0.9951542364\), normalized RMSE \(0.0984455548\), amplitude-fit
\(\chi^2/{\rm bin}=41.6684770597\), zero mean peak-location error, and mean peak-height fractional
error about \(0.0704905\). Those numbers justify fixing the theorem gates. They do not replace the
gates.
\end{remark}

\section{Vacuum and Quantum-Fluctuation Boundary}

The same finite-source discipline applies to vacuum claims. Seed noise, repair jitter, and
reference free-field baselines are not an OPH-native quantum vacuum.

\begin{target}[OPH-native vacuum gate]
An OPH-native vacuum simulation needs a quotient ensemble measure or density operator on the
observable quotient algebra, refinement compatibility, implementation invariance, and a sampler
correctness proof such as exact sampling or detailed balance. Without this gate, vacuum-like fields
in the simulator are reference baselines or diagnostics.
\end{target}

\section{Issue Ledger}

The paper-side open issues should target this manuscript before simulation promotion resumes.

\begin{longtable}{@{}p{0.16\textwidth}p{0.34\textwidth}p{0.40\textwidth}@{}}
\toprule
Issue & Paper-side theorem gate & Primary section here\\
\midrule
\endhead
\bottomrule
\endfoot
\#360 & Quotient ensemble measure and OPH-native vacuum gate & Vacuum and quantum-fluctuation boundary\\
\#363 & Boltzmann transfer and frozen likelihood closure & Boltzmann transfer and frozen likelihood\\
\#371 & Physical CMB finite-source contract hardening & Physical CMB finite-source contract\\
\#372 & OPH physical scale bridge and mode calibration & Physical scale bridge\\
\#373 & Finite covariant collar-packet stress parent & Dark/anomaly interface imported from \pathref{extra/}\\
\#374 & Physical \(B_A(k,a)\), \(\rho_A(a)\), and \(\Gamma_{\rm rec}(k,a)\) kernels & Physical kernel interface\\
\#329 & Flat-sector selection for the inflation-free branch & Inflation-free branch\\
\#330 & Screen-spectrum derivation for OPH inflation alternative & Inflation-free branch and source contract\\
\#319 & Collar remainder stress source & Dark/anomaly interface imported from \pathref{extra/}\\
\#322 & Repair-stress transport and relaxation & Dark/anomaly interface imported from \pathref{extra/}\\
\#323 & Linear OPH repair-stress perturbations & Physical kernel interface\\
\#375 & Consolidation under \pathref{/cosmology} & Closed by this staging paper\\
\end{longtable}

\section{Simulator Resumption Rule}

The simulator should resume physical-promotion work only after the paper defines the exact receipt
semantics for the objects it is being asked to produce. A good order is:
\begin{enumerate}[leftmargin=2em]
\item implement the finite-source dependency DAG and no-data-use firewall;
\item implement global pooled reducers for all nonlinear source estimates;
\item implement the physical scale bridge and freezeout certificate;
\item implement the imported finite covariant parent and stress-closure receipts from the
\pathref{extra/} dark-sector theory;
\item implement physical \(\rhoA\), \(\Bkernel\), and \(\GammaRec\) kernel receipts as imported
dark-sector source functions;
\item freeze source, solver, and likelihood hashes;
\item run official likelihood comparisons and global CDM-limit reductions;
\item only then label the result a physical CMB prediction.
\end{enumerate}

The simulator can still run diagnostics earlier, including visualization payloads, CMB overlays,
vacuum baselines, defect worldlines, observer cameras, and H3 readouts. Those outputs should carry
diagnostic labels until the relevant receipt passes.

\section{Conclusion}

The current OPH cosmology program is promising because the simulator almost-fits are not random
noise: they expose stable structure close enough to make the theorem gates worth closing. The same
data also explain why the gates are necessary. A physical cosmology prediction needs finite
source-only objects, physical scale calibration, covariant stress closure, physical anomaly kernels,
and frozen likelihoods. This paper is the staging surface for that work. Once its issue gates close,
the simulator can resume with a precise target instead of trying to infer missing theorem semantics
from diagnostic data.

\begin{thebibliography}{99}

\bibitem{ophcompact}
B.~M\"uller, A.~Osika, K.~Xue, and P.~Nguyen,
\emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency},
OPH compact paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/recovering_relativity_and_standard_model_structure_from_observer_overlap_consistency_compact.pdf}

\bibitem{ophsynthesis}
B.~M\"uller, A.~Osika, K.~Xue, B.~Cassie, P.~Nguyen, M.~Poneder, and K.~A.~Anirudha,
\emph{Observers Are All You Need},
OPH synthesis paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/observers_are_all_you_need.pdf}

\bibitem{ophconsensus}
B.~M\"uller, A.~Osika, K.~Xue, and P.~Nguyen,
\emph{Reality as Consensus Protocol},
OPH consensus paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/reality_as_consensus_protocol.pdf}

\bibitem{ophmicro}
B.~M\"uller and K.~Xue,
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH},
OPH microphysics paper, release \OPHPaperReleaseID, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/paper/screen_microphysics_and_observer_synchronization.pdf}

\bibitem{ophdark}
B.~M\"uller,
\emph{Observer-Patch Holography and the Dark Matter Phenomenon},
OPH extra paper, 2026.
\url{https://github.com/FloatingPragma/observer-patch-holography/blob/main/extra/oph_dark_matter_paper.pdf}

\bibitem{ophinflationdraft}
B.~M\"uller,
\emph{Inflation Without an Inflaton: Observer-Screen Synchronization as an OPH Cosmology Branch},
workspace cosmology draft, 2026.

\bibitem{ophsim}
B.~M\"uller,
\emph{OPH-FPE finite screen-consensus and cosmology diagnostics}.
\url{https://github.com/muellerberndt/oph-physics-sim}

\bibitem{planck2018}
Planck Collaboration,
\emph{Planck 2018 results. VI. Cosmological parameters},
Astron.\ Astrophys.\ 641, A6, 2020, arXiv:1807.06209.
\url{https://arxiv.org/abs/1807.06209}

\bibitem{camb}
A.~Lewis, A.~Challinor, and A.~Lasenby,
\emph{Efficient computation of CMB anisotropies in closed FRW models},
Astrophys.\ J.\ 538, 473--476, 2000, arXiv:astro-ph/9911177.
\url{https://arxiv.org/abs/astro-ph/9911177}

\bibitem{class}
D.~Blas, J.~Lesgourgues, and T.~Tram,
\emph{The Cosmic Linear Anisotropy Solving System (CLASS). Part II: Approximation schemes},
JCAP 07, 034, 2011, arXiv:1104.2933.
\url{https://arxiv.org/abs/1104.2933}

\end{thebibliography}

\end{document}
