\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\IfFileExists{paper/release_info.tex}{
  \input{paper/release_info.tex}
}{
  \IfFileExists{../paper/release_info.tex}{
    \input{../paper/release_info.tex}
  }{
    \newcommand{\OPHPaperReleaseID}{r1518}
    \newcommand{\OPHPaperReleaseDate}{July 7, 2026}
    \newcommand{\OPHPaperReleaseBanner}{%
      \begin{center}
      \small\textbf{Paper release:} \texttt{\OPHPaperReleaseID}\quad\textbf{Released:} \OPHPaperReleaseDate
      \end{center}}
  }
}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{target}[theorem]{Target}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{plain}

\newcommand{\OPH}{\mathrm{OPH}}
\newcommand{\LCDM}{\Lambda\mathrm{CDM}}
\newcommand{\Zsix}{\mathbb Z_6}
\newcommand{\pathref}[1]{\nolinkurl{#1}}
\newcommand{\SimSourceRepo}{\url{https://github.com/muellerberndt/oph-physics-sim}}

\title{Inflation Without an Inflaton:\\
Observer-Screen Synchronization as an OPH Cosmology Branch}
\author{B.\ M\"uller}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
Observer-Patch Holography (OPH) cosmology replaces the inflaton with finite observer-screen
synchronization. Flatness, horizon coherence, near scale invariance, hot source
release, and acoustic-transfer inputs are treated as jobs for the finite screen
state rather than for a new scalar field.

The conditional source theorem fixes the screen amplitude from a primitive
collar release law and the tilt from an edge-center generator. The radial
packet proves one-shell non-identifiability and supplies physical dilation and
cross-covariance tomography as conditional uniqueness routes. Physical
cosmological status requires one finite source instantiation, transfer
calculation, and likelihood; simulator outputs without those receipts are
diagnostics.
\end{abstract}

\section{Scope}

This is a technical companion outside the release bundle. It states the
inflation-free branch against the compact, screen-microphysics, dark-sector,
and finite-source CMB papers.

\section{Finite Quotient and Claim-Tier Firewall}

\input{../paper/tex_fragments/FINITE_QUOTIENT_ENSEMBLE_THEOREMS.tex}

\input{../paper/tex_fragments/SCREEN_SPECTRUM_THEOREMS.tex}

\section{Branch Thesis}

The branch claim is:
\[
\boxed{
\begin{gathered}
\text{On a finite-source branch, OPH may replace the logical jobs of}\\
\text{inflation by direct/CMH spatial-holonomy selection, same-boundary or low-}k\text{ repair coherence,}\\
\text{a geometric screen spectrum, MaxEnt release, and ordinary Boltzmann transfer.}
\end{gathered}}
\]
This claim is not part of the recovered SM/GR core.  It becomes predictive only when the source
objects are fixed before observational comparison.
Screen synchronization instantiates C3 of the project consistency stack:
modular self-consistency, with internal time generated by the state--algebra
pair rather than by an external clock.

Coherent-matter same-channel forcing supplies a local scalar-channel identity for
nondegenerate OPH-coherent material sources under Scalar Edge-Center Exhaustion.
It does not supply the finite covariant dark-stress parent needed for
cosmological \(w_A\), \(c_{s,A}^2\), \(\sigma_A\), \(Q_A^\mu\),
recipient-stress, gauge-variable, CDM-limit, and refinement-convergence
receipts.

The anomaly abundance selector is owned by
\pathref{cosmology/oph_dark_matter_paper.tex}.  The finite-source branch may
use a source-only \(\bar\rho_A(a)\) only when
\[
\emph{anomaly abundance source receipt}
\]
passes.  Otherwise the dark continuation is either \(\texttt{OFF}\) or
\(\text{conditional source state}\).

\section{Paper Targets}

\begin{longtable}{@{}p{0.28\textwidth}p{0.62\textwidth}@{}}
\toprule
Target & Required theorem or receipt\\
\midrule
\endhead
\bottomrule
\endfoot
Finite early state & Quotient normal-form branch with declared base measure and implementation
invariance.\\
Flatness & Zero clock-slice spatial Levi--Civita holonomy identifies \(\kappa=0\). Exact selection
requires \textsc{DirectTheorem}, \textsc{ConditionalCMH}, or \textsc{ExplicitAssumption}; damping
is only an approximate \(|K|\) or \(|\Omega_K|\) bound.\\
Horizon coherence & Same-boundary unique-extension theorem or a uniform low-\(k\) repair gap.\\
Near scale invariance & Geometric screen scalar, normalized scalar precision, source release
energy, infinitesimal reserve-generator tilt, and angular screen-spectrum receipts.\\
Amplitude & The conditional theorem fixes \(A_q=2E_q^{\rm src}/d\) and its source-family
conversion to \(A_\zeta\). A finite collar release law and energy receipt must supply their
values without CMB data.\\
Hot start & MaxEnt release into the realized radiation branch with a common release clock.\\
Acoustic transfer & Declared source functions and Boltzmann transfer owned by the finite-source CMB
and data-contract papers.\\
\end{longtable}

\section{Simulator Contract}

The simulator reference is \SimSourceRepo.  For this paper the simulator may emit diagnostic
screen spectra, observer-screen synchronization receipts, and release-amplitude candidates.  It
must not label them inflation replacement, OPH primordial field, or physical CMB prediction unless
the E4 and E5 receipts in the shared theorem fragment pass in the concrete run bundle.

\section{Flatness Boundary}

The flatness branch is split into identification and selection.  On a clocked FLRW continuation
with \(u_a=-N\nabla_a\chi\), \(h_{ab}=g_{ab}+u_au_b\), and
\(K(\tau)=\kappa/a(\tau)^2\), the area-normalized small-loop holonomy of the spatial
Levi--Civita connection identifies \(K=0\) and hence \(\kappa=0\).  It does not select that sector
from the raw FLRW fiber.  The simulator must therefore report one of
\(\textsc{DirectTheorem}\), \(\textsc{ConditionalCMH}\), \(\textsc{ExplicitAssumption}\), or
\(\textsc{OpenTheorem}\).  S3 screen/collar defect decay is a repair diagnostic, not a spatial
curvature holonomy.  Curvature damping can certify only an \(\textsc{ApproximateBound}\) on
\(|K|\) or \(|\Omega_K|\).

\section{Screen-Spectrum Branch}

The load-bearing screen result is the angular screen covariance, not a CMB spectrum:
\[
  C_\ell^q
  =
  A_q\frac{\Gamma(\ell-\theta/2)}{\Gamma(\ell+2+\theta/2)}.
\]
This statement requires the geometric \(q_r\) of Definition~\ref{def:oph-screen-scalar}, a
normalized conformal precision operator \(K_{\theta,r}\), the primitive collar release law,
\(E^{\rm src}_{q,r}\), the MaxEnt covariance theorem, and a finite-to-continuum refinement error
budget. The edge-center theorem gives
\[
\theta=\frac{P_\star}{48},\qquad
n_s=1-\frac{P_\star}{48},\qquad
\kappa_{\rm rep}^{\rm edge}=\frac{P_\star}{48(P_\star-\varphi)}.
\]
Its premise is a source-emitted full-collar generator density \(P_\star/24\) with the
orientation-half identity. A finite one-step survival probability is converted through
\(-\log u/\log b\). The \(e(P_\star-\varphi)\) clock branch is a diagnostic alternative.
The finite generator and clock receipt is work in progress.

Under the declared source dilation cocycle, the primordial power law
\[
  \Delta_\zeta^2(k)=A_\zeta\left(\frac{k}{k_\star}\right)^{-\theta}
\]
is the unique member of the one-dimensional source family. The exact thin-shell identity fixes
the amplitude conversion
\[
A_\zeta=\frac{A_q}{\pi^{3/2}}
\frac{\Gamma(3/2+\theta/2)}{\Gamma(1+\theta/2)}
\]
at the source pivot. A finite run requires \(R_\star\), the radial window, the unrestricted
null-space report, the forward residual, and the physical scale. The screen theorem proves no
TT, TE, EE, lensing, acoustic peak, or likelihood statement.

\section{Unclosed Claim Boundaries}

\begin{enumerate}[leftmargin=2em]
\item Prove the same-boundary or low-\(k\) coherence branch in quotient language.
\item Emit the geometric collar-volume field
\(q_r=\Pi_{\ge2,r}(1/3)\log(J_{X,r}/\bar J_{X,r})\) from one finite source.
\item Emit the primitive collar release law and pooled release energy that fix \(A_q\).
\item Emit the full-collar infinitesimal reserve generator and orientation-half receipt that
instantiate the conditional \(P_\star/48\) theorem.
\item Pass the source-stress, clock, freezeout, physical-scale, radial-window, null-space, and
forward-residual receipts on the same DAG.
\item Hand the resulting source inputs to the CMB and likelihood-contract papers.
\end{enumerate}

\end{document}
