\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{longtable,booktabs,array,multirow}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{framed}
\usepackage{fancyvrb}
\usepackage{ragged2e}
\usepackage{hyperref}
\usepackage{xurl}
\input{release_info.tex}

% Springer/pdflatex compatibility: provide fallbacks for Unicode math/text glyphs.
\newcounter{none}
\providecommand{\theHnone}{\arabic{none}}
\providecommand{\textsubscript}[1]{$_{\mathrm{#1}}$}
\newcommand{\ellbar}{\bar{\ell}}
\newcommand{\ophid}[1]{\path{#1}}
\ifdefined\DeclareUnicodeCharacter
\DeclareUnicodeCharacter{00B1}{\ensuremath{\pm}}
\DeclareUnicodeCharacter{00B2}{\textsuperscript{2}}
\DeclareUnicodeCharacter{00B3}{\textsuperscript{3}}
\DeclareUnicodeCharacter{00B7}{\ensuremath{\cdot}}
\DeclareUnicodeCharacter{00B9}{\textsuperscript{1}}
\DeclareUnicodeCharacter{00D7}{\ensuremath{\times}}
\DeclareUnicodeCharacter{02B8}{\textsuperscript{y}}
\DeclareUnicodeCharacter{0393}{\ensuremath{\Gamma}}
\DeclareUnicodeCharacter{0394}{\ensuremath{\Delta}}
\DeclareUnicodeCharacter{039B}{\ensuremath{\Lambda}}
\DeclareUnicodeCharacter{03A3}{\ensuremath{\Sigma}}
\DeclareUnicodeCharacter{03A6}{\ensuremath{\Phi}}
\DeclareUnicodeCharacter{03A9}{\ensuremath{\Omega}}
\DeclareUnicodeCharacter{03B1}{\ensuremath{\alpha}}
\DeclareUnicodeCharacter{03B2}{\ensuremath{\beta}}
\DeclareUnicodeCharacter{03B3}{\ensuremath{\gamma}}
\DeclareUnicodeCharacter{03B4}{\ensuremath{\delta}}
\DeclareUnicodeCharacter{03B5}{\ensuremath{\varepsilon}}
\DeclareUnicodeCharacter{03B7}{\ensuremath{\eta}}
\DeclareUnicodeCharacter{03B8}{\ensuremath{\theta}}
\DeclareUnicodeCharacter{03BA}{\ensuremath{\kappa}}
\DeclareUnicodeCharacter{03BB}{\ensuremath{\lambda}}
\DeclareUnicodeCharacter{03BC}{\ensuremath{\mu}}
\DeclareUnicodeCharacter{03BD}{\ensuremath{\nu}}
\DeclareUnicodeCharacter{03BE}{\ensuremath{\xi}}
\DeclareUnicodeCharacter{03C0}{\ensuremath{\pi}}
\DeclareUnicodeCharacter{03C1}{\ensuremath{\rho}}
\DeclareUnicodeCharacter{03C3}{\ensuremath{\sigma}}
\DeclareUnicodeCharacter{03C4}{\ensuremath{\tau}}
\DeclareUnicodeCharacter{03C6}{\ensuremath{\phi}}
\DeclareUnicodeCharacter{03C7}{\ensuremath{\chi}}
\DeclareUnicodeCharacter{03C8}{\ensuremath{\psi}}
\DeclareUnicodeCharacter{03C9}{\ensuremath{\omega}}
\DeclareUnicodeCharacter{1D9C}{\textsuperscript{c}}
\DeclareUnicodeCharacter{2020}{\ensuremath{\dagger}}
\DeclareUnicodeCharacter{2070}{\textsuperscript{0}}
\DeclareUnicodeCharacter{2074}{\textsuperscript{4}}
\DeclareUnicodeCharacter{2075}{\textsuperscript{5}}
\DeclareUnicodeCharacter{2076}{\textsuperscript{6}}
\DeclareUnicodeCharacter{2077}{\textsuperscript{7}}
\DeclareUnicodeCharacter{2078}{\textsuperscript{8}}
\DeclareUnicodeCharacter{2079}{\textsuperscript{9}}
\DeclareUnicodeCharacter{207A}{\textsuperscript{+}}
\DeclareUnicodeCharacter{207B}{\textsuperscript{-}}
\DeclareUnicodeCharacter{207D}{\textsuperscript{(}}
\DeclareUnicodeCharacter{207E}{\textsuperscript{)}}
\DeclareUnicodeCharacter{207F}{\textsuperscript{n}}
\DeclareUnicodeCharacter{2080}{\textsubscript{0}}
\DeclareUnicodeCharacter{2081}{\textsubscript{1}}
\DeclareUnicodeCharacter{2082}{\textsubscript{2}}
\DeclareUnicodeCharacter{2083}{\textsubscript{3}}
\DeclareUnicodeCharacter{2085}{\textsubscript{5}}
\DeclareUnicodeCharacter{2086}{\textsubscript{6}}
\DeclareUnicodeCharacter{2087}{\textsubscript{7}}
\DeclareUnicodeCharacter{2088}{\textsubscript{8}}
\DeclareUnicodeCharacter{208B}{\textsubscript{-}}
\DeclareUnicodeCharacter{2102}{\ensuremath{\mathbb{C}}}
\DeclareUnicodeCharacter{210B}{\ensuremath{\mathcal{H}}}
\DeclareUnicodeCharacter{2113}{\ensuremath{\ell}}
\DeclareUnicodeCharacter{2124}{\ensuremath{\mathbb{Z}}}
\DeclareUnicodeCharacter{2192}{\ensuremath{\to}}
\DeclareUnicodeCharacter{2193}{\ensuremath{\downarrow}}
\DeclareUnicodeCharacter{2194}{\ensuremath{\leftrightarrow}}
\DeclareUnicodeCharacter{21D2}{\ensuremath{\Rightarrow}}
\DeclareUnicodeCharacter{2202}{\ensuremath{\partial}}
\DeclareUnicodeCharacter{2208}{\ensuremath{\in}}
\DeclareUnicodeCharacter{220F}{\ensuremath{\prod}}
\DeclareUnicodeCharacter{2212}{\ensuremath{-}}
\DeclareUnicodeCharacter{221A}{\ensuremath{\surd}}
\DeclareUnicodeCharacter{221D}{\ensuremath{\propto}}
\DeclareUnicodeCharacter{221E}{\ensuremath{\infty}}
\DeclareUnicodeCharacter{2229}{\ensuremath{\cap}}
\DeclareUnicodeCharacter{222B}{\ensuremath{\int}}
\DeclareUnicodeCharacter{223C}{\ensuremath{\sim}}
\DeclareUnicodeCharacter{2245}{\ensuremath{\cong}}
\DeclareUnicodeCharacter{2248}{\ensuremath{\approx}}
\DeclareUnicodeCharacter{2261}{\ensuremath{\equiv}}
\DeclareUnicodeCharacter{2264}{\ensuremath{\leq}}
\DeclareUnicodeCharacter{2265}{\ensuremath{\geq}}
\DeclareUnicodeCharacter{226A}{\ensuremath{\ll}}
\DeclareUnicodeCharacter{2272}{\ensuremath{\lesssim}}
\DeclareUnicodeCharacter{2295}{\ensuremath{\oplus}}
\DeclareUnicodeCharacter{2297}{\ensuremath{\otimes}}
\DeclareUnicodeCharacter{2609}{\ensuremath{\odot}}
\DeclareUnicodeCharacter{2713}{\ensuremath{\checkmark}}
\DeclareUnicodeCharacter{27E8}{\ensuremath{\langle}}
\DeclareUnicodeCharacter{27E9}{\ensuremath{\rangle}}
\DeclareUnicodeCharacter{27F9}{\ensuremath{\Longrightarrow}}
\fi

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{3}
\setlength{\LTleft}{0pt}
% Stretchable right margin lets longtable rows sit at natural width instead of
% forcing rigid full-width rows, which emitted badness-10000 alignment warnings.
\setlength{\LTright}{0pt plus 1fill}
\setlength{\tabcolsep}{1.2pt}
\setlength{\emergencystretch}{3em}
\renewcommand{\arraystretch}{1.05}

\providecommand{\tightlist}{%
 \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CommentTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\AttributeTok}[1]{#1}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\U}{\mathrm{U}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{target}[theorem]{Target}

\title{Observers Are All You Need}
\author{Bernhard Mueller\textsuperscript{1}\thanks{\protect\raggedright Corresponding authors: Bernhard Mueller,
\href{mailto:bernhard@floatingpragma.ai}{\texttt{bernhard@floatingpragma.ai}};
Alexander Osika, \href{mailto:alex@snrgystudios.com}{\texttt{alex@snrgystudios.com}}.}
\and Alexander Osika\textsuperscript{2} \and Mario Poneder \and Kai Xue \and Ben Cassie \and Peter Nguyen
\and Maarten Antonie Visser \and Kale Arnav Anirudha \and David Matscheko \and Jonathan Hill}
\date{\OPHPaperReleaseDate}

% #542 typesetting hardening (layout only, no claim change)
\usepackage{microtype}
\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{center}
\small\textbf{Author af\kern0pt f\kern0pt iliations:} \textsuperscript{1}Pragma Inc., Washington, USA; \textsuperscript{2}SNRGY Inc., Gothenburg, Sweden.
\end{center}

\begin{abstract}
Observer-Patch Holography (OPH) starts with finite observers that keep records,
compare what both sides can read on an overlap, and repair disagreements. Public
physics is the stable record left by that process. Finite repair gives normal
forms and repeatable measurement records. Modular screen geometry supplies the
three-dimensional observer chart, Lorentz kinematics, and a conditional Einstein
branch. Compact sector reconstruction under the stated matter assumptions gives
the Standard Model quotient, exact charge assignments, three colors, and three
generations.

The primary quantitative closure asks one screen cell to reproduce its own
electromagnetic resolution,
\[
P=\varphi+\frac{\sqrt\pi}{A_T(P)}.
\]
Here \(A_T(P)\) is the Thomson-limit inverse electromagnetic coupling emitted
by the trial cell.
The fixed-point existence and uniqueness theorem used by this equation,
together with outward-rounded interval certificates, gives one root for each
declared map. The secondary global extension \(N=\log M_0(\mathfrak U_N)\) asks a trial
universe to reproduce its logarithmic correctable-record capacity. Its direct
physical capacity packet, unique finite-size selector, horizon and Higgs
identifications, particle pole masses, and the common-domain Einstein
construction are work in progress.
\end{abstract}

\input{tex_fragments/A5_WZ_PHYSICAL_STATUS_PORT.tex}

\begin{center}
\begin{minipage}{0.88\textwidth}
\centering
\bfseries
The paper's thesis is that public physical structure is the fixed point of
finite observer records, overlap comparison, and repair; spacetime and matter
are then recovered as observer-facing readouts of that settled structure.
\end{minipage}
\end{center}

\noindent\textbf{Keywords:} observer patch holography; quantum foundations; emergent spacetime;
fixed-point consensus; Standard Model structure; quantum gravity

\section*{What This Paper Contributes}

This synthesis paper owns the observer interpretation and the two quantitative
closures. The local equation
\[
P=\varphi+\frac{\sqrt\pi}{A_T(P)}
\]
is the stronger result: its fixed-point uniqueness schema and outward-rounded
interval certificates give one root for each declared map on
the full analytic domain. The global equation
\(N=\log M_0(\mathfrak U_N)\) asks a trial universe to reproduce its
logarithmic correctable-record capacity. The finite consensus and capacity
algebra is established separately. The source-derived physical
hadronic transport for \(P\), the physical public-record producer and unique
finite-size selector for \(N\), the horizon/record identification, and the
common screen/electroweak load carrier are work in progress. Numerical
comparisons and falsifiers are stated in their owning sections.

OPH combines familiar mathematics under one operational constraint. Finite
observers compare the records visible on overlaps, repair mismatches by
declared recovery moves, and accept as public the normal form that survives
those comparisons. The finite patch is the primitive object. Spacetime,
fields, and particles enter only through additional physical readout maps.

The consensus paper proves the same-source finite normal-form result. The
substrate-neutral treatment in Ref.~\cite{observableNormalForms} separates it
from cross-source boundary identification, schedule-independent liveness, and
refinement compatibility. The compact SM/GR paper owns the controlled modular
route to Lorentz and Einstein structure and the compact-gauge route to the
Standard Model quotient selected by Minimal Admissible Realization (MAR). The
particle paper owns the downstream hierarchy, mass, and flavor calculations;
the screen paper owns the finite carrier and record model. The common-domain
Einstein tower and the physical closure packets required for \(P\) and \(N\)
are work in progress.

This paper supplies the shared interpretation and closure language. Its claims
remain typed: finite theorem, controlled scaling result, conditional physical
branch, numerical diagnostic, and interpretation are not interchangeable. A
counterexample to a load-bearing theorem, a nonunique or target-leaking
closure, failure of the physical readout premises, or a carrier-dependent
change in the observable quotient falsifies the corresponding OPH claim.

\section*{Canonical Observer Language}

An abstract observer patch is the algebraic object
\[
\mathsf O_i=
\left(
\mathcal A_i,\rho_i,\mathcal R_i,
\{(\mathcal I_e,\pi_{i,e})\}_{e\ni i},
\mathcal U_i,\mathrm{Chk}_i
\right).
\]
Here \(\mathcal A_i\) is the finite or regulated accessible algebra, \(\rho_i\) the accessible
state, \(\mathcal R_i\) the exact or approximate record algebra, \(\mathcal I_e\) the overlap-visible
interface algebra, \(\pi_{i,e}\) the visible restriction, \(\mathcal U_i\) the allowed update and
repair instruments, and \(\mathrm{Chk}_i\) the checkpoint data used for continuation.

A support patch, such as a cap \(P_i\subset S^2\) or a causal diamond, is a geometric chart of the
abstract patch on a geometric branch. A carrier patch is a physical or digital implementation that
realizes the same visible interface and record statistics within a declared error. Echosahedral
hardware is therefore a reference carrier architecture for a fixed-cutoff implementation surface.
The physical claim lives at the quotient of visible records, interface statistics, repair maps, and
checkpoint continuation.

The observer patch is therefore the formal access structure used by the proof. A human observer, a
horizon cap, and a hardware module can realize or chart it, but none of those examples is the
definition. Physical predictions attach to quotient data: visible interface statistics, record
readout, repair maps, and checkpoint continuation. A carrier implementation is admissible only when
those data are invariant within its declared error model.

\begin{definition}[Semantic observer history]\label{def:semantic-observer-history}
For an observer token \(O\), the observer-readable history is a labeled causal poset
\[
\mathsf H_O=(E_O,\preceq_O,\ell_O).
\]
The elements of \(E_O\) are semantic record events, \(\preceq_O\) is physical or informational
dependence, and \(\ell_O\) is the observer-visible event label. Event identity is derived from the
canonical semantic payload, observer token, visible footprint, and semantic causal parents. It is
not derived from worker ID, repair iteration, queue position, retry counter, timestamp, or packet
latency metadata. Latency is execution gauge only when it does not alter semantic causality,
delivered data, timeout-sensitive operations, or operational clock records.
\end{definition}

\begin{definition}[Observer registry groupoid and namespaces]\label{def:observer-registry-groupoid}
Observer identities live in a registry groupoid, not in a flat UUID table. Objects are observer
tokens
\[
\mathrm{RID}(O)=\bigl(\mathrm{kind}(O),[\mathrm{birth}(O)]_{\mathsf H},\mathrm{lineage}(O)\bigr),
\]
where \(\mathrm{kind}(O)\) lies in the disjoint namespace
\[
\{\text{patch observer},\ \text{cap observer},\ \text{future observer}\}.
\]
The birth event is a semantic event class in \(\mathsf H\), and lineage is carried by explicit
continuation, split, and merge arrows. Local registries on overlapping presentations must preserve
observer kind, birth event, lineage arrows, visible observer structure, and checkpoint cuts. The
global registry is the descent groupoid or colimit of those local registries when the cocycle and
trivial-monodromy checks pass. A split creates child tokens with parent links; it does not silently
assign one identity to multiple descendants.
\end{definition}

\begin{definition}[Operational observer clock]\label{def:operational-observer-clock}
The modular parameter of an observer-facing cap pair is not, by itself, an arbitrary operational
clock reading. A clock claim supplies an observer-accessible instrument
\[
\Theta_O:\mathrm{Chk}_O(D)\to\operatorname{Prob}(\mathbb R)
\]
and a declared affine calibration law. For a corresponding observer \(O'\), the required finite
or exact certificate has the form
\[
\Theta_{O'}(\Phi_{O*}\rho)
\approx
(A_{a,b})_*\Theta_O(\rho),
\qquad
A_{a,b}(\tau)=a\tau+b,
\]
with an explicit residual bound from state mismatch, calibration error, and record-readout error.
Execution counters are provenance; observer record order, modular parameter, and clock
uncertainty are separate semantic or operational fields.
\end{definition}

\begin{remark}[Observer-clock naturality gate]\label{rem:observer-clock-naturality-gate}
This paper proves observer-first quotient and readback claims only where the cited theorem
surface supplies the required data. Scheduler-independent observer history and clock naturality
require a history-augmented quotient relation with history-coherent diamonds, registry descent,
state-preserving observer-algebra extraction, support-cap chart naturality, and the operational
clock instrument above. A public evidence bundle can falsify the claim by showing counter-dependent
semantic event keys, duplicate or namespace-colliding registry identities, broken registry
cocycles, non-isomorphic semantic history DAGs across executors, or clock residuals exceeding the
declared bound. Implementation field names alone are not the proof.
\end{remark}

This definition leaves the primitive observer size open. The axioms require finite or regulated
access at fixed cutoff and permit connected support regions with different finite or regulated
algebras. A primitive observer may therefore be a variable finite federation of screen cells. The
stronger claim that elementary carriers are isomorphic fixed-capacity cells would require a separate
branch: homogeneous UV cellulation, isomorphic local cell algebras, equivariant overlap maps,
refinement preservation of the cell type, and a proof identifying one cell or a fixed block of cells
with the primitive carrier.

\section*{Failure Tests}

OPH is wrong as stated if a load-bearing theorem admits a counterexample under its declared
assumptions, if the controlled modular/Einstein branch cannot be instantiated under physically
realizable conditions, if MAR fails to select the stated realized package on the declared
admissible class, if a quantitative closure is nonunique or target-leaking, or if a physical
implementation shows branch-essential dependence on hidden carrier presentation after visible
quotient data are held fixed. Concrete falsifiers include failure of a displayed Maxwell,
pure-Yang--Mills, or pure-Einstein quadratic kernel to have its stated transverse or transverse-traceless (TT) classical
mode under all of that theorem's action/background/phase hypotheses; failure of a claimed quantum
pole after its full quantization and spectral receipt is supplied; an observed
low-energy \(X/Y\)-type \((3,2,\pm5/6)\) gauge generator on the realized
product branch; a fourth
light matter generation in the realized low-energy branch; a smaller admissible one-Higgs Standard
Model package; nonunique \(P_\star\) or \(N_{\mathrm{CRC}}\) closure; a failed fixed-cap
entropy-to-Einstein tensor upgrade; or carrier-dependent observables after the visible interface is
held fixed. A failed continuation does not erase the recovered core unless that continuation is one
of the stated parents of the core claim.
	
\tableofcontents
\newpage

\section{Introduction}

Observer-Patch Holography asks how much of physics is forced once the world is described from the
inside. No observer has access to a view from nowhere. In the idealized description there is a
shared screen net, often charted by \(S^2\), but each finite observer has access only to a local
patch \(P_O\) of that net. The observer carries records inside that patch and can compare only the
observables shared with neighboring patches. OPH takes that comparison rule literally: where
descriptions overlap, they must agree. Thus an "observer screen" is an operational access cut, not a
private physical sphere assigned to the observer.

The formalism used here is deliberately quantum-algebraic. Patches carry algebras and states,
record events use the trace/Born rule on their declared operator surface, and the gravity branch
uses generalized entropy. OPH's theory-of-everything claim is that the observed effective universe
can be recovered from this axiom set and its stated branch conditions if the framework is correct.
The reconstruction may use declared standard mathematics and branch hypotheses without treating
those ingredients as hidden empirical constants.

The computational interpretation has a sharp boundary. A conventional simulation evolves surrogate
universe states,
\[
U_t\longrightarrow U_{t+1}\longrightarrow U_{t+2}\longrightarrow\cdots .
\]
OPH uses a fixed-point computation, but the equation alone is not the definition of
simulation. In the fundamental description there is no global timeline on which the contents
of spacetime are updated. The readback-and-repair operator acts on observer-readable world
candidates and selects a stable solution
\[
\mathcal T(W)=W .
\]
The companion consensus paper~\cite{ophconsensus} defines an OPH simulation by
five independent clauses: recovery-derived endogenous
update, nontrivial quotient-readable records, strict overlap-repair descent with a
schedule-independent normal form, elimination of a proper candidate basin in the selected
boundary/sector fiber, and implementation/clock closure. Its simulation theorem
proves that the selected finite OPH packet meets those clauses
under the stated boundary and record hypotheses and then derives the fixed-point equation.
The same theorem gives an identity-map/constant-functional counterexample, so an ordinary
equilibrium is insufficient as a simulation.

The local readout of the selected normal form supplies history for observers who subjectively
experience time. Time is therefore internal record order instead of an external update
parameter. In OPH, ``simulation'' means this certified observer-facing self-consistency
structure, not a bare fixed point and not a frame renderer. The executable OPH-FPE simulator
and its finite-run receipt bundles are a separate public evidence surface for finite OPH
experiments~\cite{ophfpe}; they do not replace the theorem-level definition above.

The effective bulk is reconstructed
from compatible screen data. Locality comes from the way collars control recovery across patch
boundaries. Gauge freedom is the freedom to change the local description without changing any shared
observable. Records are the stable parts of a patch that can be checked by other patches. Matter is
the stable charge and excitation content that survives transport, fusion, and minimal admissible
realization.

The first major result is spacetime kinematics. Modular flow on screen caps becomes geometric,
and the compact cap-normal theorem identifies a sky direction with \(q(\Omega)=(1,\Omega)\),
represents an oriented round cap by \(n_C=(\cot\alpha,\csc\alpha\,\mathbf c)\), proves
\(\eta(n_C,q(\Omega))=0\) exactly on the cap boundary with the interior/exterior sign rule, and
gives \(n_{gC}=\Lambda_g n_C\). Future unit observer frames then form
\(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\), exactly three-dimensional. A cap determines an
\(H^3\) plane/half-space, not an event position or populated bulk. On the conditional frame-response
branch, quotient-visible record tokens whose calibrated modular cap responses factor through
frame-local \(H^3\) data admit exact frame identification and stable finite-noise frame estimates.
The finite frame radius is
\(R_H[(L/\alpha)\varepsilon+(2/\alpha)\sigma]\) for exact net minimization, with a positive
residual gap required before a unique finite frame value is reported. Event location requires the
separate affine translation and ancestry receipts of the event-manifold branch. Generalized
entropy at fixed cap then gives a tensor first-variation relation in the
large-scale regime. The absolute Einstein equation additionally uses one
source-derived common-domain tower with uniform asymptotics, universal
coupling, a vacuum reference, and independent scale readouts; construction
and certification of that tower are work in progress. The proposed cosmological
capacity relation is
\[
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
The Gibbons--Hawking entropy and the Planck-2018 late-time de Sitter benchmark give a concrete normalization~\cite{gibbonsHawking77,planck18}. With
\(R_{\mathrm{dS}}\simeq1.66\times10^{26}\,\mathrm m\) and
\(\ell_P\simeq1.616\times10^{-35}\,\mathrm m\), the bare horizon ratio is
\[
N_{\mathrm{patch}}=\left(\frac{R_{\mathrm{dS}}}{\ell_P}\right)^2\simeq1.05\times10^{122}.
\]
The entropy capacity is
\[
N_{\mathrm{scr}}=S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4\ell_P^2}
=\pi N_{\mathrm{patch}}\simeq3.31\times10^{122},
\]
so \(\Lambda\ell_P^2\simeq2.85\times10^{-122}\). OPH uses \(N_{\mathrm{scr}}\) for the
Gibbons--Hawking entropy capacity and \(N_{\mathrm{patch}}\) for the bare horizon area ratio.
The proposed input-free closure begins at finite cutoff with a frozen carrier
dimension \(D\), the unclosed terminal quotient fiber, local and interface
record atoms, compatible public global sections, endogenous reachability, a
frozen publicness policy, and the globally coupled semantic checkpoint
kernels. Their compound confusability graph \(G_q\) gives the exact finite
readback
\[
M_0(q)=\alpha(G_q).
\]
This correctable-code capacity includes joint checkpoint compatibility and
confusability. A cyclic checkpoint can preserve every label while fixing only constant
functions, and equal local marginals can hide different joint capacities. The
first producer is the set
\[
\mathfrak F_{r,\varepsilon}(D)
=\{M_\varepsilon(q):q\in\widetilde\Omega_{r,D}\}.
\]
A scalar exists only when the whole nonempty terminal fiber agrees. A faithful
capacity-carrier representation gives \(M_\varepsilon\le D\); exact equality
means a complete rank-one public record basis. If the scalar exact map is
total, monotone, and deflationary on a declared finite chain, top-down
iteration reaches its greatest fixed point. The official universe-level
cosmic record-closure equation and its selector-free finite implementation are
\[
N=\log M_0(\mathfrak U_N),
\qquad
\mathfrak F_{r,0}(D_\star)=\{D_\star\},
\qquad N_{\mathrm{CRC}}=\log D_\star.
\]
The finite public-section, correctable-code, boundary, scalarization, order,
extension, refinement, and sewing implications can be proved from the stated
data. They do not select a cosmic value: \(M(D)=D\) and \(M(D)=1\) are both
compatible with monotone deflation. The remaining source constructions are the
record-atom restrictions, endogenous reachability, publicness policy, global
checkpoint coupling, capacity-carrier representation, whole-fiber scalar
producer, confusability-reflecting extension and refinement packets, and an exact
finite-size slack law
\[
s(D)=\log D-\log M_0(D)
\]
with one physical zero. Two physical identifications remain afterward: the
correctable-record carrier must be identified with the de Sitter horizon
record for the de Sitter area law, and the screen load must be identified with the
electroweak load by a positive, unital, refinement-natural map for the
electroweak bridge. An independently
produced operational scale is a commuting-square test of the code capacity,
not its definition. The electroweak bridge supplies a mathematical candidate
of about \(3.532\times10^{122}\) only after the common-load receipt. The Planck--\(\Lambda\) central read-off is about
\(3.313\times10^{122}\), which is about \(6.6\) percent below the bridge candidate. The joint
Planck posterior, propagated through the \(\Lambda\)-to-\(N\) map across three degeneracy routes,
places the gap at \(2.4\) to \(2.5\) one-dimensional standard deviations under the consumed
likelihood combination and \(3.8\) to \(3.9\) under Planck+BAO, so the combination freeze is part
of any future test registration; a final statement requires the closed premises. Thus neither
the physical fixed-point identity nor the cosmological display
\(\Lambda_{\mathrm{CRC}}=3\pi/(G N_{\mathrm{CRC}})\) is established by the bridge calculation.

The second result is a conditional finite Standard Model recognition package. On a cofinal tail carrying the explicit
compact-gauge refinement receipt (including coherent surjective charge pullbacks, finite block
embeddings, tensor realizations, \(3+1\)D symmetry, and compatible forgetful fibers), edge sectors reconstruct the
bosonic compact-gauge branch. On the declared low-energy packet with the explicit
one-generation/one-Higgs matter witness, minimal admissible realization then selects the
compact gauge quotient
\[
\SU(3)\times\SU(2)\times\U(1)/\mathbb Z_6.
\]
The packet fixes exact hypercharge and a three-color carrier, gives
\(3\leq N_g\leq5\), and selects \(N_g=3\) only as the least value of the
declared MAR economy class. It also gives integer charge for color singlets
and the absence of the simple-GUT \(X/Y\) gauge channel. The canonical
rank-three screen band remains a candidate family fiber until the physical
rank-45 attachment receipt is supplied. On a declared trace-balanced block carrier
\(V=C\oplus W\), with dimensions \(3+2\) and hypercharges
\((-1/3,1/2)\), the exact exterior package
\(\Lambda^2V\oplus\Lambda^4V\) branches as one fifteen-state Standard Model
generation, supports the three one-Higgs invariant lines, cancels all five
listed perturbative gauge and mixed anomalies, and has weak-doublet
multiplicity \(3+1=4\) with even Witten parity.
This is a conditional representation witness. A physically forced Standard Model
requires physical current, determinant, spin-lift, deck-descent,
carrier-selection, extra-sector-exclusion, family-attachment, genuine 1PI,
and complement-complete refinement receipts. The subsequent QFT landing is a
typed DAG: QFT-Q2 and QFT-Q3 are parallel descendants of QFT-Q1, while
QFT-Q4 requires its own nonperturbative observable tower; the conditional
implications are now explicit, but the OPH-native producers remain open.
The selected exterior package is not the full even Clifford module, because
\(\Lambda^0V\) is omitted. On separately
stated Maxwell, perturbative/deconfined Yang--Mills, and pure-Einstein action/phase branches, the
quadratic reductions have the corresponding classical null carrier modes. Photon, gluon, or
graviton particle claims require the additional physical-Hilbert-space and spectral-pole receipts.

The third result is quantitative and sits outside the recovered core. Its
primary equation closes one local observation cell on its own electromagnetic
readout:
\[
P=\varphi+\frac{\sqrt\pi}{A_T(P)},
\qquad A_T(P)=\alpha_{\mathrm{em}}^{-1}(0;P).
\]
The outside reading is the normalized pixel detuning
\((P-\varphi)/\sqrt\pi\). The inside reading is the Thomson-limit coupling
emitted by the same trial cell. The contraction-based theorem gives existence
and uniqueness on a closed interval. Outward-rounded interval
certificates verify the concrete hypotheses, enclose one root for each declared
map, and exclude a second root across the full analytic domain. No measured
value is inserted into either solve. The source-derived same-scheme hadronic
transport is still required before a declared-map root can be identified with
the physical Thomson endpoint.

The secondary global extension uses the exact finite correctable-record capacity
\(M_0(q)=\alpha(G_q)\) and the universe-level equation
\(N=\log M_0(\mathfrak U_N)\). Its finite public-section, carrier-bound,
scalarization, order, and refinement implications are conditional theorems.
The physical checkpoint packet, whole-fiber scalar producer, unique finite-size
slack zero, horizon identification, and common screen/electroweak carrier are
work in progress. The Planck--\(\Lambda\) central capacity
\(3.313\times10^{122}\) and the conditional electroweak value
\(3.532\times10^{122}\) are comparison coordinates. Their \(6.6\)-percent
difference does not enter the construction of the direct capacity map.

The local pixel coordinate and independent scale certificate are
\[
P:=\frac{a_{\mathrm{cell}}}{\ell_\star^2},
\qquad
\gamma_\star=\frac{\ell_\star\nu_{\mathrm{Cs}}}{c},
\qquad
B_\star=\frac{3\pi}{\ell_\star^2}.
\]
If the two declared-map outputs acquire their missing physical identifications,
\(P_\star\) and \(N_{\mathrm{CRC}}\) fix
\(\Lambda_\star\ell_\star^2=3\pi/N_{\mathrm{CRC}}\) and
\(\Lambda_\star a_{\mathrm{cell}}=3\pi P_\star/N_{\mathrm{CRC}}\). They fix the dimensionless
geometry. The selected scale certificate supplies the SI scale product
\(B_\star=\Lambda_\star N_{\mathrm{CRC}}=3\pi/\ell_\star^2\).
The selected scale certificate does not construct the cosmic readback map or remove the
\(6.6\)-percent central-value mismatch.
Under those same identifications, the pixel \(P_\star\) together with the \(\Lambda\)-located
working capacity \(N_\Lambda=3.31\times10^{122}\) fixes a canonical geometric pixel area and a
total geometric cell count on an equal-area screen chart,
\[
K_{\mathrm{cell}}
=\frac{A_{\mathrm{screen}}}{a_{\mathrm{cell}}}
=\frac{4N_\Lambda}{P_\star}
\simeq 8.12\times10^{122}.
\]
This count is a measured-side comparison display and does not enter either
closure. At the conditional bridge capacity the same chart count reads
\(8.66\times10^{122}\). The result supplies a geometric chart count. It does
not choose a primitive observer capacity. The
quantity \(P_\star/4\simeq0.408\) nats, or about \(0.588\) bits, should not be read as
\(\log\dim\mathcal H_{\mathrm{cell}}\) for an autonomous tensor factor. OPH capacity lives on
shared cuts, edge centers, and constrained overlap data; adjacent geometric pixels are not assumed
to factor into independent Hilbert components. No fixed primitive observer algebra follows from
\(P_\star\) and \(N_{\mathrm{CRC}}\) alone.
The no-\(G\) burden of the scale proof record is the clock hierarchy. The first load-bearing object
must be a strict source-root proof for \(\alpha_U(P_\star)\); the source-audit
branch is only a witness. After that, the cesium gap
\(\varepsilon_{\mathrm{Cs}}\sim10^{-33}\) must be emitted by source-side electroweak
transmutation, QCD/hadronic data, flavor and nuclear data, and a cesium hyperfine spectral
readout, with no dependency path from measured gravity or any calibrated electroweak or
gravity scale.
The public \(\alpha_U\) record is a one-dimensional comparison-branch fixed-point certificate:
\[
\begin{aligned}
\alpha_U(P_\star)&=0.041124336195630495,\\
\frac{v}{E_\star}&=2.0199803239725553\times10^{-17},
\end{aligned}
\]
and the Krawczyk image of
\([0.041123336195630494,\;0.041125336195630496]\) lies strictly inside that interval. The
source-side diagnostic branch excludes the public Thomson endpoint upstream. Its certified
forward pixel is
\(P_{\mathrm{fwd}}=1.630972095858897\ldots\).
That source branch is a witness, not a full endpoint proof; it does not supply the strict interval
root for the Ward-projected self-map. The dimensionless formula is the
strongest clean hierarchy statement. It does not supply an independently physical \(E_\star\), a mass
in GeV, or a complex propagator pole. The full SI gravity row requires the full set of
cesium-clock source records.
The QCD and hadronic weakpoint is narrow. The low-energy Thomson endpoint and the cesium-clock
display require confined-quark and nuclear source payloads that the first-principles trunk in this
paper does not emit. For a source-only Thomson endpoint, the missing object is the source-derived hadronic spectral
hadronic backend: source QCD parameters, a quotient ensemble, finite Euclidean vacuum transfer,
Ward-normalized electromagnetic currents, the two-current spectral marginal, same-scheme
remainder, systematics, and no-target-leak receipts.

Four fine-structure coordinates must be kept separate. The source/root audit records the
undressed declared-map witness
\(\alpha_{\mathrm{root}}^{-1}=136.994835177413\ldots\) (interval-certified unique fixed
point of that numerical map, with enclosure width \(7.2\times10^{-24}\)).
The declared map is incomplete: no derivation identifies this root with a physical
fine-structure endpoint. Adding the finite-screen unified
gauge-width contribution at the CODATA-derived comparison pixel gives the mixed-provenance,
no-hadron diagnostic
\[
A_{\alpha_U}^{\mathrm{fp}}=137.0359595136\ldots.
\]
The certified self-consistent gauge-width fixed point is
\(\alpha^{-1}=137.035660136946577\ldots\). The mixed diagnostic
\(137.0359595136\ldots\) combines the inner value at \(P_{\mathrm{fwd}}\) with
\(\alpha_U\) at the CODATA-derived comparison pixel, is not a fixed point of any single declared map, and is
excluded from the physical output ledger.
An executed empirical closure, using external
\(e^+e^-\to\mathrm{hadrons}\) spectral data, records
\[
\Delta\alpha_{\mathrm{had}}^{(5)}(M_Z)
=0.0267591200\pm0.0007524955,
\qquad
\alpha_{\mathrm{emp}}^{-1}(0)=136.2636589431
\]
with interval \([136.1583832834,136.3690975240]\). The measured endpoint is
\(\alpha^{-1}(0)=137.035999177(21)\), outside that interval. The resulting same-scheme
anchor correction is \([0.6485541111,0.8547920666]\) inverse-alpha units. This empirical payload
tests the endpoint map and exposes the missing contribution; it does not supply a source-only OPH
hadron law. The two-current spectral measure covers the running-\(\alpha\)/HVP marginal. HLbL and
rare-decay rows require higher-point and transition spectral sectors from the same source law.
For that reason the compact quantitative stress test is the hierarchy row above: it avoids the
public Thomson endpoint, \(G\), \(\Lambda\), \(W/Z\), Higgs mass, hadronic payloads, and the
cesium clock.

The same hierarchy exponent has a local/global capacity form:
\[
\frac{v}{E_{\mathrm{cell}}}
=
\left(\frac{N_{\mathrm{CRC}}^{\mathrm{EW}}}{\pi}\right)^{-P_\star/12},
\qquad
N_{\mathrm{CRC}}^{\mathrm{EW}}
=
\pi\exp\!\left[\frac{6\pi}{P_\star\alpha_U(P_\star)}\right].
\]
This is the electroweak bridge capacity, about
\(3.53235\times10^{122}\) on the declared comparison branch. Identifying it with the cosmic
capacity requires the source-derived correctable-public-record producer and
the common screen/electroweak load-carrier identification. The
Planck-\(\Lambda\) central capacity, about \(3.313\times10^{122}\), is lower by about \(6.6\)
percent. The factor \(12\) has a branch-specific geometric reading. On the
declared echosahedral carrier lineage, twelve equal-trace primitive central
port atoms and the integer defect fiber \(\sum_pq_p=12\) give the source
readback cost \(H(q)=\sum_pq_p^2\). The identity
\(H(q)=12+\sum_p(q_p-1)^2\) uniquely selects one unit per port with exact gap
two. Oriented \((12,30,20)\) incidence then derives the unique graph-distance
three antipode, six axes, proper automorphism group \(A_5\), and the canonical
rank-three icosahedral Gram frame. Edge-center collars expose the defects as
central ports. Reversible write/check orientation
gives an oriented 24-slot screen register. Independently, the product adjoint
has count \(m_{\rm rep}=2(8+3+1)=24\). Their equality is bookkeeping and
supplies no load or clock. The exterior matter package gives the exact
four-copy weak multiplicity; attaching that multiplicity to the physical
screen load remains an explicit hypothesis.

The oriented coefficient module is
\[
 P_{12}\cong_{A_5}\mathbf1\oplus\mathbf3\oplus\mathbf3'\oplus\mathbf5.
\]
For the six antipodal axes, the exact frame maps split the even and odd modes,
and the outward faces orient the complementary triplet. Pulling the block
commutator back through
\[
 \Theta(b+d_G+d_W)=
 \bigl(\kappa_E(\tfrac12Ud_G)+i\Phi(b),\kappa_W(d_W)\bigr)
\]
constructs
\[
 (P_{12},[\ ,\ ]_\Theta)\cong
 \mathfrak u(1)\oplus\mathfrak{su}(3)\oplus\mathfrak{su}(2)
\]
with center \(\mathbf1\), derived dimension eleven, and a noncentral
\(\mathbf5\). This bracket acts on coefficient fluctuations; the central
record projectors commute. Compact classification gives the same Lie type for
every full-rank, compact skew-adjoint, commutator-closed physical current lift
with an inner \(A_5\) action. Source production of that lift is work in
progress.

A chosen trace balance completes the map to
\(\mathfrak{s}(\mathfrak u(3)\oplus\mathfrak u(2))\), whose connected group is
\[
 S(U(3)\times U(2))
 \cong\frac{SU(3)\times SU(2)\times U(1)}{\mathbb Z_6}.
\]
The six-axis lattice independently has quotient \(\mathbb Z_6\). These exact
constructions require determinant balance, a physical spin lift, and
refinement-natural deck-holonomy descent before they identify a physical
global group. Hypercharge, chiral content, and the selected quotient are on
the MAR route. One sufficient branch contract combines source-derived screen
tomography with a reversible physical current; its realization from
the recovered core is work in progress.

The finite algebra establishes the positive twelve-term sum-to-twelve unit split, abstract
matrix commutator, dimension \(9+3\), a matrix noncentrality witness, the
six-axis lattice quotient, and the \(B_6\) arithmetic. On the declared
echosahedral lineage, the source-derived central readback and oriented
incidence now also establish the strict unit cost and gap, inverse pairing,
proper \(A_5\) action, rank-three port frame, and refinement/relabeling
naturality. This does not derive the echosahedral carrier from arbitrary OPH
data. The noncentral physical current lift, trace-balanced group, spin/deck
descent, and matter attachment remain separate open receipts.
The face-\(C_3\) representation theorem gives a three-dimensional minimal
extension; physical family attachment is work in progress. See
Ref.~\cite{ophcompact}.

The compact proof packages this quantitative surface as a source-certified
compression test. A row counts in the accidental-hit estimate only when its
declared source map has no dependency path from the measured target or a
calibrated proxy. If \(p_i\) bounds the conditional accidental-hit probability
for row \(i\) after the preceding accepted rows, then
\[
P_{\rm acc}\le\prod_i p_i .
\]
The closure ledger records the qualifying rows, including the structural
gauge-boson zeros and the clause-conditional hypercharge lattice. Any compression claim cites
those declared settings and landed basins.
The proof load is the fixed-point maps, uniqueness certificates, source
records, and falsifiers.

The declared map for \(P\) gives the same screen cell two readings. From outside, the cell
sits a little above the exact self-similar
entropy balance point \(\varphi=(1+\sqrt5)/2\). From inside, the same cell appears as the smallest
electromagnetic observation step available in the encoded world. The unique
source-map root defines the local closure coordinate. The measured
fine-structure constant tests the resulting electromagnetic endpoint and does
not enter the solve. The physical low-energy relation requires the unconstructed
same-scheme hadronic spectral transport.

The named \(P\) branches organize the electroweak carrier chart, the low-energy electromagnetic
endpoint, the conditional Higgs/top surface, the rejected reciprocal-ray quark candidate and its
six-coordinate physical interface, a target-informed weighted-cycle neutrino comparison candidate, and the local cell/edge
consistency used by the gravity readout. The hierarchy theorem fixes \(v/E_\star\). An independent
physical \(E_\star\) and the separate pole receipt govern any mass in GeV. The gravity
normalization itself comes from \(\ell_\star^2\), and \(P\) cancels in the Newton area-law readout.
The support table records the distinct electroweak chart, conditional law, and inverse target adapter,
the target-informed charged-lepton candidate, the NuFIT 6.1 rejection of the neutrino candidate,
its tautological declared-basis transport and missing physical charged basis, and the hadron
construction~\cite{nufit61}.

The fourth result is implementation. The screen-microphysics construction makes patches,
overlaps, edge observables, records, repair maps, and observer checkpoints explicit at finite
cutoff through a federated patch-carrier architecture. OPH has a regulated observer-and-record surface on which the basic consistency
machinery can be written directly.

\paragraph{Axioms in words.}
The theory uses five axioms. A screen net assigns algebras to connected screen patches. Overlap
consistency requires agreement on shared observables. Local MaxEnt selects the least biased local
state compatible with the finite constraint data and keeps the realized construction stable under
refinement. Recoverable generalized entropy supplies the collar-recovery and focusing structure
used by the gravity lane. Minimal admissible realization selects the simplest low-energy sector
compatible with the consistency constraints. These axioms define a quantum-algebraic
starting point. Quantum mechanics and quantum field theory are treated as effective descriptions
carried by the deeper observer-patch architecture, not as structures whose use here depends on
first deriving every mathematical ingredient from operational records alone.

\paragraph{The quantitative selection chain.}
Self-reading, overlap consensus, modular geometry, transportable charge,
entropic gravity, and stable records define the structural branch. They do not
prove that the branch is inhabited, force the icosahedral
screen-to-Standard-Model attachment, or construct the global capacity packet.
The two closure equations test independently produced local and global readback
maps. If both equations hold with the declared selection rules, the branch
admits at most one coordinate pair \((P,N)\). This statement does not prove
that exactly one physical universe exists. The local uniqueness certificate
gives existence and uniqueness on its certified interval, and the domain-global certificate
bounds \(\sup|g'|<1\) on every piece of a 256-piece subdivision of the declared numerical domain
(\(\alpha^{-1}\in[100,200]\), both readout maps, empty exceptional set), so each declared readout
map has exactly one fixed point on that domain. This certificate does not derive a physical
endpoint relation for the incomplete declared map. The global uniqueness
claim has a proved conditional implication layer and a physical execution that
is work in progress. Public global sections, zero-error graph capacity, approximate
stability, the carrier bound, whole-fiber scalarization, greatest-fixed-point
order theory, and exact refinement stabilization are finite implication
theorems. Execution needs the source-derived public checkpoint packet,
capacity-carrier representation, confusability-reflecting embeddings, and an exact
finite-size slack law with one physical zero. The de Sitter and electroweak
consequences then require the horizon--record identification and the common
screen/electroweak load-carrier identification, respectively. The operational resolution
experiment is an independent test, not the producer. The
certified value \(3.5321315434\times10^{122}\) is a solution of the declared
bridge equation, not of the unconstructed direct public-record producer; it is about
\(6.6\) percent above the Planck--\(\Lambda\) central coordinate
\(3.313\times10^{122}\). The two electromagnetic endpoint residuals have no
valid target-blind score: the exposed target conflates total and residual coordinates, and no active
decision threshold exists. A valid test requires a complete method
frozen against genuinely withheld data or an audited clean-room producer.

The synthesis surface gives the operational picture first, then places the technical proof machinery
after the reader has the construction in hand.

\section{Main Results}

The OPH papers support the following unified picture.

\subsection{Proof, witness, and receipt map across the paper stack}
\label{sec:stack-proof-witness-map}

The stack uses three distinct jobs.  A paper theorem proves that stated finite or analytic premises
imply a conclusion.  A simulator or source construction produces the premises on a declared
refinement tower.  A receipt records enough public data for an independent verifier to check that
the produced object satisfies them.  A successful finite run does not replace an implication
proof, and an implication proof does not construct its physical source object.

\begin{longtable}{@{}p{0.18\linewidth}p{0.38\linewidth}p{0.36\linewidth}@{}}
\toprule
\textbf{Owning surface} & \textbf{Paper theorem} & \textbf{Source object and current gate} \\
\midrule
\endhead
Consensus protocol &
Semantic-dependency-complete transactions with one coherent canonical union-collar aggregate per
conflict component satisfy the local diamond.  Descent, this diamond, and repair completeness give
a schedule-independent quotient normal form.  Coherent recovery squares and pentagons give
parenthesization-independent collar gluing. &
The engine supplies functional supports, read/write closures, aggregate payloads, protected and
history data, repair completeness, and concrete finite peaks.  Atomicity without semantic closure
fails on a two-bit protected-observable countermodel; pairwise collar compatibility without
coherent union data fails on parity and GHZ countermodels. \\
\addlinespace
Compact relativity and gravity &
Event germs form the base while \(H^3\) remains the local frame fiber.  Finite oriented
four-ball degree and two-sided metric control imply open four-dimensional charts.  A convergent
symmetric form with a spectral margin and two-sided causal classification has Lorentzian inertia.
\(C^{1,1}\) tetrads give the metric regularity used by the curvature lane.  Proper time is chart
invariant, while clock comparison between worldlines requires an explicit event correspondence
and calibration cocycle. &
The source tower supplies event equivalence and pseudometric data, finite chart maps and degree,
quadratic-form samples, tetrads and inverses, causal tests, clock correspondences, calibration
cycles, and their refinement moduli.  The mixed-GNS modular transport packet is an independent
producer assumption; local MaxEnt does not supply it. \\
\addlinespace
Screen microphysics &
Exact finite coarse graining sends modular potentials through log-sum-exp.  A faithful equilibrium
state leaves the reversible generator underdetermined.  Rate affinities, the weighted graph Hodge
split, entropy production, and a convention-fixed finite KMS jump theorem give the equilibrium
operator layer.  The \(A_5\times\mathbb Z_2\) register has an eight-parameter self-adjoint
commutant, its twelve-port commutant is generated by icosahedral adjacency, and it admits no
equivariant directed 24-cycle.  A source-derived \(24\)-channel realization carries the edge
modular grading exactly when its channel-closure residual vanishes; with \(A_5\) and reversal
covariance, the compressed spectrum has sign-paired \(1,3,3,5\) degeneracies, while the four gap
values remain source-rate data. &
The source supplies coarse states or channels, conductances or rates, KMS frequency operators,
positive rate matrices, the oriented channel map and its provenance, quotient lumpability,
cycle-affinity, channel-closure, commutant, and refinement receipts.  Register symmetry classifies
finite operators only.  It supplies neither a clock nor a physical gauge-current lift. \\
\addlinespace
Finite event algebra &
For nonselective projective pinching,
\(S(\mathcal E\rho)-S(\rho)=D(\rho\Vert\mathcal E\rho)\ge0\).  This identity is separate from a
normalized selective L\"uders branch. &
The projective partition and input state are finite source data.  The entropy identity is an
analytic matrix proof outside the current Lean export; the pinching and trace identities it uses
belong to the machine-checked core. \\
\addlinespace
Boltzmann transport &
Convergence of the discrete generators to the null Hamiltonian vector field, vanishing carré du
champ, tightness, and uniqueness of the limiting ODE imply deterministic Liouville transport.
A limiting collision generator gives Boltzmann transport; nonzero limiting quadratic variation
gives a diffusive limit. &
The simulator supplies quotient-lumpable transition kernels, physical time steps, first and second
conditional moments, mass-shell and boundary defects, and schedule/refinement-natural convergence.
Path confluence alone supplies none of these transport limits. \\
\addlinespace
Particle and gauge sectors &
The finite \(A_5\) coefficient/register statements and the compact classification of a full-rank,
compact skew-adjoint, commutator-closed current lift are separate theorems.  Given the physical
lift and its inner \(A_5\) action, the compact classification fixes the Lie type used by the
Standard Model branch. &
Production of the physical current lift, its nondegenerate pairing, current brackets, inner action,
and refinement-natural descent remains a source obligation.  A register adjacency or modular
generator cannot be relabeled as this current. \\
\addlinespace
Yang--Mills gap &
For the source-defined finite collar family, the finite-type Dobrushin/minorization theorem gives
one positive projection/transfer-gap modulus uniform in location, boundary condition, system size,
and the declared cofinal refinement tower.  Removing locality or the stated mixing control admits
finite countermodels with a collapsing gap. &
The physical compact-gauge branch must produce the admissible collar types, transition matrices,
uniform constants, refinement maps, reflection-positive vacuum, and continuum regularity packet.
The finite theorem closes the repair-gap implication.  The Clay-facing continuum construction
remains conditional on that source receipt. \\
\bottomrule
\end{longtable}

This map is the status boundary used by the results below.  The specialist papers own the detailed
definitions and proofs.  This synthesis owns the cross-paper dependency order and prevents a
finite operator, receipt, or simulation trace from changing type as it moves between surfaces.

\begin{enumerate}[leftmargin=2em]
\item \textbf{Observers and records become physical objects.} Finite patches, shared overlaps,
record algebras, repair maps, and observer checkpoints are represented on the screen as part of the
construction.
\item \textbf{Spacetime is reconstructed.} On the controlled Einstein-branch geometry readout,
the finite cap-normal Bisognano--Wichmann (BW) certificate (support-order faithfulness, regularized mixed-GNS modular
transport, BW framing, held-out oriented cross-ratio rigidity, and independently normalized
geometric \(2\pi\)-KMS (Kubo--Martin--Schwinger) convergence) makes the support-visible cap modular automorphism geometric
and supplies Lorentz kinematics. Recoverable
generalized entropy together with the null modular bridge, bounded-interval transport, fixed-volume
small-ball area variation, admissible fixed-cap stationarity, and timelike tensor upgrade then
		supplies the Einstein relation on one source-derived common-domain tower with certified tails and independent physical identifications. The finite artifacts test algebra, evaluator logic, manifests, deletion rules, and synthetic controls. They do not certify such a tower. Its construction is work in progress. Bare finite consensus supplies only the upstream quotient-normal-form input. The screen-capacity branch proposes the dimensionless
		cosmological-constant relation below. The identification of its cosmic record-closure value with
		the electroweak bridge requires the common screen/electroweak load-carrier identification, and the physical
		public checkpoint packet is work in progress:
\[
\mathfrak F_{r,0}(D_\star)=\{D_\star\},
\qquad N_{\mathrm{CRC}}=\log D_\star,
\qquad
\Lambda_{\mathrm{CRC}}\ell_\star^2=\frac{3\pi}{N_{\mathrm{CRC}}},
\qquad
\Lambda_{\mathrm{CRC}}=\frac{3\pi}{G N_{\mathrm{CRC}}}.
\]
The last display uses the selected scale certificate \(G_{\mathrm{geom}}=\ell_\star^2\).
	The bridge formula has a certified mathematical value near \(3.532\times10^{122}\); the
	Planck-\(\Lambda\) central value near \(3.313\times10^{122}\) is lower by about \(6.6\) percent.
	A uniqueness certificate for the bridge formula does not establish the unique zero of the
	public-record slack or construct its physical checkpoint packet.
\item \textbf{The Standard Model quotient is conditionally selected by MAR.} Under the stated coherent transportable-sector
refinement conditions, edge sectors reconstruct a bosonic compact-gauge branch. The overlap/holonomy calculus classifies transportable sectors; it does not by itself choose the Standard Model. The realized low-energy branch
with the explicit one-generation/one-Higgs matter packet and MAR then selects the compact gauge quotient, exact hypercharge,
a three-color carrier, and the conditional economy value \(N_g=3\), together with the structural absence of the simple-GUT
\(X/Y\) gauge channel. General proton stability is not implied. On the ordinary electromagnetic branch, the unbroken
\(\U(1)_Q\) factor reduces the compact-gauge curvature to \(F_Q=dA_Q\); after separately
assuming the low-energy Maxwell action and its nonzero kinetic term, variation gives
\(dF_Q=0\) and \(d{*}F_Q=g_Q^2{*}J_Q\), i.e. Maxwell's equations after
canonical electromagnetic normalization.
The rank-three candidate screen band is not thereby attached to three
physical families; that requires the separate complex rank-45 response,
Spin/locality, residue, excluded-band, and refinement receipts.
\item \textbf{The measured endpoint tests the local closure.} The comparison pixel
\(P_C\simeq1.6309682094\) is inferred from the measured fine-structure constant solely for comparison:
\(\alpha^{-1}(0)=137.035999177(21)\),
\(\alpha(0)\simeq0.00729735256433\). The forward model with
the source anchor and Ward-projected electromagnetic transport measures the
loop-closure residual: \(3.0\times10^{-4}\) relative on the source chain and
\(2.5\times10^{-6}\) relative for the certified numerical gauge-width
fixed point \(\alpha^{-1}=137.035660136946577\ldots\), a certified fixed point of the
declared map with the Ward-projected hadronic transport open. The mixed-provenance diagnostic
\(137.0359595136\ldots\) is a fixed point of no single declared map and is excluded from the
physical output ledger. The separate root \(136.994835177413\ldots\) is an interval-certified
output of an incomplete declared map; no derivation relates it to the physical fine-structure
endpoint.
The claim table
records the source-side diagnostic trunk and endpoint residual.
\item \textbf{The framework has a regulated implementation surface.} The microphysics paper turns
the observer language into explicit finite patch carriers, edge observables, records, and repair
cycles.
\item \textbf{Edge sectors also admit two-dimensional Yang--Mills and worldsheet-style effective descriptions.} The heat-kernel
edge partition function reorganizes the same boundary data into the two-dimensional
Yang--Mills form, and on the declared large-edge branch this yields a controlled worldsheet
effective description. This 2D bridge sits beside the compact paper's controlled
compact-gauge repair-gap theorem. The string-vacuum selector uses this bridge only as the
effective edge-language input; critical worldsheet closure, Bouchard-Donagi cohomology,
operator-safety realization, threshold matching, and moduli locking are separate gates. The
selector's rank certificate gives proxy rank zero on the published pre-completion slice and supplies
no completed physical slice or Jacobian. The BD row is not a selected string witness, and the
recovered OPH core is unchanged.
\item \textbf{The compact-gauge branch carries the 4D Euclidean Yang--Mills form and isolates the
gap theorem.} On the declared controlled compact-gauge branch, with the four-dimensional
scaling chart, reflection-positive ordinary vacuum, no additional gauge-invariant relevant
dimension-four pure-gauge operator on that branch besides curvature squared, repair completeness,
and the compact paper's explicit finite cylinder system in force, OPH proves projective weak-* /
GNS extraction of a support-visible cylinder cluster family. Identification of that family with
the Euclidean Yang--Mills action additionally uses the renormalized four-dimensional
regularity/universality receipt. Weighted observation-fiber resampling is the finite
conditional-expectation projector, with the noncircular matrix-recognition criterion of
Ref.~\cite{observableNormalForms}. A concrete active repair law is identified with that projector
only after its independently extracted transition matrix passes the support, equal-fiber-row, and
weighted detailed-balance receipt. Identification of Euclidean transfer with the repair generator,
vacuum persistence, and passage of a uniform finite-stage gap use the separate finite
ground-state-transform, transfer/vacuum, OS-regularity/noncollapse, and uniform-gap receipts.
The checked \(244\)-type Ising collar table is an exact calibration of that finite receipt format,
not evidence for the physical compact-gauge source family.
Only on that certified branch is
\(\Delta_{\mathrm{YM}}=\Delta_{\mathrm{rep}}\). Weak-* extraction alone is not the
Clay-facing axiomatic construction.
\end{enumerate}

\section{Physical Implementation and \(A_5\)/\(E_8\) Significance}

The implementation question is what must exist below the observer-level axioms so they have a
physical carrier. OPH's answer is a fixed-cutoff federation of finite patch carriers. Each carrier
exposes overlap ports, record registers, repair maps, and checkpoint interfaces. The screen is the
observer-facing geometry chart. It is not the carrier itself in the sense of one literal smooth ball.
The implementation is the finite algebraic machinery that makes compare, write, repair, and re-read
operations available.

The term ``sphere folding'' has a restricted technical meaning in this stack. It is the
observer-facing spherical presentation of the repaired quotient normal form:
\[
\operatorname{Fold}_{S,r}(s)=\chi_{S,r}\!\left(n_r(\pi_r(s))\right).
\]
The quotient map removes hidden carrier presentation, the normal-form map performs accepted
repair, and the spherical chart displays caps, collars, cuts, edge sectors, and boundary records.
Folding is therefore the geometric face of overlap repair on the screen chart.
On the consensus surface this repair is defined first as the quotient operator
\(\operatorname{Rep}_\lambda:Q\to Q\), with representative-level maps only serving as lifts, so
hidden carrier labels do not become additional physical data.

Spherical geometry carries several pieces of the construction at once. An observer-accessible cut
has a closed two-dimensional angular chart. Caps and collars on that chart supply the cut data used
by modular flow, entropy variation, and overlap comparison. The orientation-preserving conformal
group of the same \(S^2\) chart is the celestial-sphere realization of
\(\mathrm{SO}^+(3,1)\), so the sphere is the kinematic bridge between finite screen cuts and the
emergent \(3+1\)-dimensional Lorentz branch once the controlled cap-pair theorem is
satisfied. Finite cellulations of the chart provide the regulator surface on which ports, edge
sectors, and local comparison data can be made explicit; they are not by themselves a Lorentz
invariant continuum.

The echosahedral carrier is the concrete local realization of this chart data. Its multi-port
interface supplies discrete boundary directions, face and edge incidence, exposed readout
channels, record slots, and repair channels. Recurrent toroidal subchannels supply local winding
and memory structure. The smooth spherical chart describes the observer-facing cut; the
echosahedral carrier supplies the fixed-cutoff local machine whose quotient data can present that
cut.

The \(A_5\) and \(E_8\) labels mark different roles in that machinery. \(A_5\)-icosahedral symmetry
is the local finite-screen language used when a patch carrier is made concrete: it organizes ports,
faces, and overlap data with enough discrete symmetry to stabilize observer-facing cuts.
\(E_8\)-type language is the exceptional closure language used by the high-symmetry branch. It names
the root-lattice and affine exceptional structure in which the icosahedral data can sit. The term
is representation-closure language for the branches that call for it.

One finite certificate lives on the \(E_8\)-side of that split. The
\(E_8/\mathrm{Spin}(8)\) triality sidecar gives exact matrices for an \(A_8\) root subsystem inside
\(E_8\), the subgroup \(\mathrm{Alt}(9)\subset W(A_8)\cong\mathrm{Sym}(9)\), its nonsplit
\(2\!\cdot\!\mathrm{Alt}(9)\) lift in \(\mathrm{Spin}(8)\), and a positive half-spin image
preserving an \(E_8\) lattice. The vector and half-spin presentations have distinct
\(E_8/2E_8\) orbit fingerprints, \(\{9,36,84,126\}\) and \(\{120,135\}\), before Spin(8)
triality fuses them. This is a finite exceptional representation-closure receipt. It is not a
recovered-core theorem, a new particle or force, a heterotic edge-CFT proof, or hardware evidence.

This distinction matters for the synthesis paper. The physical claim lives at the observer-visible
quotient: finite patches must expose the same records and shared observables after allowed
implementation-hiding changes. The microphysics paper gives the concrete reference architecture for
that quotient surface, including the federated patch-carrier model, fixed-cutoff edge
heat-kernel/Casimir law, central-record/Born--L\"uders measurement interface, Bell/CHSH event
surface, and checkpoint/restoration package. See Ref.~\cite{ophmicrophysics}, available as the
numbered GitHub reference in the bibliography.

\subsection*{Famous equations and structural outputs recovered}

The table below maps headline formulas by logical role. Some rows are core theorem results, some
are short corollaries of recovered actions, and some are standard limits once the parent OPH
branch is established.

\begingroup
\footnotesize
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.18\textwidth}>{\raggedright\arraybackslash}p{0.30\textwidth}>{\raggedright\arraybackslash}p{0.20\textwidth}@{}}
\toprule
Recovered result & OPH role & Famous display & Support boundary \\
\midrule
\endhead
\bottomrule
\endfoot
Three-dimensional observer-frame chart, Lorentz kinematics, and invariant light cone & core theorem & \(q(\Omega)=(1,\Omega)\), \(n_C=(\cot\alpha,\csc\alpha\,\mathbf c)\), \(n_{gC}=\Lambda_gn_C\), \(H^3\simeq\mathrm{SO}^+(3,1)/\mathrm{SO}(3)\) & scaling-limit geometric subnet; chart population and neutral bulk are separate gates \\
Record-conditioned \(H^3\) frame estimate & conditional theorem & \(R_i(C,t,O)\to F(X_i)+e\), \(\alpha\bar d\le |F(X)-F(Y)|_W\), \(S_i(t)=B_H(\widehat X_i,r_i)\) & frame-local calibrated cap responses, compact frame domain, bounded error, quantitative cap frame, and positive gap for unique finite output; no event position is inferred \\
Einstein equation & conditional composition theorem & \(G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle\) & one source-derived common-domain tower with uniform asymptotics, universal coupling, a vacuum reference, and independent scale readouts; tower construction and certification are work in progress \\
Newton-Poisson gravity & inherited weak-field limit & \(\nabla^2\Phi=4\pi G\rho\), \(\ddot{\mathbf x}=-\nabla\Phi\) & absolute Einstein-branch premises, weak field, and slow motion \\
Maxwell equations & electromagnetic corollary & \(dF_Q=0,\quad d{*}F_Q=g_Q^2{*}J_Q\) & ordinary \(\mathrm U(1)_Q\) branch plus explicit Maxwell action/current hypothesis \\
Yang--Mills equations & compact-gauge corollary & \(DF=0,\quad D{*}F=g^2{*}J\) & compact-gauge connection branch plus explicit Yang--Mills action/current hypothesis \\
Bekenstein--Hawking / de Sitter area law & global capacity branch & \(N_{\mathrm{scr}}=A/(4\ell_P^2)=3\pi/(G\Lambda)\) & screen-capacity closure \\
Born rule and L\"uders update & fixed-cutoff theorem & \(\mathbb P(E)=\operatorname{Tr}(\rho P_E)\), \(\rho|_E=P_E\rho P_E/\operatorname{Tr}(\rho P_E)\) & central record algebra \\
Tsirelson bound & fixed-cutoff theorem & \(|S_{\mathrm{CHSH}}|\le2\sqrt2\) & Bell event surface \\
Charge quantization & core theorem & \(Q=T_3+Y\), color singlets have \(Q\in\mathbb Z\) & quarks are confined fractional-charge fields \\
Classical carrier-mode poles & conditional action theorem & \(K_X^{\mathrm{phys}}\propto(\omega^2-c_\star^2|\mathbf k|^2)\Pi_X\) & Maxwell, perturbative pure-Yang--Mills, or pure-Einstein action/phase receipt; quantum particle gate separate \\
Coherent-matter scalar susceptibility & conditional scalar theorem & \(\chi_\nu^{\rm can}=1-P_\chi/24=0.9320429912748350\ldots\) & nondegenerate OPH-coherent material source, Scalar Edge-Center Exhaustion, and protected-reserve collar closure; force additionally requires repair charge, an external gradient, and field-momentum closure \\
\end{longtable}
\endgroup

\subsection*{Particle Support Status}

The particle paper treats the closure matrix explicitly. The non-hadron
bundle has the following support levels:

Full \(W/Z\) promotion requires a strict source root, an independently physical
\(E_\star\), the finite quotient-transport certificate, a frozen RG/matching/scheme
packet, branch rigidity, target-independent precommitment, and complex-pole and
uncertainty receipts.

\begin{table}[h]
\centering
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.26\textwidth}>{\raggedright\arraybackslash}p{0.18\textwidth}@{}}
\toprule
Lane & Output & Role & Support boundary \\
\midrule
Carrier modes & two transverse Maxwell modes; \(2\dim G\) perturbative Yang--Mills modes; two Einstein TT modes & symmetry-protected massless classical kernels on the stated action branches & no quantum zero-mass particle row until the physical Hilbert-space, pole-residue, and phase gates pass \\
\(W/Z\) & no nonzero source-only physical mass emitted & strict source-audit zero-selector branch; exact selected-carrier chart; conditional quotient-transport implication; reference-fitted inverse adapter & the coordinate pairs have different provenance. The finite-carrier certificate and the source-law selection principle deciding the discrete two-law choice are not emitted, and no physical complex-pole pair is promoted \\
Fine structure & four distinct coordinates & source witness, mixed diagnostic, empirical closure, and measurement & the empirical interval misses the measured endpoint. Source-only promotion requires the source-derived hadronic spectral backend \\
Higgs/top & no nonzero source-only physical mass emitted & double-criticality family from the gauge sector; frozen boundary-scale candidate; declared-surface calibration fit kept separate & promotion inherits the boundary-scale selection theorem plus the source-root, physical-scale, running, matching, rigidity, provenance, uncertainty, and complex-pole gates \\
Charged leptons & no nonzero source-only physical mass emitted & target-anchored diagnostic, exact \(A_5/C_3\) face-carrier lemma, and conditional nature/pole transport & the affine map and engineered record model are authored. The nature bridge assumes the physical Yukawa response identity, while the pole bridge assumes the face-quotient Dyson singularity readout; its explicit zero-self-energy kernel is only a free witness. Physical source selection, attachment, interacting kernel, infrared completion, coherent branch, and cofinal refinement are open \\
Quarks & no nonzero source-only physical mass emitted & common-scale reciprocal-ray falsification; exact six-scalar interface; restricted source-spread lower bound & the candidate fails across the audited common scales. Its sub-percent residuals use a target-anchored mixed-convention chart. The simulator contains no Yukawa coupling or Yukawa information, while generation-blind flavor singlets supply no physical flavor-orbit selector \\
Neutrinos & no nonzero source-only physical mass emitted & rejected target-informed template candidate & the correlated profile rejects the candidate; the shared-basis recovery was tautological, the charged basis is open, and no source-only PMNS or absolute-mass row is emitted~\cite{nufit61} \\
Hadrons & no first-principles prediction emitted; empirical electromagnetic closure executed separately & source-derived hadronic spectral backend absent; external spectral payload integrated & source-only rows require source QCD parameters, quotient ensemble, Ward current ledger, higher-point and transition spectral exports, same-scheme remainder, and no-target-leak receipts \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Conditional and audit coordinates.}
The source-audit zero-selector law outputs the running/chart coordinates
\((80.330,91.119)~\mathrm{GeV}\), with a residual freedom of one discrete
two-law choice (\(9.3\)~MeV on the \(W\) coordinate and \(5.1\)~MeV on the \(Z\)
coordinate). These values are not commensurate with the PDG mass-dependent-width
Breit--Wigner masses or with complex-pole masses, so their numerical proximity supplies no
physical mass evidence. The selected
carrier, conditional value law, and reference-fitted inverse adapter give the
downstream audit coordinates
\[
\begin{array}{rcl}
\text{selected carrier} && (80.3862916924,91.1829044467)~\mathrm{GeV},\\
\text{conditional value law} && (80.3770000154,91.1879780779)~\mathrm{GeV},\\
\text{reference-fitted inverse adapter} && (80.3625,91.1879)~\mathrm{GeV}.
\end{array}
\]
The two-loop audit returned \((79.115335,89.802735)~\mathrm{GeV}\) in its designated primary
cell. Its prescription adds an SM two-loop increment to an MSSM one-loop baseline, making it an
inconsistent MSSM-1L+SM-2L hybrid prescription test rather than a consistent two-loop
calculation. The pole audit returned approximately
\((79.53284,89.71232)~\mathrm{GeV}\) under a partial PRTS/Feynman-gauge prescription. The
definition of \(v\), tadpole treatment, field-content and threshold matching, scale selection,
and higher-order terms are open. These audits establish neither a unique scheme conversion
nor a unique \(1\)--\(2\%\) defect, and they do not exhaust the physical prescription family.
For the PDG-2026 reference values, the exact convention map gives energy-pole
masses \((M_W,M_Z)=(80.3411410,91.1623040)~\mathrm{GeV}\), while the distinct
legacy coordinates \(\sqrt{\operatorname{Re}s}\) are
\((80.3340218,91.1537725)~\mathrm{GeV}\). The running/chart coordinates carry
no OPH theory covariance and acquire physical comparison meaning only when the
physical readout contract closes, so no pull is assigned.
The Higgs/top pair is read on the double-criticality branch, a
zero-continuous-parameter family whose comparison-exposed boundary-scale
candidate \(E_\star e^{-\pi}P^{-1/6}\) gives
\((m_H,m_t)=(125.77,172.63)~\mathrm{GeV}\) at two loops, with
\(m_H=125.72~\mathrm{GeV}\) on the fit-free curve at the measured top. The
declared calibration surface \((125.1995304097,172.3523553288)~\mathrm{GeV}\)
is a data-anchored fit that validates the formula stack and never predicts.
For the quark audit at \(M_Z\),
\[
(\rho_u,\rho_d)=(1.1108888543,0.7519410008),
\qquad \rho_u\rho_d=0.8353228768,
\]
where the reciprocal ray requires one. Granting four endpoints leaves a
\(21.556\%\) held-out minimax error. The generic exact interface is
\[
(\mu_u,\sigma_u,\rho_u,\mu_d,\sigma_d,\rho_d).
\]
The
\(0.2946\%\) and \(0.29436\%\) target-anchored residuals use mixed conventions,
and a lower-order ablation fits that chart better. These conditional and audit
coordinates are excluded from the particle-output ledger. Ref.~\cite{ophparticles}
contains the detailed receipt audit.

\subsection*{Stack-Wide Claim Boundary}

The paper stack uses one no-relabeling rule throughout. A finite diagnostic or
calibration field does not become a physical observable merely because it is
renamed. Capacity bookkeeping needs an independent energy readout before it can
count as mass; an archive needs a physical source, propagation, and detector
channel before it can count as radiation; a finite repair spectrum needs a
continuum operator/readout bridge before it can count as a physical spectrum;
and a finite reconstruction threshold needs physical entropy and clock data
before it can count as a Page-time claim. The compact paper records this as the
source-separation rule behind the support-level table.
The \(\chi_\nu\) scalar-channel identity is theorem-grade for nondegenerate
OPH-coherent material sources once Scalar Edge-Center Exhaustion is imported.
Device-scale force, cosmological abundance, and finite covariant dark stress
require their own receipt packages.

\paragraph{Open evidence boundary.}
Four generating objects and one selector delimit the open rows; the underlying prescription
families are not proved exhaustive. G1 is the
Ward-projected hadronic transport for the two electromagnetic endpoint residuals. Its broad internal-mass bracket
\(S_{\mathrm{hadronic}}\in[0.5578,1.0543]\) contains the zero-electroweak point diagnostic 0.8954,
but it spans about \(1.16\times10^8\) declared tolerance widths. The value is compare-only,
and the evaluation pixel differs from the comparison pixel; the bracket carries no promotion.
G2 requires construction of the direct correctable-public-record producer.
Its removable conditions are record-atom restriction maps, endogenous public
reachability, a frozen publicness policy, the global checkpoint coupling,
exact or approximate correctable-code certification across the terminal
fiber, the capacity-carrier representation, confusability-reflecting capacity
extension and refinement packets, and a finite-size slack law with one
physical zero. The de Sitter and electroweak identifications separately require
the horizon--record identification and the common screen/electroweak
load-carrier identification. The interval certificate at
\(3.5321315434\times10^{122}\) applies to the conditional electroweak bridge;
it does not construct \(F\), and it differs from the Planck--\(\Lambda\) central
capacity by about \(6.6\) percent. G3 carries the forward electroweak chain. Its preregistered
96-entry one-loop sweep excludes entries inside that frozen menu only; higher-order, matching,
threshold, tadpole, scale, and field-content prescriptions are open. G4 supplies numerical
solver hygiene for the declared map. Twelve preregistered flavor candidates were also excluded,
which excludes those candidates rather than the broader selector family.

A third-party audit of forty-two findings identifies no false theorem in the recovered
mathematical core. Fail-closed gates and adversarial regression tests reject the hadronic
target-coordinate algebra defect and the finite transition-clock eligibility defect; the printed
epistemic statuses include those gates.
The evidence ledger contains zero discriminating precommitted target-blind hits. The electroweak checks
freeze analysis choices against known targets, so they are audits rather than target-blind
predictions. Other positive rows are theorem-level, conditional, target-exposed, or
non-discriminating.

\subsection*{Companion Papers}

The detailed depth surfaces used throughout this synthesis are:
\begin{enumerate}[leftmargin=2em]
\item \emph{Observation-Determined Normal Forms: Stability, Obstructions, and Refinement in Constraint and Rewrite Systems}~\cite{observableNormalForms}, which gives the substrate-neutral same-source/cross-source quantifier split, endpoint and refinement bounds, collar-repair obstructions, and the finite conditional-resampling receipt used by the repair papers.
\item \emph{Recovering Relativity and the Standard Model from Observer Overlap Consistency}~\cite{ophcompact}, which gives the compact technical core for relativity, gravity, receipt-conditional combined-zero-obstruction compact-gauge reconstruction (central or higher-associator strictification plus an allowed trivial-holonomy strict representative), and MAR-selected Standard Model structure.
\item \emph{Reality as a Consensus Protocol: The Fixed-Point Computation That Implements Physics}~\cite{ophconsensus}, which carries the finite patch-net fixed-point, defect, quotient, and operator-record consensus package. Its semantic-complete transaction theorem derives the local diamond from coherent aggregate gluing and full acceptance dependencies; repair completeness remains a separate condition. QECC/min-cut, spectral, BFT, and hardware-speedup claims remain gated by separate certificates.
\item \emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer Synchronization in OPH}~\cite{ophmicrophysics}, which carries the regulated federated patch-carrier architecture, the fixed-cutoff edge heat-kernel / Casimir theorem, exact finite modular and rate statements, the \(A_5\times\mathbb Z_2\) register classification, and the measurement and observer checkpoint/restoration packages.
\item \emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}, which carries the particle derivations, masses, couplings, and sector calculations.
\item \emph{Theoretical Bounds on \(\chi_\nu\) in Observer-Patch Holography} and \emph{Observer-Patch Holography and Dark Matter}~\cite{ophchinu,ophdarkmatter}, which carry the coherent-matter channel theorem and the conditional repair-charge condensate action with its current, stress, normal-phase, deep-galaxy, and device-force consequences.
\item \emph{Explaining the Yang--Mills Mass Gap with Observer-Patch Repair Dynamics}~\cite{ophyangmills}, which isolates the controlled compact-gauge repair mechanism and states the continuum certificate needed before the finite repair gap becomes a Clay-facing four-dimensional Yang--Mills gap.
\item \emph{Observer-Patch Holography as a String-Vacuum Selector}~\cite{ophstringselector}, which treats string theory as an effective edge language and applies OPH gates to critical-string candidates; its rank certificate classifies the Bouchard-Donagi row as a structural benchmark rather than a selected witness.
\end{enumerate}

The sections that follow give the synthesis view. Detailed proof burdens sit with the companion
papers and with the late dependency checklist in this paper.

\def\OPHSkipEmbeddedReferences{1}
\input{tex_fragments/PAPER.tex}
\input{tex_fragments/OBSERVERS_SYNTHESIS_SECTIONS.tex}

\appendix
\input{tex_fragments/OBSERVERS_APPENDICES.tex}
\input{tex_fragments/OBSERVERS_REFERENCES.tex}

\section*{Statements and Declarations}

\noindent\textbf{Funding declaration:} The authors declare that no external grants or dedicated
third-party research funding were received for the preparation of this manuscript.

\noindent\textbf{Author af\kern0pt f\kern0pt iliations declaration:} Bernhard Mueller is af\kern0pt f\kern0pt iliated with
Pragma Inc., Washington, USA. Alexander Osika is af\kern0pt f\kern0pt iliated with SNRGY Inc.,
Gothenburg, Sweden. No institutional af\kern0pt f\kern0pt iliations were declared for Mario Poneder, Kai
Xue, Ben Cassie, Peter Nguyen, Maarten Antonie Visser, Kale Arnav Anirudha, David Matscheko, or
Jonathan Hill in this submission.
Correspondence email addresses are provided in the correspondence declaration.

\noindent\textbf{Consent to Participate declaration:} not applicable.

\noindent\textbf{Consent to Publish declaration:} not applicable.

\noindent\textbf{Author Contribution declaration:} Bernhard Mueller developed the OPH concept,
mathematical formulation, paper-stack synthesis, main manuscript text, cross-surface integration, and
submission package. Alexander Osika contributed to the OPH/Karma and OMEGA hardware path,
experimental prototype framing, hardware evidence boundary, and submission review. Mario Poneder
contributed proof and validation work on the hierarchy certificates, the edge-entropy area-law
route to the Einstein/Newton coupling, coupling normalization, particle and neutrino certificate
surfaces, and manuscript/book consistency surfaces. Kai Xue contributed broad paper-stack work,
including audit passes, consistency checks, implementation-surface review, simulator and OPH
Universe evidence-surface feedback, receipt and visualization data-surface review, and prototype
engineering boundary review. Ben Cassie contributed audit work across the hardware evidence
surface, implementation claims, receipt boundary, experimental-prototype framing, and submission
package. Peter Nguyen contributed proof-surface hardening, branch-boundary audits, claim-tier
alignment across the paper and book stack, Yang-Mills and compact-gauge status surfaces, finite
packet-quotient closure, fine-structure certification surfaces, and manuscript consistency passes.
Maarten Antonie Visser contributed to the P/N=24 repair-resonance material, consensus-protocol
consistency review, and physics feedback on the foundations and emergent-spacetime framing. Kale
Arnav Anirudha contributed consensus-paper material, formal review of the consensus-protocol
surface, QBFT assumptions, FLP citation handling, repair-map definitions, QECC notation,
asynchronous bound wording, and the BFT/QECC appendix material. David Matscheko provided the
finite proof review for the consensus repair, Rule-90 boundary-reconstruction,
Route-A assembly, finite modular-flow, Einstein-algebra, hypercharge/\(Z_6\),
scalar-channel/collar/channel-bridge, dark-sector, energy-cage, and
run-matrix theorem surfaces; he also provided audit material for the dark-sector and
coherent-matter susceptibility surfaces and contributed to the anti-gravity experiment path. All
authors reviewed and approved the manuscript.

\noindent\textbf{Correspondence declaration:} Correspondence should be addressed to Bernhard
Mueller, \href{mailto:bernhard@floatingpragma.ai}{\texttt{bernhard@floatingpragma.ai}}, and
Alexander Osika, \href{mailto:alex@snrgystudios.com}{\texttt{alex@snrgystudios.com}}.

\noindent\textbf{Data Availability declaration:} The paper stack, source manuscripts, public
PDFs, simulation code, and implementation notes are available through the OPH project
repository and linked public artifact surfaces. Some hardware and prototype evidence requires a
sanitized ancillary audit bundle before public disclosure because raw logs may include device
configuration, operational metadata, or private infrastructure details. The intended audit bundle
contains source hashes, simulator configs, finite-receipt JSON, verifier code, hardware acceptance
records, calibration logs, and selected run traces sufficient to replay the stated implementation
claims.

\noindent\textbf{Code Availability declaration:} The OPH simulator, finite-consensus harnesses,
visualization payload schemas, and public paper build sources are maintained in the OPH project
repositories. Submission artifacts include a standalone source file and a source bundle so that the
manuscript can be rebuilt without relying on private local paths.

\noindent\textbf{Ethics declaration:} not applicable.

\noindent\textbf{Competing Interests declaration:} The authors participate in OPH-related research
and implementation programs, including prototype hardware and simulator development. The authors
declare no external competing financial interests for this manuscript.

\noindent\textbf{Use of AI-assisted tools declaration:} AI-assisted tools were used for language
editing, drafting assistance, formatting support, and submission-package preparation. The authors
reviewed and are responsible for all scientific content, claims, references, and declarations.
\end{document}
